### 2019-11-07 tex/Tracking.tex
add tex file

\documentclass[3p,times]{elsarticle}

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}
%% The ecrc package defines commands needed for running heads and logos.
%% For running heads, you can set the journal name, the volume, the starting page and the authors

%% set the volume if you know. Otherwise `00'
\volume{00}

%% set the starting page if not 1
\firstpage{1}

%% Give the name of the journal
\journalname{}

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{}

%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo

%% Give the abbreviation of the Journal.
\jid{procs}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{}

%% Hereafter the template follows `elsarticle'.
%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.

%% Elsevier CRC generally uses a numbered reference style
%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
%% If using BibTeX, use the style file elsarticle-num.bst

%% End of ecrc-specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}

\usepackage{xcolor}
\usepackage[version=4]{mhchem}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\diag}{\textbf{diag}}
\newtheorem{defn}{Definition}
\newtheorem{hypo}{H}
\newtheorem{lemma}{Lemma}
\newtheorem{theo}{Theorem}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

% if you have landscape tables
\usepackage[figuresright]{rotating}

\graphicspath{{Images/}}
% put your own definitions here:
%   \newcommand{\cZ}{\cal{Z}}
%   \newtheorem{def}{Definition}[section]
%   ...

% add words to TeX's hyphenation exception list
%\hyphenation{author another created financial paper re-commend-ed Post-Script}

% declarations for front matter

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\dochead{}
%% Use \dochead if there is an article header, e.g. \dochead{Short communication}

\title{A Model of Microbial Interactions in a Chemostat Setting : Analysis and Application}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author{Pablo Ugalde-Salas, Jérôme Harmand, Elie Desmond Le-Quemener, Héctor Ramirez}

\address{}

\begin{abstract}
	A model of microbial interactions applied to a nitrifying process in a chemostat setting is revisited. To overcome the shortcomings of this earlier model an optimal tracking method is developed to include the genetic measurements for the prediction of a bioreactor. The resulting model is a high order (24 variables) differential equations system with a good prediction of measured metabolites. Numerical simulations of the model are presented and discussed.
\end{abstract}

\end{frontmatter}

\section{Introduction}

Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}. A thorough review in current methodologies in the deterministic modelling approaches of microbial community dynamics is presented by Song \textit{et al.} \cite{Song2014}. Using their terminology this articles deals with population-based approaches where species are taken as the interacting units. Particularly the model here studied could be classified as a stoichiometric model of multiple species and at the same time as a generalized Lotka Volterra Model \cite{Hernandez-Bermejo1997}.

The classical ecological concept of species and niche in the microbial world is an elusive one: In the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring. In the case of bacteria and archea, reproduction goes simply by mitosis and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}. Therefore as an ecological problem is hard to precise the 'niche' of 'species'.

These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based in 16sRNA analysis. There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria. The abundance of the present OTU allows to account for a group of Bacteria that behave similarly in terms of which substances catabolyzes and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.

In the past years considerable efforts have been made to measure the bacterial community composition. Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA, RNA, proteins and metabolites have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.

The objective of this article is to show a method to predict the reactor performance based on any technique that can track the species relative abundances through time. This work revisits the model proposed by Dumont et al \cite{Dumont2016} in which a model with intra and inter species interactions were they claimed coexistence of two species consuming the same substrate: The rigorous mathematical and numerical analysis of this work states the contrary. However, using a different set of parameters than the ones proposed on their article, the model proposed becomes very rich in steady states, and different coexistences may emerge depending on operational parameters of the working chemostat. Their approach suffers from a quadratic growing number of parameters on the number of species considered, thus its scope of applicability for diverse ecosystems seems limited.

In the present paper this difficulty is overcame by generalizing their interactions approach and using method of optimal tracking for parameter identification, where the growth rate of each species is modulated by a constrained regular control of the system.  The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the abundances of each species. The main novelty of the article lies in proposing/testing/using microbial interactions as the driver of the reactor's performance  through an optimal control approach.

The article is divided in a first section that re-examines the properties of the work of Dumont \textit{et al.} \cite{Dumont2016}, and a second section that generalizes their approach.

\section{Model Definition}

Notations used throughout the article are:
\begin{enumerate}
	\item $n$: the number of $OTU$ considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
	\item $s$:  vector $(s_1,s_2,s_3)$.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: Dilution Rate of the continuous reactor in $[1/day]$. 
	\item $y_i$: Yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
	\item $y$: vector $y_1,\dots,y_n$.
	\item $k_i$: Yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
	\item $k$: vector $k_1,\dots,k_n$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
\end{enumerate}

\subsection{Stoichiometric Equations}
A cascade (bio)reaction process is considered. Suppose $n$ different OTU are present in the chemostat. The cascade reaction refers to the situation where a group of microorganisms ($G_1 \subset [n] $) consumes a substrate $s_1$ and produces $s_2$ and biomass, while another group of microorganisms ($G_2\subset [n]$) consumes $s_2$ and produces $s_3$ and biomass. $G_1$ and $G_2$ are called functional groups. The number of organisms in each functional will be denoted $n_1$ and $n_2$ respectively, that is $\vert G_1 \vert = n_1$ and $\vert G_2 \vert = n_2$ . This work treats the case when the $G_1$ and $G_2$ are disjoint sets:

\begin{hypo}  Sets $G_1$ and $G_2$ satisfy: $G_1 \cap G_2 = \emptyset$ and $G_1 \cup G_2 = [n]$. 
\end{hypo}

The situation is described as simplified reactions \eqref{Reaction1} and \eqref{Reaction2}. The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather it represents the direction of the bioprocess and the proportions of different consumed and formed compounds of interest.

The terms $y_i$ are known as yields, it represents the number of grams of biomass produced per gram of substrate consumed. In this work the unit grams of dry biomass per gram of substrate is used for yields. Furthermore, for each $ i \in [n]$, OTU $i$ is characterized by its process rate (also known as growth function) $\mu_i(s,x)$. Notice that for being as generic as possible, the growth rate may be a function of the whole state in order to model the influence of all OTU on the growth rates of others.

\begin{align}
\label{Reaction1} \tag{R G1} 	s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_1 \quad \forall i \in G_1 \\
\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
\end{align}

\subsection{Kinetic Equations}
The growth rate of each species is given by:
\begin{align}
\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2
\end{align}
The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU. Let $A$ denote the matrix
with entries $a_{ij}$, which will be referred to as the interaction matrix.

\subsection{Mass Balance Equations}

Consider the scenario of an continuous and homogeneous reactor: the input flow is the same as the output flow, with a dilution rate of $D$. The input flow contains a concentration $s_{in}$ of substrate $s_1$. Note that $s_{in}$ and $D$ are time dependent. Each OTU grows at a rate $\mu_i(s,x)$. System \eqref{system} represents this situation. A specific case of $\mu_i(s,x)$ is given by \cite{Dumont2016}, and the first part of this article deals with the mathematical analysis of that model. A second part then generalizes its growth function and calibrates it against experimental data using an optimal control approach.

\begin{align} 
\label{system}
\begin{array}{cl}
\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_1\\
\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_2 \\
\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i\in G_1} \frac{1}{y_i}\mu_i(s_1,x) x_i  \\
\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in G_1}\frac{1}{y_i}\mu_i(s,x)x_i 		-\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i  \\
\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i 
\end{array}
\end{align}

\section{Mathematical Analysis}

The system of equations \eqref{system} is defined in the region

\begin{align*}
\Omega := \{ (x_1,\dots,x_n,s_1,s_2,s_3)\in  \R^{n+3} | x_1,\dots,x_n,s_1,s_2,s_3  \geq 0  \}
\end{align*}

First sufficient conditions for the system to be well posed are established: meaning that solutions remain bounded and non-negative in time, this ultimately implies that the solution exists for every $t \geq 0$ \cite{Khalil1996}.

Second the equilibria of the system are derived. Possible equilibrium points for this system grow exponentially with the number of OTU considered ($n$).  Stability is not analytically addressed, a numerical scheme calculating every equilibrium point and the system's Jacobian eigenvalues at the equilibrium point were implemented for studying the system.

\subsection{Properties of the system}

 By bounding the norm of the interaction matrix on the initial conditions and parameters one establishes that solutions will remain positive and bounded.

\begin{lemma}
	\label{l1}
	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists positive scalars $M_1$, $M_2$, and $M_3$ such that solutions to \eqref{system} satisfy the following inequalities:
	\begin{align}
	&\sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1 \leq M_1 \\
	&\sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 +s_2 \leq M_2 \\
	&s_1 + s_2 + s_2 \leq M_3
	\end{align}
\end{lemma}

The proof can be seen in the appendix. A bound on the norm of $A$ is found such that every matrix $A$, respecting the bound, guaranties that $\Omega$ is a positively invariant set.

\begin{theo}
	\label{theoWellPosedness}
	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions remain in $\Omega$ and are bounded.
\end{theo}

The proof can be seen in the appendix.

\subsection{Equilibrium Points}

In this section analytical expressions for equilibrium points are derived. Analytic expressions of equilibrium points are obtained, however no analytic expression concerning the stability of such points is presented. To answer the question of stability a numeric scheme is used by evaluating the Jacobian at the equilibrium point. At the end of the section an algorithm is provided for exploring all the possible equilibria.

\begin{defn} 
	An equilibrium point (or steady state) is a point $(x^{eq},s^{eq}) \in \R^{n+3}_+$ so that the right hand side of equations \eqref{Eq1},\eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4} equals zero. 
\end{defn}

Observe that equilibrium points are by definition non-negative so the state variables can have biological meaning. Details of the calculations are given in the appendix.

This model \eqref{system} is restated in a more compact form using matrix notation.

\begin{defn} Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$:
	\begin{align}
	\begin{array}{rc}
	\diag:\R^n \rightarrow & \mathbb{M}_{n\times n}(\R)\\
	& \\
	v \rightarrow & \begin{pmatrix}
	v_1 & 0 & \dots & 0 \\
	0 & v_2 & \ddots & \vdots\\ 
	\vdots & \ddots & \ddots& 0 \\
	0 & \dots &0 & v_n 
	\end{pmatrix}
	\end{array}
	\end{align}
\end{defn}

The former function places a vector $v$ in the diagonal of a matrix. By noting $A$ the matrix with coefficients $a_{ij}$, system \eqref{system} is restated as follows:
\begin{align}
\label{Eq1}	\dot{x} = & \diag(x)(\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}) \\
\label{Eq2}	\dot{s_1} = & (s_{in}-s_1)D + \begin{bmatrix}
-(1_{n_1\times 1} +A_1x) \\0
\end{bmatrix}^\top \diag(k) \diag(f(s))x \\
\label{Eq3}	\dot{s_2} = & -s_2D+
\begin{bmatrix}
1_{n_1\times 1} +A_1x \\ -(1_{n_2\times 1} +A_2x)
\end{bmatrix}^\top \diag(k) \diag(f(s))x \\	
\label{Eq4}	\dot{s_3} = & -s_3D+\begin{bmatrix}
0	\\(1_{n_2\times 1} +A_2x) 
\end{bmatrix}^\top \diag(k) \diag(f(s))x 
\end{align}

%
%The following notation was used:
%$A = \begin{bmatrix}
%A_1\\A_2
%\end{bmatrix}$.
%
%Where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$. $A_2$ is a matrix of dimension $n_2 \times n$ rows corresponding to the interaction coefficients of OTU $i \in G_2$.

\subsubsection{Complete Coexistence}

This section derives the equations for an equilibrium point with every OTU being positive: $x^{eq}_i>0$.

From equation \eqref{Eq1} one gets that an equilibrium point satisfies: \begin{align*}
\diag(x)(\diag(f(s)(1_{n\times 1} + Ax) - D_{n\times 1}) & = 0 \\
\Rightarrow x_i = 0 \vee (\diag (f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i & = 0 \quad \forall i\in (1,\dots,n)
\end{align*}

Since $x_i>0$ one has 
\begin{align}
\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}=0 \\
\label{xEquilibria}\Leftrightarrow x = A^{-1}(\diag (f(s))^{-1}D_{n\times 1} - 1_{n\times 1})
\end{align}

By replacing \eqref{xEquilibria} in equation \eqref{Eq2}:

\begin{align}
\label{s1Equilibria} (s_{in}-s_1)-	\begin{bmatrix}
1_{n_1\times 1} \\0_{n_2\times 1}
\end{bmatrix}^\top \diag (k) A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0 
\end{align}

A similar expression is obtained when replacing \eqref{xEquilibria} in equation \eqref{Eq3}

\begin{align}
\label{s2Equilibria}-s_2+
1_{n\times 1}^{\top}\diag (k)  A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0
\end{align}

From equation \eqref{s1Equilibria} $s_2$ can be written as a function of $s_1$:
\begin{align}
s_2 = \frac{s_1}{c_1s_1^2+c_2s_1+c_3} \label{S2(S1)}
\end{align}

Then by replacing  \eqref{S2(S1)} in equation \eqref{s2Equilibria}, one gets a fourth degree polynomial for $s_1$.

\begin{align}
\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
\end{align}

Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in the appendix.

Finally, in equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :

\begin{align}
s_{in} = s_1+s_2+s_3 \label{s1s2s3}
\end{align}

If the system of equations \eqref{xEquilibria}, \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} provides only solutions with some negative entries then complete coexistence is not possible.

\subsubsection{Washout of some OTU}

\begin{defn}
	Given an equilibria point $(x^{eq},s^{eq})$ of system \eqref{system}, then the set of non-active coordinates $\mathcal{J}\subset \{1,\dots,n\}$ is defined as:
	$\mathcal{J} = \{j_1, \dots, j_m\ : \, x^{eq}_{j_i} = 0 , \;i \in [m] \} $.

	The active point $x^{act}\in \R^{n-m}$ is defined by the positive entries of $x^{eq}$. The relationship between the two is given by:

	\begin{align}\label{EquilibriaFormula} (x^{eq})_i = \begin{cases}
	x^{act}_i & \text{for } i < j_1\\
	x^{act}_{i-k} & \text{for } j_{k}< i <j_{k+1}  \text{ and } k \in \{1,\dots,m-1\}\\
	x^{act}_{i-m} & \text{for } j_{m}< i \\
	0 & \text{for } i \in \{j_1, \dots, j_m\}
	\end{cases} \end{align}

	The active growths $f^{act}(s)$ and yields $k^{act}$ are defined analogously by the positive entries of $x^{eq}$. The active interactions $A^{act}$ is defined as matrix $A$ without the $\mathcal{J}$ rows and columns.
\end{defn}

From equation \eqref{Eq1} equilibrium points satisfy:

\begin{align}
\Rightarrow  (\diag (f(s))(1_{n\times 1}+ Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n]\setminus \mathcal{J} \\
\Leftrightarrow f_i(s)(1 + A_{i\bullet}x) - D = 0 \quad \forall i \in [n]\setminus \mathcal{J} \label{Extinction}
\end{align}

But since $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ then the coefficients $a_{ij}$ play no role in the equation \eqref{Extinction} one can rewrite equation \eqref{Extinction} as $\diag(f^{act}(s))(1_{(n-m)\times 1} + A^{act}x^{act}) - D_{(n-m) \times 1}=0 $.

\begin{lemma} 
	The active point of the solution of \eqref{Extinction} solves the system of equations \eqref{EqSome}. 
	\begin{align}
	\label{EqSome}x^{act} = (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})
	\end{align} 
\end{lemma}

The following hypothesis represents the case where in each functional group remains at least one OTU :
\begin{hypo}The set $\mathcal{J}$ satisfies $ G_1 \not \subset \mathcal{J} , \, G_2 \not \subset \mathcal{J} $.
	\label{noWashoutHyp}
\end{hypo}

Under H \ref{noWashoutHyp}, the equilibrium of the system is solved as described by equations \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} as before, but coefficients are calculated differently (essentially the same, but only uses the coefficients corresponding to the active points).

\subsubsection{Washout of $G_2$}

The washout of $G_2$ is equivalent to the following hypothesis:

\begin{hypo}
	$G_2 \subset \mathcal{J}$ and $G_1 \not \subset \mathcal{J}$
	\label{WashoutG2}
\end{hypo}

In the case that $x_i = 0, \, \forall i \in G_2$ then from equation \eqref{Eq4}.
\begin{align}
\dot{s_3} = 0 = -s_3D \\
\Rightarrow s_3 = 0;
\end{align}

Then by \eqref{s1s2s3} one obtains:

\begin{align}
s_{in} = s_1 + s_2
\end{align}

Then by replacing  \eqref{EqSome} and \eqref{EquilibriaFormula} in \eqref{Eq2}.
\begin{align}
\label{S1NOBWashout}  (s_{in}-s_1)-1_{(n-m)\times 1}^\top
\diag(k)(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1}) = 0 
\end{align}

Notice \eqref{S1NOBWashout} does not contain terms with $s_2$. By reordering the terms \eqref{S1NOBWashout} one finds a two degree polynomial of $s_1$:

\begin{align}
a'_2 s_1^2 + a'_1s_1 + a'_0 = 0
\end{align}

Where $a'_i$ can be found in the appendix.

\subsubsection{Washout}	
Notice that $x_i = 0$ for every $i \in \{1,\dots, n_1\}$ implies the washout equilibria (no OTU surviving):

From equation \eqref{Eq2}, one gets 
\begin{align*} s_{in} = s_1 \end{align*}
then \eqref{s1s2s3} implies \begin{align*}s_2 &= s_3 = 0 \\ \Rightarrow \dot{x_i} &= -Dx_i \quad \forall i = n_1+1, \dots, n\end{align*}   
which has an equilibria at $x_i = 0$.

All the former discussion leads to a potential number of   $ (2^{n_1}-1)\cdot (4\cdot(2^{n_2}-1)+2)+1 $  different equilibria. 
\begin{align} \overbrace{(2^{n_1}-1)}^{\substack{\text{nonempty subsets} \\ \text{of }G_1 }} (\underbrace{4}_{\substack{\text{possible} \\ \text{solutions of} \\ \text{equation \eqref{Poly4}}}} \cdot\overbrace{(2^{n_2}-1)}^{\substack{\text{nonempty subsets} \\ \text{of  }G_2}}+\underbrace{2}_{\substack{G_2 \\ \text{Washout}}})+\overbrace{1}^\text{Washout} 
\end{align}

\subsection{Local Stability and Operating Diagrams}
For checking local asymptotic stability of the equilibria points, the Jacobian of the system is provided and evaluated at each of these points. The resulting matrix's eigenvalues must satisfy that their real parts are less than zero. A general formula for this Jacobian is presented in the appendix.

The former discussion proposes an algorithm for finding the positive stable equilibrium points

\begin{algorithm}[H]
	\KwData{$A \in M_{n\times n}(\R)$, $D, s_{in}, \bar{\mu}_i,K_i, k_i,  \in \R \, i\in [n], $, $n_1, n_2 \in \N$}
	\KwResult{Set PSP containing all Positive Stable Equilibrium Points}
	$PSP = \emptyset$ \\
	eig = Eigenvalues of $J(0,s_{in},0,0)$. \\
	\If{$Real(eig) < 0$}{$PSP = PSP \cup (0,s_{in},0,0)$} 
	\For{$A'$ square submatrix of $A$}{	Calculate $(x,s_1,s_2,s_3)$ from equations \eqref{Poly4}, \eqref{S2(S1)}, \eqref{s1s2s3}, and \eqref{xEquilibria} \\
		\If{$(x,s_1,s_2,s_3) \geq 0$}{eig = Eigenvalues of $J(x,s_1,s_2,s_3)$ \\
			\If{$Real(eig) < 0$}{$PSP = PSP \cup (x,s_1,s_2,s_3)$}}}
	\label{StabilityAnalysis}
\end{algorithm}

The algorithm implicitly assumes that every submatrix $A'$ is invertible.

Operating diagrams are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters. Operating diagrams are created by running algorithm \eqref{StabilityAnalysis} for different pairs $(s_{in},D)$ . One then regroups all the pairs such that the set of non-active coordinates of the points of the set $PSP$ are the same. This regrouping represents graphically the coexistence of the different OTU in a $D-s_{in}$ plot. In particular for the biological process of nitrification, this implies when partial nitrification (PN) or complete nitrification (CN) may arise. PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ concentration is very low and thus almost no conversion from $s_2$  to $s_3$ takes place. On the contrary CN is when nitrate ($s_3$) accumulates because of the presence of OTU of $G_2$.

The operating diagram from the parameter identification from Dumont et al. is presented in figure \ref{OD Dumont}. Two species per functional group were considered. One can see that coexistence in the same functional group is not attained. However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}. In the latter case CN can be achieved at a more elevated dilution rats than in the former case. Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.

The model isalso  able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm. The CEP roughly states that if two species are growing on the same limiting resource, and their growth law is monotonic in the substrate, then only one of them will survive in the long run. However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors has\cite{Wagner2002}.

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Parameters Dumont & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_1 \in G_1$ & 0.828  & 0.147 & 3.85  \\ \hline
		$x_2\in G_1$ &0.828   & 0.147 &  3.85\\ \hline
		$x_3\in G_2$ & 0.18 & 0.026 &  100 \\ \hline
		$x_4\in G_2$ & 0.18 & 0.026 &  100 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} from \cite{Dumont2016}.}
	\label{Parameters Dumont}
\end{table}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_Dumont}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
	\includegraphics[width=\textwidth]{OD_parameters_Dumont}
	\end{subfigure}
	\caption{Left: interactions of the system. Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Dumont}. The different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD Dumont}
\end{figure}

\begin{table}[ht]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
		$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
		$x_2\in G_1$ & 0.621 & 0.0147 & 3 \\ \hline
		$x_3\in G_2$ & 0.18 & 0.026 & 110 \\ \hline
		$x_4\in G_2$ & 0.135& 0.0026& 90 \\ \hline
	\end{tabular}
	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
	\label{Parameters Modified}
\end{table}
\begin{figure}[ht]
	\centering	
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{OD_parameters_modified}
	\end{subfigure}
	\caption{Left: interactions of the system. Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Modified}. The different zones represent the surviving species in the steady state. PN takes place when neither $x_3$ nor $x_4$ are present. CN takes place if $x_3$ or $x_4$ are present.}
	\label{OD modified}
\end{figure}
\clearpage

\subsection{Remarks}
The model here presented serves to illustrate that by considering interactions complete nitrification with a bigger dilution rate can be explained. It also shows a mechanism by which the CEP no longer holds. However the quadratic increase of parameters with the number of OTU considered makes it difficult to accurately calibrate the model. Simulations always show a single stable equilibrium point, however no proof is offered to such conjecture. In the next section, in the spirit of this model, a more systematic treatment is provided to include genetic sequencing in order to predict the outcome of the reactor.

\section{Generalized approach for modelling interactions}
In the previous sections interactions were modelled as an affine function of the OTU concentration that multiplies a substrate dependent growth equation.

More generally the interaction function is defined. It represents how the growth rate of species $i$ is affected by the concentration of other Bacteria, $x$:

Given a vector $(v_1,\dots,v_n)^\top$ the interaction function $\I$ is noted as:
\begin{align}
\begin{array}{rc}
\I: \R^n \rightarrow & \R_+^n\\
& \\
v \rightarrow & \begin{pmatrix}
I_1(v) \\
I_2(v) \\ 
\vdots  \\
I_n(v)
\end{pmatrix}
\end{array}
\end{align}

	Let $f_i(s)$ be a bounded, positive, and continuous function of $s$ (e.g. Monod, Haldane). The growth equation of OTU $i$ becomes:
	\begin{align}
	\mu_i(s,x) = f_i(s)I_i(x)
	\end{align}
	Note $f(s) := (f_1(s),\dots,f_n(s))^\top$.
	\label{growthForm}

Since the growth of a single strain in batch experiments is driven by the substrate concentration, when no interactions are present one should recover expression $f_i(s)$. Therefore if there are no interactions then $I_i(x) = 1$. From this hypothesis, note that $ \lim \limits_{x \rightarrow 0} I_i(x) = 1$ since if there is minimal presence of OTU, interactions can not exist. Furthermore for this first study it is assumed that $I_i(\cdot)$ is a continuously differentiable function on $x$. For making explicit all of the former:

\begin{hypo}
	The interaction function $\I$ previously defined satisfies:
	\begin{enumerate}
		\item\begin{align}
		\I \left( (0,\dots,0)^\top \right) = 
		(1,\dots,1)^\top 
		\end{align}
		\item Let $\Omega$ be an open subset of $ \R^n $ then $\I \in C^1(\Omega)$.
	\end{enumerate} 
\end{hypo}

Note $J_I(x)$ the Jacobian matrix of function $\mathcal{I}$. then a first order approximation of $\I(\cdot)$ centred at $\bar{x}$ gives: $\I(x) = \I(\bar{x}) + J_I(\bar{x})(x-\bar{x}) + o(\Vert x- \bar{x} \Vert)$. I $\bar{x}= 0$, one recovers the growth expression from the previous section and $J_I(\bar{0})$ can be seen as the interaction matrix from model \eqref{system}.

\subsection{Reconstructing the Interaction Function}

Suppose that the functions $f_i(s)$, and the yields $y_i$ are well-known. By using experimental measurements of $x$, represented by $z(t)$, the objective is to reconstruct function $I(x)$. For doing so, the terms $I_i(x)$ are replaced by a control $u_i(t)$  and a state feedback is obtained by solving a nonlinear optimal tracking problem.

Consider the observable system \eqref{Controlsystem} ($y(t)$ being the observer) where $g(\cdot)$ is a known function.

\begin{align} 
\label{Controlsystem}
\begin{array}{cl}
\dot{x_i} =& \left(f_i(s)u_i(t) -D \right)x_i \quad \forall i \in G_1\\
\dot{x_i} =& \left(f_i(s)u_i(t) -D \right)x_i \quad \forall i \in G_2\\
\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)u_i(t) x_i  \\
\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)u_i(t)	-\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)u_i(t) x_i  \\
\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)u_i(t) x_i \\
y(t) & = g(x,s)
\end{array}
\end{align}

For this model $g(x,s) = x$, since we are observing measurements coming from genetic sequencing. Consider the weighted norms defined by positive definite matrices $F,Q$, and $R$, represented by $\Vert \cdot \Vert_F$, $\Vert \cdot \Vert_Q$, and $\Vert \cdot \Vert_R$, respectively. The optimal tracking problem is defined as:

\begin{align}
\label{Optimal Control} \begin{array}{cc} \min &  \int \limits_{0}^{T} \Vert g(x,s) - z \Vert_Q + \Vert(u -\vec{1}) \Vert_R dt\\
s.t.& 
(x,s_1,s_2,s_3)\mbox{ solution of \eqref{Controlsystem}} \\
&u_i(t) \in [0,1]
\end{array}	
\end{align}

The control $u(t)$ is intended to drive the system to be near a desired output $z(t)$, which in this context are the measurements of the concentrations of OTU and metabolites. The term $\lambda \Vert(u -\vec{1}) \Vert_R$, was added for two reasons:

First because the interest is testing the idea that interactions could be driving the system. Therefore adding a penalization in the objective function for each control to remain near $1$ can be seen as an attempt to explain data without any interaction.

Second, to force a regularized control. Otherwise note that $u$ is linear in \eqref{Controlsystem}, therefore if the integral cost does not have a non-linear expression of $u$ the optimal control will be of a bang-bang type with possibly singular arcs. Since the objective is to find a differentiable expression of $I(x)$ the addition of the regularization term is deemed necessary.

The problem of approximating the solution of the system to a desired reference ($z$ in this case) is called the optimal tracking problem. For solving such a problem the approach developed by Cimen \textit{et al.} \cite{Cimen2004} was adapted to our problem. The method proposed involves the resolution of Approximating Sequences of Ricatti Equations (ASRE).

Two points of departure from the original method are made clear, details can be seen in the appendix: first the tracking problem does not consider a constrained control, so one should consider a reformulation as proposed by the same author in other works \cite{Cimen2008}. Nevertheless, the methods were directly used, and an explicit constraint in the synthesis of the control was added for the control to remain within the desired bounds. Second, when implementing equation (12) of their article \cite{Cimen2008} a linearised dynamic is not used. Instead the original dynamic with the control given by equation (9) of their article is used. This modification of the original method was performed after experiencing poor numerical integration (ill conditioning) of the proposed linear equation.

The problem with implementing the linearisation fo the dynamic can be partially explained because the dynamic used in this article has the property of remaining in the positive octant, while a linearisation of it may not posses this property, thus hindering the next iteration by -for example- providing a solution with negative substrate or biomass. Partially explained, because even when controlling positivity of the output of the differential equation solver, numerical integration problems were also encountered.

The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the appendix section. This in turn implies $v_i(t) \in [-1,0]$.

The feedback control $v(t)$, will be of the form $v(t) = -R^{-1}\tilde{B}^\top(t)\left(\tilde{P}(t)x(t)-s_f(t)\right)$. Where matrix $P(t)$ and vector $s_f(t)$ solve differential equations. Note that the control becomes a function of the OTU concentration so it represents the interaction function.

For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against noised synthetic data and then against real experimental data. The first test consisted in simulating
\subsection{Numerical results}

In this section the tracking problem was solved in the chemostat setting discussed before with data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}. Only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics; for exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept constant as possible.

A method was used in order to classify OTU in either $G_1$ or $G_2$ from data ranging from day $184$ and $245$ which yields as well the $k_i$ of each OTU.  12 OTU were present in the $G_1$ group and 9 in the $G_2$ functional group. The system state dimension becomes 24. Then the tracking method was used from day $245$ to day $362$.

The knowledge of function $f_i(s)$ were based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}. Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ while a Haldane function (eq. \eqref{Haldane})was used for $G_2$. Since flock formation was seen in the chemostat experiment, the $K_s$ constant proposed by \cite{Wiesmann1994} was multiplied by a hundred times, in order to model for less substrate availability inside a flock.

\begin{align}
\label{monod} f_i(s) &= \bar{\mu}_i \dfrac{s_1}{K_i +s_1} \, \forall i \in G_1 \\
\label{Haldane} f_i(s) &= \bar{\mu}_i \dfrac{s_2}{K_i +s_2 + \frac{s_2^2}{KI}} \, \forall i \in G_2
\end{align}

The choice of the matrix $F$, $Q$ and $R$, influence the quality of the fitting, and three cases are presented. Before for the reader to gain understanding of the situation a simulation in figure \ref{NoControlSimulation} is shown without control. One can see that simulation predicts CN (accumulation of $s_3$), while data is showing PN  (accumulation of $s_2$).

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{OTU_no_control}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{metabolites_no_control}
	\end{subfigure}
	\caption{Simulation with no control. Warm colors for OTU belonging to $G_1$. Cold colors for OTU belonging to $G_2$. Dotted line represents data.}
	\label{NoControlSimulation}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_1}
	\end{subfigure}
	~	
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_25}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_25}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_45}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_45}
	\end{subfigure}
	\caption{Case 1 Metabolites and OTU concentration,  $R = 0.01 I_n$. Let $Q = I_n$, and $F = 10Q$. Left OTU fitting, right Metabolites. Continuous lines are the fit. Dotted lines represent data. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
	\label{Case 1 Metabolites OTU}
\end{figure}

\clearpage

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_25}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
	\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_45}
	\end{subfigure}
	\caption{Case 1: Control for tracking. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
	\label{Case 1 Control}
\end{figure}  
In this case from figure \ref{Case 1 Metabolites OTU} one can see that $s_1$ accumulation is predicted and not $s_2$ which was the most abundant metabolite. By choosing the identity matrix as the weight matrix of the tracking part it privileges the most abundant species (OTU 11), and thus the behaviour is predicted based only on OTU 11. From figure \ref{Case 1 Control} it can be seen that the control for OTU in $G_2$ tends to $1$, while the control for OTU in $G_1$ (with exception of OTU 11) remain almost zero until day $320$. The method seems to converge: note that the control for iterations $25$ and $45$ vary slightly from one another.

\clearpage
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_1}
	\end{subfigure}
	~	
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_15}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_15}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_25}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_25}
	\end{subfigure}
	\caption{Case 2: $R = 0.001 I_n$. Let $\bar{k} =  \max \{k_i| i\in [n] \}$, $Q = \diag(k) /\bar{k}$, and $F = 10Q$. Left OTU fitting, right Metabolites. Continuous lines are the fit. Dotted lines represent data. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
	\label{Case 2 Metabolites OTU}
\end{figure}
\clearpage
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_15}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_25}
	\end{subfigure}
	\caption{Case 2 Control for tracking.Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
	\label{Case 2 Control}
\end{figure}

In this case from figure \ref{Case 2 Metabolites OTU} one can see that $s_2$ accumulation is predicted which was the most abundant metabolite. It was also able to detect an $s_1$ peak at day $340$.  The rationale for choosing the yields as the diagonal of the weight matrix of the tracking part is that a higher yielding organism will cause a more pronounced difference in the metabolites of the system, thus more weight is given to correctly tracking those OTU. From figure \ref{Case 2 Control} it can be seen that the control for OTU in $G_2$ remains zero until day 300, while the control for OTU in $G_1$ vary differently throughout the trajectory.

\clearpage
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_5}
	\end{subfigure}
	~
		\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_15}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_15}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_25}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_25}
	\end{subfigure}
\caption{Case 3: $R = 0.0001 I_n$. Let $\bar{k} =  \max \{k_i| i\in [n] \}$, $Q = \diag(k) /\bar{k}$, and $F = 10Q$. Left OTU fitting, right Metabolites. Continuous lines are the fit. Dotted lines represent data. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
\label{Case 3 Metabolites OTU}
\end{figure}
\clearpage
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_1}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_5}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_15}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.32\textheight}
	\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_25}
	\end{subfigure}
	\caption{Case 3: Control for tracking. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
	\label{Case 3 Control}
\end{figure}

In this case from figure \ref{Case 3 Metabolites OTU} one can see that $s_2$ accumulation is predicted which was the most abundant metabolite. It was also able to detect an $s_1$ peak at day $340$ and an $s_3$ peak at the beginning of the trajectory.  The same rationale as case two was used for picking the weight matrix of the tracking part. From figure \ref{Case 3 Control} it can be seen that the control for OTU in $G_2$ remains zero until day 300 (except for OTU 20, responsible for the $s_3$ peak), while the control for OTU in $G_1$ vary differently throughout the trajectory. The only difference from case two is that the weight matrix for the control part was divided by 10, thus allowing a better fit of the OTU at the expense of more steep variations in the control.

\clearpage
In two out of three cases it can be seen that the accumulation of $s_2$ instead of $s_3$ (i.e. PN) was predicted. The cases were accumulation of $s_2$ was predicted are explained by a weight matrix  that used the yields of each OTU. It also seems that the control (and therefore the solution) converge, however since departures from the original method were used, one can not ensure they converge to the optimal value. But given that the fit of the OTU follows the trend of data, and one is able to predict $s_2$ accumulation, the results seems satisfactory from a numerical standpoint. All cases matrix $F$ (the final point weight) was taken as 10 times $Q$, otherwise the control always ended up in $0$ ($v(t_f) = 0$).

\section{Conclusion}

This article dealt with the problem of how to include genetic data in the prediction of performance of bioreactors, a previous model which deals with such an issue was revisited. The former model suffers from poor scalability, and therefore its application is limited. Inspired by their model a novel approach was here developed in order to systematically integrate the available genetic data. The approach is fairly straightforward for chemostat systems because it consists in multiplying a control to the growth expression of each OTU to be tracked. Nevertheless a method for previous identification of the microbial community must be used beforehand.

\clearpage
\section{Appendix}

\textbf{Proof of lemma \ref{l1}}
\begin{proof}
	Define 
	\begin{align}
	z_1 &: = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1  \\
	z_2 &: = \sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 + s_2 \\
	z_3 &: = s_1 + s_2 + s_3
	\end{align}

	Computing $\dot{z_{1}}$ one gets:
	\begin{align*}
	\dot{z_{1}} &=\sum \limits_{i \in G_1} \frac{1}{y_i}\dot{x_i} + \dot{s_1} \\
	& = \sum \limits_{i \in G_1} \frac{1}{y_i}\left(\mu_i(s_1,x) -D \right)x_i + (s_{in}-s_1)D-\sum\limits_{i \in G_1}\frac{1}{y_i}\mu_i(s_1,x) x_i   \\
	&= 	D\left(-\sum \limits_{i \in G_1} \frac{1}{y_i}x_i - s_1 + s_{in}\right)  \\
	& = D(s_{in} - z_1)
	\end{align*}

	Define $\bar{s} =\max\{s_{in}(t) | t\geq 0\}$ and consider the differential equation:

	\begin{align}
	\label{compareEquation}
	\begin{array}{l}
	\dot{w} = D(\bar{s} - w) \\
	w(0) = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i(0) + s_1(0)
	\end{array}
	\end{align}

	If there is a time interval $H$ such that $t^*\in H  \Rightarrow D(t^*) = 0$, then $z_1$ is constant and therefore bounded by  the value of the solution in $z(t^*)$. 
	If $D(t) > 0$, then $w = \bar{s}$ is a stable asymptotic equilibrium. Define $M_1 :=  \max\{w(0),\bar{s}\}$. If $ w(0) > \bar{s}$ then by the Picard-Lindeloff theorem $ \forall t \; \dot{w}(t) < 0 $, otherwise it would cross the solution of the initial value problem \eqref{compareEquation} with starting point $\bar{s}$ , therefore $w(t) \geq \bar{s}$. The same reasoning may be applied if $ w(0) < \bar{s}$. One concludes that $ w(t) \leq M_1 $.

	Consider  
	\begin{align}
	\label{z1} \begin{array}{l}
	\dot{z_1} =  D(s_{in} - z_1)\\
	z_1(0) = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i(0) + s_1(0)
	\end{array} 
	\end{align}
	From a comparison lemma (see chapter 3 \cite{Khalil1996}), the solution of \eqref{z1} is bounded by $w$ and therefore $z_1(t) \leq M_1$.

	By defining $M_2 = \max\left \{ \displaystyle \sum \limits_{i=n_1 +1 }^{n} \frac{1}{y_i}x_i(0) + s_1(0) +s_2(0), \bar{s} \right\}$, and $M_3 =\max\left \{ s_1(0) +s_2(0) + s_3(0), \bar{s} \right\} $ and noting that $z_2(t)$ and $z_3(t)$ satisfies the same differential equations as $z_1$ the above reasoning may be applied and one has the desired bounds.
\end{proof}

\textbf{Proof of theorem \ref{theoWellPosedness}}

\begin{proof}
	If any coordinate of the solution becomes zero, then it's derivative is either zero, or positive. The bound will follow from Lemma \ref{l1}.

	Note that for any $i \in \{1,\dots, n\} $ if $x_i = 0$ then $\dot{x_{i}} = 0$, therefore all solutions of system \eqref{system} with initial condition $x_i(t_0) = 0$ remain in these planes. By the Picard Lindeloff theorem a solution starting in $int(\Omega)$ cannot cross these planes, therefore $x_i(t)\geq 0$ for $t \geq 0$.

	If $s_1 = 0$, then $\dot{s_1} = Ds_{in} > 0$. Therefore $s_1(t) \geq 0$.

	If $s_2 = 0$ then note first that by adding both inequalities from Lemma \eqref{l1} and since, $s_1,x_i \geq 0$ one has:
	\begin{align*}
	\sum \limits_{i \in G_1 \cup G_2}  \frac{1}{y_i} x_i + 2s_1 + s_2 \leq M_1 + M_2 \\
	\Rightarrow \sum \limits_{i = 1}^{n}  \frac{1}{y_i} x_i + 2s_1 \leq M_1 + M_2 \\
	\Rightarrow \sum \limits_{i = 1}^{n}  \frac{1}{y_i} x_i \leq M_1 + M_2\\ 
	\Rightarrow \bar{k} \sum  \limits_{i = 1}^{n}   x_i  \leq M_1 + M_2  \\
	\Leftrightarrow \bar{k} \sum  \limits_{i = 1}^{n}   \vert x_i \vert  \leq M_1 + M_2  \\
	\Leftrightarrow \bar{k} \Vert x \Vert_1  \leq M_1 + M_2  \\
	\Rightarrow   \bar{k} \Vert x \Vert_{\infty} \leq M_1 + M_2
	\end{align*}

	Where $\bar{k} = \min \left\{ \frac{1}{y_i}  : \; i\in [n] \right \}$.

	Define $M := \dfrac{\bar{k}}{M_1 + M_2}$, and let $A$ be a matrix such that $\Vert A \Vert_{\infty} \leq M$. Then since $\Vert Ax \Vert_{\infty} \leq 1 \Rightarrow \forall i=1,\dots,n \; (1 + A_{i\bullet}x) \geq 0 $, and $\Vert Ax \Vert_{\infty} \leq \Vert A \Vert_{\infty} \Vert x\Vert_{\infty} \leq M \frac{1}{M}$.
	One has proven that:
	\begin{align}
	\label{Bound1} \forall i=1,\dots,n \;  \;  (1 + A_{i\bullet}x) \geq 0 
	\end{align}

	Therefore $\dot{s_2} = \displaystyle \sum \limits_{i \in G_1 } \frac{1}{y_i}\mu_i(s_1,x)x_i =  \sum \limits_{i \in G_1 } \frac{1}{y_i}\bar{\mu_i}f_i(s)(1+A_{i \bullet }x)x_i \geq 0$. Therefore $s_2(t) \geq 0$.

	Note that since one has proven that $s_2 \geq 0$, bound \eqref{Bound1} is valid for any time, and not only when $s_2 = 0$. 
	If $s_3 = 0$ then $\dot{s_3} = \sum \limits_{i \in G_2 }^{n}\frac{1}{y_i}\mu_i(s_2,x)\geq 0$. Therefore $s_3 \geq 0$.

	For the boundedness it suffices to notice from Lemma \ref{l1} that the sum of positive elements is bounded, therefore each element is bounded.
\end{proof}

\subsection{Properties of diag operator}

Notice that for two vectors $v_1$ and $v_2$ the following holds:
\begin{align}
\diag(v_1)\diag(v_2) = \diag(v_2)\diag(v_1) 
\end{align}

Suppose $v \in \R^n$ such that $v_i \neq 0 \forall i \in [n]$. Define $v^{-1}:= \left( \dfrac{1}{v_1},\dots,\dfrac{1}{v_n} \right)$ then the inverse of $\diag(v)$ exists and is $\diag(v^{-1})$:

\begin{align}
\diag(v)^{-1} = \diag(v^{-1}) 
\end{align}

\subsection{Inverse of A and products}
Notice that $\begin{bmatrix}
A_1 \\ A_2
\end{bmatrix} A^{-1} = \begin{bmatrix}
A_1A^{-1} \\ A_2A^{-1}
\end{bmatrix}=I $.

Then $A_1A^{-1}= \begin{bmatrix}
I_{n_1}& 0_{n_2 \times 1} 
\end{bmatrix}$ and $A_2A^{-1}= \begin{bmatrix}
0_{n_1 \times 1} & I_{n_2}
\end{bmatrix}$.

For notation purposes it is useful to define: \begin{align}
B := \diag(k) A^{-1}.
\end{align}

\subsection{Deduction of  \eqref{s1Equilibria}}

Replacing \eqref{xEquilibria} in \eqref{Eq2} yields :
\begin{align}
(s_{in}-s_1)D- \begin{bmatrix}
1_{n_1 \times 1}+A_1A^{-1}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1}) \\0_{n_2 \times 1}
\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1})=0 \\
(s_{in}-s_1)D-	\begin{bmatrix}
1_{n_1 \times 1}+\begin{bmatrix}
I_{n_1} & 0_{n_2 \times 1} 
\end{bmatrix}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) \\0_{n_2\times 1}
\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0 \\
(s_{in}-s_1)D-	\begin{bmatrix}
D_{n_1 \times 1}\\0_{n_2 \times 1}
\end{bmatrix}^T\diag(f(s))^{-1}\diag(f(s)) \diag(k) A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0  \\
(s_{in}-s_1)D-\begin{bmatrix}
D_{n_1 \times 1} \\0_{n_2\times 1}
\end{bmatrix}^\top \diag(k)A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n_1 \times 1}) = 0 \\
(s_{in}-s_1)- \begin{bmatrix}
1_{n_1 \times 1}\\0_{n_2 \times 1}
\end{bmatrix}^\top B (\diag(f(s))^{-1}D_{n \times 1} - 1_{n \times 1}) = 0 
\end{align}

\subsection{Deduction of \eqref{s2Equilibria}}
Analogous as before, replacing \eqref{xEquilibria} in \eqref{Eq3} yields :
\begin{align}
-s_2D+
\begin{bmatrix}
(\diag(\mu_A)^{-1} \vec{D}) \\ -(\diag(\mu_B)^{-1} \vec{D})
\end{bmatrix}^\top \diag(\mu)\diag(y)^{-1} A^{-1}(\diag(\mu)^{-1}\vec{D}-\vec{1}) = 0 \\
-s_2D+
\begin{bmatrix}
\vec{D} \\ - \vec{D}
\end{bmatrix}^\top \diag(y)^{-1} A^{-1}(\diag(\mu)^{-1}\vec{D}-\vec{1}) = 0\\
-s_2+
\begin{bmatrix}
\vec{1} \\ - \vec{1}
\end{bmatrix}^\top B(\diag(\mu)^{-1}\vec{D}-\vec{1}) = 0
\end{align}
\begin{align} 
-s_2D+ \begin{bmatrix}
1_{n_1 \times 1}+A_1A^{-1}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1}) \\-(1_{n_1 \times 1}+A_2A^{-1}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1})
\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0 \\
-s_2D+	\begin{bmatrix}
1_{n_1 \times 1}+\begin{bmatrix}
I_{n_1} & 0_{n_2 \times 1} 
\end{bmatrix}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) \\-(1_{n_1 \times 1}+\begin{bmatrix}
0_{n_1 \times 1} & I_{n_2} 
\end{bmatrix}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1})
\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0 \\
-s_2D +	\begin{bmatrix}
D_{n_1 \times 1}\\-D_{n_2 \times 1}
\end{bmatrix}^T\diag(f(s))^{-1}\diag(f(s)) \diag(k) A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0  \\
-s_2D+\begin{bmatrix}
D_{n_1 \times 1} \\-D_{n_2\times 1}
\end{bmatrix}^\top \diag(k)A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n_1 \times 1}) = 0 \\
-s_2 + \begin{bmatrix}
1_{n_1 \times 1}\\1_{n_2 \times 1}
\end{bmatrix}^\top B (\diag(f(s))^{-1}D_{n \times 1} - 1_{n \times 1}) = 0 
\end{align}
\subsection{Deduction of \eqref{S2(S1)}}

Note that 
\begin{align}  (\diag(f(s))^{-1}D_{n\times 1}-1_{n\times1})  & = \begin{array}{cc} 
\begin{bmatrix}
\left(D\frac{K_1+s_1}{\bar{\mu}_{1}s_1}-1 \right) \\ \vdots \\ \left(D\frac{K_n+s_2}{\bar{\mu}_{n}s_2}-1\right) 
\end{bmatrix} & \hspace{-0.5cm}\begin{array}{c} \left\} n_1\right. \\ \\ \left\} n_2\right.\end{array}
\end{array} \\
\label{invMu} 
& = \begin{bmatrix}
\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_n+(D-\bar{\mu}_n)s_2}{\bar{\mu}_{n}s_2} 
\end{bmatrix}
\end{align}

Replacing \eqref{invMu} in \eqref{s1Equilibria}.

\begin{align}
(s_{in}-s_1)-	\begin{bmatrix}
1_{n_1 \times 1} \\0_{n_2\times 1}
\end{bmatrix}^\top  B\begin{bmatrix}
\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_n+(D-\bar{\mu}_n)s_2}{\bar{\mu}_{n}s_2} 
\end{bmatrix} = 0 \\
(s_{in}-s_1) - \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1} +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}s_2} \right) = 0 \quad / \cdot s_1s_2 \\
(s_{in}-s_1)s_1s_2 - \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}}s_1 \right) = 0 \\
(s_{in}-s_1)s_1s_2 - \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_2s_1 + \sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1 \right) = 0  \\
s_2\left((s_{in}-s_1)s_1 - \sum \limits_{i=1}^{n_1}  \left( \sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}} + \sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_1 \right)  \right) =  \sum \limits_{i=1}^{n_1}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1 \\
s_2\left(-s_{1}^2  +  \left( s_{in}\underbrace{- \sum \limits_{i=1}^{n_1} \sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}}_{\beta_1}\right) s_1 \underbrace{ - \sum \limits_{i=1}^{n_1}  \sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_2}  \right) = \underbrace{\sum \limits_{i=1}^{n_1}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_3}s_1 \\
s_2\left(-s_{1}^2  +  \left( s_{in}+\beta_1 \right) s_1 +\beta_2  \right) = \beta_3 s_1
\end{align}

From the last expression it should be clear that formula \eqref{S2(S1)} holds, it is just a matter of identifying the coefficients.
\begin{itemize}
	\item $\beta_1 =  - \sum \limits_{i=1}^{n_1} \sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}$
	\item $\beta_2 =-\sum \limits_{i=1}^{n_1}  \sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$
	\item $\beta_3 = \sum \limits_{i=1}^{n_1}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}} $
	\item $c_1 = \dfrac{-1}{\beta_3}$
	\item $c_2 =  \dfrac{s_{in} + \beta_1}{\beta_3}$
	\item $c_3 = \dfrac{\beta_2}{\beta_3}$
\end{itemize}

\subsection{Deduction of \eqref{Poly4}}

Again, replacing \eqref{invMu} in \eqref{s2Equilibria}.
\begin{align}
-s_2+
\begin{bmatrix}
1_{n_1 \times 1}\\ - 1_{n_2 \times 1}
\end{bmatrix}^\top B\begin{bmatrix}
\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_n+(D-\bar{\mu}_n)s_2}{\bar{\mu}_{n}s_2} 
\end{bmatrix} = 0 \\
\begin{array}{c} \displaystyle  -s_2 + \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1} +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}s_2} \right) \\
\displaystyle - \sum \limits_{i=n_1+1}^{n}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1} +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}s_2} \right)= 0
\end{array} \quad / \cdot s_1s_2 \\
\begin{array}{c} \displaystyle  -s_1s_2^2 +\sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}}s_1 \right) \\
\displaystyle -  \sum \limits_{i=n_1+1}^{n}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}}s_1 \right)= 0
\end{array} \\
\begin{array}{c} \displaystyle  -s_1s_2^2 + \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_2s_1 + \sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1\right) \\
\displaystyle -  \sum \limits_{i=n_1+1}^{n}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_2s_1 + \sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1 \right)= 0
\end{array}\\
\begin{array}{c} \displaystyle  -s_1s_2^2  - \beta_2s_2 -\beta_1s_1s_2 + \beta_3s_1 
\underbrace{- \sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_4}s_2 \underbrace{-\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}}_{\beta_5}s_2s_1\underbrace{ -\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_6}s_1 = 0
\end{array}\\
-s_1s_2^2  - \beta_2s_2 -\beta_1s_1s_2 + \beta_3s_1 + \beta_4s_2 +\beta_5s_1s_2 + \beta_6s_1  = 0 \\
\label{Prepoly4} (\beta_4-\beta_2)s_2 + (\beta_3+\beta_6)s_1 + (\beta_5 - \beta_1)s_1s_2- s_1s_2^2 = 0 
\end{align}
\begin{itemize}
	\item  $\displaystyle  \beta_4 = - \sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$
	\item $\displaystyle  \beta_5 = -\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}$
	\item $\displaystyle \beta_6 =  -\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$
\end{itemize}

Then replace \eqref{S2(S1)} in \eqref{Prepoly4}: 
\begin{align}
(\beta_4-\beta_2)\dfrac{s_1}{c_1s_1^2+c_2s_1+c_3} + (\beta_3+\beta_6)s_1 + (\beta_5 - \beta_1)s_1\dfrac{s_1}{c_1s_1^2+c_2s_1+c_3}- s_1\left(\frac{s_1}{c_1s_1^2+c_2s_1+c_3}\right)^2 = 0 \quad / \cdot \frac{1}{s_1} \\
(\beta_4-\beta_2)\dfrac{1}{c_1s_1^2+c_2s_1+c_3} + (\beta_3+\beta_6) + (\beta_5 - \beta_1)\dfrac{s_1}{c_1s_1^2+c_2s_1+c_3}- \left(\frac{s_1}{c_1s_1^2+c_2s_1+c_3}\right)^2 = 0  \quad / \cdot (c_1s_1^2+c_2s_1+c_3)^2 \\
(\beta_4-\beta_2)(c_1s_1^2+c_2s_1+c_3)+ (\beta_3+\beta_6)(c_1s_1^2+c_2s_1+c_3)^2 + (\beta_5 - \beta_1)(c_1s_1^2+c_2s_1+c_3)s_1 - s_1^2 = 0   \\
\begin{array}{c}(\beta_4-\beta_2)(c_1s_1^2+c_2s_1+c_3)+ (\beta_3+\beta_6)(c_1^2s_1^4+c_2^2s_1^2+c_3^2 + 2 c_1c_2s_1^3 + 2c_2c_3s_1 + 2 c_1c_3s_1^2)\\ \\  + (\beta_5 - \beta_1)(c_1s_1^2+c_2s_1+c_3)s_1 - s_1^2 = 0 \end{array} \\
\begin{array}{c} \underbrace{(\beta_3+\beta_6)c_1^2}_{a_4} s_1^4 + (\underbrace{(\beta_3 + \beta_6)(2c_1c_2) +  (\beta_5 -\beta_1)c_1}_{a_3})s_1^3 + (\underbrace{(\beta_4 - \beta_2)c_1 +(\beta_3 + \beta_6)(c_2^2 + 2c_1c_3) + (\beta_5-\beta_1)c_2-1}_{a_2})s_1^2 \\ 
+(\underbrace{(\beta_4 -\beta_2)c_2 + (\beta_3 + \beta_6)2c_2c_3+(\beta_5-\beta_1)c_3}_{a_1})s_1 + \underbrace{(\beta_4-\beta_2)c_3 + (\beta_3 + \beta_6)c_3^2}_{a_0} = 0
\end{array}
\end{align}

Which yields \eqref{Poly4}.
\begin{itemize}
	\item $a_4 = (\beta_3+\beta_6)c_1^2$ 
	\item $a_3 = (\beta_3 + \beta_6)(2c_1c_2) +  (\beta_5 -\beta_1)c_1$
	\item $a_2 = (\beta_4 - \beta_2)c_1 +(\beta_3 + \beta_6)(c_2^2 + 2c_1c_3) + (\beta_5-\beta_1)c_2-1$
	\item $a_1 = (\beta_4 -\beta_2)c_2 + (\beta_3 + \beta_6)2c_2c_3+(\beta_5-\beta_1)c_3$
	\item $a_0 = (\beta_4-\beta_2)c_3 + (\beta_3 + \beta_6)c_3^2$
\end{itemize}

\textbf{Note:} When calculating the equilibria with the extinction of some OTU under H \ref{noWashoutHyp}, coefficients are calculated with $B = \diag(k^{act})(A^{act})^{-1}$. The indexes are redefined to be taken only in $i,j \in [n] \setminus \mathcal{J}$ by formula \eqref{EquilibriaFormula}.

\subsection{Deduction of \eqref{S1NOBWashout}}
For auxiliary purposes $B:= \diag(k^{act})(A^{act})^{-1}$.

Under hypothesis \ref{WashoutG2}, the $j \in \mathcal{J}$ entries of vector $\diag(k) \diag(f(s))x^{eq} $ are zero. 
Note also that $(A_1x^{eq})_i = (A^{act}x^{act})_i, \, \forall i \in [n] \setminus \mathcal{J}$.

Then the cross product in equation \eqref{Eq2} can be reduced:
\begin{align} 
\begin{bmatrix}
1_{n_1\times 1}+A_1x^{eq} \\0
\end{bmatrix}^\top \diag(k) \diag(f(s))x^{eq} = [1_{(n-m)\times 1} - A^{act}x^{act}]^\top \diag(k^{act}) \diag(f^{act}(s))x^{act} 
\end{align} 
Therefore replacing \eqref{EquilibriaFormula} and \eqref{EqSome} in \eqref{Eq2}.

\begin{align}
0 &= (s_{in}-s_1)D- [1_{(n-m)\times 1} - A^{act}x^{act}]^\top \diag(k^{act}) \diag(f^{act}(s))x^{act}\\
&= (s_{in}-s_1)D- [1_{(n-m)\times 1} - A^{act}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})]^\top \dots \\ & \diag(k^{act}) \diag(f^{act}(s))(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})\\
&  =  (s_{in}-s_1)-1_{(n-m)\times 1}^\top
B(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})
\end{align}

$s_2$ does not appear in the previous equation. Then as before (using the numeration of active indexes):
\begin{align}
\diag(\mu^{act})^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1} = \begin{bmatrix}
\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_{n-m}+(D-\bar{\mu}_{n-m})s_1}{\bar{\mu}_{n-m}s_1}
\end{bmatrix}
\end{align}

Therefore:

\begin{align}
(s_{in}-s_1)- 1_{(n-m)\times 1}^\top 
B\begin{bmatrix}
\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_{n-m}+(D-\bar{\mu}_{n-m})s_1}{\bar{\mu}_{n-m}s_1}
\end{bmatrix} = 0 \\
(s_{in}-s_1) -\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1}  = 0 \quad /\cdot s_1 \\
(s_{in} - s_1)s_1   -\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}  = 0 \\
-s_1^2 + \left( s_{in}-\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}} \right)s_1 - \frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}} =0
\end{align}

Identifying coefficients
\begin{itemize}
	\item $a'_2 = -1$
	\item $a'_1 = s_{in}-\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j = 1}^{n-m} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}$
	\item $a'_0 =- \frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j = 1}^{n-m} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$ 
\end{itemize}

\subsection{Jacobian of the system}
The jacobian is a square matrix of dimension $n\times 3$. The entries corresponding to the derivative of the first $n$ functions in the first $n$ variables can be calculated by the use of the chain rule. Define (for a fixed $s$):
\begin{align*} 
& \begin{array}{rc}
h_1:\mathcal{M}_{n \times n}(\R) \times \R^n \rightarrow & \R^n \\
(M,y) \rightarrow & My
\end{array}  \\
&\begin{array}{rl}
h_2: \R^n \rightarrow & \R^n \\
x \rightarrow & \diag(f(s))\left(1_{n\times 1}+ Ax\right)-D_{n\times 1}
\end{array} 	
\end{align*}

The first $n$ equations of system \eqref{system} may be written then as$\dot{x} =  h(x) = h_1(\diag(x), h_2(x))$, by the chain rule: 
\begin{align*} J_h(x) &= D_M h_1(\diag(x),h_2(x))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x))\circ D_xh_2(x)  \\ &=
\diag(h_2(x))+\diag(x)\diag(f(s))A  \label{n2_entries}
\end{align*}

Expression \eqref{n2_entries} corresponds to the first $n\times n$ entries of the Jacobian of system \eqref{system}.

\begin{align*}
f_A' := \left( \dfrac{\partial f_1}{\partial s_1}, \dots, \dfrac{\partial f_{n_1}}{\partial s_1} \right)^\top = \left(\dfrac{\bar{\mu}_1K_1}{(K_1 + s_1)^2},\dots, \dfrac{\bar{\mu}_{n_1}K_{n_1}}{(K_{n_1} + s_1)^2} \right)^\top \in \R^{n_1} \\
f_B' := \left( \dfrac{\partial f_{n_1+1}}{\partial s_2}, \dots, \dfrac{\partial f_{n}}{\partial s_2} \right)^\top = \left( \dfrac{\bar{\mu}_{n_1+1}K_{n_1+1}}{(K_{n_1+1} + s_2)^2},\dots, \dfrac{\bar{\mu}_{n}K_{n}}{(K_{n} + s_2)^2} \right)^\top \in \R^{n_2}
\end{align*}

Then the Jacobian of the system may be expressed as:
$J(x,s_1,s_2,s_3) = \begin{bmatrix}
J_{11} & J_{12} & J_{13} & J_{14} \\
J_{21} & J_{22} & J_{23} & J_{24} \\
J_{31} & J_{32} & J_{33} & J_{34} \\
J_{41} & J_{42} & J_{43} & J_{44} 
\end{bmatrix} $

\begin{align}
J_{11} &=  \diag(\diag(f(s))(1_{n\times 1} +Ax)-D_{n\times 1})
+\diag(f(s))\diag(x)A \\
J_{12} &= \diag(x)\diag(1_{n \times 1}+Ax)\begin{bmatrix} f_A' \\ 0_{n_2 \times 1} \end{bmatrix}  \\
J_{13} &=\diag(x)\diag(1_{n\times 1}+Ax)\begin{bmatrix} 0_{n_1 \times 1} \\ f_B' \end{bmatrix} \\
J_{14} &= 0_{n\times 3}\\
J_{21} &= -\begin{bmatrix}
1_{n_1 \times 1} + A_1 x \\ 0_{n_2 \times 1} \end{bmatrix}^\top \diag(y)^{-1} \diag (f(s))  + (\diag(k)\diag(f(s))x)^\top\begin{bmatrix} A_1 \\ 0 \end{bmatrix}  \\
J_{22} &= -D  - \begin{bmatrix} 1_{n_1 \times 1} + A_1x \\ 0 \end{bmatrix}^\top \diag(k) \diag\left( \begin{bmatrix}\mu_A' \\ 0 \end{bmatrix}\right)x \\
J_{23} & = 0 \\
J_{24} &= 0 \\
J_{31} &= \begin{bmatrix} \left(1_{n_1 \times 1}+A_1x \right)\\ - \left(1_{n_2 \times 1} + A_2x \right)  \end{bmatrix}^\top \diag(k) \diag(f(s)) 
+  (\diag(k)\diag(f(s))x)^\top \begin{bmatrix}A_1 \\ -A_2\end{bmatrix} \\
J_{32} &= \begin{bmatrix}\left(1_{n_1 \times 1} + A_1x\right)\\ -\left(1_{n_2 \times 1} + A_2x\right)\end{bmatrix}^\top \diag(k) \diag\left( \begin{bmatrix}
f_A' \\ 0\end{bmatrix}\right)x \\
J_{33} &= -D + \begin{bmatrix} \left(1_{n_1 \times 1} + A_1x\right) \\ -\left(1_{n_2\times 1}+ A_2x\right) \end{bmatrix}^\top \diag(k)\diag\left(
\begin{bmatrix}
0 \\ f_B'
\end{bmatrix}\right)x  \\
J_{34} &= 0 \\
J_{41} &= \begin{bmatrix}0 \\ 1_{n_2 \times 1} + A_2x \end{bmatrix}^\top\diag(k) \diag(f(s)) 
+ (\diag(k)\diag(f(s))x)^\top\begin{bmatrix} 
0 \\ A_2
\end{bmatrix} \\
J_{42} &= 0 \\
J_{43} &= \begin{bmatrix} 0 \\(1_{n_2\times 1} + A_2x) \end{bmatrix}^\top \diag(k) \diag\left(\begin{bmatrix}
0 \\ f_B'
\end{bmatrix}\right) x \\
J_{44} &= -D
\end{align}

\subsection{Tracking Problem reformulation and details}

For applying the methods developed in \cite{Cimen2004}. Define the system state $X = (x,s)$. Make the change of variables $v_i = u_i - 1$ with $v = (v_1,\dots,v_n)$ are applied to system \eqref{Controlsystem}. The system may be rewritten then as:
\begin{align} 
\begin{array}{cl}
\dot{x_i} =& \left(f_i(s)(1+v_i(t)) -D \right)x_i \quad \forall i \in G_1\\
\dot{x_i} =& \left(f_i(s)(1+v_i(t)) -D \right)x_i \quad \forall i \in G_2\\
\dot{s_1} =& \displaystyle s_1\left(\frac{s_{in}}{s_1}-1\right)D-\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)(1+v_i(t)) x_i  \\
\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)(1+v_i(t))	-\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)(1+v_i(t)) x_i  \\
\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}^{n_1+n_2}\frac{1}{y_i}f_i(s)(1+v_i(t)) x_i \\
y(t) & = g(x,s)
\end{array}
\end{align}

Define $k_{G_1} = \left ( \frac{1}{y_1},\dots,\frac{1}{y_{nA}}\right )^\top \in \R^{n_1}$,  $k_{G_2} = \left(\frac{1}{y_{n_1+1}},\dots,\frac{1}{y_{n}}\right )^\top \in \R^{n_2}$, and

\begin{align}
A(X) & = \begin{bmatrix} 
\diag(f(s)- D_{n\times 1} ) & 0_{n \times 3}\\
\begin{matrix} 
f(s)^\top \begin{bmatrix} -\diag(k_{G_1}) & 0_{n_1 \times n_2} \end{bmatrix}^\top  \\
f(s)^\top \begin{bmatrix} \diag(k_{G_1}) & -\diag(k_{G_2}) \end{bmatrix}^\top   \\
f(s)^\top \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top  \end{matrix} & \begin{matrix} \left(\frac{s_{in}}{s_1}-1\right)D & 0 & 0 \\ 
0 &-D & 0 \\ 
0 & 0 &-D \end{matrix}
\end{bmatrix}  \\
B(X) & = \begin{bmatrix} \diag(f(s)\diag(x)  \\
\begin{matrix}
f(s)^\top \diag(x) \begin{bmatrix} -\diag(k_{G_1}) & 0_{n_1 \times n_2} \end{bmatrix}^\top \\
f(s)^\top \diag(x) \begin{bmatrix} \diag(k_{G_1}) & -\diag(k_{G_2}) \end{bmatrix}^\top  \\
f(s)^\top \diag(x) \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top  
\end{matrix}
\end{bmatrix} \\
C(X) = \begin{bmatrix}
I_n & 0_{n\times 3} \\
\end{bmatrix}
\end{align}

Then the system \eqref{Controlsystem} can be rewritten as:

\begin{align}
\dot{X} &= A(X)X + B(X)v \\
y &= C(X)X
\end{align}

$z(t)\in \R^n$ is the measured vector containing the OTU concentrations in time. The cost functional is given by
\begin{align}
J(v) = \left(z(t_f) - C(X) X(t_f)\right)^\top F\left(z(t_f) - C(X) X(t_f)\right) +  \int \limits_{t_0}^{t_f} \left(z(t) - C(X) X(t)\right)^\top Q \left(z(t) -C(X)X(t)\right) + v(t)^\top R v(t)
\end{align}

where $F,Q$ and $R$ are positive definite matrices. Particularly in all simulations $R = \lambda I_n$ for some $\lambda >0$, so all controls have the same weight. Since there is no interest in the final time, we define $F = 0$. $Q$ is a diagonal matrix.

Define the dynamic sequences for $i \in \N \cup \{0\}$, $\dot{X}^{[i]}$ as :

\begin{align}
\dot{X}^{[i]} &= A(X^{[i]})X^{[i]} + B(X^{[i]})v^{[i]} \quad i\in \N \\
y^{[i]} &= X^{[i]} \quad i\in \N \\
X^{[i]}(t_0) &= X_0 \quad i\in \N
\end{align}

And for $i = -1$ define $X^{[-1]}(t) = X_0$.

The control law is given by
\begin{align}
v^{[i]}(t)_j = \max \left\{ -1,\min\left\{0,\left( -R^{-1}B^\top\left(X^{[i-1]}(t)\right)\left(P^{[i]}(t)X^{[i]}(t)-s_f^{[i]}(t)\right)\right)_j \right\}\right\} \forall j \in [n]
\end{align}

Where $P^{[i]}(t) \in \mathcal{M}_{n+3\times n+3}(\R)$ and $s_f^{[i]}(t)\in \R^{n+3}$ are the solution to the differential equations:
\begin{align}
\dot{P}^{[i]} &= -C^T\left(X^{[i-1]}(t)\right)QC\left(X^{[i-1]}(t)\right) - P^{[i]}A\left (X^{[i-1]}(t)\right) -A^\top \left( X^{[i-1]}(t)\right)P^{[i]} \\&+ P^{[i]}B\left( X^{[i-1]}(t) \right)R^{-1}B^\top\left(X^{[i-1]}(t)\right)P^{[i]} \\
P^{[i]}(t_f) &= C^\top \left( X^{[i-1]}(t_f) \right) F C \left( X^{[i-1]}(t_f) \right)
\end{align}

\begin{align}
\dot{s_f^{[i]}} &= - C^\top\left(X^{[i-1]}(t)\right)Qz(t)- \left[A\left(X^{[i-1]}(t)\right) -B\left(X^{[i-1]}(t)\right)R^{-1}B^\top \left(X^{[i-1]}(t)\right)P^{[i]}(t) \right]^\top s_f^{[i]} \\
s_f^{[i]}(t_f) &= C^\top\left(X^{[i-1]}(t_f)\right)Fz(t_f)
\end{align}

Replacing the matrices of our problem

\begin{align}
\dot{P}^{[i]}(t) &= -\begin{bmatrix}
Q & 0_{n\times 3} \\ 0_{3\times n} & 0_{3\times 3}
\end{bmatrix}- P^{[i]}A\left (X^{[i-1]}(t)\right) -A^\top \left( X^{[i-1]}(t)\right)P^{[i]} + \frac{1}{\lambda}P^{[i]}B\left( X^{[i-1]}(t) \right)B^\top\left(X^{[i-1]}(t)\right)P^{[i]} \\
P^{[i]}(t_f) &= \begin{bmatrix}
0_{n\times n} & 0_{n\times 3} \\ 0_{3\times n} & 0_{3\times 3}
\end{bmatrix}
\end{align}

\begin{align}
\dot{s_f}^{[i]}(t) &= -\begin{bmatrix}Qz(t) \\ 0_{3\times 1} \end{bmatrix}- \left[A\left(X^{[i-1]}(t)\right) -\frac{1}{\lambda}B\left(X^{[i-1]}(t)\right)B^\top \left(X^{[i-1]}(t)\right)P^{[i]}(t) \right]^\top s_f^{[i]} \\
s_f^{[i]}(t_f) &=   \begin{bmatrix}
0_{n\times n}  & 0_{n\times 3} \\
\end{bmatrix}^\top z(t_f)
\end{align}

For certain entries of the dynamic the constantly zero function is a solution for them, implying by existence and uniqueness that they should be constantly zero. Then $P^{[i]}$ has $n\times n$ non zero entries and $s^{[i]}$ has $n$ non zero entries, explicitly:

\begin{align}
P^{[i]}(t) = \begin{bmatrix}
\tilde{P}^{[i]}(t) & 0_{n\times 3} \\ 0_{3 \times n} & 0_{3 \times 3}
\end{bmatrix} \\
s_f^{[i]}(t) = \begin{bmatrix}
\tilde{s}_f^{[i]}(t) \\ 0_{1\times 3}
\end{bmatrix} \\
A\left (X^{[i-1]}(t)\right) = \begin{bmatrix}
A_{11} & A_{12} \\ A_{21} & A_{22}
\end{bmatrix} \\
B\left (X^{[i-1]}(t)\right) = \begin{bmatrix}
B_1 \\ B_2
\end{bmatrix} 
\end{align}

Where $A_{11} = \diag \left( f\left(s^{[i-1]}\right)- D_{n\times 1} \right)$, and $B_1 = \diag\left(f\left(s^{[i-1]}\right)\right)\diag \left(x^{[i-1]} \right) $ The equations for $\tilde{P}^{[i]}(t)$:
\begin{align}
\dot{\tilde{P}}^{[i]}(t)= -Q- \tilde{P}^{[i]}A_{11} -A_{11}^\top \tilde{P}^{[i]} + \dfrac{1}{\lambda} \tilde{P}^{[i]}B_1B_1^\top \tilde{P}^{[i]} \\
\tilde{P}^{[i]}(t_f) = 0
\end{align}

Inspecting the former equation one notices that if $i\neq j$, $P_{ij}(t) = 0$ is a solution of all non diagonal entries. And therefore by existence and uniqueness they should be constantly zero. Hence only the diagonal entries should be calculated. 
\begin{align}
\dot{\tilde{P}}^{[i]}_{jj}(t)= -Q_{jj}- 2 \left(f_j\left(s^{[i-1]}\right)- D \right)\tilde{P}^{[i]}_{jj} + \dfrac{1}{\lambda}\left(\tilde{P}^{[i]}_{jj}\right)^2f_j\left(s^{[i-1]}\right)^2\left(x^{[i-1]}_j\right)^2  \\
\tilde{P}^{[i]}_{jj}(t_f) = 0
\end{align}

For and  $\tilde{s_f}^{[i]}(t)$ the system reduces to:

\begin{align}
\dot{\tilde{s}}_f^{[i]}(t) &= -z(t)- \left[A_{11} -\frac{1}{\lambda}B_1B_1^\top \tilde{P}^{[i]}(t) \right]^\top \tilde{s}_f^{[i]} \\
\tilde{s}_f^{[i]}(t_f) &= 0
\end{align}

And the control law is given by
\begin{align}
v^{[i]}(t)_j = \max \left\{ -1,\min\left\{0,\left( -\dfrac{1}{\lambda}B_1^\top\left(X^{[i-1]}(t)\right)\left(\tilde{P}^{[i]}(t)x^{[i]}(t)-\tilde{s}_f^{[i]}(t)\right)\right)_j \right\}\right\} \forall j \in [n]
\end{align}

They were solved using standard backward numerical integration.

\bibliographystyle{elsarticle-num}
\bibliography{mybibfile}
\end{document}

### 2019-11-07 Tracking/synthetic_data.m
changed in synthetic data

@@ -6,31 +6,34 @@ nB = 5;
 n = nA + nB;
 a = ones(nA,1);
 b = ones(nB,1);
-indexAOB = 1:nA;
-indexNOB = nA+1:n;
+class_AOB = [ones(nA,1); zeros(nB,1)];
+class_NOB = [zeros(nA,1); ones(nB,1)];
 time_steps_index = 1;
 muARef = 0.77;
 muBRef = 1.07;
 kSARef = 0.7e-1;
 kSBRef = 1.4982e-1;
 kIRef = 1.217;
-x0 = [0.0001*ones(n,1); 0; 0; 0];
+x0 = [0.01*random('Unif',0,1,nA,1);0.001*random('Unif',0,1,nB,1); 0.1; 0.1; 0.1];
 d_interp = @(t) 0.2;
 s_in_interp = @(t) 0.5;
-yields_AOB = 1/0.251*ones(nA,1);
-yields_NOB = 1/0.062*ones(nB,1);
+kA = 1/0.251*ones(nA,1);
+kB = 1/0.062*ones(nB,1);
 A = random('Normal',0,1,n,n);
+% A = zeros(n,n);
 growth1 = @(X) (1+A(1:nA,:)*X(1:n))*growth_monod(X(n+1),muARef,kSARef);
 growth2 = @(X) (1+A(nA+1:n,:)*X(1:n))*growth_monod(X(n+2),muBRef,kSBRef);
 dynamic = @(t,X) [diag(growth1(X) - d_interp(t))*X(1:nA);
    diag(growth2(X) - d_interp(t))*X(nA+1:n);
-   (s_in_interp(t) - X(n+1))*d_interp(t) - yields_AOB'*diag(growth1(X))*X(1:nA);
-    -X(n+2)*d_interp(t) + yields_AOB'*diag(growth1(X))*X(1:nA)-yields_NOB'*diag(growth2(X))*X(nA+1:n);
-    -X(n+3)*d_interp(t) + yields_NOB'*diag(growth2(X))*X(nA+1:n);];
-[t_obs, Y] = ode15s(dynamic,[0 200],x0);
+   (s_in_interp(t) - X(n+1))*d_interp(t) - kA'*diag(growth1(X))*X(1:nA);
+    -X(n+2)*d_interp(t) + kA'*diag(growth1(X))*X(1:nA)-kB'*diag(growth2(X))*X(nA+1:n);
[…]

### 2019-11-07 Tracking/plot_data_fit.m
add plot_data_fit

@@ -1,0 +1,128 @@
+%plotting
+clear
+close all
+name_file_in = 'MAT_Files\\061119_Try1_iter_500';
+load(name_file_in);
+numbering_AOB = strsplit(num2str(1:nA)) ;
+legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_AOB{:}),...
+    sprintf(',OTU %s (data)', numbering_AOB{:})),',');
+numbering_NOB = strsplit(num2str(nA+1:n)) ;
+legend_tags_NOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_NOB{:}),...
+    sprintf(',OTU %s (data)', numbering_NOB{:})),',');
+legend_tags_biomass{1} = 'Sum of species measured biomass';
+legend_tags_biomass{2} = 'Sum of species model biomass';
+legend_tags_AOB_control = strsplit(sprintf('Control OTU %s,', numbering_AOB{:}),',');
+legend_tags_AOB_control(end) = [];
+legend_tags_NOB_control = strsplit(sprintf('Control OTU %s,', numbering_NOB{:}),',');
+legend_tags_NOB_control(end) = [];
+colors_OTU = mat2cell([autumn(nA); winter(nB)], ones(1,n), 3);
+colors_AOB = mat2cell(autumn(nA), ones(1,nA), 3);
+colors_NOB = mat2cell(winter(nB), ones(1,nB), 3);
+colors2 = mat2cell(hsv(3), ones(1,3),3);
+% xFun = @(t) interp1(tNew,xNew,t)';    
+% control = @(t) trackingControl(lambda,B(t),P(t),xFun(t),sfInterpol(t),n);
+% controlEval = arrayfun(control,tNew,'UniformOutput',false);
+index_t_OTU = find(t_OTU<max(tS) & t_OTU>min(tS));
+%%Total Biomass
+figure
+hold on
+total_biomass_plot = plot(t_OTU(index_t_OTU),sum(OTU_interp(index_t_OTU,:),2),'k*','LineWidth',1.5);
+total_biomass_plot2 = plot(t_new,sum(x_new(:,1:n),2),'k.-','LineWidth',1.5);
+xlabel('\fontsize{12}Time [days]'),...
+    ylabel('\fontsize{12}  Concentration [g/l]'),...
+    title(sprintf('Tracking results total biomass iteration:%.0f',iter));
[…]

### 2019-11-18 Tracking/plot_data_fit.m
changed font labels

@@ -1,16 +1,16 @@
 %plotting
 clear
 close all
-name_file_in = 'MAT_Files\\061119_Try1_iter_500';
+name_file_in = 'MAT_Files\\061119_Try1_iter_300';
 load(name_file_in);
 numbering_AOB = strsplit(num2str(1:nA)) ;
-legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_AOB{:}),...
+legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_AOB{:}),...
     sprintf(',OTU %s (data)', numbering_AOB{:})),',');
 numbering_NOB = strsplit(num2str(nA+1:n)) ;
-legend_tags_NOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_NOB{:}),...
+legend_tags_NOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_NOB{:}),...
     sprintf(',OTU %s (data)', numbering_NOB{:})),',');
-legend_tags_biomass{1} = 'Sum of species measured biomass';
-legend_tags_biomass{2} = 'Sum of species model biomass';
+legend_tags_biomass{1} = 'Data: Sum of species biomass';
+legend_tags_biomass{2} = 'Tracking: Sum of species biomass';
 legend_tags_AOB_control = strsplit(sprintf('Control OTU %s,', numbering_AOB{:}),',');
 legend_tags_AOB_control(end) = [];
 legend_tags_NOB_control = strsplit(sprintf('Control OTU %s,', numbering_NOB{:}),',');
@@ -28,12 +28,12 @@ figure
 hold on
 total_biomass_plot = plot(t_OTU(index_t_OTU),sum(OTU_interp(index_t_OTU,:),2),'k*','LineWidth',1.5);
 total_biomass_plot2 = plot(t_new,sum(x_new(:,1:n),2),'k.-','LineWidth',1.5);
-xlabel('\fontsize{12}Time [days]'),...
-    ylabel('\fontsize{12}  Concentration [g/l]'),...
+xlabel('\fontsize{15}Time [days]'),...
+    ylabel('\fontsize{15}  Concentration [g/l]'),...
     title(sprintf('Tracking results total biomass iteration:%.0f',iter));
 %     title(sprintf('Simulation v(t) = -1'));
 set(gca,'fontsize',15),
[…]

### 2019-11-18 Tracking/main.m
initial iteration is the system without control.

@@ -47,9 +47,12 @@ legend_tags = strsplit(strjoin({num2str(1:n),' s_1 s_2 s_3'}));
 legend_tags_OTU = strsplit(strjoin({num2str(1:n)}));
 tF = tS(end);
 t0 = tS(1);
-%x0 = [z(t0)' s1Interpol(t0) s2Interpol(t0) s3Interpol(t0)]';
-x0 = [0.001*ones(1,n) s1_interp(t0) s2_interp(t0) s3_interp(t0)]'; 
-x_fun = @(t) x0;
+x0 = [0.001*ones(1,n) s1_interp(t0) s2_interp(t0) s3_interp(t0)]';
+dynamic = @(t,X) Ax(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,s_in_interp(t),...
+    d_interp(t))*X ;
+options = odeset('NonNegative',(1:n+3)');
+[t_new,x_new] = ode15s(dynamic,[t0 tF], x0,options);
+x_fun = @(t) interp1(t_new,x_new,t)';
 B = @(t) Bx(x_fun(t),nA,nB,kA,kB,muA,muB,kSA,kSB,kI);
 PtF = F;
 system_ricatti = @(t,P_lin) ricatti_diff(P_lin,x_fun(t),Q,nA,nB,kA,kB,muA,...

### 2019-11-19 Tracking/main.m
changes on variables position

@@ -1,8 +1,10 @@
+%Reference: Cimen et al 2002 Nonlinear optimal tracking control
+
 %main: process and filter data to model.
 close all
 clear
-load('MAT_files\synthetic_data_no_noise')
-name_file = '061119_Try1';
+load('MAT_files\synthetic_data_noise')
+name_file = '191119_Try1';
 nA = round(sum(a));
 nB = round(sum(b)); 
 n = nA+nB;
@@ -72,14 +74,13 @@ dynamic = @(t,X) Ax(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,s_in_interp(t),...
     d_interp(t))*X + Bx(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI)...
     *tracking_control(lambda,B(t),P(t),X,sf_interp(t),n);
 tic
-options = odeset('NonNegative',(1:n+3)');
 [t_new,x_new] = ode15s(dynamic,[t0 tF], x0,options);
 toc
 %%SRE
 x_cell = arrayfun(x_fun,t_new,'UniformOutput',false);
 X = reshape(cell2mat(x_cell),length(t_new),n+3);
 x_old = X;
-csTolerance = 4; %cauchy sequence tolerance
+csTolerance = 0.001; %cauchy sequence tolerance
 iter = 1;
 diff = norm(x_old - x_new);
 save(sprintf('MAT_files\\%s_iter_%.0f',name_file,iter))
@@ -103,9 +104,9 @@ while diff > csTolerance
     fig.PaperPositionMode = 'auto';
     print(sprintf('Images\\%s',sprintf('%s_Trajectory_Iter_%.0f',...
         name_file,iter)),'-dpng','-r0')
-    figure
+    figure 
     control_plot = plot(t_new,reshape(cell2mat(control_eval),n,...
-        length(t_new)),'LineWidth',1.5);
+        length(t_new)),'LineWidth',1.5,'Visible','on');
         xlabel('\fontsize{12}Time [days]'),...
         ylabel('\fontsize{12}  v(t)'),...
         title(sprintf('Control for the tracking of z iteration: %.0f',iter))

### 2019-11-19 tex/Tracking.tex
title change
modified intro

@@
 
-\title{A Model of Microbial Interactions in a Chemostat Setting : Analysis and Application}
+\title{A general model of microbial interactions in a chemostat.}
 
@@
 Using their terminology this articles deals with population-based approaches where species are taken as the interacting units.
-Particularly the model here studied could be classified as a stoichiometric model of multiple species and at the same time as a generalized Lotka Volterra Model \cite{Hernandez-Bermejo1997}.
 
@@
 In the past years considerable efforts have been made to measure the bacterial community composition.
-Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA, RNA, proteins and metabolites have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.
-
-The objective of this article is to show a method to predict the reactor performance based on any technique that can track the species relative abundances through time.
-This work revisits the model proposed by Dumont et al \cite{Dumont2016} in which a model with intra and inter species interactions were they claimed coexistence of two species consuming the same substrate: The rigorous mathematical and numerical analysis of this work states the contrary.
-However, using a different set of parameters than the ones proposed on their article, the model proposed becomes very rich in steady states, and different coexistences may emerge depending on operational parameters of the working chemostat.
-Their approach suffers from a quadratic growing number of parameters on the number of species considered, thus its scope of applicability for diverse ecosystems seems limited.
-
-In the present paper this difficulty is overcame by generalizing their interactions approach and using method of optimal tracking for parameter identification, where the growth rate of each species is modulated by a constrained regular control of the system.
-The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the abundances of each species.
-The main novelty of the article lies in proposing/testing/using microbial interactions as the driver of the reactor's performance  through an optimal control approach.
-
-The article is divided in a first section that re-examines the properties of the work of Dumont \textit{et al.} \cite{Dumont2016}, and a second section that generalizes their approach.
+Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA, RNA, proteins, and metabolites have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.
+
+The main contribution of this article is a procedure to integrate the microbial community measurements in chemostat models, based on any technique that can quantify the species abundances through time.
+This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.
+
+As a departing point the work of Dumont et al.\cite{Dumont2016} is reinspected in section 2.
+They model a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression.
+Section 3 deals with the mathematical analysis of their model.
+It is shown that the number of possible equilibrium points grows exponentially with the number of species.
+Finally after a numerical analysis it is conjectured that there always exists a single stable equilibrium point depending on the operational parameters.
+
+Section 4 is the article's most original contribution.
+The concept of interaction function is developed such that it generalizes the gLV model.
+For the identification of the interaction function a method of optimal tracking was adapted: The growth rate of each species is modulated by a constrained regular control of the system.
+The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species.
+
+In section 5 the methodology from section 4 is applied to the data from the experiments perform by Dumont et al \cite{Dumont2009}.
+Finally, a discussion on the scope of the method, its shortcomings and perspectives is presented.
 

### 2019-11-19 tex/Tracking.tex
jerome corrections

@@
 
-\begin{defn} Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$:
+\begin{defn} Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
 	\begin{align}
@@
 For checking local asymptotic stability of the equilibria points, the Jacobian of the system is provided and evaluated at each of these points.
-The resulting matrix's eigenvalues must satisfy that their real parts are less than zero.
+The resulting matrix's eigenvalues must have negative real part.
 A general formula for this Jacobian is presented in the appendix.
@@
 Operating diagrams are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters.
-Operating diagrams are created by running algorithm \eqref{StabilityAnalysis} for different pairs $(s_{in},D)$ .
-One then regroups all the pairs such that the set of non-active coordinates of the points of the set $PSP$ are the same.
+Operating diagrams are created by running algorithm \eqref{StabilityAnalysis} for different pairs $(s_{in},D)$ \cite{lobry2017chemostat}.
+One then regroups all the pairs such that the set of non-active coordinates of the points of the set $PSP$ are the same and have the same stability properties.
 This regrouping represents graphically the coexistence of the different OTU in a $D-s_{in}$ plot.
-In particular for the biological process of nitrification, this implies when partial nitrification (PN) or complete nitrification (CN) may arise.
+In particular for the biological process of nitrification, this allows to represent when partial nitrification (PN) or complete nitrification (CN) may arise \cite{KHIN2004519}.
 PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ concentration is very low and thus almost no conversion from $s_2$  to $s_3$ takes place.
@@
 
-The operating diagram from the parameter identification from Dumont et al.
-is presented in figure \ref{OD Dumont}.
+The operating diagram from one of the sets of the parameter identification from Dumont et al.
+is presented in figure \ref{OD Dumont} from a Bayesian estimation method.
 Two species per functional group were considered.
-One can see that coexistence in the same functional group is not attained.
+One can see that coexistence in the same functional group is never attained.
 However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
@@
 
-The model isalso  able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+The model is also  able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
 The CEP roughly states that if two species are growing on the same limiting resource, and their growth law is monotonic in the substrate, then only one of them will survive in the long run.
@@
 \subsection{Remarks}
-The model here presented serves to illustrate that by considering interactions complete nitrification with a bigger dilution rate can be explained.
-It also shows a mechanism by which the CEP no longer holds.
+
+The model here presented serves to illustrate that by considering a more complex growth rate that accounts for ecological interactions one might explain differences in reactors operating similarly.
+It also shows a new mechanism by which the CEP no longer holds.
 However the quadratic increase of parameters with the number of OTU considered makes it difficult to accurately calibrate the model.
-Simulations always show a single stable equilibrium point, however no proof is offered to such conjecture.
-In the next section, in the spirit of this model, a more systematic treatment is provided to include genetic sequencing in order to predict the outcome of the reactor.
+The operating diagrams always show a single stable equilibrium point for each pair $(s_in,D)$, however no proof is offered to such conjecture.
+In the next section, a generalization of the former model, and a schema for calibrating a class of models is presented as well.
 
@@
 
-More generally the interaction function is defined. It represents how the growth rate of species $i$ is affected by the concentration of other Bacteria, $x$:
+More generally the interaction function is defined. It represents how the growth rate of species $i$ is affected by the concentration of other species, $x$:
 
@@
 \begin{array}{rc}
-\I: \R^n \rightarrow & \R_+^n\\
+\I: \R_+^n \rightarrow & \R_+^n\\
 & \\
@@
 For this model $g(x,s) = x$, since we are observing measurements coming from genetic sequencing.
-Consider the weighted norms defined by positive definite matrices $F,Q$, and $R$, represented by $\Vert \cdot \Vert_F$, $\Vert \cdot \Vert_Q$, and $\Vert \cdot \Vert_R$, respectively.
+Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively.
 The optimal tracking problem is defined as:

### 2019-11-19 tex/Tracking.tex
proof of concept and application section updated

@@
 
-The model here presented serves to illustrate that by considering a more complex growth rate that accounts for ecological interactions one might explain differences in reactors operating similarly.
+The model here presented serves to illustrate that by considering a more complex growth rate that accounts for ecological interactions one might explain differences in reactors operating under similar conditions.
 It also shows a new mechanism by which the CEP no longer holds.
@@
 
+The method consists on iteratively calculating trajectories of system \eqref{Controlsystem} with a certain control and feeding a non-autonomous Ricatti differential equation with the resulting trajectory.
+Then a control law that uses the Ricatti equation is proposed and a new trajectory is calculated.
+The iteration is stopped when a convergence in the output or in the control is observed.
+
 Two points of departure from the original method are made clear, details can be seen in the appendix: first the tracking problem does not consider a constrained control, so one should consider a reformulation as proposed by the same author in other works \cite{Cimen2008}.
 Nevertheless, the methods were directly used, and an explicit constraint in the synthesis of the control was added for the control to remain within the desired bounds.
+
+First the tracking problem does not consider a constrained control, so one should consider a reformulation as proposed by the same author in other works \cite{Cimen2008}.
+Nevertheless, the methods in \cite{Cimen2004} were directly used, and an explicit constraint in the synthesis of the control was added for the control to remain within the desired bounds (see equation \eqref{control synthesis}).
+Even though this is probably suboptimal it worked for our purposes.
+
+Second in their problem they used an approximation of their original dynamics for calculating the trajectories and subsequently proved that such linearisation converged to the original dynamics.
+In the case here presented the linearisation of the dynamics was not necessary.
 Second, when implementing equation (12) of their article \cite{Cimen2008} a linearised dynamic is not used.
 Instead the original dynamic with the control given by equation (9) of their article is used.
-This modification of the original method was performed after experiencing poor numerical integration (ill conditioning) of the proposed linear equation.
-
-The problem with implementing the linearisation fo the dynamic can be partially explained because the dynamic used in this article has the property of remaining in the positive octant, while a linearisation of it may not posses this property, thus hindering the next iteration by -for example- providing a solution with negative substrate or biomass.
-Partially explained, because even when controlling positivity of the output of the differential equation solver, numerical integration problems were also encountered.
+This modification of the original method Second in their problem they used an approximation of their original dynamics for calculating the trajectories and subsequently proved that such linearisation converged to the original dynamics.
+In the case here presented the linearisation of the dynamics was not necessary.
 
@@
 Where matrix $P(t)$ and vector $s_f(t)$ solve differential equations.
-Note that the control becomes a function of the OTU concentration so it represents the interaction function.
-
-For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against noised synthetic data and then against real experimental data.
-The first test consisted in simulating
-\subsection{Numerical results}
-
-In this section the tracking problem was solved in the chemostat setting discussed before with data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}.
-Only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics; for exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept constant as possible.
-
-A method was used in order to classify OTU in either $G_1$ or $G_2$ from data ranging from day $184$ and $245$ which yields as well the $k_i$ of each OTU.
-12 OTU were present in the $G_1$ group and 9 in the $G_2$ functional group.
-The system state dimension becomes 24.
-Then the tracking method was used from day $245$ to day $362$.
-
-The knowledge of function $f_i(s)$ were based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
-Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ while a Haldane function (eq.
-\eqref{Haldane})was used for $G_2$.
-Since flock formation was seen in the chemostat experiment, the $K_s$ constant proposed by \cite{Wiesmann1994} was multiplied by a hundred times, in order to model for less substrate availability inside a flock.
-
-\begin{align}
-\label{monod} f_i(s) &= \bar{\mu}_i \dfrac{s_1}{K_i +s_1} \, \forall i \in G_1 \\
-\label{Haldane} f_i(s) &= \bar{\mu}_i \dfrac{s_2}{K_i +s_2 + \frac{s_2^2}{KI}} \, \forall i \in G_2
-\end{align}
-
-The choice of the matrix $F$, $Q$ and $R$, influence the quality of the fitting, and three cases are presented.
-Before for the reader to gain understanding of the situation a simulation in figure \ref{NoControlSimulation} is shown without control.
-One can see that simulation predicts CN (accumulation of $s_3$), while data is showing PN  (accumulation of $s_2$).
-
-\begin{figure}[ht]
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{OTU_no_control}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{metabolites_no_control}
-	\end{subfigure}
-	\caption{Simulation with no control. Warm colors for OTU belonging to $G_1$. Cold colors for OTU belonging to $G_2$. Dotted line represents data.}
+In the appendix one may prove that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method.
+Which renders the method- at least theoretically- scalable.
+
+Finally for the parametric identification of a particular class of interaction functions the following static optimization problem is proposed.
+Suppose $u(t)$ is the optimal control of problem \eqref{Optimal Control}, and $x(t)$ is the associated trajectory.
+Suppose a set of parameters $\theta \in \Theta$, such that the interaction function has a explicit form that depends on this parameters $I_{\theta}(x)$ ($\theta$ would represent matrix $A$ from section 2 for example).
+Then one solves the following optimization problem:
+\begin{align}
+\label{Parameter Identification} \min & \quad \Vert I_{\theta}(x(\cdot)) - u(\cdot) \Vert_{L^2([0,T])} \\
+s.t. &  \quad \theta \in \Theta \notag \\
+& \quad t \in [0,T] \notag
+\end{align}
+
+In practice $t \in [0,T]$ from \eqref{Parameter Identification} is replaced by considering the time steps given by the differential equation solver.
+\subsection{Proof of concept}
+
+For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against synthetic data.
+The first test consisted in simulating system \eqref{Controlsystem} with $I(x) = 1 + Ax$, for $n_1 = 10$ and $n_2 = 5$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_Biomass_Iter_300}
+	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_AOB_Iter_300}
+	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_NOB_Iter_300}
+	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_metabolites_Iter_300}
+	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_Control_AOB_Iter_300}
+	\caption{Control for the AOB population.}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_Control_NOB_Iter_300}
+	\caption{Control for the NOB population.}
+\end{figure}
+
+Finally in the parametric identification one can compare the original matrix, with the identified one.
+
+The procedure is repeated but with noise on the simulated trajectory.
+
+Again the method follows the tendencies from data.
+
+And the reconstructed matrix
+
+\clearpage
+\section{Application}
+
+The choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
+$Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear.
+In the simulations here presented $Q = I_n$ and $R = 0.0001I_n$, found by trial and error in order for the control to fit accurately the species abundance.
+The method stopped after 110 iterations where each iteration took approximately 600 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.
+
+The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}.
+For exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept as constant as possible.
+Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics.
+For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $230$: 17 OTU were identified in the $G_1$ group (known as Ammonium oxidizing bacteria AOB) and 8 in the $G_2$ functional group (known as Nitrite oxidizing bacteria NOB).
+The system state dimension becomes 28.
+
+The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
+Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$.
+\begin{align}
+\label{monod} f_i(s) &= \bar{\mu}_2 \dfrac{s_1}{K_1 +s_1} \, \forall i \in G_1 \\
+\notag  f_i(s) &= \bar{\mu}_2 \dfrac{s_2}{K_2 +s_2 } \, \forall i \in G_2
+\end{align}
+
+For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e.
+$v(t)= 0$) in  Figure \ref{NoControlSimulation}.
+$s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{Prediction_No_Control_metabolites}
+	\caption{Simulation when $u=1$. }
 	\label{NoControlSimulation}
 \end{figure}
-\clearpage
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_1}
-	\end{subfigure}
-	~	
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_25}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_25}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_OTU_Iter_45}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_metabolites_Iter_45}
-	\end{subfigure}
-	\caption{Case 1 Metabolites and OTU concentration,  $R = 0.01 I_n$.
-Let $Q = I_n$, and $F = 10Q$.
-Left OTU fitting, right Metabolites.
-Continuous lines are the fit.
-Dotted lines represent data.
-Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
-	\label{Case 1 Metabolites OTU}
+
+When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}.
+The method captures the tendencies in the measured substrates, but not their absolute values.
+The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively.
+Note that the fit of $G_1$ seems better than the fit of $G_2$, which can be explained by the 1 order of magnitude difference of abundance between the members of the group.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{260919_Try1_metabolites_Iter_110}
+	\caption{Simulation applying the control strategy.}
+	\label{ControlSimulation}
 \end{figure}
 
-\clearpage
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_25}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-	\includegraphics[width=\textwidth]{Case_1//Prediction_Constrained_Control_2_Control_Iter_45}
-	\end{subfigure}
-	\caption{Case 1: Control for tracking. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
-	\label{Case 1 Control}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{260919_Try1_AOB_Iter_110}
+	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
+	\label{AOBSimulation}
 \end{figure}
-In this case from figure \ref{Case 1 Metabolites OTU} one can see that $s_1$ accumulation is predicted and not $s_2$ which was the most abundant metabolite.
-By choosing the identity matrix as the weight matrix of the tracking part it privileges the most abundant species (OTU 11), and thus the behaviour is predicted based only on OTU 11.
-From figure \ref{Case 1 Control} it can be seen that the control for OTU in $G_2$ tends to $1$, while the control for OTU in $G_1$ (with exception of OTU 11) remain almost zero until day $320$.
-The method seems to converge: note that the control for iterations $25$ and $45$ vary slightly from one another.
-
-\clearpage
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_1}
-	\end{subfigure}
-	~	
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_15}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_15}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_OTU_Iter_25}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_metabolites_Iter_25}
-	\end{subfigure}
-	\caption{Case 2: $R = 0.001 I_n$.
-Let $\bar{k} =  \max \{k_i| i\in [n] \}$, $Q = \diag(k) /\bar{k}$, and $F = 10Q$.
-Left OTU fitting, right Metabolites.
-Continuous lines are the fit.
-Dotted lines represent data.
-Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
-	\label{Case 2 Metabolites OTU}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{260919_Try1_NOB_Iter_110}
+	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
+	\label{NOB Simulation}
+\end{figure}
+
+One can observe that in figure \ref{ControlSimulation} the predicted $s_3$ around day 240 is much higher than the measurement.
+If one looks at figure \ref{NOB Simulation} it suggests attributing this extra production of $s_3$ around day 240 to the growth of OTU 24.
+What would have happened if OTU 24 had been classified in the other functional group?
+One would have seen a decrease in $s_1$, an increase in $s_2$, and a decrease in $s_3$ which could have better fitted the measurements.
+Thus suggesting that OTU 24 was misclassified from the method presented in \cite{Ugalde-Salas2019}.
+
+In figures \ref{AOB_control} and \ref{NOB_control} it can be seen the obtained controls for each functional group.
+Both controls saturate at certain points, but in general terms they vary throughout the dynamic.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{260919_Try1_Control_AOB_Iter_110}
+	\caption{Control obtained for OTU in $G_1$ (AOB).}
+	\label{AOB_control}
+	\includegraphics[width= 0.4\textwidth]{260919_Try1_Control_NOB_Iter_110}
+	\caption{Control obtained for OTU in $G_2$ (NOB).}
+	\label{NOB_control}
+\end{figure}
+
+Recalling that $u(t)$ is supposed to represent $I(x(t))$ (the interactions terms), one could try to fit different forms of $I(\cdot)$ for example $I(x) = 1 + Ax$, where  $A$ is a real valued square matrix.
+In figure \ref{LV_fit} the simulation of the system after the identification of matrix A is presented, suggesting that an affine interaction function is not able to capture the behaviour of the system.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{260919_Try1_metabolites_Iter_110_LV}
+	\caption{Simulation obtained for the interaction function $I(x) = 1 + Ax$, where $A$ was fitted with the obtained controls from figures \ref{AOB_control} and \ref{NOB_control}.}
+	\label{LV_fit}
 \end{figure}
 \clearpage
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_15}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_2//Prediction_Constrained_Control_6_Control_Iter_25}
-	\end{subfigure}
-	\caption{Case 2 Control for tracking.Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
-	\label{Case 2 Control}
-\end{figure}
-
-In this case from figure \ref{Case 2 Metabolites OTU} one can see that $s_2$ accumulation is predicted which was the most abundant metabolite.
-It was also able to detect an $s_1$ peak at day $340$.
-The rationale for choosing the yields as the diagonal of the weight matrix of the tracking part is that a higher yielding organism will cause a more pronounced difference in the metabolites of the system, thus more weight is given to correctly tracking those OTU.
-From figure \ref{Case 2 Control} it can be seen that the control for OTU in $G_2$ remains zero until day 300, while the control for OTU in $G_1$ vary differently throughout the trajectory.
-
-\clearpage
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_5}
-	\end{subfigure}
-	~
-		\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_15}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_15}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_OTU_Iter_25}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_metabolites_Iter_25}
-	\end{subfigure}
-\caption{Case 3: $R = 0.0001 I_n$.
-Let $\bar{k} =  \max \{k_i| i\in [n] \}$, $Q = \diag(k) /\bar{k}$, and $F = 10Q$.
-Left OTU fitting, right Metabolites.
-Continuous lines are the fit.
-Dotted lines represent data.
-Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
-\label{Case 3 Metabolites OTU}
-\end{figure}
-\clearpage
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_1}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_5}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-		\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_15}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.32\textheight}
-	\includegraphics[width=\textwidth]{Case_3//Prediction_Constrained_Control_7_Control_Iter_25}
-	\end{subfigure}
-	\caption{Case 3: Control for tracking. Warm colors for OTU in $G_1$, cold colors for OTU in $G_2$.}
-	\label{Case 3 Control}
-\end{figure}
-
-In this case from figure \ref{Case 3 Metabolites OTU} one can see that $s_2$ accumulation is predicted which was the most abundant metabolite.
-It was also able to detect an $s_1$ peak at day $340$ and an $s_3$ peak at the beginning of the trajectory.
-The same rationale as case two was used for picking the weight matrix of the tracking part.
-From figure \ref{Case 3 Control} it can be seen that the control for OTU in $G_2$ remains zero until day 300 (except for OTU 20, responsible for the $s_3$ peak), while the control for OTU in $G_1$ vary differently throughout the trajectory.
-The only difference from case two is that the weight matrix for the control part was divided by 10, thus allowing a better fit of the OTU at the expense of more steep variations in the control.
-
-\clearpage
-In two out of three cases it can be seen that the accumulation of $s_2$ instead of $s_3$ (i.e.
-PN) was predicted.
-The cases were accumulation of $s_2$ was predicted are explained by a weight matrix  that used the yields of each OTU.
-It also seems that the control (and therefore the solution) converge, however since departures from the original method were used, one can not ensure they converge to the optimal value.
-But given that the fit of the OTU follows the trend of data, and one is able to predict $s_2$ accumulation, the results seems satisfactory from a numerical standpoint.
-All cases matrix $F$ (the final point weight) was taken as 10 times $Q$, otherwise the control always ended up in $0$ ($v(t_f) = 0$).
-
 \section{Conclusion}
@@
 Nevertheless a method for previous identification of the microbial community must be used beforehand.
-
-\clearpage
+All the codes can be downloaded from Github.
+
+\section{Acknowledgements}
+ Alain Rapaport, CMM, Thermomic
+
 \section{Appendix}

### 2019-11-20 Stability Analysis gLV/d_monod.m
stability analysis files

@@ -1,0 +1,3 @@
+function y=d_monod(s,muMax,kS)
+y =  muMax.*kS./(s+kS).^2;
+end

### 2019-11-20 Stability Analysis gLV/dynamic.m

@@ -1,0 +1,8 @@
+function y = dynamic(A,nA,nB,kA,kB,muA,muB,kSA,kSB,D,S_in)
+n = nA+nB;
+dynamicX =  @(t,z) diag(z(1:n))*(diag([growth_monod(z(n+1),muA,kSA); growth_monod(z(n+2),muB,kSB)])*(ones(n,1)+A*z(1:n)) - ones(n,1)*D(t));
+dynamicS1 =  @(t,z) (S_in(t) - z(n+1))*D(t) +(diag(-kA)*(ones(nA,1) + A(1:nA,:)*z(1:n)))'*diag(growth_monod(z(n+1),muA,kSA))*z(1:nA);
+dynamicS2 =  @(t,z) -z(n+2)*D(t) + (diag([kA; -kB])*(ones(n,1)+A*z(1:n)))'*diag([growth_monod(z(n+1),muA,kSA); growth_monod(z(n+2),muB,kSB)])*z(1:n);
+dynamicS3 =  @(t,z) -z(n+3)*D(t) +(diag(kB)*(ones(nB,1) + A((nA+1):n,:)*z(1:n)))'*diag(growth_monod(z(n+2),muB,kSB))*z((nA+1):n);
+y  = @(t,z)  [dynamicX(t,z) ; dynamicS1(t,z); dynamicS2(t,z); dynamicS3(t,z)];
+end

### 2019-11-20 Stability Analysis gLV/dynamic_jacobian.m

@@ -1,0 +1,30 @@
+function J = dynamic_jacobian(z,A,nA,nB,kA,kB,muA,muB,kSA,kSB,D)
+n = nA+nB;
+J = zeros(n+3,n+3);
+A1 = A(1:nA,:);
+A2 = A(nA+1:n,:);
+growthA = growth_monod(z(n+1),muA,kSA);
+growthB = growth_monod(z(n+2),muB,kSB);
+d_growthA = d_monod(z(n+1),muA,kSA);
+d_growthB = d_monod(z(n+2),muB,kSB);
+%growth(s,muMax,kS)
+%dGrowth(s,muMax,kS)
+J(1:n, 1:n) = diag([growthA; growthB].*(ones(n,1) +A*z(1:n))-D*ones(n,1))+diag([growthA; growthB].*z(1:n))*A;
+J(1:n,n+1) = z(1:n).*[d_growthA ; zeros(nB,1)].*(ones(n,1) + A*z(1:n));
+J(1:n,n+2) = z(1:n).*[zeros(nA,1) ; d_growthB].*(ones(n,1) + A*z(1:n));
+J(1:n,n+3) = zeros(n,1);
+J(n+1,1:n) = -([ones(nA,1) + A1*z(1:n) ; zeros(nB,1)]'*diag([kA; kB].*[growthA; growthB]))...
+    + (diag([kA; kB].*[growthA; growthB])*z(1:n))'*[A1; zeros(nB,n)]  ;
+J(n+1,n+1) = -D - [ones(nA,1) + A1*z(1:n) ; zeros(nB,1)]'*([kA; kB].*[d_growthA; zeros(nB,1)].*z(1:n));
+J(n+1,n+2:n+3) = zeros(1,2);
+J(n+2,1:n) = [(ones(nA,1) + A1*z(1:n)) ;-(ones(nB,1) +A2*z(1:n))]'*diag([kA;kB].*[growthA; growthB])...
+    + (diag([kA;kB].*[growthA; growthB])*z(1:n))'*[A1; -A2];
+J(n+2,n+1) = [(ones(nA,1) + A1*z(1:n)) ;-(ones(nB,1) +A2*z(1:n))]'*([kA; kB].*[d_growthA; zeros(nB,1)].*z(1:n));
[…]

### 2019-11-20 Stability Analysis gLV/equilibria.m

@@ -1,0 +1,64 @@
+function [possible_x, possible_s1, possible_s2, possible_s3] = equilibria(A,...
+    nA,nB,kA,kB,muA,muB,kSA,kSB,D,s_in)
+n = nA+nB;
+possible_x = zeros(n, (2^nA-1)*(4*(2^nB-1)+2)+1);
+possible_s1 = zeros(1,(2^nA-1)*(4*(2^nB-1)+2)+1);
+possible_s2 = zeros(1,(2^nA-1)*(4*(2^nB-1)+2)+1);
+possible_s3 = zeros(1,(2^nA-1)*(4*(2^nB-1)+2)+1);
+counter = 1;
+k = [kA;kB];
+vec_aux1 = (D-[muA; muB])./[muA; muB];
+vec_aux2 = D*[kSA ; kSB]./[muA; muB];
+for i = 1:2^nA-1
+    for j = 1:2^nB-1
+        considered_species = find([de2bi(i,nA) de2bi(j,nB)]);
+        A_act = A(considered_species, considered_species);
+        B = diag(k(considered_species))/A_act;
+        AOB_species = find(considered_species <= nA);
+        NOB_species = find(considered_species > nA);
+        beta1 = -sum(B(AOB_species,:)*vec_aux1(considered_species));
+        beta2 = -sum(B(AOB_species,AOB_species)*vec_aux2(considered_species(AOB_species)));
+        beta3 = sum(B(AOB_species,NOB_species)*vec_aux2(considered_species(NOB_species)));
+        beta4 = -sum(B(NOB_species,AOB_species)*vec_aux2(considered_species(AOB_species)));
+        beta5 = -sum(B(NOB_species,:)*vec_aux1(considered_species));
+        beta6 = -sum(B(NOB_species,NOB_species)*vec_aux2(considered_species(NOB_species)));
+        c1 = -1/beta3;
+        c2 = (s_in+beta1)/beta3;
+        c3 = beta2/beta3;
+        a4 = (beta3+beta6)*c1^2;
+        a3 = (beta3+beta6)*2*c1*c2+(beta5-beta1)*c1;
+        a2 = (beta4-beta2)*c1+(beta3+beta6)*(c2^2+2*c1*c3)+(beta5-beta1)*c2-1;
+        a1 = (beta4-beta2)*c2+(beta3+beta6)*2*c2*c3+(beta5-beta1)*c3;
[…]

### 2019-11-20 Stability Analysis gLV/growth_monod.m

@@ -1,0 +1,3 @@
+function y = growth_monod(s,mu_max,kS)
+y =  mu_max.*s./(s + kS);
+end

### 2019-11-20 Stability Analysis gLV/inv_growth_monod.m

@@ -1,0 +1,3 @@
+function y = inv_growth_monod(s,mu_max,kS)
+y = 1./mu_max.*(1+kS./s);
+end

### 2019-11-20 Stability Analysis gLV/parametres_modified.m

@@ -1,0 +1,17 @@
+clear
+nA = 2;
+nB = 2;
+n = nA + nB;
+A =[   -0.0664    0.6279   -1.8849   -0.3030;
+    1.3460   -1.5750   -1.1231   -0.1666;
+    3.5464    0.3289   -0.2537    0.0796;
+    2.8857   -0.1071    0.6042   -0.4122];
+muA= [0.828 0.75*0.828]';
+muB= [0.18 0.75*0.18]';
+kSA = 10^(-3)*[0.147 0.0147]';
+kSB = 10^(-3)*[0.026 0.0026]';
+ %D = 1.1875; %0.7/6.5- 
+%D = 2.2/6.5;
+kA = [5; 3];
+kB = [110; 90];
+save('MAT_files\parameters_modified');

### 2019-11-20 Stability Analysis gLV/test_equilibria.m

@@ -1,0 +1,38 @@
+clear
+close all
+% generateParameters;
+file_name_in = 'parameters_modified';
+load(sprintf('MAT_files\\%s',file_name_in));
+z0 = random('Uniform',0,1,n+3,1);
+OTU = 1:n;
+options = odeset('NonNegative',1:(nA+nB+3));
+dilution = 0.1993;
+D = @(t) dilution;
+s_in = 1.035;
+sIn = @(t) s_in;
+tF = 2000;
+fun =  dynamic(A,nA,nB,kA,kB,muA,muB,kSA,kSB,D,sIn);
+[T,Y] = ode15s(fun,[0 tF], z0,options);
+end_point_string = sprintf('%1.4f ', Y(end,:)');
+eval_end_point =  fun(tF,Y(end,:)');
+eval_end_point_string = sprintf('%1.4f ', eval_end_point);
+fprintf('Trajectory at T= %d \n Point =%s \n Evaluated in dynamic = %s',...
+    tF, end_point_string,eval_end_point_string);
+[possible_x, possible_s1, possible_s2, possible_s3]  = equilibria(A,...
+    nA,nB,kA,kB,muA,muB,kSA,kSB,dilution,s_in);
+possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
+num_equilibria = 0;
+
+for i=1:length(possible_equilibria(1,:))
+if all(possible_equilibria(:,i) >=0) && isreal(possible_equilibria(:,i))
+    num_equilibria = num_equilibria +1;
+    fprintf('\n Positive Equilibrium %d =', num_equilibria);
+    disp(possible_equilibria(:,i)')
+    J = dynamic_jacobian(possible_equilibria(:,i),A,nA,nB,kA,kB,muA,muB,kSA,kSB,dilution);
+     eigenvalues = eig(J);
+     if all(real(eig(J)) <0)
+         fprintf('Equilibrium %d: Stable Equilibrium! \n Eigenvalues of the Jacobian in the Equilibrium : \n', num_equilibria);
+         disp(eigenvalues)
+     end
+end
+end

### 2019-11-20 Stability Analysis gLV/operating_diagram.m
operating diagram working

@@ -1,0 +1,44 @@
+close all
+clear
+file_name_in = 'Parameters_modified';
+load(sprintf('MAT_files\\%s',file_name_in));
+file_name_out = 'Parameters_modified';
+number_of_points = 200;
+d_initial = 0.7/6.5;
+d_final = 2.2/6.5;
+s_in_initial = 0.5;
+s_in_final = 2;
+s_in_vector = linspace(s_in_initial,s_in_final,number_of_points);
+D_vector =  linspace(d_initial,d_final,number_of_points);
+n1 = length(s_in_vector);
+n2 = length(D_vector);
+%parametersLVarticle;
+%Structure to save points.
+map_zones = containers.Map;
+zones = zeros(n1,n2);
+tic
+for i = 1:n1
+    for j = 1:n2
+        [possible_x, possible_s1, possible_s2, possible_s3] = equilibria(A,...
+            nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j),s_in_vector(i));
+        possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
+        for k=1:length(possible_equilibria(1,:))
+            if all(possible_equilibria(:,k) >=0) && isreal(possible_equilibria(:,k))
+                J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j));
+                if all(real(eig(J)) <0)
+                    positive_equilibria = (possible_x(:,k)>0)';
+                    keyString = num2str(positive_equilibria);
+                    if  isKey(map_zones,keyString)
+                        zones(i,j) = map_zones(keyString);
+                    else
+                        count = length(map_zones);
+                        map_zones(keyString) = count + 1;
+                        zones(i,j) = map_zones(keyString);
+                    end
+                end
+            end
+        end
+    end
+end
+toc
+save(sprintf('MAT_files\\Operating_Diagram_%s',file_name_out))

### 2019-11-20 Tracking/main.m
erase useless line

@@ -136,7 +136,6 @@ while diff > csTolerance
         d_interp(t))*X + Bx(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI)...
         *tracking_control(lambda,B(t),P(t),X,sf_interp(t),n);
     tic
-    options = odeset('NonNegative',(1:n+3)');
     [t_new,x_new] = ode15s(dynamic,[t0 tF], x0,options);
     toc
     xOldCell = arrayfun(x_fun,t_new,'UniformOutput',false);

### 2019-11-25 Tracking/main.m
added 20% margin to muRef

@@ -3,8 +3,8 @@
 %main: process and filter data to model.
 close all
 clear
-load('MAT_files\synthetic_data_noise')
-name_file = '191119_Try1';
+load('MAT_files\synthetic_data_no_noise')
+name_file = '241119_no_noise';
 nA = round(sum(a));
 nB = round(sum(b)); 
 n = nA+nB;
@@ -22,8 +22,8 @@ biomass_filtered(biomass_filtered == 0) = min_biomass;
 z = @(t) interp1(t_OTU,biomass_filtered,t)';
 kA = yields_AOB(index_AOB);
 kB = yields_NOB(index_NOB);
-muARef = 0.77;
-muBRef = 1.07;
+muARef = 0.77*1.2;
+muBRef = 1.07*1.2;
 kSARef = 0.7e-1;
 kSBRef = 1.4982e-1;
 kIRef = 1.217;
@@ -80,44 +80,44 @@ toc
 x_cell = arrayfun(x_fun,t_new,'UniformOutput',false);
 X = reshape(cell2mat(x_cell),length(t_new),n+3);
 x_old = X;
-csTolerance = 0.001; %cauchy sequence tolerance
+csTolerance = 0.01; %cauchy sequence tolerance
 iter = 1;
 diff = norm(x_old - x_new);
 save(sprintf('MAT_files\\%s_iter_%.0f',name_file,iter))
 while diff > csTolerance
     x_fun = @(t) interp1(t_new,x_new,t)';    
-    control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
-    control_eval = arrayfun(control,t_new,'UniformOutput',false);
-    figure
-    hold on
-    OTU_plot = plot(t_new,x_new(:,1:n),'LineWidth',1.5);
-    metabolite_plot = plot(t_new,x_new(:,(n+1):end),'-.','LineWidth',1.5);
-    xlabel('\fontsize{12}Time [days]'),...
-        ylabel('\fontsize{12}  Concentration'),...
-        title(sprintf('Tracking results iteration:%.0f',iter));
-    set(gca,'fontsize',15),
-    set(OTU_plot,{'Color'}, colors)
-    set(metabolite_plot,{'Color'},colors2);
-    legend(legend_tags,'fontsize',7);
-    fig.PaperUnits = 'inches';
-    fig.PaperPosition = [0 0 9 3];
-    fig.PaperPositionMode = 'auto';
[…]

### 2019-11-25 tex/Tracking.tex
modification to proof of concept

@@
 
-\title{A general model of microbial interactions in a chemostat.}
+\title{A general model of microbial interactions in a chemostat}
 
@@
 \begin{abstract}
-	A model of microbial interactions applied to a nitrifying process in a chemostat setting is revisited.
-To overcome the shortcomings of this earlier model an optimal tracking method is developed to include the genetic measurements for the prediction of a bioreactor.
-The resulting model is a high order (24 variables) differential equations system with a good prediction of measured metabolites.
-Numerical simulations of the model are presented and discussed.
+	This article deals with the inclusion of microbial ecology in bioprocess modelling.
+The first part exposes the mathematical analysis of a model that included pairwise linear interactions fitted to experimental data in a chemostat setting.
+The limitations and the insights of such an approach are discussed.
+The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented.
+The method revisits the data used for the first model presented and proposes a way to calibrate and discriminate .
 \end{abstract}
@@
 However the quadratic increase of parameters with the number of OTU considered makes it difficult to accurately calibrate the model.
-The operating diagrams always show a single stable equilibrium point for each pair $(s_in,D)$, however no proof is offered to such conjecture.
+The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
 In the next section, a generalization of the former model, and a schema for calibrating a class of models is presented as well.
@@
 Nevertheless, the methods were directly used, and an explicit constraint in the synthesis of the control was added for the control to remain within the desired bounds.
-
-First the tracking problem does not consider a constrained control, so one should consider a reformulation as proposed by the same author in other works \cite{Cimen2008}.
-Nevertheless, the methods in \cite{Cimen2004} were directly used, and an explicit constraint in the synthesis of the control was added for the control to remain within the desired bounds (see equation \eqref{control synthesis}).
-Even though this is probably suboptimal it worked for our purposes.
+Even though this is probably suboptimal it worked in a first implementation.
 
 Second in their problem they used an approximation of their original dynamics for calculating the trajectories and subsequently proved that such linearisation converged to the original dynamics.
-In the case here presented the linearisation of the dynamics was not necessary.
-Second, when implementing equation (12) of their article \cite{Cimen2008} a linearised dynamic is not used.
-Instead the original dynamic with the control given by equation (9) of their article is used.
-This modification of the original method Second in their problem they used an approximation of their original dynamics for calculating the trajectories and subsequently proved that such linearisation converged to the original dynamics.
 In the case here presented the linearisation of the dynamics was not necessary.
@@
 In the appendix one may prove that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method.
-Which renders the method- at least theoretically- scalable.
+Which renders the method- at least theoretically- scalable for a growing number of OTU.
 
@@
 For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against synthetic data.
-The first test consisted in simulating system \eqref{Controlsystem} with $I(x) = 1 + Ax$, for $n_1 = 10$ and $n_2 = 5$.
+The test consisted in simulating system \eqref{Controlsystem} with $I(x) = 1 + Ax$, for $n_1 = 10$ and $n_2 = 5$.
+In all figures, dotted lines represent the synthetic data, while the continuous lines represent the method's output.
+
+The choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
+$Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear.
+In the simulations here presented $Q = I_n$ and $R = \begin{bmatrix}
+10^{-4}I_{n_1} & 0 \\ 0 & 10^{-5}I_{n_2}
+\end{bmatrix}$, found by trial and error in order for the control to fit accurately the species abundance.
+The rational behind choosing a smaller value for the group $G_2$ is related to the one order of magnitude difference in yields between $G_1$ and $G_2$.
+
+Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively.
+It can be seen that the method approaches well the trajectories.
+The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated data as well.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_Biomass_Iter_300}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_Biomass_Iter_5}
 	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{Total Biomass no noise}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_AOB_Iter_300}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_AOB_Iter_5}
 	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{AOB no noise}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_NOB_Iter_300}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_NOB_Iter_5}
 	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{NOB no noise}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_metabolites_Iter_300}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_metabolites_Iter_5}
 	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-\end{figure}
+	\label{Metabolites no noise}
+\end{figure}
+\clearpage
+
+The resulting controls correcting the growth rate can be seen in figure \eqref{Control AOB no noise} and \eqref{Control NOB no noise}.
+Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.
+Problem \eqref{Parameter Identification} is then solved from the obtained trajectories (figures \eqref{AOB no noise} and \eqref{NOB no noise} and controls.
+The difference between the control and the fit is expressed in Figure \ref{Difference fit}.
+Not  Considering that the control is contained in $[0,1]$, the error is below 5 \% throughout the trajectory.
+
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_Control_AOB_Iter_300}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_Control_AOB_Iter_5}
 	\caption{Control for the AOB population.}
+	\label{Control AOB no noise}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//061119_Try1_Control_NOB_Iter_300}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_Control_NOB_Iter_5}
 	\caption{Control for the NOB population.}
-\end{figure}
-
-Finally in the parametric identification one can compare the original matrix, with the identified one.
-
-The procedure is repeated but with noise on the simulated trajectory.
-
-Again the method follows the tendencies from data.
-
-And the reconstructed matrix
+	\label{Control NOB no noise}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_difference_fit_5_LV}
+	\caption{Difference between $u(t)$ and the $1+Ax(t)$, with $A$ shown in the right hand side of Figure \ref{Comparison Interaction Matrices}}
+	\label{Difference fit}
+\end{figure}
+
+\begin{figure}[h]
+	\centering	
+\begin{subfigure}[b]{0.45\textwidth}
+	\includegraphics[width=\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+	\includegraphics[width=\textwidth]{Synthetic_data_no_noise//Interactions_221119_no_noise_iter_5}
+\end{subfigure}
+\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}}
+\label{Comparison Interaction Matrices}
+\end{figure}
+
+Finally
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_AOB_Iter_5_LV}
+	\caption{AOB trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_NOB_Iter_5_LV}
+	\caption{NOB trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_metabolites_Iter_5_LV}
+	\caption{Metabolites trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+\end{figure}
 
@@
 
-This article dealt with the problem of how to include genetic data in the prediction of performance of bioreactors, a previous model which deals with such an issue was revisited.
-The former model suffers from poor scalability, and therefore its application is limited.
-Inspired by their model a novel approach was here developed in order to systematically integrate the available genetic data.
-The approach is fairly straightforward for chemostat systems because it consists in multiplying a control to the growth expression of each OTU to be tracked.
-Nevertheless a method for previous identification of the microbial community must be used beforehand.
-All the codes can be downloaded from Github.
+Last decades advances in genetic sequencing and microbial ecology has opened a gap for modellers in biochemical reactors to integrate this valuable information.
+Considering the success of mass balance models to predict and pilot bioreactors, one should build upon these existing models.
+This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, and observing what would that imply in the chemical species involved.
+If one already posses a model for describing a particular bioprocess the use of the techniques here presented can be applied in a straightforward manner if one has already identified the microbial species involved with a particular functionality.
+
+The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat.
+The question remains open to other classes of interaction functions that could prove capable of prediction.
+
+In the experiments used, the environmental factors were controlled, thus the term is interpreted as microbial interaction.
+However in other contexts the correction term might also be interpreted as a non accounted phenomena ranging from virus to environmental factors (e.g.
+temperature variations) and not only from microbial interactions.
 

### 2019-11-25 Tracking/identify_interactions.m
identify and simulate interactions files

@@ -1,0 +1,21 @@
+%Calculating Interactions
+clear
+close all
+file_in = '221119_no_noise_iter_5';
+load(sprintf('MAT_files/%s',file_in));
+control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
+control_eval = arrayfun(control,t_new,'UniformOutput',false);
+optim_fun = @(interactions) sum(norm(reshape(cell2mat(control_eval),n,...
+    length(t_new)) - reshape(interactions,n,n)*x_new(:,1:n)'));
+options = optimset('MaxFunEvals',2000000,'MaxIter',100000)';
+% ms = MultiStart;
+% problem = createOptimProblem('fminunc','x0',zeros(n^2,1),...
+%     'objective',optim_fun,'options',options);
+% tic
+% [xmin,fmin,flag,outpt,allmins] = run(ms,problem,50);
+% toc
+[xmin, fval] = fminunc(optim_fun,zeros(n^2,1),options);
+A = reshape(xmin,n,n);
+save(sprintf('mat_Files\\%s_iter_%.0f_interactions_ms',name_file,iter));
+
+

### 2019-11-25 Tracking/noise_data.m

@@ -1,0 +1,16 @@
+clear
+close all
+name_file = 'no_noise';
+name_save_file = 'synthetic_data_noise_2';
+load(sprintf('MAT_files\\synthetic_data_%s',name_file))
+mean_Y = mean(Y);
+noise = zeros(size(Y));
+for i=1:length(Y(1,:))
+    noise(:,i) = random('unif',0,mean_Y(i)/2,size(noise(:,i)));
+end
+Y = max(0,Y+noise);
+S1 = Y(:,n+1);
+S2 = Y(:,n+2);
+S3 = Y(:,n+3);
+OTU_interp = Y(:,1:n);
+save(sprintf('MAT_files\\%s',name_save_file));

### 2019-11-25 Tracking/simulate_interactions.m

@@ -1,0 +1,109 @@
+clear 
+close all
+file_in = '221119_no_noise_iter_5_interactions';
+load(sprintf('MAT_files/%s',file_in));%Simulation and plotting
+numbering_AOB = strsplit(num2str(1:nA)) ;
+legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_AOB{:}),...
+    sprintf(',OTU %s (data)', numbering_AOB{:})),',');
+numbering_NOB = strsplit(num2str(nA+1:n)) ;
+legend_tags_NOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_NOB{:}),...
+    sprintf(',OTU %s (data)', numbering_NOB{:})),',');
+colors_AOB = mat2cell(autumn(nA), ones(1,nA), 3);
+colors_NOB = mat2cell(winter(nB), ones(1,nB), 3);
+colors_both = mat2cell([autumn(nA); winter(nB)], ones(1,n), 3);
+numbering_diff = strsplit(num2str(1:n));
+legend_tags_diff = strsplit(sprintf('Difference %s,', numbering_diff{:}),',');
+legend_tags_diff(end) = [];
+%Quality of the Fit
+fit = A*x_new(:,1:n)'+1;
+control_matrix = reshape(cell2mat(control_eval),n,length(t_new))+1;
+diff = abs(control_matrix - fit);
+figure
+diff_plot = plot(t_new,diff,'LineWidth',1.5);
+xlabel('\fontsize{12}Time [days]'),...
+    ylabel('\fontsize{12}  Absolute difference between Ax+1 and u(t)'),...
+    title('Difference of LV and Control');
+%     title(sprintf('Simulation v(t) = -1'));
+set(gca,'fontsize',15),
+set(diff_plot,{'Color'}, colors_both)
+legend(legend_tags_diff,'fontsize',7,'Location','bestoutside');
+fig.PaperUnits = 'inches';
+fig.PaperPosition = [0 0 9 3];
+fig.PaperPositionMode = 'auto';
+print(sprintf('Images\\%s',sprintf('%s_difference_fit_%.0f_LV',...
+    file_in,iter)),'-dpng','-r0')
+%Simulation
+muARef = 0.77;
+muBRef = 1.07;
+kSARef = 0.7e-1;
[…]

### 2019-11-25 Tracking/identify_interactions.m
use of index in calibration

@@ -3,10 +3,12 @@ clear
 close all
 file_in = '221119_no_noise_iter_5';
 load(sprintf('MAT_files/%s',file_in));
+index_control = find(t_new > 20 & t_new < 130);
+t_used = t_new(index_control);
 control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
-control_eval = arrayfun(control,t_new,'UniformOutput',false);
+control_eval = arrayfun(control,t_used,'UniformOutput',false);
 optim_fun = @(interactions) sum(norm(reshape(cell2mat(control_eval),n,...
-    length(t_new)) - reshape(interactions,n,n)*x_new(:,1:n)'));
+    length(index_control)) - reshape(interactions,n,n)*x_new(index_control,1:n)'));
 options = optimset('MaxFunEvals',2000000,'MaxIter',100000)';
 % ms = MultiStart;
 % problem = createOptimProblem('fminunc','x0',zeros(n^2,1),...
@@ -16,6 +18,6 @@ options = optimset('MaxFunEvals',2000000,'MaxIter',100000)';
 % toc
 [xmin, fval] = fminunc(optim_fun,zeros(n^2,1),options);
 A = reshape(xmin,n,n);
-save(sprintf('mat_Files\\%s_iter_%.0f_interactions_ms',name_file,iter));
+save(sprintf('mat_Files\\%s_iter_%.0f_interactions',name_file,iter));
 
 

### 2019-11-25 Tracking/simulate_interactions.m

@@ -15,8 +15,8 @@ numbering_diff = strsplit(num2str(1:n));
 legend_tags_diff = strsplit(sprintf('Difference %s,', numbering_diff{:}),',');
 legend_tags_diff(end) = [];
 %Quality of the Fit
-fit = A*x_new(:,1:n)'+1;
-control_matrix = reshape(cell2mat(control_eval),n,length(t_new))+1;
+fit = A*x_new(index_control,1:n)'+1;
+control_matrix = reshape(cell2mat(control_eval),n,length(index_control))+1;
 diff = abs(control_matrix - fit);
 figure
 diff_plot = plot(t_new,diff,'LineWidth',1.5);

### 2019-11-26 tex/Tracking.tex
added conclusions

@@
 	This article deals with the inclusion of microbial ecology in bioprocess modelling.
-The first part exposes the mathematical analysis of a model that included pairwise linear interactions fitted to experimental data in a chemostat setting.
+The first part exposes the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting.
 The limitations and the insights of such an approach are discussed.
@@
 The concept of interaction function is developed such that it generalizes the gLV model.
-For the identification of the interaction function a method of optimal tracking was adapted: The growth rate of each species is modulated by a constrained regular control of the system.
+For the identification of the interaction function a method of optimal tracking was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected to fit the experimental data.
 The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species.
@@
 \begin{enumerate}
-	\item $n$: the number of $OTU$ considered.
+	\item $n$: the number of OTU considered.
 	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
@@
 The model is also  able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
-The CEP roughly states that if two species are growing on the same limiting resource, and their growth law is monotonic in the substrate, then only one of them will survive in the long run.
-However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors has\cite{Wagner2002}.
+The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
+However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law is required to include microbial diversity.
 
@@
 Where matrix $P(t)$ and vector $s_f(t)$ solve differential equations.
-In the appendix one may prove that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method.
+In the appendix it is proved that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method.
 Which renders the method- at least theoretically- scalable for a growing number of OTU.
@@
 For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against synthetic data.
-The test consisted in simulating system \eqref{Controlsystem} with $I(x) = 1 + Ax$, for $n_1 = 10$ and $n_2 = 5$.
+The test consisted in simulating system \eqref{Controlsystem} with $I(x) = 1 + Ax$, (with $A$ in figure \ref{Comparison Interaction Matrices}) for $n_1 = 10$ and $n_2 = 5$.
 In all figures, dotted lines represent the synthetic data, while the continuous lines represent the method's output.
@@
 
-The resulting controls correcting the growth rate can be seen in figure \eqref{Control AOB no noise} and \eqref{Control NOB no noise}.
+The resulting controls that correct the growth rate can be seen in figures \eqref{Control AOB no noise} and \eqref{Control NOB no noise}.
 Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.
-Problem \eqref{Parameter Identification} is then solved from the obtained trajectories (figures \eqref{AOB no noise} and \eqref{NOB no noise} and controls.
+Problem \eqref{Parameter Identification} was solved from the obtained trajectories (figures \eqref{AOB no noise} and \eqref{NOB no noise}) and controls, with no bounds on the parameters.
 The difference between the control and the fit is expressed in Figure \ref{Difference fit}.
-Not  Considering that the control is contained in $[0,1]$, the error is below 5 \% throughout the trajectory.
+Considering that the control is contained in $[0,1]$, the error of fit is below 5 \% almost everywhere through the trajectory.
 
@@
 \end{figure} 
+\clearpage
+
+The obtained matrix from the fit can be seen an compared to the original matrix for simulating data in \eqref{Comparison Interaction Matrices}.
+It can be seen that the new matrix is very different from the original one, in both order of magnitude and sign.
+Implying that the model is probably not identifiable.
+The system was simulated again with the new matrix, and one can see that it in general terms it captures the outcome of the system as shown in figures \ref{AOB LV simulation}, \ref{NOB LV simulation}, and \ref{Metabolites LV simulation}.
+The final message of this section is that if the interaction function is of the form $1+Ax$, one could be able to get a fit from the data with the method here presented.
 
@@
 \end{subfigure}
-\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}}
+\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}.}
 \label{Comparison Interaction Matrices}
 \end{figure}
-
-Finally
 
@@
 	\caption{AOB trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+	\label{AOB LV simulation}
 \end{figure}
@@
 	\caption{NOB trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+	\label{NOB LV simulation}
 \end{figure}
@@
 	\caption{Metabolites trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+	\label{Metabolites LV simulation}
 \end{figure}
@@
 
-The choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
-$Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear.
-In the simulations here presented $Q = I_n$ and $R = 0.0001I_n$, found by trial and error in order for the control to fit accurately the species abundance.
 The method stopped after 110 iterations where each iteration took approximately 600 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.
@@
 \clearpage
-\section{Conclusion}
+\section{Conclusions and Perspectives}
 
@@
 This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, and observing what would that imply in the chemical species involved.
-If one already posses a model for describing a particular bioprocess the use of the techniques here presented can be applied in a straightforward manner if one has already identified the microbial species involved with a particular functionality.
-
-The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat.
-The question remains open to other classes of interaction functions that could prove capable of prediction.
-
-In the experiments used, the environmental factors were controlled, thus the term is interpreted as microbial interaction.
-However in other contexts the correction term might also be interpreted as a non accounted phenomena ranging from virus to environmental factors (e.g.
-temperature variations) and not only from microbial interactions.
+If one already posses a model for describing a particular bioprocess the use of the techniques here presented can be applied in a straightforward manner if one has already identified the microbial species involved with a particular functionality of the system.
+
+The tracking model was proposed  in a chemostat setting as a way to correct a substrate limited expression.
+However the technique could be used in contexts where less information on the growth function of microbes is known.
+If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model actually becomes a linear model and one recovers a classic quadratic regulator for linear systems.
+Nevertheless the synthesis of the optimal bounded control remains an open theoretical challenge.
+
+The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.
+Furthermore from the proof of concept section, one might conjecture that models with a large number of parameters such as an gLV model may be unidentifiable, thus proving to be a real problem in calibration, and therefore of reduced applicability.
+This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems.
+The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
+
+The interpretation of the correction term as interactions is not the only possible reading.
+In other contexts the correction term might also be interpreted as a non accounted phenomena ranging from environmental factors (e.g.
+temperature, pH) to other biological factors (viruses, flock formation, pathogens).
+Alternative hypothesis for explaining the observed patterns in the microbial community should be considered as well.
 

### 2019-11-28 Tracking/main.m
changed a to class_AOB

@@ -1,12 +1,11 @@
 %Reference: Cimen et al 2002 Nonlinear optimal tracking control
-
 %main: process and filter data to model.
 close all
 clear
-load('MAT_files\synthetic_data_no_noise')
-name_file = '241119_no_noise';
-nA = round(sum(a));
-nB = round(sum(b)); 
+load('MAT_files\Classification_day183_gurobi')
+name_file = '191127_Reactor_A_modified';
+nA = round(sum(class_AOB));
+nB = round(sum(class_NOB)); 
 n = nA+nB;
 index_t_obs = find(t_obs <300);
 index_span = time_steps_index(1):index_t_obs(end);

### 2019-11-28 Classification/observer_study.m
multistart problem

@@ -5,11 +5,11 @@ reactor = 'A';
 [t_obs,biomass,s_in,S1,S2,S3,dilution_rate] = load_biomass(reactor);
 [t_OTU_rel,OTU_rel] = load_relative_abundance(reactor);
 d_inter = @(t) interp1(t_obs,dilution_rate,t);
-s_in_inter = @(t) interp1(t_obs,s_in,t);
+s_in_inter = @(t) interp1(t_obs,s_in,t,'previous');
 s1_inter = @(t) interp1(t_obs,S1,t);
 s2_inter = @(t) interp1(t_obs,S2,t);
 t_change = 183; %incrase of temperature
-time_steps_index = find(t_obs > t_change & t_obs < t_change + 50);
+time_steps_index = find(t_obs > t_change & t_obs < t_change + 60);
 t_used = t_obs(time_steps_index);
 dynamic = @(t,z) -1*d_inter(t)*(z - s_in_inter(t));
 % z0 = random('Uniform',0,4,3,1);
@@ -23,7 +23,7 @@ hold on
 plot(T,Z,'--','LineWidth',2.5);
 plot(T2,Z2,'--','LineWidth',2.5);
 plot(T3,Z3,'--','LineWidth',2.5);
-[ax,p1,p2] = plotyy(t_used,arrayfun(s_in_inter,t_used),t_used,arrayfun(d_inter,t_used));
+[ax,p1,p2] = plotyy(T2,arrayfun(s_in_inter,T2),T2,arrayfun(d_inter,T2));
 xlabel('\fontsize{12}Time [days]'),...
 ylabel('\fontsize{12} Concentration [g/l]'),...
 ylabel(ax(2),'\fontsize{12} Dilution Rate [day]^{-1}'),
@@ -46,7 +46,15 @@ xG2 = max(0,arrayfun(invariant,t_used)...
 optim_fun = @(x) norm(biomass(time_steps_index) - x(1)*xG1 - x(2)*xG2);
 yA_ref = 0.167;
 yB_ref = 0.027;
-[y_opt , val] = fmincon(optim_fun,[yA_ref yB_ref],[],[],[],[],[0 0],[],[]);
+% [y_opt , val] = fmincon(optim_fun,[yA_ref yB_ref],[],[],[],[],[0 0],[],[]);
+% [y_opt , val] = simulannealbnd(optim_fun,[yA_ref yB_ref]);
+ms = MultiStart;
[…]

### 2019-11-28 tex/Tracking.tex
changes in tex

@@
 	This article deals with the inclusion of microbial ecology in bioprocess modelling.
-The first part exposes the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting.
+The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting.
 The limitations and the insights of such an approach are discussed.
 The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented.
-The method revisits the data used for the first model presented and proposes a way to calibrate and discriminate .
+The method revisits the data used for the first model presented and proposes a way to calibrate and discriminate for a class .
 \end{abstract}
@@
 The number of organisms in each functional will be denoted $n_1$ and $n_2$ respectively, that is $\vert G_1 \vert = n_1$ and $\vert G_2 \vert = n_2$ .
-This work treats the case when the $G_1$ and $G_2$ are disjoint sets:
+This work treats the case when $G_1$ and $G_2$ are disjoint sets:
 
@@
 Notice that for being as generic as possible, the growth rate may be a function of the whole state in order to model the influence of all OTU on the growth rates of others.
-
 \begin{align}
@@
 
-\subsection{Kinetic Equations}
-The growth rate of each species is given by:
-\begin{align}
-\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
-\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2
-\end{align}
-The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU. Let $A$ denote the matrix
-with entries $a_{ij}$, which will be referred to as the interaction matrix.
-
+An example of this process is the nitrification process where group $G_1$ is known as Ammonium oxidizer Bacteria (AOB), and group $G_2$ is known as Nitrite oxidizing Bacteria (NOB) \cite{SHARMA1977897}.
 \subsection{Mass Balance Equations}
@@
 System \eqref{system} represents this situation.
-A specific case of $\mu_i(s,x)$ is given by \cite{Dumont2016}, and the first part of this article deals with the mathematical analysis of that model.
-A second part then generalizes its growth function and calibrates it against experimental data using an optimal control approach.
+A specific case of $\mu_i(s,x)$ is given in the next subsection.
 
@@
 \dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_2 \\
-\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i\in G_1} \frac{1}{y_i}\mu_i(s_1,x) x_i  \\
+\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i\in G_1} \frac{1}{y_i}\mu_i(s,x) x_i  \\
 \dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in G_1}\frac{1}{y_i}\mu_i(s,x)x_i 		-\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i  \\
@@
 
+\subsection{Kinetic Equations}
+In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rate seen in equations \eqref{gLV growth1} and \eqref{gLV growth2} was calibrated against experimental data for the two most abundant OTU of each functional group.
+
+\begin{align}
+\label{gLV growth1}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
+\label{gLV growth2}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2 
+\end{align}
+
+The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU. Let $A$ denote the matrix
+with entries $a_{ij}$, which will be referred to as the interaction matrix.
+The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
+
 \section{Mathematical Analysis}
@@
 	\label{theoWellPosedness}
-	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions remain in $\Omega$ and are bounded.
+	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}, remain in $\Omega$ and are bounded.
 \end{theo}
@@
 In this section analytical expressions for equilibrium points are derived.
-Analytic expressions of equilibrium points are obtained, however no analytic expression concerning the stability of such points is presented.
+However no analytic expression concerning the stability of such points is presented.
 To answer the question of stability a numeric scheme is used by evaluating the Jacobian at the equilibrium point.
@@
 
-The former function places a vector $v$ in the diagonal of a matrix. By noting $A$ the matrix with coefficients $a_{ij}$, system \eqref{system} is restated as follows:
+The former function places a vector $v$ in the diagonal of a matrix. Recalling $A$ the matrix with coefficients $a_{ij}$. The following notation is introduced.
+
+\begin{align} A = \begin{bmatrix}
+A_1\\A_2
+\end{bmatrix}\end{align}
+ Where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$.
+$A_2$ is a matrix of dimension $n_2 \times n$ rows corresponding to the interaction coefficients of OTU $i \in G_2$.
+And  $f(s) \in \R^n$, such that 
+\begin{align}
+f_i(s) = \begin{cases}
+\bar{\mu}_i \dfrac{s_1}{K_i + s_1} \quad \forall i \in G_1 \\
+\bar{\mu}_i \dfrac{s_2}{K_i + s_2} \quad \forall i \in G_2
+\end{cases}
+\end{align}
+With the above system \eqref{system}, is rewritten in equations \eqref{Eq1}, \eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4}.
+
 \begin{align}
@@
 \end{align}
-
-%
-%The following notation was used:
-%$A = \begin{bmatrix}
-%A_1\\A_2
-%\end{bmatrix}$.
-%
-%Where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$.
-$A_2$ is a matrix of dimension $n_2 \times n$ rows corresponding to the interaction coefficients of OTU $i \in G_2$.
 
@@
 then a first order approximation of $\I(\cdot)$ centred at $\bar{x}$ gives: $\I(x) = \I(\bar{x}) + J_I(\bar{x})(x-\bar{x}) + o(\Vert x- \bar{x} \Vert)$.
-I $\bar{x}= 0$, one recovers the growth expression from the previous section and $J_I(\bar{0})$ can be seen as the interaction matrix from model \eqref{system}.
+When $\bar{x}= 0$ one recovers the growth expression from the previous section (equations \eqref{gLV growth1} and \eqref{gLV growth2}) implying that $J_I(\bar{0})$ can be seen as the interaction matrix from model \eqref{system}.
 
@@
 
-The control $u(t)$ is intended to drive the system to be near a desired output $z(t)$, which in this context are the measurements of the concentrations of OTU and metabolites.
+The control $u(t)$ is intended to drive the system to be near a desired output $z(t)$, which in this context are the measurements of the concentrations of OTU.
 The term $\lambda \Vert(u -\vec{1}) \Vert_R$, was added for two reasons:
@@
 The problem of approximating the solution of the system to a desired reference ($z$ in this case) is called the optimal tracking problem.
-For solving such a problem the approach developed by Cimen \textit{et al.} \cite{Cimen2004} was adapted to our problem.
+For solving such a problem the approach developed by Cimen \textit{et al.} \cite{Cimen2004, Cimen2008} was adapted to our problem.
 The method proposed involves the resolution of Approximating Sequences of Ricatti Equations (ASRE).
@@
 
-Two points of departure from the original method are made clear, details can be seen in the appendix: first the tracking problem does not consider a constrained control, so one should consider a reformulation as proposed by the same author in other works \cite{Cimen2008}.
-Nevertheless, the methods were directly used, and an explicit constraint in the synthesis of the control was added for the control to remain within the desired bounds.
-Even though this is probably suboptimal it worked in a first implementation.
-
-Second in their problem they used an approximation of their original dynamics for calculating the trajectories and subsequently proved that such linearisation converged to the original dynamics.
+The tracking problem does not consider a constrained control.
+Nevertheless, the methods of Cimen \textit{et al.}\cite{Cimen2004} were directly used with an explicit constraint in the synthesis of the control.
+Even though this is probably suboptimal it worked fairly well.
+
+Another departure from their method is that in their formulation an approximation of the dynamics for calculating the trajectories is used.
+They proved that such a linearisation converged to the original dynamics.
 In the case here presented the linearisation of the dynamics was not necessary.
@@
 
-Finally for the parametric identification of a particular class of interaction functions the following static optimization problem is proposed.
-Suppose $u(t)$ is the optimal control of problem \eqref{Optimal Control}, and $x(t)$ is the associated trajectory.
+Finally for the parametric identification of a particular class of interaction functions an static optimization problem is proposed \eqref{Parameter Identification}.
+Suppose $u(t)$ is the optimal control of problem \eqref{Optimal Control}, and $x(t)$ is the associated optimal trajectory.
 Suppose a set of parameters $\theta \in \Theta$, such that the interaction function has a explicit form that depends on this parameters $I_{\theta}(x)$ ($\theta$ would represent matrix $A$ from section 2 for example).
-Then one solves the following optimization problem:
 \begin{align}
@@
 For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against synthetic data.
-The test consisted in simulating system \eqref{Controlsystem} with $I(x) = 1 + Ax$, (with $A$ in figure \ref{Comparison Interaction Matrices}) for $n_1 = 10$ and $n_2 = 5$.
+The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2} (therefore $I(x) = 1 + Ax$) for $n_1 = 10$ and $n_2 = 5$.
 In all figures, dotted lines represent the synthetic data, while the continuous lines represent the method's output.
@@
 10^{-4}I_{n_1} & 0 \\ 0 & 10^{-5}I_{n_2}
-\end{bmatrix}$, found by trial and error in order for the control to fit accurately the species abundance.
+\end{bmatrix}$, found by trial and error in order for the control to fit accurately the species abundance, instead of the control approaching 1.
 The rational behind choosing a smaller value for the group $G_2$ is related to the one order of magnitude difference in yields between $G_1$ and $G_2$.
@@
 
-The obtained matrix from the fit can be seen an compared to the original matrix for simulating data in \eqref{Comparison Interaction Matrices}.
+The original interaction matrix and the fitted interaction matrix can be seen and compared in figure \eqref{Comparison Interaction Matrices}.
 It can be seen that the new matrix is very different from the original one, in both order of magnitude and sign.
 Implying that the model is probably not identifiable.
-The system was simulated again with the new matrix, and one can see that it in general terms it captures the outcome of the system as shown in figures \ref{AOB LV simulation}, \ref{NOB LV simulation}, and \ref{Metabolites LV simulation}.
-The final message of this section is that if the interaction function is of the form $1+Ax$, one could be able to get a fit from the data with the method here presented.
+The system was simulated again with the new matrix, and one can see that in general terms it captures the outcome of the system as shown in figures \ref{AOB LV simulation}, \ref{NOB LV simulation}, and \ref{Metabolites LV simulation}.
+The final and central message of this section is that if the interaction function is of the form $1+Ax$, one could be able to get a good fit from the data with the method here presented.
 
@@
 	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_AOB_Iter_5_LV}
-	\caption{AOB trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+	\caption{AOB trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
 	\label{AOB LV simulation}
@@
 	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_NOB_Iter_5_LV}
-	\caption{NOB trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+	\caption{NOB trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
 	\label{NOB LV simulation}
@@
 	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_metabolites_Iter_5_LV}
-	\caption{Metabolites trajectories using the identified matrix seen in \eqref{Comparison Interaction Matrices}.}
+	\caption{Metabolites trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
 	\label{Metabolites LV simulation}

### 2019-11-28 Classification/main.m
use optimized yields

@@ -2,7 +2,7 @@ clear
 addpath('..\\General Functions')
 reactor = 'A';
 delta = 0.01; %Between 0 and 1
-id = 'all_data_intlinprog';
+id = 'day_183_243_intlinprog';
 file_name = sprintf('Classification_%s',id);
 [t_obs,biomass,s_in,S1,S2,S3,dilution_rate] = load_biomass(reactor);
 [t_OTU,OTU_rel] = load_relative_abundance(reactor);
@@ -10,9 +10,9 @@ OTU_rel = diag(1./sum(OTU_rel,2))*OTU_rel;
 number_OTU = length(OTU_rel(1,:));
 minimal_abundance = 0;
 t_change = 183; % From dumont et al
-delta_t = 50;
-% time_steps_index = find(t_obs > t_change & t_obs < t_change + delta_t);
-time_steps_index = 1:length(t_obs);
+delta_t = 60;
+time_steps_index = find(t_obs > t_change & t_obs < t_change + delta_t);
+% time_steps_index = 1:length(t_obs);
 time_steps_index_OTU = find(t_OTU > t_change & t_OTU < t_change + delta_t);
 OTU_series = timeseries(OTU_rel(time_steps_index_OTU,:),...
     t_OTU(time_steps_index_OTU));
@@ -22,13 +22,13 @@ considered_OTU = find(max_abundance > minimal_abundance);
 OTU_interp = interpolate_biomass(t_obs,biomass,t_OTU,OTU_rel);
 OTU_interp_fun = @(t) interp1(t_OTU,OTU_interp(:,considered_OTU),t);
 d_interp = @(t) interp1(t_obs,dilution_rate,t);
-s_in_interp = @(t) interp1(t_obs,s_in,t);
+s_in_interp = @(t) interp1(t_obs,s_in,t,'previous');
 s1_interp = @(t) interp1(t_obs,S1,t);
 s2_interp = @(t) interp1(t_obs,S2,t);
 dynamic = @(t,z) -1*d_interp(t)*(z - s_in_interp(t));
 t0 = t_obs(time_steps_index(1));
 tF = t_obs(time_steps_index(end));
-[T, Z] = ode15s(dynamic,[t0 tF],S1(time_steps_index(1)));
+[T, Z] = ode15s(dynamic,[t0 tF],s_in(time_steps_index(1)));
 invariant = @(t) interp1(T,Z,t);
[…]

### 2019-12-02 tex/Tracking.tex
Update tex

@@
 \begin{abstract}
-	This article deals with the inclusion of microbial ecology in bioprocess modelling.
+	This article deals with the inclusion of microbial ecology advances in bioprocess modelling.
 The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting.
@@
 The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented.
-The method revisits the data used for the first model presented and proposes a way to calibrate and discriminate for a class .
+The method revisits the data used for the first model presented and proposes a way to calibrate and discriminate for a class of growth kinetics.
 \end{abstract}
@@
 
-The main contribution of this article is a procedure to integrate the microbial community measurements in chemostat models, based on any technique that can quantify the species abundances through time.
+The main contribution of this article is a procedure to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time.
 This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.
@@
 
-Section 4 is the article's most original contribution.
+Section 4 is the article's core contribution.
 The concept of interaction function is developed such that it generalizes the gLV model.
-For the identification of the interaction function a method of optimal tracking was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected to fit the experimental data.
-The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species.
-
-In section 5 the methodology from section 4 is applied to the data from the experiments perform by Dumont et al \cite{Dumont2009}.
-Finally, a discussion on the scope of the method, its shortcomings and perspectives is presented.
+For the identification of the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data.
+The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species, it is solved via state-dependent ricatti equations \cite{Cimen2008}.
+Finally the obtained optimal trajectory and control are used in a static optimization problem in order to estimate the parameters of a specific interaction function.
+
+In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of \cite{Dumont2016}.
+The article ends with a discussion on the use of gLV models, the scope of applicability of the method, and its shortcomings.
 
@@
 
-The washout of $G_2$ is equivalent to the following hypothesis:
+The washout of $G_2$ is equivalent to  hypothesis \ref{WashoutG2}.
 
@@
 
-The model here presented serves to illustrate that by considering a more complex growth rate that accounts for ecological interactions one might explain differences in reactors operating under similar conditions.
+The model here presented serves to illustrate that by considering a more complex growth rate that tries to model ecological interactions one might explain differences in reactors operating under similar conditions.
 It also shows a new mechanism by which the CEP no longer holds.
-However the quadratic increase of parameters with the number of OTU considered makes it difficult to accurately calibrate the model.
 The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
-In the next section, a generalization of the former model, and a schema for calibrating a class of models is presented as well.
+The quadratic increase of parameters with the number of OTU considered makes it difficult to accurately calibrate the model.
+Parameter estimation in A classic way to approach this is by a least square approach, however Some methods for parameter estimation and uncertainty in biochemical systems of ODE can be seen in Vanlier \textit{et al.} \cite{Vanlier2013} and even a "robust approach" is proposed for biological systems by Gabor \textit{et al.} \cite{Gabor2015}, however parameter estimation in ODE is still an open problem.
+In the next section, a generalization of the former model, and a schema for parameter estimation where the uncertainty lies in the growth function is presented as well.
 
@@
 
-Finally for the parametric identification of a particular class of interaction functions an static optimization problem is proposed \eqref{Parameter Identification}.
+Finally for the parametric identification of a particular class of interaction functions a static optimization problem is proposed \eqref{Parameter Identification}.
 Suppose $u(t)$ is the optimal control of problem \eqref{Optimal Control}, and $x(t)$ is the associated optimal trajectory.
 Suppose a set of parameters $\theta \in \Theta$, such that the interaction function has a explicit form that depends on this parameters $I_{\theta}(x)$ ($\theta$ would represent matrix $A$ from section 2 for example).
+In practice $t \in [0,T]$ from \eqref{Parameter Identification} is replaced by considering the time steps given by the differential equation solver.
 \begin{align}
@@
 
-In practice $t \in [0,T]$ from \eqref{Parameter Identification} is replaced by considering the time steps given by the differential equation solver.
 \subsection{Proof of concept}
 
-For compensating the lack of a theoretical optimal control, the approach presented in here was first tested against synthetic data.
+The approach was tested against synthetic data.
 The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2} (therefore $I(x) = 1 + Ax$) for $n_1 = 10$ and $n_2 = 5$.
@@
 
-The method stopped after 110 iterations where each iteration took approximately 600 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.
+The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.
 
@@
 Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics.
-For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $230$: 17 OTU were identified in the $G_1$ group (known as Ammonium oxidizing bacteria AOB) and 8 in the $G_2$ functional group (known as Nitrite oxidizing bacteria NOB).
-The system state dimension becomes 28.
+For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (known as Ammonium oxidizing bacteria AOB) and 5 in the $G_2$ functional group (known as Nitrite oxidizing bacteria NOB).
+The system state dimension becomes 38.
 
@@
 One can observe that in figure \ref{ControlSimulation} the predicted $s_3$ around day 240 is much higher than the measurement.
-If one looks at figure \ref{NOB Simulation} it suggests attributing this extra production of $s_3$ around day 240 to the growth of OTU 24.
-What would have happened if OTU 24 had been classified in the other functional group?
-One would have seen a decrease in $s_1$, an increase in $s_2$, and a decrease in $s_3$ which could have better fitted the measurements.
-Thus suggesting that OTU 24 was misclassified from the method presented in \cite{Ugalde-Salas2019}.
 
@@
 
-Recalling that $u(t)$ is supposed to represent $I(x(t))$ (the interactions terms), one could try to fit different forms of $I(\cdot)$ for example $I(x) = 1 + Ax$, where  $A$ is a real valued square matrix.
-In figure \ref{LV_fit} the simulation of the system after the identification of matrix A is presented, suggesting that an affine interaction function is not able to capture the behaviour of the system.
+Then the procedure from the proof of concept section was applied and one can see that a gLV model is far from describing the pronounced control changes.
 
@@
 Furthermore from the proof of concept section, one might conjecture that models with a large number of parameters such as an gLV model may be unidentifiable, thus proving to be a real problem in calibration, and therefore of reduced applicability.
+Furthermore the ecological interpretations to be drawn from the sign of the interaction matrix might be useless.
 This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems.
@@
 
+\section{Codes}
+
+All the codes can be recovered from the following repository \url{https://github.com/paus-5/Class-and-Track}.
 \section{Acknowledgements}
- Alain Rapaport, CMM, Thermomic
+ The authors would like to thank Alain Rapaport for the fruitful exchanges. This work was financed by grant Thermomic. And a sejour
 
@@
 They were solved using standard backward numerical integration.
-
+\section{References}
 \bibliographystyle{elsarticle-num}

### 2019-12-03 Tracking/nonlinear_con.m
add nonlinear constraint

@@ -1,0 +1,5 @@
+function [c,ceq] = nonlinear_con(interactions,x)
+[n, m] = size(x);
+c = -reshape(1+interactions*x,n*m,1);     % Compute nonlinear inequalities at x.
+ceq = 0;   % Compute nonlinear equalities at x.
+end

### 2019-12-03 Classification/observer_study.m
changes to plots in observer study

@@ -4,17 +4,18 @@ addpath('..\\General Functions')
 reactor = 'A';
 [t_obs,biomass,s_in,S1,S2,S3,dilution_rate] = load_biomass(reactor);
 [t_OTU_rel,OTU_rel] = load_relative_abundance(reactor);
-d_inter = @(t) interp1(t_obs,dilution_rate,t);
+d_inter = @(t) interp1(t_obs,dilution_rate,t,'previous');
 s_in_inter = @(t) interp1(t_obs,s_in,t,'previous');
 s1_inter = @(t) interp1(t_obs,S1,t);
 s2_inter = @(t) interp1(t_obs,S2,t);
-t_change = 183; %incrase of temperature
-time_steps_index = find(t_obs > t_change & t_obs < t_change + 60);
+t_initial = 183; %incrase of temperature day = 183
+delta_t = 132;
+time_steps_index = find(t_obs > t_initial & t_obs < t_initial + delta_t);
 t_used = t_obs(time_steps_index);
 dynamic = @(t,z) -1*d_inter(t)*(z - s_in_inter(t));
 % z0 = random('Uniform',0,4,3,1);
 t0 = t_obs(time_steps_index(1));
-z0 = [0.3 1 2.9]';
+z0 = [0.3 s_in_inter(t_initial) 3]';
 [T, Z] = ode15s(dynamic,[t_used(1) t_used(end)],z0(1));
 [T2, Z2] = ode15s(dynamic,[t_used(1) t_used(end)],z0(2));
 [T3, Z3] = ode15s(dynamic,[t_used(1) t_used(end)],z0(3));
@@ -68,7 +69,7 @@ ylabel('\fontsize{12} Concentration [g/l]'),...
 title(sprintf('Observers in Time Reactor %s',reactor))
     set(gca,'fontsize',15);
     set(ax,'fontsize',15);
-    l = legend('$$y^{A}_{ref}\hat{x}_{G_1}$$','$$y^{B}_{ref}\hat{x}_{G_2}$$',...
+    l = legend('$$y^{A}_{opt}\hat{x}_{G_1}$$','$$y^{B}_{opt}\hat{x}_{G_2}$$',...
         '$$y^A_{opt}\hat{x}_{G_1}+y^B_{opt}\hat{x}_{G_2}$$ ','Measured Biomass');
     set(l,'Interpreter','latex')
 fig.PaperUnits = 'inches';

### 2019-12-03 Tracking/plot_data_fit.m
change data display to star in plot

@@ -1,7 +1,7 @@
 %plotting
 clear
 close all
-name_file_in = 'MAT_Files\\061119_Try1_iter_300';
+name_file_in = 'MAT_Files\\191130_Reactor_A_iter_10';
 load(name_file_in);
 numbering_AOB = strsplit(num2str(1:nA)) ;
 legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_AOB{:}),...
@@ -43,7 +43,7 @@ print(sprintf('Images\\%s',sprintf('%s_Biomass_Iter_%.0f',...
 figure
 hold on
 AOB_plot = plot(t_new,x_new(:,1:nA),'LineWidth',1.5);
-AOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,1:nA),'--','LineWidth',1.5);
+AOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,1:nA),'*','LineWidth',0.7);
 xlabel('\fontsize{15}Time [days]'),...
     ylabel('\fontsize{15}  Concentration [g/l]'),...
     title(sprintf('Tracking results AOB iteration:%.0f',iter));
@@ -61,7 +61,7 @@ print(sprintf('Images\\%s',sprintf('%s_AOB_Iter_%.0f',...
 figure
 hold on
 NOB_plot = plot(t_new,x_new(:,nA+1:n),'LineWidth',1.5);
-NOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,nA+1:end),'--','LineWidth',1.5);
+NOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,nA+1:end),'*','LineWidth',0.7);
 xlabel('\fontsize{15}Time [days]'),...
     ylabel('\fontsize{15}  Concentration [g/l]'),...
     title(sprintf('Tracking results NOB iteration:%.0f',iter));
@@ -79,14 +79,14 @@ print(sprintf('Images\\%s',sprintf('%s_NOB_Iter_%.0f',...
 figure
 hold on
 metabolite_plot = plot(t_new,x_new(:,(n+1):end),'LineWidth',1.5);
-data_metabolite_plot = plot(tS,[S1(index_span) S2(index_span) S3(index_span)],'--');
+data_metabolite_plot = plot(tS,[S1(index_span) S2(index_span) S3(index_span)],'*');
[…]

### 2019-12-03 Tracking/simulate_interactions.m

@@ -19,7 +19,7 @@ fit = A*x_new(index_control,1:n)'+1;
 control_matrix = reshape(cell2mat(control_eval),n,length(index_control))+1;
 diff = abs(control_matrix - fit);
 figure
-diff_plot = plot(t_new,diff,'LineWidth',1.5);
+diff_plot = plot(t_used,diff,'LineWidth',1.5);
 xlabel('\fontsize{12}Time [days]'),...
     ylabel('\fontsize{12}  Absolute difference between Ax+1 and u(t)'),...
     title('Difference of LV and Control');
@@ -47,14 +47,14 @@ dynamic_inter = @(t,X) [diag(growth1(X) - d_interp(t))*X(1:nA);
 t0_interactions = tS(1);
 tF_interactions = tS(end);
 x0_interactions = x_new(1,:);
-ode_optionss = odeset('Nonnegative',1:(n+3));
-[T_inter, Y_inter] = ode45(dynamic_inter,[t0_interactions tF_interactions],x0_interactions);
+ode_options = odeset('Nonnegative',1:(n+3));
+[T_inter, Y_inter] = ode45(dynamic_inter,[t0_interactions tF_interactions],x0_interactions,ode_options);
 indexTSOTU = find(t_OTU<tF_interactions & t_OTU>t0_interactions);
 %AOB
 figure
 hold on
 AOB_plot = plot(T_inter,Y_inter(:,1:nA),'LineWidth',1.5);
-dataAOB_plot = plot(t_OTU(indexTSOTU),biomass_filtered(indexTSOTU,1:nA),'--','LineWidth',1.5);
+dataAOB_plot = plot(t_OTU(indexTSOTU),biomass_filtered(indexTSOTU,1:nA),'*','LineWidth',0.7);
 xlabel('\fontsize{12}Time [days]'),...
     ylabel('\fontsize{12}  Concentration [g/l]'),...
     title('AOB abundance simulation of LV model');
@@ -71,7 +71,7 @@ print(sprintf('Images\\%s',sprintf('%s_AOB_Iter_%.0f_LV',...
 figure
 hold on
 NOB_plot = plot(T_inter,Y_inter(:,nA+1:n),'LineWidth',1.5);
-dataNOB_plot = plot(t_OTU(indexTSOTU),biomass_filtered(indexTSOTU,nA+1:n),'--','LineWidth',1.5);
[…]

### 2019-12-03 Tracking/identify_interactions.m
added non linear constraint

@@ -3,21 +3,32 @@ clear
 close all
 file_in = '221119_no_noise_iter_5';
 load(sprintf('MAT_files/%s',file_in));
-index_control = find(t_new > 20 & t_new < 130);
+index_control = find(t_new>20 & t_new<130);
+% index_control = 1:length(t_new);
 t_used = t_new(index_control);
+clear diff
+time_intervals = diff(t_used);
+time_weights_middle = 0.5*time_intervals(2:end) + 0.5*time_intervals(1:end-1);
+time_weight = [time_intervals(1); time_weights_middle; time_intervals(end)];
 control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
+x_trajectories = x_new(index_control,1:n)';
 control_eval = arrayfun(control,t_used,'UniformOutput',false);
-optim_fun = @(interactions) sum(norm(reshape(cell2mat(control_eval),n,...
-    length(index_control)) - reshape(interactions,n,n)*x_new(index_control,1:n)'));
-options = optimset('MaxFunEvals',2000000,'MaxIter',100000)';
-% ms = MultiStart;
-% problem = createOptimProblem('fminunc','x0',zeros(n^2,1),...
-%     'objective',optim_fun,'options',options);
+optim_fun = @(interactions) norm((reshape(cell2mat(control_eval),n,...
+    length(index_control)) - interactions*...
+    x_trajectories)*diag(time_weight),'fro');
+options = optimset('MaxFunEvals',2000000,'MaxIter',100000)'; 
+nonlcon = @(interactions) nonlinear_con(interactions,x_trajectories);
+ms = MultiStart;
+problem = createOptimProblem('fmincon','x0',zeros(n,n),...
+    'objective',optim_fun,'nonlcon',nonlcon,'options',options);
+tic
+[xmin,fmin,flag,outpt,allmins] = run(ms,problem,1);
+toc
 % tic
-% [xmin,fmin,flag,outpt,allmins] = run(ms,problem,50);
+% [xmin, fval] = fmincon(optim_fun,zeros(n,n),[],[],[],[],[],[],nonlcon,options);
+% % [xmin, fval] = fminunc(optim_fun,zeros(n,n),options);
 % toc
-[xmin, fval] = fminunc(optim_fun,zeros(n^2,1),options);
-A = reshape(xmin,n,n);
+A = xmin;
 save(sprintf('mat_Files\\%s_iter_%.0f_interactions',name_file,iter));
 
 

### 2019-12-12 Tracking/tracking_control.m
added more margin to control

@@ -1,5 +1,5 @@
 function v = tracking_control(lambda,B,P,X,sF,n)
 B1_vec = diag(B(1:n,:));
 x_trunc = X(1:n);
-v = max(-1,min(-1./lambda.*B1_vec.*(P.*x_trunc - sF),0));
+v = max(-1,min(-1./lambda.*B1_vec.*(P.*x_trunc - sF),0.2));
 end

### 2019-12-12 Tracking/simulate_interactions.m
new nomenclature of A_new

@@ -1,6 +1,6 @@
 clear 
 close all
-file_in = '221119_no_noise_iter_5_interactions';
+file_in = '191211_no_noise_iter_10_interactions';
 load(sprintf('MAT_files/%s',file_in));%Simulation and plotting
 numbering_AOB = strsplit(num2str(1:nA)) ;
 legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_AOB{:}),...
@@ -15,9 +15,9 @@ numbering_diff = strsplit(num2str(1:n));
 legend_tags_diff = strsplit(sprintf('Difference %s,', numbering_diff{:}),',');
 legend_tags_diff(end) = [];
 %Quality of the Fit
-fit = A*x_new(index_control,1:n)'+1;
-control_matrix = reshape(cell2mat(control_eval),n,length(index_control))+1;
-diff = abs(control_matrix - fit);
+fit = new_A*x_new(index_control,1:n)';
+% control_matrix = reshape(cell2mat(control_eval),n,length(index_control))+1;
+diff = abs(control_matrix_med_filter - fit);
 figure
 diff_plot = plot(t_used,diff,'LineWidth',1.5);
 xlabel('\fontsize{12}Time [days]'),...
@@ -37,8 +37,8 @@ muARef = 0.77;
 muBRef = 1.07;
 kSARef = 0.7e-1;
 kSBRef = 1.4982e-1;
-growth1 = @(X) (1+A(1:nA,:)*X(1:n))*growth_monod(X(n+1),muARef,kSARef);
-growth2 = @(X) (1+A(nA+1:n,:)*X(1:n))*growth_monod(X(n+2),muBRef,kSBRef);
+growth1 = @(X) (1+new_A(1:nA,:)*X(1:n))*growth_monod(X(n+1),muARef,kSARef);
+growth2 = @(X) (1+new_A(nA+1:n,:)*X(1:n))*growth_monod(X(n+2),muBRef,kSBRef);
 dynamic_inter = @(t,X) [diag(growth1(X) - d_interp(t))*X(1:nA);
    diag(growth2(X) - d_interp(t))*X(nA+1:n);
    (s_in_interp(t) - X(n+1))*d_interp(t) - kA'*diag(growth1(X))*X(1:nA);

### 2019-12-12 Tracking/main.m
changed details

@@ -2,12 +2,12 @@
 %main: process and filter data to model.
 close all
 clear
-load('MAT_files\Classification_day183_gurobi')
-name_file = '191127_Reactor_A_modified';
+load('MAT_files\synthetic_data_no_noise')
+name_file = '191211_no_noise';
 nA = round(sum(class_AOB));
 nB = round(sum(class_NOB)); 
 n = nA+nB;
-index_t_obs = find(t_obs <300);
+index_t_obs = find(t_obs <315);
 index_span = time_steps_index(1):index_t_obs(end);
 tS = t_obs(index_span); 
 s1_interp = @(t) interp1(tS,S1(index_span),t);
@@ -21,8 +21,8 @@ biomass_filtered(biomass_filtered == 0) = min_biomass;
 z = @(t) interp1(t_OTU,biomass_filtered,t)';
 kA = yields_AOB(index_AOB);
 kB = yields_NOB(index_NOB);
-muARef = 0.77*1.2;
-muBRef = 1.07*1.2;
+muARef = 0.77;
+muBRef = 1.07;
 kSARef = 0.7e-1;
 kSBRef = 1.4982e-1;
 kIRef = 1.217;
@@ -33,7 +33,8 @@ kSB = kSBRef*ones(nB,1);
 kI = kIRef*ones(nB,1);
 % %%Parameters
 % lambda = 0.001;
-lambda = [0.0001*ones(nA,1); 0.00001*ones(nB,1)];
+% lambda = [0.001*ones(nA,1); 0.001*ones(nB,1)];
+lambda = ones(n,1)*10^-7;
 Q2= [kA; kB];
 % Q = Q2/norm(Q2,'inf');
 Q = [ones(nA,1); ones(nB,1)];
@@ -48,7 +49,7 @@ legend_tags = strsplit(strjoin({num2str(1:n),' s_1 s_2 s_3'}));
 legend_tags_OTU = strsplit(strjoin({num2str(1:n)}));
 tF = tS(end);
 t0 = tS(1);
-x0 = [0.001*ones(1,n) s1_interp(t0) s2_interp(t0) s3_interp(t0)]';
+x0 = [biomass_filtered(1,:) s1_interp(t0) s2_interp(t0) s3_interp(t0)]';
 dynamic = @(t,X) Ax(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,s_in_interp(t),...
     d_interp(t))*X ;
[…]

### 2019-12-12 Tracking/identify_interactions.m
changes in optim function

@@ -1,9 +1,9 @@
 %Calculating Interactions
 clear
 close all
-file_in = '221119_no_noise_iter_5';
+file_in = '191211_no_noise_iter_10';
 load(sprintf('MAT_files/%s',file_in));
-index_control = find(t_new>20 & t_new<130);
+index_control = find(t_new>20 & t_new<80);
 % index_control = 1:length(t_new);
 t_used = t_new(index_control);
 clear diff
@@ -13,22 +13,31 @@ time_weight = [time_intervals(1); time_weights_middle; time_intervals(end)];
 control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
 x_trajectories = x_new(index_control,1:n)';
 control_eval = arrayfun(control,t_used,'UniformOutput',false);
-optim_fun = @(interactions) norm((reshape(cell2mat(control_eval),n,...
-    length(index_control)) - interactions*...
-    x_trajectories)*diag(time_weight),'fro');
-options = optimset('MaxFunEvals',2000000,'MaxIter',100000)'; 
+control_matrix = reshape(cell2mat(control_eval),n,length(index_control));
+control_matrix_med_filter = medfilt1(control_matrix',200)';
+% optim_fun = @(interactions) norm((control_matrix_med_filter - (interactions*...
+%     x_trajectories)*diag(time_weight)),'fro');
+optim_fun = @(interactions) norm(control_matrix_med_filter - (interactions*...
+    x_trajectories),'fro');
 nonlcon = @(interactions) nonlinear_con(interactions,x_trajectories);
+options = optimset('MaxFunEvals',2000000,'MaxIter',100000)'; 
 ms = MultiStart;
 problem = createOptimProblem('fmincon','x0',zeros(n,n),...
     'objective',optim_fun,'nonlcon',nonlcon,'options',options);
 tic
 [xmin,fmin,flag,outpt,allmins] = run(ms,problem,1);
-toc
 % tic
-% [xmin, fval] = fmincon(optim_fun,zeros(n,n),[],[],[],[],[],[],nonlcon,options);
-% % [xmin, fval] = fminunc(optim_fun,zeros(n,n),options);
-% toc
-A = xmin;
+% [xmin, fval] = fmincon(optim_fun,A,[],[],[],[],[],[],nonlcon,options);
+toc
+new_A = xmin;
[…]

### 2019-12-12 Tracking/plot_data_fit.m

@@ -1,7 +1,7 @@
 %plotting
 clear
 close all
-name_file_in = 'MAT_Files\\191130_Reactor_A_iter_10';
+name_file_in = 'MAT_Files\\191211_no_noise_iter_10';
 load(name_file_in);
 numbering_AOB = strsplit(num2str(1:nA)) ;
 legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_AOB{:}),...

### 2019-12-12 Stability Analysis gLV/plot_interactions.m
changes in parameters

@@ -1,4 +1,6 @@
-file_in = 'synthetic_data_no_noise';
+clear
+close all
+file_in = '191204_no_noise_iter_4_interactions';
 load(sprintf('MAT_files/%s',file_in));
 labels = cell(n);
 % for i =1:n
@@ -15,7 +17,7 @@ for i=1:n
 end
 imagesc(A);
 colormap(jet)
-text_strings = num2str(A(:), '%0.1f');       % Create strings from the matrix values
+text_strings = num2str(A(:), '%1.0f');       % Create strings from the matrix values
 text_strings = strtrim(cellstr(text_strings));  % Remove any space padding
 [x, y] = meshgrid(1:n);  % Create x and y coordinates for the strings
 hStrings = text(x(:), y(:), text_strings(:), ...  % Plot the strings
@@ -34,4 +36,4 @@ title(sprintf('\\fontsize{20} Interaction Matrix'))
     set(gca,'fontsize',16)
 h.PaperPositionMode = 'manual';
 h.PaperPosition = [.25 .25 90 60];
-print(sprintf('Images/Interactions_%s',file_in),'-dpng','-r0')
+print(sprintf('Images/Interactions_%s_ms',file_in),'-dpng','-r0')

### 2019-12-12 tex/Tracking.tex
changes in tex

@@
 
-The main contribution of this article is a procedure to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time.
+The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time.
 This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{260919_Try1_metabolites_Iter_110}
+	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_metabolites_Iter_10}
 	\caption{Simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{260919_Try1_AOB_Iter_110}
+	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_AOB_Iter_10}
 	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{260919_Try1_NOB_Iter_110}
+	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_NOB_Iter_10}
 	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
@@
 
-One can observe that in figure \ref{ControlSimulation} the predicted $s_3$ around day 240 is much higher than the measurement.
-
 In figures \ref{AOB_control} and \ref{NOB_control} it can be seen the obtained controls for each functional group.
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{260919_Try1_Control_AOB_Iter_110}
+	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_AOB_Iter_10}
 	\caption{Control obtained for OTU in $G_1$ (AOB).}
 	\label{AOB_control}
-	\includegraphics[width= 0.4\textwidth]{260919_Try1_Control_NOB_Iter_110}
+	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_NOB_Iter_10}
 	\caption{Control obtained for OTU in $G_2$ (NOB).}

### 2019-12-12 Classification/main.m
parameter change

@@ -2,7 +2,7 @@ clear
 addpath('..\\General Functions')
 reactor = 'A';
 delta = 0.01; %Between 0 and 1
-id = 'day_183_243_intlinprog';
+id = 'day_183_315_gurobi';
 file_name = sprintf('Classification_%s',id);
 [t_obs,biomass,s_in,S1,S2,S3,dilution_rate] = load_biomass(reactor);
 [t_OTU,OTU_rel] = load_relative_abundance(reactor);
@@ -10,7 +10,7 @@ OTU_rel = diag(1./sum(OTU_rel,2))*OTU_rel;
 number_OTU = length(OTU_rel(1,:));
 minimal_abundance = 0;
 t_change = 183; % From dumont et al
-delta_t = 60;
+delta_t = 132;
 time_steps_index = find(t_obs > t_change & t_obs < t_change + delta_t);
 % time_steps_index = 1:length(t_obs);
 time_steps_index_OTU = find(t_OTU > t_change & t_OTU < t_change + delta_t);
@@ -36,10 +36,12 @@ Z1 = invariant(t_obs(time_steps_index));
 % xG2 = max(0,Z1 - S1 - S2);
 xG1 = Z1 - S1(time_steps_index);
 xG2 = Z1 - S1(time_steps_index) - S2(time_steps_index);
-yA_ref = 0.2298; %Values obtained from y_opt observer_study
-yB_ref = 0.0109;
-% [a, b, y_AOB, y_NOB, error_AOB, error_NOB] = MIP_gurobi(partial_weights, xG1, xG2,yA_ref,yB_ref,delta);
-[a, b, y_AOB, y_NOB, error_AOB, error_NOB] = MIP_intlinprog(partial_weights, xG1, xG2,yA_ref,yB_ref,delta);
+yA_ref = 0.2229; %Values obtained from y_opt observer_study
+yB_ref = 0.0215;
+% yA_ref = 0.2039;
+% yB_ref = 0.0243;
+[a, b, y_AOB, y_NOB, error_AOB, error_NOB] = MIP_gurobi(partial_weights, xG1, xG2,yA_ref,yB_ref,delta);
+% [a, b, y_AOB, y_NOB, error_AOB, error_NOB] = MIP_intlinprog(partial_weights, xG1, xG2,yA_ref,yB_ref,delta);
 class_AOB = zeros(number_OTU,1);
 class_NOB = zeros(number_OTU,1);
 yields_AOB = zeros(number_OTU,1);

### 2019-12-17 tex/Tracking.tex
deleted parameter identification

@@
 Which renders the method- at least theoretically- scalable for a growing number of OTU.
-
-Finally for the parametric identification of a particular class of interaction functions a static optimization problem is proposed \eqref{Parameter Identification}.
-Suppose $u(t)$ is the optimal control of problem \eqref{Optimal Control}, and $x(t)$ is the associated optimal trajectory.
-Suppose a set of parameters $\theta \in \Theta$, such that the interaction function has a explicit form that depends on this parameters $I_{\theta}(x)$ ($\theta$ would represent matrix $A$ from section 2 for example).
-In practice $t \in [0,T]$ from \eqref{Parameter Identification} is replaced by considering the time steps given by the differential equation solver.
-\begin{align}
-\label{Parameter Identification} \min & \quad \Vert I_{\theta}(x(\cdot)) - u(\cdot) \Vert_{L^2([0,T])} \\
-s.t. &  \quad \theta \in \Theta \notag \\
-& \quad t \in [0,T] \notag
-\end{align}
 
@@
 \begin{align}
-A(X) & = \begin{bmatrix} 
-\diag(f(s)- D_{n\times 1} ) & 0_{n \times 3}\\
-\begin{matrix} 
+\label{A_matrix} A\left (X\right) = \begin{bmatrix}
+A_{11}(X) & A_{12}(X) \\ A_{21}(X) & A_{22}(X)
+\end{bmatrix} \\
+\label{B_matrix} B\left (X\right) = \begin{bmatrix}
+B_1(X) \\ B_2(X)
+\end{bmatrix} 
+\end{align}
+
+\begin{align}
+A_{11}(X) &= \diag(f(s)- D_{n\times 1} ) \\
+A_{21}(X) &=  \begin{bmatrix} 
 f(s)^\top \begin{bmatrix} -\diag(k_{G_1}) & 0_{n_1 \times n_2} \end{bmatrix}^\top  \\
 f(s)^\top \begin{bmatrix} \diag(k_{G_1}) & -\diag(k_{G_2}) \end{bmatrix}^\top   \\
-f(s)^\top \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top  \end{matrix} & \begin{matrix} \left(\frac{s_{in}}{s_1}-1\right)D & 0 & 0 \\ 
+f(s)^\top \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top 
+\end{bmatrix}  \\
+A_{12}(X) &=  0_{n \times 3} \\
+A_{22}(X) &= \begin{bmatrix} \left(\frac{s_{in}}{s_1}-1\right)D & 0 & 0 \\ 
 0 &-D & 0 \\ 
-0 & 0 &-D \end{matrix}
-\end{bmatrix}  \\
-B(X) & = \begin{bmatrix} \diag(f(s)\diag(x)  \\
-\begin{matrix}
+0 & 0 &-D \end{bmatrix}
+\end{align}
+
+\begin{align}
+B_1(X) &= \diag(f(s))\diag(x)  \\
+B_2(X) &= \begin{bmatrix}
 f(s)^\top \diag(x) \begin{bmatrix} -\diag(k_{G_1}) & 0_{n_1 \times n_2} \end{bmatrix}^\top \\
@@
 f(s)^\top \diag(x) \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top  
-\end{matrix}
-\end{bmatrix} \\
-C(X) = \begin{bmatrix}
-I_n & 0_{n\times 3} \\
 \end{bmatrix}
@@
 Q & 0_{n\times 3} \\ 0_{3\times n} & 0_{3\times 3}
-\end{bmatrix}- P^{[i]}A\left (X^{[i-1]}(t)\right) -A^\top \left( X^{[i-1]}(t)\right)P^{[i]} + \frac{1}{\lambda}P^{[i]}B\left( X^{[i-1]}(t) \right)B^\top\left(X^{[i-1]}(t)\right)P^{[i]} \\
+\end{bmatrix}- P^{[i]}A\left (X^{[i-1]}(t)\right) -A^\top \left( X^{[i-1]}(t)\right)P^{[i]} + P^{[i]}B\left( X^{[i-1]}(t) \right)R^{-1}B^\top\left(X^{[i-1]}(t)\right)P^{[i]} \\
 P^{[i]}(t_f) &= \begin{bmatrix}
@@
 \begin{align}
-\dot{s_f}^{[i]}(t) &= -\begin{bmatrix}Qz(t) \\ 0_{3\times 1} \end{bmatrix}- \left[A\left(X^{[i-1]}(t)\right) -\frac{1}{\lambda}B\left(X^{[i-1]}(t)\right)B^\top \left(X^{[i-1]}(t)\right)P^{[i]}(t) \right]^\top s_f^{[i]} \\
+\dot{s_f}^{[i]}(t) &= -\begin{bmatrix}Qz(t) \\ 0_{3\times 1} \end{bmatrix}- \left[A\left(X^{[i-1]}(t)\right) -B\left(X^{[i-1]}(t)\right)R^{-1}B^\top \left(X^{[i-1]}(t)\right)P^{[i]}(t) \right]^\top s_f^{[i]} \\
 s_f^{[i]}(t_f) &=   \begin{bmatrix}
@@
 
-Where $A_{11} = \diag \left( f\left(s^{[i-1]}\right)- D_{n\times 1} \right)$, and $B_1 = \diag\left(f\left(s^{[i-1]}\right)\right)\diag \left(x^{[i-1]} \right) $ The equations for $\tilde{P}^{[i]}(t)$:
+Recall $A_{11} = \diag \left( f\left(s^{[i-1]}\right)- D_{n\times 1} \right)$, and $B_1 = \diag\left(f\left(s^{[i-1]}\right)\right)\diag \left(x^{[i-1]} \right) $ The equations for $\tilde{P}^{[i]}(t)$:
 \begin{align}

### 2019-12-17 tex/Tracking.tex
deleting parameter identification

@@
 The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated data as well.
+\begin{figure}[h]
+	\centering	
+	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
+	\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}.}
+	\label{Comparison Interaction Matrices}
+\end{figure}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_difference_fit_5_LV}
-	\caption{Difference between $u(t)$ and the $1+Ax(t)$, with $A$ shown in the right hand side of Figure \ref{Comparison Interaction Matrices}}
-	\label{Difference fit}
-\end{figure} 
 \clearpage
@@
 The final and central message of this section is that if the interaction function is of the form $1+Ax$, one could be able to get a good fit from the data with the method here presented.
-
-\begin{figure}[h]
-	\centering	
-\begin{subfigure}[b]{0.45\textwidth}
-	\includegraphics[width=\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
-\end{subfigure}
-\begin{subfigure}[b]{0.45\textwidth}
-	\includegraphics[width=\textwidth]{Synthetic_data_no_noise//Interactions_221119_no_noise_iter_5}
-\end{subfigure}
-\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}.}
-\label{Comparison Interaction Matrices}
-\end{figure}
 

### 2019-12-17 tex/Tracking.tex
delete images

@@
 Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.
-Problem \eqref{Parameter Identification} was solved from the obtained trajectories (figures \eqref{AOB no noise} and \eqref{NOB no noise}) and controls, with no bounds on the parameters.
-The difference between the control and the fit is expressed in Figure \ref{Difference fit}.
-Considering that the control is contained in $[0,1]$, the error of fit is below 5 \% almost everywhere through the trajectory.
 
@@
 	\label{Control NOB no noise}
-\end{figure}
-
-\clearpage
-
-The original interaction matrix and the fitted interaction matrix can be seen and compared in figure \eqref{Comparison Interaction Matrices}.
-It can be seen that the new matrix is very different from the original one, in both order of magnitude and sign.
-Implying that the model is probably not identifiable.
-The system was simulated again with the new matrix, and one can see that in general terms it captures the outcome of the system as shown in figures \ref{AOB LV simulation}, \ref{NOB LV simulation}, and \ref{Metabolites LV simulation}.
-The final and central message of this section is that if the interaction function is of the form $1+Ax$, one could be able to get a good fit from the data with the method here presented.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_AOB_Iter_5_LV}
-	\caption{AOB trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
-	\label{AOB LV simulation}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_NOB_Iter_5_LV}
-	\caption{NOB trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
-	\label{NOB LV simulation}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_metabolites_Iter_5_LV}
-	\caption{Metabolites trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
-	\label{Metabolites LV simulation}
 \end{figure}
@@
 
-Then the procedure from the proof of concept section was applied and one can see that a gLV model is far from describing the pronounced control changes.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width= 0.4\textwidth]{260919_Try1_metabolites_Iter_110_LV}
-	\caption{Simulation obtained for the interaction function $I(x) = 1 + Ax$, where $A$ was fitted with the obtained controls from figures \ref{AOB_control} and \ref{NOB_control}.}
-	\label{LV_fit}
-\end{figure}
 \clearpage

### 2019-12-17 tex/Tracking.tex
changed case for proof of concept

@@
 
-\title{A general model of microbial interactions in a chemostat}
-
+\title{Interactions in a chemostat as the driver of an ecosystem.}
+%% \title{Correcting/Improving chemostat models from microbial interactions}
+%% Including microbial ecology in a chemostat model: tracking microbial interactions
+%% 
+%% Extending a chemostat model 
 %% use optional labels to link authors explicitly to addresses:
@@
 
-\author{Pablo Ugalde-Salas, Jérôme Harmand, Elie Desmond Le-Quemener, Héctor Ramirez}
+\author{Pablo Ugalde-Salas, Jérôme Harmand, Elie Desmond Le-Quéméner, Héctor Ramirez}
 
@@
 The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented.
-The method revisits the data used for the first model presented and proposes a way to calibrate and discriminate for a class of growth kinetics.
+The method revisits the data used for the first model presented.
 \end{abstract}
@@
 The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species, it is solved via state-dependent ricatti equations \cite{Cimen2008}.
-Finally the obtained optimal trajectory and control are used in a static optimization problem in order to estimate the parameters of a specific interaction function.
-
-In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of \cite{Dumont2016}.
-The article ends with a discussion on the use of gLV models, the scope of applicability of the method, and its shortcomings.
+
+In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 2\cite{Dumont2016}.
+The article ends with a discussion on the scope of applicability of the method and further development.
 
@@
 \dot{s_3} = 0 = -s_3D \\
-\Rightarrow s_3 = 0;
+\Rightarrow s_3 = 0
 \end{align}
@@
 The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
-The quadratic increase of parameters with the number of OTU considered makes it difficult to accurately calibrate the model.
-Parameter estimation in A classic way to approach this is by a least square approach, however Some methods for parameter estimation and uncertainty in biochemical systems of ODE can be seen in Vanlier \textit{et al.} \cite{Vanlier2013} and even a "robust approach" is proposed for biological systems by Gabor \textit{et al.} \cite{Gabor2015}, however parameter estimation in ODE is still an open problem.
-In the next section, a generalization of the former model, and a schema for parameter estimation where the uncertainty lies in the growth function is presented as well.
 
@@
 For this model $g(x,s) = x$, since we are observing measurements coming from genetic sequencing.
-Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively.
+Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively, and a positive real $a$.
 The optimal tracking problem is defined as:
@@
 (x,s_1,s_2,s_3)\mbox{ solution of \eqref{Controlsystem}} \\
-&u_i(t) \in [0,1]
+&u_i(t) \in [0,a]
 \end{array}	
@@
 Nevertheless, the methods of Cimen \textit{et al.}\cite{Cimen2004} were directly used with an explicit constraint in the synthesis of the control.
-Even though this is probably suboptimal it worked fairly well.
+Even though this is probably suboptimal when the control reaches its bounds, one at least is certain of its optimality when the control never activates its constraints.
 
@@
 
-The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the appendix section. This in turn implies $v_i(t) \in [-1,0]$.
+The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the appendix section. This in turn implies $v_i(t) \in [-1,a-1]$.
 
@@
 The approach was tested against synthetic data.
-The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2} (therefore $I(x) = 1 + Ax$) for $n_1 = 10$ and $n_2 = 5$.
-In all figures, dotted lines represent the synthetic data, while the continuous lines represent the method's output.
+The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2} (therefore $I(x) = 1 + Ax$) for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}.
+In all figures, asterisks represent the synthetic data, while the continuous lines represent the method's output.
 
@@
 $Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear.
-In the simulations here presented $Q = I_n$ and $R = \begin{bmatrix}
-10^{-4}I_{n_1} & 0 \\ 0 & 10^{-5}I_{n_2}
-\end{bmatrix}$, found by trial and error in order for the control to fit accurately the species abundance, instead of the control approaching 1.
-The rational behind choosing a smaller value for the group $G_2$ is related to the one order of magnitude difference in yields between $G_1$ and $G_2$.
+In the simulations here presented $Q = I_n$ and $R = \lambda I_n$.
+$\lambda$ is varied from $10^{-1}$ to $10^{-7}$ in the supplementary material section.
+The case $\lambda = 0.4$ is shown in here for discussion.
 
@@
 	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
-	\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}.}
-	\label{Comparison Interaction Matrices}
+	\caption{Interaction Matrix of the synthetic data.}
+	\label{Interaction Matrix Simulation}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_Biomass_Iter_5}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Biomass_Iter_10}
 	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_AOB_Iter_5}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_AOB_Iter_10}
 	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_NOB_Iter_5}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_NOB_Iter_10}
 	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_metabolites_Iter_5}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_metabolites_Iter_10}
 	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_Control_AOB_Iter_5}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Control_AOB_Iter_10}
 	\caption{Control for the AOB population.}
@@
 \end{figure}
+
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_Control_NOB_Iter_5}
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Control_NOB_Iter_10}
 	\caption{Control for the NOB population.}
@@
 Considering the success of mass balance models to predict and pilot bioreactors, one should build upon these existing models.
-This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, and observing what would that imply in the chemical species involved.
+This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, and observing what would that imply according to the (pseudo)stoichiometric equations involved.
 If one already posses a model for describing a particular bioprocess the use of the techniques here presented can be applied in a straightforward manner if one has already identified the microbial species involved with a particular functionality of the system.
@@
 If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model actually becomes a linear model and one recovers a classic quadratic regulator for linear systems.
-Nevertheless the synthesis of the optimal bounded control remains an open theoretical challenge.
-
-The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.
+Nevertheless, even in the former case, the synthesis of the optimal bounded control remains an open theoretical challenge.
+
+The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the partial conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.
 Furthermore from the proof of concept section, one might conjecture that models with a large number of parameters such as an gLV model may be unidentifiable, thus proving to be a real problem in calibration, and therefore of reduced applicability.
@@
 Alternative hypothesis for explaining the observed patterns in the microbial community should be considered as well.
+
+Discussion on how to use the method for calibration.
 

### 2019-12-18 Tracking/tracking_control.m
augmented the threshold for the contrl

@@ -1,5 +1,5 @@
 function v = tracking_control(lambda,B,P,X,sF,n)
 B1_vec = diag(B(1:n,:));
 x_trunc = X(1:n);
-v = max(-1,min(-1./lambda.*B1_vec.*(P.*x_trunc - sF),0.2));
+v = max(-1,min(-1./lambda.*B1_vec.*(P.*x_trunc - sF),0.5));
 end

### 2019-12-18 Tracking/compare_control.m
compare_control file

@@ -1,0 +1,44 @@
+clear
+close all
+file_names = {'191210_no_noise_Iter_10', '191210_no_noise_2_Iter_10',...
+    '191210_no_noise_3_Iter_10','191209_no_noise_Iter_10',...
+    '191209_no_noise_try2_Iter_10','191209_no_noise_try2_Iter_10'};
+name_plot_out = 'Comparison_different_control';
+figure
+index_show_OTU = [6 14];
+n_show_OTU = length(index_show_OTU);
+number_files = length(file_names);
+legend_tags_compare = cell((number_files+1)*n_show_OTU,1);
+lw = linspace(0.5,3,length(file_names));
+index_tags_control = reshape(1:(number_files+1)*n_show_OTU,n_show_OTU,(number_files+1));
+hold on
+for k=1:number_files
+    file_in = file_names{k};
+    load(sprintf('MAT_files/%s',file_in));
+    colors = mat2cell(hsv(n_show_OTU),ones(1,n_show_OTU),3);
+    index_control = 1:length(t_new);
+    t_used = t_new(index_control);
+    for k2 = 1:n_show_OTU
+        legend_tags_compare{index_tags_control(k2,k)} = sprintf('u_{%.0f} \\lambda = %.1g',index_show_OTU(k2),lambda(1));
+    end
+    control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
+    control_eval = arrayfun(control,t_used,'UniformOutput',false);
+    control_matrix = 1+(reshape(cell2mat(control_eval),n,length(index_control)));
+    p = plot(t_used,control_matrix(index_show_OTU,:),'--','LineWidth',lw(k));
+    set(p,{'Color'},colors)
+end
+   for k2 = 1:n_show_OTU
+        legend_tags_compare{index_tags_control(k2,number_files+1)} = sprintf('I_{%.0f}(x(t))',index_show_OTU(k2));
+    end
+    A_X_data_trajectories = A*Y(:,1:n)';
+    p = plot(t_obs,1+A_X_data_trajectories(index_show_OTU,:),'*');
+    legend(legend_tags_compare,'fontsize',12,'Location','bestoutside');
+    set(p,{'Color'},colors)
+    set(gca,'fontsize',15)
+    xlabel('\fontsize{15}Time [days]'),...
+    ylabel('\fontsize{15}  Control'),...
[…]

### 2019-12-19 Tracking/main.m
added save 0 iterarion

@@ -54,6 +54,8 @@ dynamic = @(t,X) Ax(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,s_in_interp(t),...
     d_interp(t))*X ;
 options = odeset('NonNegative',(1:n+3)');
 [t_new,x_new] = ode15s(dynamic,[t0 tF], x0,options);
+iter = 0;
+save(sprintf('MAT_files\\%s_iter_%.0f',name_file,iter))
 x_fun = @(t) interp1(t_new,x_new,t)';
 B = @(t) Bx(x_fun(t),nA,nB,kA,kB,muA,muB,kSA,kSB,kI);
 PtF = F;
@@ -81,7 +83,7 @@ x_cell = arrayfun(x_fun,t_new,'UniformOutput',false);
 X = reshape(cell2mat(x_cell),length(t_new),n+3);
 x_old = X;
 csTolerance = 0.5; %cauchy sequence tolerance
-iter = 1;
+iter = iter+1;
 difference = norm(x_old - x_new,'fro'); %L2 norm
 disp(difference)
 save(sprintf('MAT_files\\%s_iter_%.0f',name_file,iter))

### 2019-12-19 tex/Tracking.tex
changed images and add bib file

@@
 	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
-	\item $s$:  vector $(s_1,s_2,s_3)$.
+	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites, or chemical species.
 	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
@@
 
-\subsection{Reconstructing the Interaction Function}
+\subsection{Unravelling the Interaction Function}
 
@@
 By using experimental measurements of $x$, represented by $z(t)$, the objective is to reconstruct function $I(x)$.
-For doing so, the terms $I_i(x)$ are replaced by a control $u_i(t)$  and a state feedback is obtained by solving a nonlinear optimal tracking problem.
+For doing so, the terms $I_i(x)$ are replaced by controls $u_i(t)$, thus $I_i(x(t)) = u_i(t)$,  and a state feedback is obtained by solving a nonlinear optimal tracking problem.
 
@@
 $\lambda$ is varied from $10^{-1}$ to $10^{-7}$ in the supplementary material section.
-The case $\lambda = 0.4$ is shown in here for discussion.
+The case $\lambda = 10^{-4}$ is shown in here for discussion.
 
@@
 It can be seen that the method approaches well the trajectories.
-The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated data as well.
+The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements.
 \begin{figure}[h]
@@
 Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.
+It should be noted as well that since the synthesized control is not saturated (i.e.
+it does not reach the imposed bounds) it is optimal.
 
@@
 	\label{Control NOB no noise}
+\end{figure}
+
+In figure \ref{Comparison_lambda} the different controls obtained by varying $\lambda$ for two species are compared to the interaction function simulated that is $1+A(x(t))$, where $x(t)$ is the synthetic data.
+One can see that due to this property of the end value becoming 1, the two do not coincide, however, when $\lambda$ is decreased one can see that the control roughly approaches the respective interaction function at the cost of very sharp changes.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//Comparison_different_control}
+	\caption{Obtained controled for different $\lambda$ for two OTU and the interaction function used in the simulation of synthetic data.}
+	\label{Comparison_lambda}
 \end{figure}
@@
 For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e.
-$v(t)= 0$) in  Figure \ref{NoControlSimulation}.
+$u(t)= 1$) in  Figure \ref{u=1_metabolites}.
 $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
+The community dynamics is neither captured by this simulation as seen in figures \ref{u=1_AOB} and \ref{u=1_NOB}.
 
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Prediction_No_Control_metabolites}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_metabolites_Iter_0}
 	\caption{Simulation when $u=1$. }
-	\label{NoControlSimulation}
+	\label{u=1_metabolites}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_AOB_Iter_0}
+	\caption{Simulation when $u=1$. }
+	\label{u=1_AOB}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
+	\caption{Simulation when $u=1$. }
+	\label{u=1_NOB}
 \end{figure}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_metabolites_Iter_10}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_metabolites_Iter_45}
 	\caption{Simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_AOB_Iter_10}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_AOB_Iter_45}
 	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_NOB_Iter_10}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_45}
 	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_AOB_Iter_10}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_AOB_Iter_45}
 	\caption{Control obtained for OTU in $G_1$ (AOB).}
 	\label{AOB_control}
-	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_NOB_Iter_10}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_NOB_Iter_45}
 	\caption{Control obtained for OTU in $G_2$ (NOB).}
@@
 The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
-
+It is not then possible to reconstruct the original interaction matrix in the current form of the optimal control problem, thus suggesting to take the derivative of the control in the cost function, instead of the control itself.
 The interpretation of the correction term as interactions is not the only possible reading.
@@
 They were solved using standard backward numerical integration.
+
 \section{References}

### 2019-12-19 Tracking/plot_data_fit.m
divided OTU in multiple graphs

@@ -37,44 +37,69 @@ legend(legend_tags_biomass,'fontsize',12);
 fig.PaperUnits = 'inches';
 fig.PaperPosition = [0 0 9 3];
 fig.PaperPositionMode = 'auto';
-print(sprintf('Images\\%s',sprintf('%s_Biomass_Iter_%.0f',...
+print(sprintf('Images\\%s',sprintf('%s_Biomass_iter_%.0f',...
     name_file,iter)),'-dpng','-r0')
 %%AOB
-figure
-hold on
-AOB_plot = plot(t_new,x_new(:,1:nA),'LineWidth',1.5);
-AOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,1:nA),'*','LineWidth',0.7);
-xlabel('\fontsize{15}Time [days]'),...
-    ylabel('\fontsize{15}  Concentration [g/l]'),...
-    title(sprintf('Tracking results AOB iteration:%.0f',iter));
-%     title(sprintf('Simulation v(t) = -1'));
-set(gca,'fontsize',15),
-set(AOB_plot,{'Color'}, colors_AOB)
-set(AOB_data_plot,{'Color'}, colors_AOB) 
-legend(legend_tags_AOB,'fontsize',10,'Location','bestoutside');
-fig.PaperUnits = 'inches';
-fig.PaperPosition = [0 0 9 3];
-fig.PaperPositionMode = 'auto';
-print(sprintf('Images\\%s',sprintf('%s_AOB_Iter_%.0f',...
-    name_file,iter)),'-dpng','-r0')
+number_of_AOB_plots = floor(nA/10) + logical(rem(nA,10));
+for k = 1:number_of_AOB_plots
+    OTU_plot_index = (10*(k-1)+1):(10*(k-1)+10);
+    if k == number_of_AOB_plots && logical(rem(nA,10)) == 1;
+        OTU_plot_index = (10*(k-1)+1):(10*(k-1)+rem(nA,10));
+    end
+    numbering_AOB = strsplit(num2str(OTU_plot_index)) ;
+    legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_AOB{:}),...
+    sprintf(',OTU %s (data)', numbering_AOB{:})),',');
+    colors_AOB =  mat2cell(hsv(length(OTU_plot_index)),...
+        ones(1,length(OTU_plot_index)), 3);
+    figure
+    hold on
[…]

### 2019-12-19 Tracking/plot_data_fit.m
modified multiple plots for same guild

@@ -1,28 +1,19 @@
 %plotting
 clear
 close all
-name_file_in = 'MAT_Files\\191211_no_noise_iter_10';
+name_file_in = 'MAT_Files\\191218_Reactor_A_iter_45';
 load(name_file_in);
-numbering_AOB = strsplit(num2str(1:nA)) ;
-legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_AOB{:}),...
-    sprintf(',OTU %s (data)', numbering_AOB{:})),',');
-numbering_NOB = strsplit(num2str(nA+1:n)) ;
-legend_tags_NOB = strsplit(strcat(sprintf('OTU %s (tracking),', numbering_NOB{:}),...
-    sprintf(',OTU %s (data)', numbering_NOB{:})),',');
 legend_tags_biomass{1} = 'Data: Sum of species biomass';
 legend_tags_biomass{2} = 'Tracking: Sum of species biomass';
-legend_tags_AOB_control = strsplit(sprintf('Control OTU %s,', numbering_AOB{:}),',');
-legend_tags_AOB_control(end) = [];
-legend_tags_NOB_control = strsplit(sprintf('Control OTU %s,', numbering_NOB{:}),',');
-legend_tags_NOB_control(end) = [];
-colors_OTU = mat2cell([autumn(nA); winter(nB)], ones(1,n), 3);
-colors_AOB = mat2cell(autumn(nA), ones(1,nA), 3);
-colors_NOB = mat2cell(winter(nB), ones(1,nB), 3);
-colors2 = mat2cell(hsv(3), ones(1,3),3);
-% xFun = @(t) interp1(tNew,xNew,t)';    
-% control = @(t) trackingControl(lambda,B(t),P(t),xFun(t),sfInterpol(t),n);
-% controlEval = arrayfun(control,tNew,'UniformOutput',false);
 index_t_OTU = find(t_OTU<max(tS) & t_OTU>min(tS));
+%%Control
+x_fun = @(t) interp1(t_new,x_new,t)';
+B = @(t) Bx(x_fun(t),nA,nB,kA,kB,muA,muB,kSA,kSB,kI);
+control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
+tic
+control_eval = arrayfun(control,t_new,'UniformOutput',false);
+toc
+control_eval_reshape = reshape(cell2mat(control_eval),n,length(t_new));
 %%Total Biomass
 figure
[…]

### 2019-12-19 Tracking/plot_data_fit.m
bug fix

@@ -22,7 +22,6 @@ total_biomass_plot2 = plot(t_new,sum(x_new(:,1:n),2),'k.-','LineWidth',1.5);
 xlabel('\fontsize{15}Time [days]'),...
     ylabel('\fontsize{15}  Concentration [g/l]'),...
     title(sprintf('Tracking results total biomass iteration:%.0f',iter));
-%     title(sprintf('Simulation v(t) = -1'));
 set(gca,'fontsize',15),
 legend(legend_tags_biomass,'fontsize',12);
 fig.PaperUnits = 'inches';
@@ -73,7 +72,7 @@ for k = 1:number_of_AOB_plots
     fig.PaperPosition = [0 0 9 3];
     fig.PaperPositionMode = 'auto';
     print(sprintf('Images\\%s',sprintf('%s_Control_AOB_iter_%.0f_plot_%.0f',...
-        name_file,iter)),'-dpng','-r0')
+        name_file,iter,k)),'-dpng','-r0')
 end
 %%NOB
 number_of_NOB_plots = floor(nB/10) + logical(rem(nB,10));
@@ -119,8 +118,8 @@ for k = 1:number_of_NOB_plots
     fig.PaperUnits = 'inches';
     fig.PaperPosition = [0 0 9 3];
     fig.PaperPositionMode = 'auto';
-    print(sprintf('Images\\%s',sprintf('%s_Control_AOB_iter_%.0f_plot_%.0f',...
-        name_file,iter)),'-dpng','-r0')
+    print(sprintf('Images\\%s',sprintf('%s_Control_NOB_iter_%.0f_plot_%.0f',...
+        name_file,iter,k)),'-dpng','-r0')
 end
 %%Metabolites
 figure

### 2019-12-19 Tracking/plot_data_fit.m
bug fix

@@ -57,7 +57,7 @@ for k = 1:number_of_AOB_plots
     fig.PaperPositionMode = 'auto';
     print(sprintf('Images\\%s',sprintf('%s_AOB_iter_%.0f_plot_%.0f',...
         name_file,iter,k)),'-dpng','-r0')
-    %Control
+%%Control
     legend_tags_AOB_control = strsplit(sprintf('Control OTU %s,', numbering_AOB{:}),',');
     legend_tags_AOB_control(end) = [];
     figure
@@ -93,8 +93,7 @@ for k = 1:number_of_NOB_plots
     NOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,OTU_plot_index),'*','LineWidth',0.7);
     xlabel('\fontsize{15}Time [days]'),...
         ylabel('\fontsize{15}  Concentration [g/l]'),...
-        title(sprintf('Tracking results AOB iteration:%.0f',iter));
-    %     title(sprintf('Simulation v(t) = -1'));
+        title(sprintf('Tracking results NOB iteration:%.0f',iter));
     set(gca,'fontsize',15),
     set(NOB_plot,{'Color'}, colors_NOB)
     set(NOB_data_plot,{'Color'}, colors_NOB)
@@ -104,14 +103,14 @@ for k = 1:number_of_NOB_plots
     fig.PaperPositionMode = 'auto';
     print(sprintf('Images\\%s',sprintf('%s_NOB_iter_%.0f_plot_%.0f',...
         name_file,iter,k)),'-dpng','-r0')
-        %Control
+%%Control
     legend_tags_NOB_control = strsplit(sprintf('Control OTU %s,', numbering_NOB{:}),',');
     legend_tags_NOB_control(end) = [];
     figure
     control_plot_NOB = plot(t_new,control_eval_reshape(OTU_plot_index,:)+1,'LineWidth',1.5);
     xlabel('\fontsize{12}Time [days]'),...
         ylabel('\fontsize{12}  u(t)'),...
-        title(sprintf('Control for AOB iter: %.0f',iter))
+        title(sprintf('Control for NOB iter: %.0f',iter))
     set(gca,'fontsize',15),
     set(control_plot_NOB,{'Color'}, colors_NOB),
     legend(legend_tags_NOB_control,'fontsize',10,'Location','bestoutside');
[…]

### 2019-12-19 tex/Tracking.tex
multiple graphs for AOB

@@
 One can see that due to this property of the end value becoming 1, the two do not coincide, however, when $\lambda$ is decreased one can see that the control roughly approaches the respective interaction function at the cost of very sharp changes.
+
 \begin{figure}[h]
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_metabolites_Iter_0}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width= \textwidth]{Application//191218_Reactor_A_metabolites_Iter_0}
 	\caption{Simulation when $u=1$. }
 	\label{u=1_metabolites}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_AOB_Iter_0}
-	\caption{Simulation when $u=1$. }
-	\label{u=1_AOB}
-\end{figure}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width=\textwidth]{Application//191218_Reactor_A_Biomass_iter_0}
+	\label{biomass_no_control}
+	\end{subfigure}
+\end{figure}
+
 \begin{figure}[h]
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_metabolites_Iter_45}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width=\textwidth]{Application//191218_Reactor_A_metabolites_Iter_45}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width=\textwidth]{Application//191218_Reactor_A_Biomass_Iter_45}
+	\end{subfigure}
 	\caption{Simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_AOB_Iter_45}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_1}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_2}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_3}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_4}
+	\end{subfigure}
 	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_45}
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_iter_45_plot_1}
 	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
@@
 Both controls saturate at certain points, but in general terms they vary throughout the dynamic.
+At this point one can not be sure that the control is indeed optimal.
+Also note that when compared to the shape of controls obtained in the proof of concept section one might hypothesize that a gLV model can not capture the dynamic of the system.
 
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_AOB_Iter_45}
-	\caption{Control obtained for OTU in $G_1$ (AOB).}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_1}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_2}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_3}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_4}
+	\end{subfigure}
+	\caption{Control obtained of $G_1$ (AOB).}
 	\label{AOB_control}
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_NOB_Iter_45}
-	\caption{Control obtained for OTU in $G_2$ (NOB).}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_NOB_iter_45_plot_1}
+	\caption{Control obtained of $G_2$ (NOB).}
 	\label{NOB_control}
@@
 
-The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the partial conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.
-Furthermore from the proof of concept section, one might conjecture that models with a large number of parameters such as an gLV model may be unidentifiable, thus proving to be a real problem in calibration, and therefore of reduced applicability.
-Furthermore the ecological interpretations to be drawn from the sign of the interaction matrix might be useless.
+The interaction function introduced tries to address the issue of prediction from the genetic sequencing.
+The analysis of the gLV model proposed by \cite{Dumont2016}.
+From the application section one can retain the hypothesis that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.
 This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems.
@@
 It is not then possible to reconstruct the original interaction matrix in the current form of the optimal control problem, thus suggesting to take the derivative of the control in the cost function, instead of the control itself.
+
 The interpretation of the correction term as interactions is not the only possible reading.

### 2020-01-09 tex/Tracking.tex
Last changes, version sent for internal revision.

@@
 
-\title{Interactions in a chemostat as the driver of an ecosystem.}
+\title{Microbial interactions as drivers of a chemostat ecosystem}
 %% \title{Correcting/Improving chemostat models from microbial interactions}
@@
 The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented.
-The method revisits the data used for the first model presented.
+The method revisits the experimental data used for the first model.
 \end{abstract}
@@
 The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time.
-This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.
+This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.
 
@@
 In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 2\cite{Dumont2016}.
-The article ends with a discussion on the scope of applicability of the method and further development.
+The method shows that by following the community dynamics one can reconstruct the dynamics of the chemical species.
+The article ends with a discussion on the scope of applicability of the method and perspectives.
 
@@
 
-Notations used throughout the article are:
+Notations used throughout the article:
 \begin{enumerate}
@@
 	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
-	\item $D$: Dilution Rate of the continuous reactor in $[1/day]$. 
-	\item $y_i$: Yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
+	\item $D$: dilution rate of the continuous reactor in $[1/day]$. 
+	\item $y_i$: yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
 	\item $y$: vector $y_1,\dots,y_n$.
-	\item $k_i$: Yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
+	\item $k_i$: yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
 	\item $k$: vector $k_1,\dots,k_n$.
@@
 
-Observe that equilibrium points are by definition non-negative so the state variables can have biological meaning. Details of the calculations are given in the appendix.
+Observe that equilibrium points are by definition non-negative so the state variables can have physical meaning. Details of the calculations are given in the appendix.
 
@@
 	\end{pmatrix}
-	\end{array}
+	\end{array} \label{diag_operator}
 	\end{align}
@@
 
-The former function places a vector $v$ in the diagonal of a matrix. Recalling $A$ the matrix with coefficients $a_{ij}$. The following notation is introduced.
+Function \eqref{diag_operator} places a vector $v$ in the diagonal of a matrix. Recalling $A$ the matrix with coefficients $a_{ij}$. The following notation is introduced.
 
@@
 
-Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in the appendix.
+Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
 
@@
 The resulting matrix's eigenvalues must have negative real part.
-A general formula for this Jacobian is presented in the appendix.
+A general formula for this Jacobian is presented in the supplementary material.
 
@@
 
-The operating diagram from one of the sets of the parameter identification from Dumont et al.
-is presented in figure \ref{OD Dumont} from a Bayesian estimation method.
-Two species per functional group were considered.
+The operating diagram from one of the sets of the parameter identification (obtained with a Bayesian estimation method) from Dumont et al.
+is presented in figure \ref{OD Dumont}.
+Their fit describes well the dynamics of the OTU, which is not the case for measured chemical species.
+Two OTU per functional group were considered.
 One can see that coexistence in the same functional group is never attained.
@@
 Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Modified}.
-The different zones represent the surviving species in the steady state.
+The 8 different zones represent the surviving species in the steady state.
 PN takes place when neither $x_3$ nor $x_4$ are present.
@@
 The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
+Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments,
 
@@
 $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
-The community dynamics is neither captured by this simulation as seen in figures \ref{u=1_AOB} and \ref{u=1_NOB}.
+The community dynamics is neither captured by this simulation as seen in figure \ref{u=1_NOB} where the NOB community is shown.
 
@@
 \end{figure}
-
+\pagebreak
 When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}.
-The method captures the tendencies in the measured substrates, but not their absolute values.
+The method captures the tendencies in the measured substrates.
 The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively.
@@
 However the technique could be used in contexts where less information on the growth function of microbes is known.
-If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model actually becomes a linear model and one recovers a classic quadratic regulator for linear systems.
+If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model becomes a linear model and one recovers a classic quadratic regulator for linear systems.
 Nevertheless, even in the former case, the synthesis of the optimal bounded control remains an open theoretical challenge.
 
-The interaction function introduced tries to address the issue of prediction from the genetic sequencing.
-The analysis of the gLV model proposed by \cite{Dumont2016}.
-From the application section one can retain the hypothesis that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed.
+The interaction function introduced tries to address the issue of prediction from genetic sequencing.
+The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows a new mechanism by which the CEP may not hold, however we conjecture that the system seems to have only one positive stable equilibrium.
+From the application section one can see that by correcting the growth rate one is able to recuperate the chemical species dynamics, implying that interactions are driving the system.
+The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model can not capture the complexity of the particular chemostat analysed.
 This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems.
 The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
-It is not then possible to reconstruct the original interaction matrix in the current form of the optimal control problem, thus suggesting to take the derivative of the control in the cost function, instead of the control itself.
 
@@
 
-Discussion on how to use the method for calibration.
+One of the next steps in this line of research would be to synthesize a control that is able to reconstruct interactions functions, and not just the dynamics of the species as is the case presented.
+One might bypass the end point issue of the current control scheme, by, for example, taking the derivative of the control in the cost function, instead of the control itself, or alternatively by eliminating the control cost and making a very thorough use of the pontryagin maximum principle and the switch function for the synthesis of the controls.
 
@@
 \section{Acknowledgements}
- The authors would like to thank Alain Rapaport for the fruitful exchanges. This work was financed by grant Thermomic. And a sejour
-
-\section{Appendix}
+ The authors would like to thank Alain Rapaport for the fruitful exchanges. This work was financed by project Thermomic ANR-16-CE04-0003.
+
+\section{Supplementary Material}
 
@@
 \begin{align}
-\dot{\tilde{P}}^{[i]}(t)= -Q- \tilde{P}^{[i]}A_{11} -A_{11}^\top \tilde{P}^{[i]} + \dfrac{1}{\lambda} \tilde{P}^{[i]}B_1B_1^\top \tilde{P}^{[i]} \\
+\dot{\tilde{P}}^{[i]}(t)= -Q- \tilde{P}^{[i]}A_{11} -A_{11}^\top \tilde{P}^{[i]} +  \tilde{P}^{[i]}B_1R^{-1}B_1^\top \tilde{P}^{[i]} \\
 \tilde{P}^{[i]}(t_f) = 0
@@
 
-Inspecting the former equation one notices that if $i\neq j$, $P_{ij}(t) = 0$ is a solution of all non diagonal entries.
+Inspecting the former equation one notices that if $i\neq j$, $P_{ij}(t) = 0$ is a solution of all non diagonal entries when $R$ is diagonal.
 And therefore by existence and uniqueness they should be constantly zero.
@@
 \begin{align}
-\dot{\tilde{P}}^{[i]}_{jj}(t)= -Q_{jj}- 2 \left(f_j\left(s^{[i-1]}\right)- D \right)\tilde{P}^{[i]}_{jj} + \dfrac{1}{\lambda}\left(\tilde{P}^{[i]}_{jj}\right)^2f_j\left(s^{[i-1]}\right)^2\left(x^{[i-1]}_j\right)^2  \\
+\dot{\tilde{P}}^{[i]}_{jj}(t)= -Q_{jj}- 2 \left(f_j\left(s^{[i-1]}\right)- D \right)\tilde{P}^{[i]}_{jj} + R^{-1}\left(\tilde{P}^{[i]}_{jj}\right)^2f_j\left(s^{[i-1]}\right)^2\left(x^{[i-1]}_j\right)^2  \\
 \tilde{P}^{[i]}_{jj}(t_f) = 0
@@
 \begin{align}
-\dot{\tilde{s}}_f^{[i]}(t) &= -z(t)- \left[A_{11} -\frac{1}{\lambda}B_1B_1^\top \tilde{P}^{[i]}(t) \right]^\top \tilde{s}_f^{[i]} \\
+\dot{\tilde{s}}_f^{[i]}(t) &= -z(t)- \left[A_{11} -R^{-1}B_1B_1^\top \tilde{P}^{[i]}(t) \right]^\top \tilde{s}_f^{[i]} \\
 \tilde{s}_f^{[i]}(t_f) &= 0
@@
 \begin{align}
-v^{[i]}(t)_j = \max \left\{ -1,\min\left\{0,\left( -\dfrac{1}{\lambda}B_1^\top\left(X^{[i-1]}(t)\right)\left(\tilde{P}^{[i]}(t)x^{[i]}(t)-\tilde{s}_f^{[i]}(t)\right)\right)_j \right\}\right\} \forall j \in [n]
+v^{[i]}(t)_j = \max \left\{ -1,\min\left\{0,\left( -R^{-1}B_1^\top\left(X^{[i-1]}(t)\right)\left(\tilde{P}^{[i]}(t)x^{[i]}(t)-\tilde{s}_f^{[i]}(t)\right)\right)_j \right\}\right\} \forall j \in [n]
 \end{align}
@@
 They were solved using standard backward numerical integration.
+\subsection{Simulations proof of concept}
+\textbf{$\lambda = 10^{-1}$}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Biomass_iter_10}
+	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{Total Biomass no noise e1}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_AOB_iter_10_plot_1}
+	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{AOB no noise e1}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_NOB_iter_10_plot_1}
+	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{NOB no noise e1}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_metabolites_iter_10}
+	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{Metabolites no noise e1}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_AOB_iter_10_plot_1}
+	\caption{Control for the AOB population.}
+	\label{Control AOB no noise e1}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_NOB_iter_10_plot_1}
+	\caption{Control for the NOB population.}
+	\label{Control NOB no noise e1}
+\end{figure}
+\clearpage
+\textbf{$\lambda = 10^{-2}$}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Biomass_iter_10}
+	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{Total Biomass no noise e2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_AOB_iter_10_plot_1}
+	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{AOB no noise e2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_NOB_iter_10_plot_1}
+	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{NOB no noise e2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_metabolites_iter_10}
+	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\label{Metabolites no noise e2}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_AOB_iter_10_plot_1}
+	\caption{Control for the AOB population.}
+	\label{Control AOB no noise e2}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_NOB_iter_10_plot_1}
+	\caption{Control for the NOB population.}
+	\label{Control NOB no noise e2}
+\end{figure}
+
+\clearpage
 

### 2020-01-09 Tracking/analize_results_synthetic_data.m
some auxiliary files for tracking development

@@ -1,0 +1,30 @@
+clear
+close all
+file_in = '191211_no_noise_iter_10';
+load(sprintf('MAT_files/%s',file_in));
+index_control = 1:length(t_new);
+t_used = t_new(index_control);
+clear diff
+time_intervals = diff(t_used);
+time_weights_middle = 0.5*time_intervals(2:end) + 0.5*time_intervals(1:end-1);
+time_weight = [time_intervals(1); time_weights_middle; time_intervals(end)];
+colors = mat2cell(hsv(n),ones(1,n),3);
+control = @(t) tracking_control(lambda,B(t),P(t),x_fun(t),sf_interp(t),n);
+control_eval = arrayfun(control,t_used,'UniformOutput',false);
+control_matrix = (reshape(cell2mat(control_eval),n,length(index_control)));
+control_matrix_med_filter = medfilt1(control_matrix',300);
+feed_f = @(t) feed_forward(lambda,B(t),P(t),x_fun(t),n);
+feed_f_eval =  arrayfun(feed_f,t_used,'UniformOutput',false);
+feed_f_matrix = (reshape(cell2mat(feed_f_eval),n,length(index_control)));
+x_trajectories = x_new(index_control,1:n)';
+data_trajectories = Y(:,1:n)';
+figure
+hold on
+p1 = plot(t_used,A*x_trajectories);
+set(p1,{'Color'},colors)
+p2 = plot(t_used,control_matrix,'--');
+set(p2,{'Color'},colors)
+% p3 = plot(t_obs,A*data_trajectories,'*');
+% set(p3,{'Color'},colors)
+p4 = plot(t_used,control_matrix_med_filter,'.');
+set(p4,{'Color'},colors)

### 2020-01-09 Tracking/change_classification.m

@@ -1,0 +1,8 @@
+close all
+clear
+load('MAT_files\Classification_day183_gurobi')
+class_NOB(28) = 0;
+class_AOB(28) = 1;
+yields_NOB(28) = 0;
+yields_AOB(28) = 4.9539;
+save('MAT_files\Classification_day183_gurobi_modified')

### 2020-01-09 Tracking/feed_forward.m

@@ -1,0 +1,5 @@
+function v = feed_forward(lambda,B,P,X,n)
+B1_vec = diag(B(1:n,:));
+x_trunc = X(1:n);
+v = max(-1,min(-1./lambda.*B1_vec.*(P.*x_trunc ),0.2));
+end

### 2020-01-09 Tracking/simulate_no_control.m

@@ -1,0 +1,58 @@
+%Reference: Cimen et al 2002 Nonlinear optimal tracking control
+%main: process and filter data to model.
+close all
+clear
+load('MAT_files\Classification_day_183_315_gurobi')
+name_file = '191218_Reactor_A';
+nA = round(sum(class_AOB));
+nB = round(sum(class_NOB)); 
+n = nA+nB;
+index_t_obs = find(t_obs <315);
+index_span = time_steps_index(1):index_t_obs(end);
+tS = t_obs(index_span); 
+s1_interp = @(t) interp1(tS,S1(index_span),t);
+s2_interp = @(t) interp1(tS,S2(index_span),t);
+s3_interp = @(t) interp1(tS,S3(index_span),t);
+index_AOB = find(class_AOB);
+index_NOB = find(class_NOB);
+biomass_filtered = OTU_interp(:,[index_AOB; index_NOB]);
+min_biomass = min(biomass_filtered(biomass_filtered>0));
+biomass_filtered(biomass_filtered == 0) = min_biomass;
+z = @(t) interp1(t_OTU,biomass_filtered,t)';
+kA = yields_AOB(index_AOB);
+kB = yields_NOB(index_NOB);
+muARef = 0.77;
+muBRef = 1.07;
+kSARef = 0.7e-1;
+kSBRef = 1.4982e-1;
+kIRef = 1.217;
+muA = muARef*ones(nA,1);
+muB = muBRef*ones(nB,1);
+kSA = kSARef*ones(nA,1);
+kSB = kSBRef*ones(nB,1);
+kI = kIRef*ones(nB,1);
+% %%Parameters
+% lambda = 0.001;
+% lambda = [0.001*ones(nA,1); 0.001*ones(nB,1)];
+lambda = ones(n,1)*10^-4;
+Q2= [kA; kB];
+% Q = Q2/norm(Q2,'inf');
+Q = [ones(nA,1); ones(nB,1)];
+% vectorWeight = 1./max(biomass);
+% vectorWeight = [kA; kB].^2;
+% Q = diag(vectorWeight/max(vectorWeight));
+% Q = eye(n);
+F = zeros(n,1);
+colors = mat2cell([autumn(nA); winter(nB)], ones(1,n), 3);
+colors2 = mat2cell(hsv(3), ones(1,3),3);
[…]

### 2020-01-14 tex/Article_Interactions.tex
Test
Test2
Commentaires et corrections

--- 2020-01-09 tex/Tracking.tex
@@
 The classical ecological concept of species and niche in the microbial world is an elusive one: In the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring.
-In the case of bacteria and archea, reproduction goes simply by mitosis and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}.
+In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}.
 Therefore as an ecological problem is hard to precise the 'niche' of 'species'.
 
-These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based in 16sRNA analysis.
-There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria.
+These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of 16S rDNA marker gene.
+There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria\iffalse cette phrase n'est pas claire, on pourrait éventuellement simplement la retirer \fi.
 The abundance of the present OTU allows to account for a group of Bacteria that behave similarly in terms of which substances catabolyzes and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.
@@
 
-The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing technique that can quantify the species abundances through time.
+The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances through time.
 This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.
@@
 However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
-In the latter case CN can be achieved at a more elevated dilution rats than in the former case.
+In the latter case CN can be achieved at a more elevated dilution rate than in the former case.
 Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.
@@
 	\end{subfigure}
-	\caption{Left: interactions of the system.
-Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Dumont}.
+	\caption{Left: interaction matrix associated with model \eqref{system} as estimated in Dumont el al.
+\cite{Dumont2016} for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
+Right: associated operating diagram with parameters in Table \ref{Parameters Dumont}.
 The different zones represent the surviving species in the steady state.
@@
 	\end{subfigure}
-	\caption{Left: interactions of the system.
-Right: operating diagram of Model \eqref{system}, with parameters in Table \ref{Parameters Modified}.
+	\caption{Left: random interaction matrix associated with model \eqref{system} for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
+Right: associated operating diagram with parameters in Table \ref{Parameters Modified}.
 The 8 different zones represent the surviving species in the steady state.
@@
 
-More generally the interaction function is defined. It represents how the growth rate of species $i$ is affected by the concentration of other species, $x$:
+More generally the interaction function represents how the growth rate of species $i$ is affected by the concentration of other species, $x$:
 
@@
 	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
-	\caption{Interaction Matrix of the synthetic data.}
+	\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
 	\label{Interaction Matrix Simulation}
@@
 	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Biomass_Iter_10}
-	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\caption{Dotted line: simulated total biomass for model \eqref{system} with interactions shown in Figure \ref{Interaction Matrix Simulation} and parameters\iffalse quels paramètres ?\fi.
+Continuous line: total biomass as predicted  by the tracking procedure.}
 	\label{Total Biomass no noise}
@@
 	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_AOB_Iter_10}
-	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+	\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
 	\label{AOB no noise}
@@
 
-The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.
+The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.\iffalse Cette phrase devrait figurer dans la partie précédente ?\fi
 
@@
 Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics.
-For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (known as Ammonium oxidizing bacteria AOB) and 5 in the $G_2$ functional group (known as Nitrite oxidizing bacteria NOB).
+For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
 The system state dimension becomes 38.
 
-The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
+The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}\iffalse est-ce que tu donnes les paramètres quelquepart ?\fi.
 Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$.
@@
 When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}.
-The method captures the tendencies in the measured substrates.
+The method captures the tendencies in the measured substrates and products.
 The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively.
@@
 From the application section one can see that by correcting the growth rate one is able to recuperate the chemical species dynamics, implying that interactions are driving the system.
-The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model can not capture the complexity of the particular chemostat analysed.
+The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model such as the gLV model can not capture the complexity of the particular chemostat analysed.
 This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems.

### 2020-01-16 Tracking/Ax.m
Changes for linear filtering.

@@ -2,7 +2,8 @@ function A = Ax(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,sIn,dilution_rate)
 addpath('..//');
 n = nA+ nB;
 % growthRowVector = [growthMonod(X(n+1),muA,kSA)' growthHaldane(X(n+2),muB,kSB,kI)'];
-growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
+% growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
+growth_row_vector = [muA ; muB]';
 A = [diag(growth_row_vector-dilution_rate) zeros(n,3);
     [-kA; zeros(nB,1)]'.*growth_row_vector (sIn/X(n+1) -1)*dilution_rate 0 0; 
     [kA; -kB]'.*growth_row_vector 0 -dilution_rate 0;

### 2020-01-16 Tracking/Bx.m

@@ -2,7 +2,8 @@ function B = Bx(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI)
 addpath('..//');
 n = nA+ nB;
 % growthRowVector = [growthMonod(X(n+1),muA,kSA)' growthHaldane(X(n+2),muB,kSB,kI)'];
-growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
+% growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
+growth_row_vector = [muA ; muB]';
 B = [diag(growth_row_vector.*X(1:n)');
     [-kA; zeros(nB,1)]'.*growth_row_vector.*X(1:n)' ; 
     [kA; -kB]'.*growth_row_vector.*X(1:n)';

### 2020-01-16 Tracking/main.m

@@ -2,8 +2,8 @@
 %main: process and filter data to model.
 close all
 clear
-load('MAT_files\synthetic_data_no_noise')
-name_file = '191211_no_noise';
+load('MAT_files\Classification_day_183_315_gurobi')
+name_file = '200116_day_183_315_gurobi';
 nA = round(sum(class_AOB));
 nB = round(sum(class_NOB)); 
 n = nA+nB;

### 2020-01-16 Tracking/ricatti_diff.m

@@ -1,7 +1,8 @@
 function f = ricatti_diff(Plin,X,Q,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,sIn,dilution_rate,...
     lambda)
 n = nA + nB;
-growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
+% growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
+growth_vector = [muA ; muB];
 x_trunc = X(1:n);
 f = -Q -2.*Plin.*(growth_vector- dilution_rate)...
     + 1./lambda.*Plin.^2.*growth_vector.^2.*x_trunc.^2;

### 2020-01-16 Tracking/sF_diff.m

@@ -1,7 +1,8 @@
 function f = sF_diff(sF,X,z,P,nA,nB,yA,yB,muA,muB,kSA,kSB,kI,sIn,dilutionRate,...
     lambda)
 n = nA + nB;
-growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
+% growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
+growth_vector = [muA ; muB];
 x_trunc = X(1:n);
 f = -z -((growth_vector- dilutionRate) - 1./lambda.*(x_trunc.^2).*growth_vector.^2.*P).*sF;
 end

### 2020-01-16 Tracking/Ax.m
reverting the experiment

@@ -2,8 +2,8 @@ function A = Ax(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,sIn,dilution_rate)
 addpath('..//');
 n = nA+ nB;
 % growthRowVector = [growthMonod(X(n+1),muA,kSA)' growthHaldane(X(n+2),muB,kSB,kI)'];
-% growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
-growth_row_vector = [muA ; muB]';
+growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
+% growth_row_vector = [muA ; muB]';
 A = [diag(growth_row_vector-dilution_rate) zeros(n,3);
     [-kA; zeros(nB,1)]'.*growth_row_vector (sIn/X(n+1) -1)*dilution_rate 0 0; 
     [kA; -kB]'.*growth_row_vector 0 -dilution_rate 0;

### 2020-01-16 Tracking/Bx.m

@@ -2,8 +2,8 @@ function B = Bx(X,nA,nB,kA,kB,muA,muB,kSA,kSB,kI)
 addpath('..//');
 n = nA+ nB;
 % growthRowVector = [growthMonod(X(n+1),muA,kSA)' growthHaldane(X(n+2),muB,kSB,kI)'];
-% growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
-growth_row_vector = [muA ; muB]';
+growth_row_vector = [growth_monod(X(n+1),muA,kSA)' growth_monod(X(n+2),muB,kSB)'];
+% growth_row_vector = [muA ; muB]';
 B = [diag(growth_row_vector.*X(1:n)');
     [-kA; zeros(nB,1)]'.*growth_row_vector.*X(1:n)' ; 
     [kA; -kB]'.*growth_row_vector.*X(1:n)';

### 2020-01-16 Tracking/ricatti_diff.m

@@ -1,8 +1,8 @@
 function f = ricatti_diff(Plin,X,Q,nA,nB,kA,kB,muA,muB,kSA,kSB,kI,sIn,dilution_rate,...
     lambda)
 n = nA + nB;
-% growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
-growth_vector = [muA ; muB];
+growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
+% growth_vector = [muA ; muB];
 x_trunc = X(1:n);
 f = -Q -2.*Plin.*(growth_vector- dilution_rate)...
     + 1./lambda.*Plin.^2.*growth_vector.^2.*x_trunc.^2;

### 2020-01-16 Tracking/sF_diff.m

@@ -1,8 +1,8 @@
 function f = sF_diff(sF,X,z,P,nA,nB,yA,yB,muA,muB,kSA,kSB,kI,sIn,dilutionRate,...
     lambda)
 n = nA + nB;
-% growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
-growth_vector = [muA ; muB];
+growth_vector = [growth_monod(X(n+1),muA,kSA); growth_monod(X(n+2),muB,kSB)];
+% growth_vector = [muA ; muB];
 x_trunc = X(1:n);
 f = -z -((growth_vector- dilutionRate) - 1./lambda.*(x_trunc.^2).*growth_vector.^2.*P).*sF;
 end

### 2020-01-20 tex/Article_Interactions.tex
add changes

@@
 
-\title{Microbial interactions as drivers of a chemostat ecosystem}
+\title{Microbial interactions as drivers of a nitrifying ecosystem in a chemostat}
 %% \title{Correcting/Improving chemostat models from microbial interactions}
@@
 The limitations and the insights of such an approach are discussed.
-The main novelty of this work lies in the second part, where the use of an optimal tracking technique for the integration of genetic sequencing in chemostat models is presented.
-The method revisits the experimental data used for the first model.
+The main novelty of this work lies in the second part, where the use of an optimal tracking technique (developed within the framework of control theory) for the integration of genetic sequencing in chemostat models is presented.
+The method revisits the data used in the aforementioned chemostat setting.
 \end{abstract}
@@
 These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of 16S rDNA marker gene.
-There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria\iffalse cette phrase n'est pas claire, on pourrait éventuellement simplement la retirer \fi.
-The abundance of the present OTU allows to account for a group of Bacteria that behave similarly in terms of which substances catabolyzes and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.
+There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria, and thus their 'function' within a given ecosystem.
+The function of an OTU, from an engineering perspective, is given by which substances are transformed and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.
 
@@
 
-The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances through time.
+The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances over time.
 This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.
@@
 For the identification of the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data.
-The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species, it is solved via state-dependent ricatti equations \cite{Cimen2008}.
+The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species, it is solved via state-dependent Ricatti equations \cite{Cimen2008}.
 
 In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 2\cite{Dumont2016}.
-The method shows that by following the community dynamics one can reconstruct the dynamics of the chemical species.
+The method shows that by following the community dynamics one can reconstruct the dynamics of the chemical substrate.
 The article ends with a discussion on the scope of applicability of the method and perspectives.
@@
 	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
+	\item Let $A$ be a finite set with $m \in \N$ elements. Then $\vert A \vert := m$. 
 \end{enumerate}
@@
 
-The terms $y_i$ are known as yields, it represents the number of grams of biomass produced per gram of substrate consumed.
+The terms $y_i$ are known as yields, they represent the number of grams of biomass produced per gram of substrate consumed for OTU $i$.
 In this work the unit grams of dry biomass per gram of substrate is used for yields.
@@
 
-An example of this process is the nitrification process where group $G_1$ is known as Ammonium oxidizer Bacteria (AOB), and group $G_2$ is known as Nitrite oxidizing Bacteria (NOB) \cite{SHARMA1977897}.
+An example of this process is the nitrification process where group $G_1$ is known as Ammonium oxidizing Bacteria (AOB), and group $G_2$ is known as Nitrite oxidizing Bacteria (NOB) \cite{SHARMA1977897}.
 \subsection{Mass Balance Equations}
 
-Consider the scenario of an continuous and homogeneous reactor: the input flow is the same as the output flow, with a dilution rate of $D$.
+Consider the scenario of an continuous and homogeneous reactor: the input flow is the same as the output flow, with a dilution rate $D$.
 The input flow contains a concentration $s_{in}$ of substrate $s_1$.
@@
 
-The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU. Let $A$ denote the matrix
+The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU, while the term $\bar{\mu}_i\dfrac{s_j}{K_i + s_j}$ represents the substrate limitation \cite{monod1942recherches}.
+Let $A$ denote the matrix
 with entries $a_{ij}$, which will be referred to as the interaction matrix.
@@
 Possible equilibrium points for this system grow exponentially with the number of OTU considered ($n$).
-Stability is not analytically addressed, a numerical scheme calculating every equilibrium point and the system's Jacobian eigenvalues at the equilibrium point were implemented for studying the system.
+Stability is not analytically addressed, a numerical scheme calculating every equilibrium point and the system's Jacobian eigenvalues at the equilibrium point was implemented for studying the system.
 
@@
 \end{align}
-With the above system \eqref{system}, is rewritten in equations \eqref{Eq1}, \eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4}.
+
+with the above system \eqref{system}, is rewritten in equations \eqref{Eq1}, \eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4}.
 
@@
 	\label{StabilityAnalysis}
+	\caption{Algorithm for evaluating the possible equilibrium points of system \eqref{system}.}
 \end{algorithm}
@@
 Operating diagrams are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters.
-Operating diagrams are created by running algorithm \eqref{StabilityAnalysis} for different pairs $(s_{in},D)$ \cite{lobry2017chemostat}.
+Operating diagrams are created by running algorithm \ref{StabilityAnalysis} for different pairs $(s_{in},D)$ \cite{lobry2017chemostat}.
 One then regroups all the pairs such that the set of non-active coordinates of the points of the set $PSP$ are the same and have the same stability properties.
@@
 is presented in figure \ref{OD Dumont}.
-Their fit describes well the dynamics of the OTU, which is not the case for measured chemical species.
+Their fit describes well the dynamics of the OTU, but is not the case for measured substrates.
 Two OTU per functional group were considered.
-One can see that coexistence in the same functional group is never attained.
-However when using a different set of parameters one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
+One can see that coexistence in the same functional group is never attained for one of the parameter set obtained (their method provided several sets of parameters).
+On the contrary, when using a random interaction matrix, and modifying the kinetic coefficients  (note that $x_1$ and $x_3$ have the same $\mu_i$ and $K_i$ in case 1 and 2) one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
 In the latter case CN can be achieved at a more elevated dilution rate than in the former case.
@@
 The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
-However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law is required to include microbial diversity.
+However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law or model structure involving other biological processes is required to include microbial diversity.
 
@@
 It also shows a new mechanism by which the CEP no longer holds.
-The operating diagrams always show a single stable equilibrium point for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
-Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments,
+The operating diagrams always show a single stable equilibrium point- with possible coexistence of all species- for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
+Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a model to study.
 
@@
 
-Note $J_I(x)$ the Jacobian matrix of function $\mathcal{I}$.
-then a first order approximation of $\I(\cdot)$ centred at $\bar{x}$ gives: $\I(x) = \I(\bar{x}) + J_I(\bar{x})(x-\bar{x}) + o(\Vert x- \bar{x} \Vert)$.
+Note $J_I(x)$ the Jacobian matrix of function $\mathcal{I}$, then a first order approximation of $\I(\cdot)$ centred at $\bar{x}$ gives: $\I(x) = \I(\bar{x}) + J_I(\bar{x})(x-\bar{x}) + o(\Vert x- \bar{x} \Vert)$.
 When $\bar{x}= 0$ one recovers the growth expression from the previous section (equations \eqref{gLV growth1} and \eqref{gLV growth2}) implying that $J_I(\bar{0})$ can be seen as the interaction matrix from model \eqref{system}.
@@
 For this model $g(x,s) = x$, since we are observing measurements coming from genetic sequencing.
-Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively, and a positive real $a$.
+Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively, and a positive real $\bar{u}$.
 The optimal tracking problem is defined as:
@@
 (x,s_1,s_2,s_3)\mbox{ solution of \eqref{Controlsystem}} \\
-&u_i(t) \in [0,a]
+&u_i(t) \in [0,\bar{u}]
 \end{array}	
@@
 The term $\lambda \Vert(u -\vec{1}) \Vert_R$, was added for two reasons:
-
-First because the interest is testing the idea that interactions could be driving the system.
+\begin{itemize}
+\item First because the interest is testing the idea that interactions could be driving the system.
 Therefore adding a penalization in the objective function for each control to remain near $1$ can be seen as an attempt to explain data without any interaction.
-
-Second, to force a regularized control.
+\item Second, to force a regularized control.
 Otherwise note that $u$ is linear in \eqref{Controlsystem}, therefore if the integral cost does not have a non-linear expression of $u$ the optimal control will be of a bang-bang type with possibly singular arcs.
 Since the objective is to find a differentiable expression of $I(x)$ the addition of the regularization term is deemed necessary.
-
+\end{itemize} 
 The problem of approximating the solution of the system to a desired reference ($z$ in this case) is called the optimal tracking problem.

### 2020-01-20 Stability Analysis gLV/plot_operating_diagram.m
add plot_operating_diagram

@@ -1,0 +1,32 @@
+clear
+close all
+file_name_in = 'Parameters_modified';
+load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
+figure;
+cmap1 = hsv(length(map_zones));
+[X,Y] = meshgrid(sIn_vector,D_vector);
+surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
+colormap(cmap1)
+tickLabels = cell(1,length(mapZones));
+for i = mapZones.keys
+    vec_aux = str2num(char(i));
+    index_aux = find(vec_aux);
+    str_aux = sprintf('x_{%.0f} ',index_aux);
+    if max(index_aux) <= nA;
+    label = sprintf('PN: %s',str_aux);
+    else
+    label = sprintf('CN: %s',str_aux);
+    end
+    tickLabels(mapZones(char(i))) = cellstr(label);
+end
+colorbar('Ticks',1:length(mapZones),...
+         'TickLabels',tickLabels,...
+         'FontSize',9)
+view(2)
+xlabel('S_{in} [g/l]');
+ylabel('Dilution Rate [day^{-1}]')
+title(sprintf('\\fontsize{20} Operating Diagram'))
+set(gca,'fontsize',18)
+% fig.PaperPosition = [.25 .25 16 12];
+fig.PaperPositionMode = 'auto';
+print(sprintf('Images/OD_%s',file_name_in),'-dpng','-r0')

### 2020-01-21 tex/Article_Interactions.tex
added several corrections

@@
 \item Second, to force a regularized control.
-Otherwise note that $u$ is linear in \eqref{Controlsystem}, therefore if the integral cost does not have a non-linear expression of $u$ the optimal control will be of a bang-bang type with possibly singular arcs.
+Otherwise note that $u$ is linear in \eqref{Controlsystem}, therefore if the integral cost does not have a non-linear expression of $u$ the optimal control will be of a bang-bang type with possibly singular arcs \cite{harmand2019optimal}.
 Since the objective is to find a differentiable expression of $I(x)$ the addition of the regularization term is deemed necessary.
@@
 
-The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the appendix section. This in turn implies $v_i(t) \in [-1,a-1]$.
+The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the supplementary material section. This in turn implies $v_i(t) \in [-1,\bar{u}-1]$.
 
@@
 The approach was tested against synthetic data.
-The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2} (therefore $I(x) = 1 + Ax$) for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}.
+The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2}, therefore the interaction function $I(x) = 1 + Ax$), $f_i(s) = \dfrac{s_1}{K_i +s_1}$ for $i \in G_1$, and $f_i(s) = \dfrac{s_2}{K_i +s_2}$ for $i \in G_2$, for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}.
+Parameters of the simulation can be seen in table .
+A simulation of the synthetic data is presented in figure \ref{fig:nonoise200121aobplot} and figure \ref{fig:nonoise200121nobplot} depending on operating parameters $D$ and $s_{in}$.
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|l|l|l|l|}
+		\hline
+		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $k_i =\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+		$x_i \in G_1$ &0.77  &0.07  & 3.94 \\ \hline
+		$x_i\in G_2$ & 0.621 & 0.0147 & 16.12 \\ \hline
+	\end{tabular}
+	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
+	\label{Parameters_synthetic_data}
+\end{table}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+	\includegraphics[width=\linewidth]{Images/proof_of_concept/no_noise_200121_AOB_plot}
+	\caption{}
+	\label{fig:nonoise200121aobplot}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{Images/proof_of_concept/no_noise_200121_NOB_plot}
+	\caption{}
+	\label{fig:nonoise200121nobplot}
+	\end{subfigure}
+\caption{}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{Images/proof_of_concept/no_noise_200121_metabolites}
+	\caption{}
+	\label{fig:nonoise200121metabolites}
+\end{figure}
+
+\begin{figure}[h]
+	\centering	
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
+		\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
+		\label{Interaction Matrix Simulation}
+	\end{subfigure}
+\end{figure}
+
 In all figures, asterisks represent the synthetic data, while the continuous lines represent the method's output.
 
-The choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
-$Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear.
+For applying the optimal tracking approach, the choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
+$Q$ represents the covariance matrix of measurements, while $R$ is subject to interpretations depending on the context: in the case here it does not have a definite meaning, however its behaviour is studied when $\rho(R) \rightarrow 0$, with $\rho(R)$ being the spectral radius of matrix $R$.
 In the simulations here presented $Q = I_n$ and $R = \lambda I_n$.
@@
 The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements.
-\begin{figure}[h]
-	\centering	
-	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
-	\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
-	\label{Interaction Matrix Simulation}
-\end{figure}
 
@@
 The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows a new mechanism by which the CEP may not hold, however we conjecture that the system seems to have only one positive stable equilibrium.
-From the application section one can see that by correcting the growth rate one is able to recuperate the chemical species dynamics, implying that interactions are driving the system.
+From the application section one can see that by correcting the growth rate one is able to recuperate the substrates dynamics, implying that interactions are driving the system.
 The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model such as the gLV model can not capture the complexity of the particular chemostat analysed.

### 2020-01-21 Tracking/plot_synthetic_data.m
better synthetic data plots

@@ -1,7 +1,54 @@
 clear
 close all
-name_file = 'no_noise';
-load(sprintf('MAT_files\\synthetic_data_%s',name_file))
-subplot(3,1,1), plot(t_obs, Y(:,1:nA))
-subplot(3,1,2), plot(t_obs, Y(:,nA+1:n))
-subplot(3,1,3), plot(t_obs, Y(:,n+1:n+3))
+name_file_in = 'no_noise_200121';
+load(sprintf('MAT_files\\synthetic_data_%s',name_file_in))
+name_file_out = 'no_noise_200121';
+%AOB
+numbering_AOB = strsplit(num2str(1:nA));
+legend_tags_AOB = strsplit(strcat(sprintf('OTU %s,', numbering_AOB{:})),',');
+legend_tags_AOB(end) = [];
+colors_AOB =  mat2cell(hsv(nA),ones(1,nA), 3);
+figure
+AOB_plot = plot(t_obs, Y(:,1:nA),'*','LineWidth',0.7);
+xlabel('\fontsize{15}Time [days]')
+ylabel('\fontsize{15}  Concentration [g/l]')
+title(sprintf('Synthetic data simulation AOB'));
+set(gca,'fontsize',15),
+set(AOB_plot,{'Color'}, colors_AOB)
+legend(legend_tags_AOB,'fontsize',10,'Location','bestoutside');
+fig.PaperUnits = 'inches';
+fig.PaperPosition = [0 0 9 3];
+fig.PaperPositionMode = 'auto';
+print(sprintf('Images\\%s',sprintf('%s_AOB_plot',name_file_out)),'-dpng','-r0')
+%NOB
+numbering_NOB = strsplit(num2str(nA+1:n));
+legend_tags_NOB = strsplit(strcat(sprintf('OTU %s,', numbering_NOB{:})),',');
+legend_tags_NOB(end) = [];
+colors_NOB =  mat2cell(hsv(nB),ones(1,nB), 3);
+figure
+NOB_plot = plot(t_obs, Y(:,nA+1:n),'*','LineWidth',0.7);
+xlabel('\fontsize{15}Time [days]')
+ylabel('\fontsize{15}  Concentration [g/l]')
+title(sprintf('Synthetic data simulation NOB'));
+set(gca,'fontsize',15),
+set(NOB_plot,{'Color'}, colors_NOB)
+legend(legend_tags_NOB,'fontsize',10,'Location','bestoutside');
+fig.PaperUnits = 'inches';
[…]

### 2020-01-21 Stability Analysis gLV/plot_operating_diagram.m
updated name of variables

@@ -1,14 +1,14 @@
 clear
 close all
-file_name_in = 'Parameters_modified';
+file_name_in = 'synthetic_data_no_noise_200121';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
 cmap1 = hsv(length(map_zones));
-[X,Y] = meshgrid(sIn_vector,D_vector);
+[X,Y] = meshgrid(s_in_vector,D_vector);
 surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
 colormap(cmap1)
-tickLabels = cell(1,length(mapZones));
-for i = mapZones.keys
+tickLabels = cell(1,length(map_zones));
+for i = map_zones.keys
     vec_aux = str2num(char(i));
     index_aux = find(vec_aux);
     str_aux = sprintf('x_{%.0f} ',index_aux);
@@ -17,9 +17,9 @@ for i = mapZones.keys
     else
     label = sprintf('CN: %s',str_aux);
     end
-    tickLabels(mapZones(char(i))) = cellstr(label);
+    tickLabels(map_zones(char(i))) = cellstr(label);
 end
-colorbar('Ticks',1:length(mapZones),...
+colorbar('Ticks',1:length(map_zones),...
          'TickLabels',tickLabels,...
          'FontSize',9)
 view(2)

### 2020-01-22 Stability Analysis gLV/operating_diagram.m
changed bug for detection of multiple stable equilibria

@@ -1,9 +1,9 @@
 close all
 clear
-file_name_in = 'Parameters_modified';
+file_name_in = 'parameters_synthetic_data_no_noise_200121';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'Parameters_modified';
-number_of_points = 200;
+file_name_out = 'parameters_synthetic_data_no_noise_200121';
+number_of_points = 80;
 d_initial = 0.7/6.5;
 d_final = 2.2/6.5;
 s_in_initial = 0.5;
@@ -12,33 +12,37 @@ s_in_vector = linspace(s_in_initial,s_in_final,number_of_points);
 D_vector =  linspace(d_initial,d_final,number_of_points);
 n1 = length(s_in_vector);
 n2 = length(D_vector);
-%parametersLVarticle;
 %Structure to save points.
 map_zones = containers.Map;
 zones = zeros(n1,n2);
+percentage = round(linspace(1,n1,11));
 tic
 for i = 1:n1
     for j = 1:n2
         [possible_x, possible_s1, possible_s2, possible_s3] = equilibria(A,...
             nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j),s_in_vector(i));
         possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
+        keyString = [];
         for k=1:length(possible_equilibria(1,:))
             if all(possible_equilibria(:,k) >=0) && isreal(possible_equilibria(:,k))
                 J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j));
                 if all(real(eig(J)) <0)
                     positive_equilibria = (possible_x(:,k)>0)';
-                    keyString = num2str(positive_equilibria);
-                    if  isKey(map_zones,keyString)
-                        zones(i,j) = map_zones(keyString);
-                    else
-                        count = length(map_zones);
-                        map_zones(keyString) = count + 1;
-                        zones(i,j) = map_zones(keyString);
-                    end
+                    keyString = strcat(keyString,num2str(positive_equilibria));
                 end
             end
         end
+        if  isKey(map_zones,keyString)
+            zones(i,j) = map_zones(keyString);
+        else
+            count = length(map_zones);
+            map_zones(keyString) = count + 1;
+            zones(i,j) = map_zones(keyString);
+        end
+    end
[…]

### 2020-02-06 tex/Article_Interactions.tex
some changes in tex

@@
 
-The algorithm implicitly assumes that every submatrix $A'$ is invertible.
+Algorithm \ref{StabilityAnalysis} implicitly assumes that every submatrix $A'$ is invertible.
 
@@
 However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law or model structure involving other biological processes is required to include microbial diversity.
+
+As shown in operating diagram \ref{Parameters Modified}, there exists a bi stability zone, which is corroborated from a simulation: depending on the initial conditions of the system the predicted outcome might vary.
+The therefores
 
@@
 PN takes place when neither $x_3$ nor $x_4$ are present.
-CN takes place if $x_3$ or $x_4$ are present.}
+CN takes place if $x_3$ or $x_4$ are/ present.}
 	\label{OD Dumont}
@@
 It also shows a new mechanism by which the CEP no longer holds.
-The operating diagrams always show a single stable equilibrium point- with possible coexistence of all species- for each pair $(s_{in},D)$, however no proof is offered to such conjecture.
-Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a model to study.
+The operating diagrams almost always show a single stable equilibrium point- with possible coexistence of all species- for each pair $(s_{in},D)$, however a thin zone is presented where two stable equilibriums coexist, thus the behaviour of the system depends on the initial conditions.
+Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a new model to study.
 
@@
 The method consists on iteratively calculating trajectories of system \eqref{Controlsystem} with a certain control and feeding a non-autonomous Ricatti differential equation with the resulting trajectory.
-Then a control law that uses the Ricatti equation is proposed and a new trajectory is calculated.
-The iteration is stopped when a convergence in the output or in the control is observed.
+Then a control law that uses the solution of the Ricatti equation is proposed and a new trajectory is calculated.
+The iteration is stopped when a convergence in the output or  the control is observed.
 
@@
 Nevertheless, the methods of Cimen \textit{et al.}\cite{Cimen2004} were directly used with an explicit constraint in the synthesis of the control.
-Even though this is probably suboptimal when the control reaches its bounds, one at least is certain of its optimality when the control never activates its constraints.
+Even though this is probably suboptimal when the control reaches its bounds, one at least is certain of its optimality when the control never reaches its constraints.
 

### 2020-02-06 Stability Analysis gLV/operating_diagram.m
changed meaning of zone

@@ -1,9 +1,9 @@
 close all
 clear
-file_name_in = 'parameters_synthetic_data_no_noise_200121';
+file_name_in = 'parameters_Dumont';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'parameters_synthetic_data_no_noise_200121';
-number_of_points = 80;
+file_name_out = 'parameters_Dumont';
+number_of_points = 50;
 d_initial = 0.7/6.5;
 d_final = 2.2/6.5;
 s_in_initial = 0.5;
@@ -14,7 +14,10 @@ n1 = length(s_in_vector);
 n2 = length(D_vector);
 %Structure to save points.
 map_zones = containers.Map;
-zones = zeros(n1,n2);
+map_zones('PN') = 0;
+map_zones('CN') = 1;
+map_zones('B') = 2;
+zones = zeros(n1,n2) -1;
 percentage = round(linspace(1,n1,11));
 tic
 for i = 1:n1
@@ -22,22 +25,28 @@ for i = 1:n1
         [possible_x, possible_s1, possible_s2, possible_s3] = equilibria(A,...
             nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j),s_in_vector(i));
         possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
-        keyString = [];
+        flag_PN = 0;
+        flag_CN = 0;
         for k=1:length(possible_equilibria(1,:))
             if all(possible_equilibria(:,k) >=0) && isreal(possible_equilibria(:,k))
                 J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j));
                 if all(real(eig(J)) <0)
                     positive_equilibria = (possible_x(:,k)>0)';
-                    keyString = strcat(keyString,num2str(positive_equilibria));
+                    index_aux = find(positive_equilibria);
+                    if max(index_aux) <= nA
+                        flag_PN = 1;
+                    else
+                        flag_CN = 1;
+                    end
                 end
             end
         end
-        if  isKey(map_zones,keyString)
-            zones(i,j) = map_zones(keyString);
-        else
-            count = length(map_zones);
-            map_zones(keyString) = count + 1;
-            zones(i,j) = map_zones(keyString);
+        if flag_PN && ~flag_CN
+          zones(i,j) = 0;
+        elseif ~flag_PN && flag_CN
[…]

### 2020-02-06 Stability Analysis gLV/plot_operating_diagram.m
operating diagram new version

@@ -1,27 +1,22 @@
 clear
 close all
-file_name_in = 'synthetic_data_no_noise_200121';
+file_name_in = 'parameters_Dumont';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
-cmap1 = hsv(length(map_zones));
+number_of_zones = length(unique(zones));
+cmap1 = cool(number_of_zones);
 [X,Y] = meshgrid(s_in_vector,D_vector);
 surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
 colormap(cmap1)
-tickLabels = cell(1,length(map_zones));
-for i = map_zones.keys
-    vec_aux = str2num(char(i));
-    index_aux = find(vec_aux);
-    str_aux = sprintf('x_{%.0f} ',index_aux);
-    if max(index_aux) <= nA;
-    label = sprintf('PN: %s',str_aux);
-    else
-    label = sprintf('CN: %s',str_aux);
-    end
-    tickLabels(map_zones(char(i))) = cellstr(label);
+if number_of_zones == 2
+    tick_labels = {'Partial Nitrification','Complete Nitrification'};
+    tick_position = [0.2, 0.8]+1;
+else
+    tick_labels = {'Partial Nitrification','Complete Nitrification','Both equilibria present'};
+    tick_position = [0.25, 0.5, 0.75]+1;
 end
-colorbar('Ticks',1:length(map_zones),...
-         'TickLabels',tickLabels,...
-         'FontSize',9)
+colorbar('Ticks',tick_position,...
+         'TickLabels',tick_labels)
 view(2)
 xlabel('S_{in} [g/l]');
 ylabel('Dilution Rate [day^{-1}]')

### 2020-02-07 Stability Analysis gLV/operating_diagram.m
changed zone numbering

@@ -1,9 +1,9 @@
 close all
 clear
-file_name_in = 'parameters_Dumont';
+file_name_in = 'parameters_synthetic_data_no_noise_200121';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'parameters_Dumont';
-number_of_points = 50;
+file_name_out = 'parameters_synthetic_data_no_noise_200121';
+number_of_points = 10;
 d_initial = 0.7/6.5;
 d_final = 2.2/6.5;
 s_in_initial = 0.5;
@@ -42,11 +42,11 @@ for i = 1:n1
             end
         end
         if flag_PN && ~flag_CN
-          zones(i,j) = 0;
+          zones(i,j) = 2;
         elseif ~flag_PN && flag_CN
             zones(i,j) = 1;
         elseif flag_PN && flag_CN
-            zones(i,j) = 2;
+            zones(i,j) = 0;
         end
     end
     if any( i == percentage)

### 2020-02-07 Stability Analysis gLV/plot_operating_diagram.m

@@ -1,9 +1,12 @@
 clear
 close all
-file_name_in = 'parameters_Dumont';
+file_name_in = 'parameters_synthetic_data_no_noise_200121';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
 number_of_zones = length(unique(zones));
+if number_of_zones ==4
+    disp('No stable equilibria found');
+end
 cmap1 = cool(number_of_zones);
 [X,Y] = meshgrid(s_in_vector,D_vector);
 surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
@@ -12,11 +15,11 @@ if number_of_zones == 2
     tick_labels = {'Partial Nitrification','Complete Nitrification'};
     tick_position = [0.2, 0.8]+1;
 else
-    tick_labels = {'Partial Nitrification','Complete Nitrification','Both equilibria present'};
-    tick_position = [0.25, 0.5, 0.75]+1;
+    tick_labels = {'Partial Nitrification','Complete Nitrification','Depends on initial condition'};
+    tick_position = [0.3,1,1.7];
 end
 colorbar('Ticks',tick_position,...
-         'TickLabels',tick_labels)
+         'TickLabels',fliplr(tick_labels))
 view(2)
 xlabel('S_{in} [g/l]');
 ylabel('Dilution Rate [day^{-1}]')

### 2020-02-10 Stability Analysis gLV/operating_diagram.m
changed numeration to operating diagram and plot

@@ -1,11 +1,11 @@
 close all
 clear
-file_name_in = 'parameters_synthetic_data_no_noise_200121';
+file_name_in = 'parameters_modified';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'parameters_synthetic_data_no_noise_200121';
-number_of_points = 10;
+file_name_out = 'parameters_modified';
+number_of_points = 50;
 d_initial = 0.7/6.5;
-d_final = 2.2/6.5;
+d_final =  2.2/6.5;
 s_in_initial = 0.5;
 s_in_final = 2;
 s_in_vector = linspace(s_in_initial,s_in_final,number_of_points);
@@ -13,10 +13,7 @@ D_vector =  linspace(d_initial,d_final,number_of_points);
 n1 = length(s_in_vector);
 n2 = length(D_vector);
 %Structure to save points.
-map_zones = containers.Map;
-map_zones('PN') = 0;
-map_zones('CN') = 1;
-map_zones('B') = 2;
+map_equilibria = containers.Map;
 zones = zeros(n1,n2) -1;
 percentage = round(linspace(1,n1,11));
 tic
@@ -27,13 +24,16 @@ for i = 1:n1
         possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
         flag_PN = 0;
         flag_CN = 0;
+        flag_washout = 0;
         for k=1:length(possible_equilibria(1,:))
             if all(possible_equilibria(:,k) >=0) && isreal(possible_equilibria(:,k))
                 J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j));
                 if all(real(eig(J)) <0)
                     positive_equilibria = (possible_x(:,k)>0)';
                     index_aux = find(positive_equilibria);
-                    if max(index_aux) <= nA
+                    if isempty(index_aux);
+                        flag_washout = 1;
+                    elseif max(index_aux) <= nA
                         flag_PN = 1;
                     else
                         flag_CN = 1;
@@ -41,12 +41,16 @@ for i = 1:n1
                 end
             end
         end
-        if flag_PN && ~flag_CN
-          zones(i,j) = 2;
-        elseif ~flag_PN && flag_CN
+        if ~flag_PN && flag_CN
             zones(i,j) = 1;
         elseif flag_PN && flag_CN
-            zones(i,j) = 0;
+            zones(i,j) = 2;   
[…]

### 2020-02-10 Stability Analysis gLV/plot_operating_diagram.m

@@ -1,25 +1,21 @@
 clear
 close all
-file_name_in = 'parameters_synthetic_data_no_noise_200121';
+file_name_in = 'parameters_Dumont';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
-number_of_zones = length(unique(zones));
-if number_of_zones ==4
-    disp('No stable equilibria found');
-end
+present_zones = unique(zones);
+number_of_zones = length(present_zones);
 cmap1 = cool(number_of_zones);
 [X,Y] = meshgrid(s_in_vector,D_vector);
 surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
 colormap(cmap1)
-if number_of_zones == 2
-    tick_labels = {'Partial Nitrification','Complete Nitrification'};
-    tick_position = [0.2, 0.8]+1;
-else
-    tick_labels = {'Partial Nitrification','Complete Nitrification','Depends on initial condition'};
-    tick_position = [0.3,1,1.7];
-end
-colorbar('Ticks',tick_position,...
-         'TickLabels',fliplr(tick_labels))
+%     tick_labels = {'Partial Nitrification','Complete Nitrification'};
+%     tick_position = [0.2, 0.8]+1;
+tick_labels = {'Complete Nitrification','Depends on initial condition (CN or PN)','Partial Nitrification','Depends on initial condition (PN or WO)','Washout'};
+% tick_position = (linspace(1,number_of_zones,number_of_zones))*number_of_zones/(number_of_zones+1);
+tick_position = [1,2,3,4,5]; 
+colorbar('Ticks',tick_position(present_zones),...
+         'TickLabels',tick_labels(present_zones))
 view(2)
 xlabel('S_{in} [g/l]');
 ylabel('Dilution Rate [day^{-1}]')

### 2020-02-10 Stability Analysis gLV/operating_diagram.m
modified named zones

@@ -1,9 +1,9 @@
 close all
 clear
-file_name_in = 'parameters_modified';
+file_name_in = 'parameters_modified_2';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'parameters_modified';
-number_of_points = 50;
+file_name_out = 'parameters_modified_2';
+number_of_points = 300;
 d_initial = 0.7/6.5;
 d_final =  2.2/6.5;
 s_in_initial = 0.5;
@@ -14,7 +14,7 @@ n1 = length(s_in_vector);
 n2 = length(D_vector);
 %Structure to save points.
 map_equilibria = containers.Map;
-zones = zeros(n1,n2) -1;
+zones = ones(n1,n2) ;
 percentage = round(linspace(1,n1,11));
 tic
 for i = 1:n1
@@ -42,15 +42,15 @@ for i = 1:n1
             end
         end
         if ~flag_PN && flag_CN
-            zones(i,j) = 1;
+            zones(i,j) = 2;
         elseif flag_PN && flag_CN
-            zones(i,j) = 2;   
+            zones(i,j) = 3;   
         elseif flag_PN && ~flag_CN
-            zones(i,j) = 3;
+            zones(i,j) = 4;
         elseif flag_washout && flag_PN
-            zones(i,j) = 4;           
+            zones(i,j) = 5;           
         elseif flag_washout && ~flag_PN
-            zones(i,j) = 5;
+            zones(i,j) = 6;
         end
     end
     if any( i == percentage)

### 2020-02-10 Stability Analysis gLV/plot_operating_diagram.m

@@ -1,6 +1,6 @@
 clear
 close all
-file_name_in = 'parameters_Dumont';
+file_name_in = 'parameters_modified_2';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
 present_zones = unique(zones);
@@ -11,16 +11,16 @@ surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%
 colormap(cmap1)
 %     tick_labels = {'Partial Nitrification','Complete Nitrification'};
 %     tick_position = [0.2, 0.8]+1;
-tick_labels = {'Complete Nitrification','Depends on initial condition (CN or PN)','Partial Nitrification','Depends on initial condition (PN or WO)','Washout'};
+tick_labels = {'No SE','CN','CN & PN','PN','PN & WO','WO'};
 % tick_position = (linspace(1,number_of_zones,number_of_zones))*number_of_zones/(number_of_zones+1);
-tick_position = [1,2,3,4,5]; 
+tick_position = [1,2,3,4,5,6]; 
 colorbar('Ticks',tick_position(present_zones),...
          'TickLabels',tick_labels(present_zones))
 view(2)
 xlabel('S_{in} [g/l]');
 ylabel('Dilution Rate [day^{-1}]')
 title(sprintf('\\fontsize{20} Operating Diagram'))
-set(gca,'fontsize',18)
+set(gca,'fontsize',14)
 % fig.PaperPosition = [.25 .25 16 12];
 fig.PaperPositionMode = 'auto';
 print(sprintf('Images/OD_%s',file_name_in),'-dpng','-r0')

### 2020-02-12 tex/Article_Interactions.tex
final changes to OD

@@
 The resulting matrix's eigenvalues must have negative real part.
-A general formula for this Jacobian is presented in the supplementary material.
+A general formula for this Jacobian is presented in the supplementary material \eqref{Jacobian_system}.
 
@@
 One then regroups all the pairs such that the set of non-active coordinates of the points of the set $PSP$ are the same and have the same stability properties.
-This regrouping represents graphically the coexistence of the different OTU in a $D-s_{in}$ plot.
-In particular for the biological process of nitrification, this allows to represent when partial nitrification (PN) or complete nitrification (CN) may arise \cite{KHIN2004519}.
-PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ concentration is very low and thus almost no conversion from $s_2$  to $s_3$ takes place.
+This regrouping allows to represent when partial nitrification (PN),complete nitrification (CN), or washout (WO) may arise \cite{KHIN2004519}.
+PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ concentration is very low (washout of $G_2$) and thus almost no conversion from $s_2$  to $s_3$ takes place.
 On the contrary CN is when nitrate ($s_3$) accumulates because of the presence of OTU of $G_2$.
@@
 As shown in operating diagram \ref{Parameters Modified}, there exists a bi stability zone, which is corroborated from a simulation: depending on the initial conditions of the system the predicted outcome might vary.
-The therefores
 
@@
 	\label{OD modified}
+\end{figure}
+
+\begin{figure}
+		\includegraphics[width=\textwidth]{ED_parameters_modified}
 \end{figure}
@@
 The first $n$ equations of system \eqref{system} may be written then as$\dot{x} =  h(x) = h_1(\diag(x), h_2(x))$, by the chain rule: 
-\begin{align*} J_h(x) &= D_M h_1(\diag(x),h_2(x))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x))\circ D_xh_2(x)  \\ &=
+\begin{align} J_h(x) &= D_M h_1(\diag(x),h_2(x))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x))\circ D_xh_2(x)  \\ &=
 \diag(h_2(x))+\diag(x)\diag(f(s))A  \label{n2_entries}
-\end{align*}
+\end{align}
 
@@
 Then the Jacobian of the system may be expressed as:
-$J(x,s_1,s_2,s_3) = \begin{bmatrix}
+\begin{align}
+\label{Jacobian_system}
+ J(x,s_1,s_2,s_3) = \begin{bmatrix}
 J_{11} & J_{12} & J_{13} & J_{14} \\
@@
 J_{41} & J_{42} & J_{43} & J_{44} 
-\end{bmatrix} $
-
+\end{bmatrix} 
+\end{align} 
+with 
 \begin{align}

### 2020-02-12 Stability Analysis gLV/operating_diagram.m

@@ -1,8 +1,8 @@
 close all
 clear
-file_name_in = 'parameters_modified_2';
+file_name_in = 'parameters_modified';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'parameters_modified_2';
+file_name_out = 'parameters_modified';
 number_of_points = 300;
 d_initial = 0.7/6.5;
 d_final =  2.2/6.5;

### 2020-02-12 Stability Analysis gLV/plot_operating_diagram.m

@@ -1,13 +1,14 @@
 clear
 close all
-file_name_in = 'parameters_modified_2';
+file_name_in = 'parameters_modified';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
 present_zones = unique(zones);
 number_of_zones = length(present_zones);
-cmap1 = cool(number_of_zones);
+cmap1 = hsv(number_of_zones);
 [X,Y] = meshgrid(s_in_vector,D_vector);
-surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
+surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');
+%view(2)
 colormap(cmap1)
 %     tick_labels = {'Partial Nitrification','Complete Nitrification'};
 %     tick_position = [0.2, 0.8]+1;

### 2020-02-12 Stability Analysis gLV/test_equilibria.m

@@ -6,17 +6,17 @@ load(sprintf('MAT_files\\%s',file_name_in));
 z0 = random('Uniform',0,1,n+3,1);
 OTU = 1:n;
 options = odeset('NonNegative',1:(nA+nB+3));
-dilution = 0.1993;
+dilution = 0.2906 ;
 D = @(t) dilution;
-s_in = 1.035;
+s_in = 1.829;
 sIn = @(t) s_in;
-tF = 2000;
+tF = 20000;
 fun =  dynamic(A,nA,nB,kA,kB,muA,muB,kSA,kSB,D,sIn);
 [T,Y] = ode15s(fun,[0 tF], z0,options);
 end_point_string = sprintf('%1.4f ', Y(end,:)');
 eval_end_point =  fun(tF,Y(end,:)');
 eval_end_point_string = sprintf('%1.4f ', eval_end_point);
-fprintf('Trajectory at T= %d \n Point =%s \n Evaluated in dynamic = %s',...
+fprintf('Trajectory at T= %d \n Point =%s \n Evaluated in dynamic = %s\n',...
     tF, end_point_string,eval_end_point_string);
 [possible_x, possible_s1, possible_s2, possible_s3]  = equilibria(A,...
     nA,nB,kA,kB,muA,muB,kSA,kSB,dilution,s_in);
@@ -24,15 +24,16 @@ possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
 num_equilibria = 0;
 
 for i=1:length(possible_equilibria(1,:))
-if all(possible_equilibria(:,i) >=0) && isreal(possible_equilibria(:,i))
-    num_equilibria = num_equilibria +1;
-    fprintf('\n Positive Equilibrium %d =', num_equilibria);
-    disp(possible_equilibria(:,i)')
-    J = dynamic_jacobian(possible_equilibria(:,i),A,nA,nB,kA,kB,muA,muB,kSA,kSB,dilution);
-     eigenvalues = eig(J);
-     if all(real(eig(J)) <0)
-         fprintf('Equilibrium %d: Stable Equilibrium! \n Eigenvalues of the Jacobian in the Equilibrium : \n', num_equilibria);
-         disp(eigenvalues)
-     end
-end
+    if all(possible_equilibria(:,i) >=0) && isreal(possible_equilibria(:,i))
+        num_equilibria = num_equilibria +1;
+%         fprintf('\n Positive Equilibrium %d =', num_equilibria);
[…]

### 2020-02-12 Stability Analysis gLV/plot_ecological_diagram.m
add ecological diagram

@@ -1,0 +1,32 @@
+clear
+close all
+file_name_in = 'parameters_modified';
+load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
+figure;
+cmap1 = hsv(length(map_zones));
+[X,Y] = meshgrid(s_in_vector,D_vector);
+surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
+colormap(cmap1)
+tickLabels = cell(1,length(map_zones));
+for i = map_zones.keys
+    vec_aux = str2num(char(i));
+    index_aux = find(vec_aux);
+    str_aux = sprintf('x_{%.0f} ',index_aux);
+    if max(index_aux) <= nA;
+    label = sprintf('PN: %s',str_aux);
+    else
+    label = sprintf('CN: %s',str_aux);
+    end
+    tickLabels(map_zones(char(i))) = cellstr(label);
+end
+colorbar('Ticks',1:length(map_zones),...
+         'TickLabels',tickLabels,...
+         'FontSize',9)
+view(2)
+xlabel('S_{in} [g/l]');
+ylabel('Dilution Rate [day^{-1}]')
+title(sprintf('\\fontsize{20} Ecological Diagram'))
+set(gca,'fontsize',18)
+% fig.PaperPosition = [.25 .25 16 12];
+fig.PaperPositionMode = 'auto';
+print(sprintf('Images/ED_%s',file_name_in),'-dpng','-r0')

### 2020-02-12 Stability Analysis gLV/operating_diagram.m
Operating diagram gives ED too.

@@ -13,8 +13,9 @@ D_vector =  linspace(d_initial,d_final,number_of_points);
 n1 = length(s_in_vector);
 n2 = length(D_vector);
 %Structure to save points.
-map_equilibria = containers.Map;
-zones = ones(n1,n2) ;
+map_zones_ED = containers.Map;
+zones_OD = ones(n1,n2);
+zones_ED = zeros(n1,n2);
 percentage = round(linspace(1,n1,11));
 tic
 for i = 1:n1
@@ -25,12 +26,14 @@ for i = 1:n1
         flag_PN = 0;
         flag_CN = 0;
         flag_washout = 0;
+        key_string = [];
         for k=1:length(possible_equilibria(1,:))
             if all(possible_equilibria(:,k) >=0) && isreal(possible_equilibria(:,k))
                 J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j));
                 if all(real(eig(J)) <0)
                     positive_equilibria = (possible_x(:,k)>0)';
                     index_aux = find(positive_equilibria);
+                    key_string = strcat(key_string,num2str(positive_equilibria),',');
                     if isempty(index_aux);
                         flag_washout = 1;
                     elseif max(index_aux) <= nA
@@ -42,15 +45,22 @@ for i = 1:n1
             end
         end
         if ~flag_PN && flag_CN
-            zones(i,j) = 2;
+            zones_OD(i,j) = 2;
         elseif flag_PN && flag_CN
-            zones(i,j) = 3;   
+            zones_OD(i,j) = 3;   
         elseif flag_PN && ~flag_CN
-            zones(i,j) = 4;
+            zones_OD(i,j) = 4;
         elseif flag_washout && flag_PN
-            zones(i,j) = 5;           
+            zones_OD(i,j) = 5;           
         elseif flag_washout && ~flag_PN
-            zones(i,j) = 6;
+            zones_OD(i,j) = 6;
+        end
+        if  isKey(map_zones_ED,key_string)
+            zones_ED(i,j) = map_zones_ED(key_string);
+        else
+            count = length(map_zones_ED);
+            map_zones_ED(key_string) = count + 1;
+            zones_ED(i,j) = map_zones_ED(key_string);
         end
     end
     if any( i == percentage)

### 2020-02-12 Stability Analysis gLV/plot_operating_diagram.m

@@ -3,11 +3,11 @@ close all
 file_name_in = 'parameters_modified';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
 figure;
-present_zones = unique(zones);
+present_zones = unique(zones_OD);
 number_of_zones = length(present_zones);
 cmap1 = hsv(number_of_zones);
 [X,Y] = meshgrid(s_in_vector,D_vector);
-surfc(X,Y,zones','EdgeColor','none','LineStyle','none','FaceLighting','phong');
+surfc(X,Y,zones_OD','EdgeColor','none','LineStyle','none','FaceLighting','phong');
 %view(2)
 colormap(cmap1)
 %     tick_labels = {'Partial Nitrification','Complete Nitrification'};

### 2020-02-24 tex/Article_Interactions.tex
changes in stability analysis discussion

@@
 
-\subsection{Local Stability and Operating Diagrams}
+\subsection{Stability: Operating and Ecological Diagrams}
+
+In this subsection the stability of the equilibrium points is addressed.
+Operating and ecological diagrams are created from this stability analysis.
+Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$.
+
 For checking local asymptotic stability of the equilibria points, the Jacobian of the system is provided and evaluated at each of these points.
@@
 A general formula for this Jacobian is presented in the supplementary material \eqref{Jacobian_system}.
-
-The former discussion proposes an algorithm for finding the positive stable equilibrium points
+Algorithm \ref{StabilityAnalysis} summarizes such a procedure.
+Algorithm \ref{StabilityAnalysis} implicitly assumes that every submatrix $A'$ is invertible.
 
@@
 	\KwData{$A \in M_{n\times n}(\R)$, $D, s_{in}, \bar{\mu}_i,K_i, k_i,  \in \R \, i\in [n], $, $n_1, n_2 \in \N$}
-	\KwResult{Set PSP containing all Positive Stable Equilibrium Points}
-	$PSP = \emptyset$ \\
+	\KwResult{Set $\mathcal{P}$ containing all Positive Stable Equilibrium Points}
+	$\mathcal{P} = \emptyset$ \\
 	eig = Eigenvalues of $J(0,s_{in},0,0)$. \\
@@
 		\If{$(x,s_1,s_2,s_3) \geq 0$}{eig = Eigenvalues of $J(x,s_1,s_2,s_3)$ \\
-			\If{$Real(eig) < 0$}{$PSP = PSP \cup (x,s_1,s_2,s_3)$}}}
+			\If{$Real(eig) < 0$}{$\mathcal{P} = \mathcal{P} \cup (x,s_1,s_2,s_3)$}}}
 	\label{StabilityAnalysis}
@@
 
-Algorithm \ref{StabilityAnalysis} implicitly assumes that every submatrix $A'$ is invertible.
-
-Operating diagrams are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters.
-Operating diagrams are created by running algorithm \ref{StabilityAnalysis} for different pairs $(s_{in},D)$ \cite{lobry2017chemostat}.
-One then regroups all the pairs such that the set of non-active coordinates of the points of the set $PSP$ are the same and have the same stability properties.
-This regrouping allows to represent when partial nitrification (PN),complete nitrification (CN), or washout (WO) may arise \cite{KHIN2004519}.
-PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ concentration is very low (washout of $G_2$) and thus almost no conversion from $s_2$  to $s_3$ takes place.
+Operating and ecological diagrams are created by running algorithm \ref{StabilityAnalysis} for different pairs $(s_{in},D)$ \cite{lobry2017chemostat}.
+In the case of operating diagrams all the pairs $(s_{in},D)$ are regrouped such that the points of the set $\mathcal{P}$ represent when partial nitrification (PN), complete nitrification (CN), washout (WO), or a combination of them may arise \cite{KHIN2004519}.
+PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ are washed out and thus no conversion from $s_2$  to $s_3$ takes place.
 On the contrary CN is when nitrate ($s_3$) accumulates because of the presence of OTU of $G_2$.
 
-The operating diagram from one of the sets of the parameter identification (obtained with a Bayesian estimation method) from Dumont et al.
-is presented in figure \ref{OD Dumont}.
+In the case of ecological diagrams the pairs are regrouped such that the points in the set $\mathcal{P}$ have the same non-active coordinates.
+Ecological diagrams have more information than operating diagrams, in the sense that one can infer the operating diagram from an ecological diagram.
+However for exposure of the subject both of them are shown.
+
+The operating diagram from one of the sets of the parameter identification (they proposed a distribution of parameters obtained with a Bayesian estimation method) from Dumont \textit{et al.} \cite{Dumont2016} is presented in figure \ref{OD Dumont}.
 Their fit describes well the dynamics of the OTU, but is not the case for measured substrates.
 Two OTU per functional group were considered.
-One can see that coexistence in the same functional group is never attained for one of the parameter set obtained (their method provided several sets of parameters).
-On the contrary, when using a random interaction matrix, and modifying the kinetic coefficients  (note that $x_1$ and $x_3$ have the same $\mu_i$ and $K_i$ in case 1 and 2) one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
-In the latter case CN can be achieved at a more elevated dilution rate than in the former case.
 Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.
-
-The model is also  able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+In the latter case CN can be achieved at a more elevated dilution rate than in the former case, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are strongly positive in case 2, thus helping them survive through bigger dilution rates.
+
+Ecological diagrams show that the model is able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
 The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
 However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law or model structure involving other biological processes is required to include microbial diversity.
-
-As shown in operating diagram \ref{Parameters Modified}, there exists a bi stability zone, which is corroborated from a simulation: depending on the initial conditions of the system the predicted outcome might vary.
+One can see that coexistence in the same functional group is never attained for one of the parameter set shown.
+On the contrary, when using a random interaction matrix, and modifying the kinetic coefficients note that $x_1$ and $x_3$ have the same $\mu_i$ and $K_i$ in case 1 and 2) one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
+
+Multiple equilibrium points have been found stable for the same pair $D-s_{in}$ in this type of model.
+Meaning that in those zones the outcome of the reactor is dependent on initial conditions.
+In the operating diagram this is shown in the
+
+As shown in operating diagram \ref{Parameters Modified}, there exists a bi stability zone.
 
@@
 PN takes place when neither $x_3$ nor $x_4$ are present.
-CN takes place if $x_3$ or $x_4$ are/ present.}
+CN takes place if $x_3$ or $x_4$ are present.}
 	\label{OD Dumont}
@@
 		\includegraphics[width=\textwidth]{ED_parameters_modified}
+		\caption{Ecological Diagram for system.
+A complex situation emerges in ecological terms, depending on the operating parameters the community can go from a single species surviving in the chemostat to full coexistence.}
+		\label{ED_modified}
 \end{figure}
@@
 The model here presented serves to illustrate that by considering a more complex growth rate that tries to model ecological interactions one might explain differences in reactors operating under similar conditions.
-It also shows a new mechanism by which the CEP no longer holds.
-The operating diagrams almost always show a single stable equilibrium point- with possible coexistence of all species- for each pair $(s_{in},D)$, however a thin zone is presented where two stable equilibriums coexist, thus the behaviour of the system depends on the initial conditions.
+It also shows a new mechanism by which the CEP no longer holds and where multiple stable equilibria may appear.
 Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a new model to study.

### 2020-02-26 tex/Article_Interactions.tex
finished stability analysis section

@@
 In the case of ecological diagrams the pairs are regrouped such that the points in the set $\mathcal{P}$ have the same non-active coordinates.
-Ecological diagrams have more information than operating diagrams, in the sense that one can infer the operating diagram from an ecological diagram.
+Ecological diagrams provide more information than operating diagrams, in the sense that one can infer the operating diagram from an ecological diagram.
 However for exposure of the subject both of them are shown.
 
-The operating diagram from one of the sets of the parameter identification (they proposed a distribution of parameters obtained with a Bayesian estimation method) from Dumont \textit{et al.} \cite{Dumont2016} is presented in figure \ref{OD Dumont}.
-Their fit describes well the dynamics of the OTU, but is not the case for measured substrates.
-Two OTU per functional group were considered.
-Parameters of cases 1 and 2 can be seen in table \ref{Parameters Dumont} and \ref{Parameters Modified}, respectively.
-In the latter case CN can be achieved at a more elevated dilution rate than in the former case, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are strongly positive in case 2, thus helping them survive through bigger dilution rates.
-
-Ecological diagrams show that the model is able to overcome the  competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
-The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
-However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law or model structure involving other biological processes is required to include microbial diversity.
-One can see that coexistence in the same functional group is never attained for one of the parameter set shown.
-On the contrary, when using a random interaction matrix, and modifying the kinetic coefficients note that $x_1$ and $x_3$ have the same $\mu_i$ and $K_i$ in case 1 and 2) one can see a more complex situation where coexistence in the same functional group is possible as seen in figure \ref{OD modified}.
-
-Multiple equilibrium points have been found stable for the same pair $D-s_{in}$ in this type of model.
-Meaning that in those zones the outcome of the reactor is dependent on initial conditions.
-In the operating diagram this is shown in the
-
-As shown in operating diagram \ref{Parameters Modified}, there exists a bi stability zone.
+Two examples are used for illustrating the diversity of situations that may arise from this type of system.
+Kinetic parameters of cases 1 and 2 can be seen in table \ref{kinetic_parameters}.
+Interaction matrices of each case are shown in figure \ref{Interactions}.
+Case 1 was taken from Dumont \textit{et al.}\cite{Dumont2016} where they proposed a distribution of parameters obtained with a Bayesian estimation method.
+Their fit describes well the dynamics of the OTU two most abundant OTU in each functional group, but is not the case for measured substrates.
 
@@
 		\hline
-		Parameters Dumont & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+		Case 1 & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
 		$x_1 \in G_1$ & 0.828  & 0.147 & 3.85  \\ \hline
@@
 	\end{tabular}
-	\caption{Kinetic parameters of model \eqref{system} from \cite{Dumont2016}.}
-	\label{Parameters Dumont}
-\end{table}
-
-\begin{figure}[ht]
-	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=\textwidth]{Interactions_Parameters_Dumont}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.45\textwidth}
-	\includegraphics[width=\textwidth]{OD_parameters_Dumont}
-	\end{subfigure}
-	\caption{Left: interaction matrix associated with model \eqref{system} as estimated in Dumont el al.
-\cite{Dumont2016} for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
-Right: associated operating diagram with parameters in Table \ref{Parameters Dumont}.
-The different zones represent the surviving species in the steady state.
-PN takes place when neither $x_3$ nor $x_4$ are present.
-CN takes place if $x_3$ or $x_4$ are present.}
-	\label{OD Dumont}
-\end{figure}
-
-\begin{table}[ht]
-	\centering
+~
 \begin{tabular}{|l|l|l|l|}
 	\hline
-		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+	Case 2  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
 	$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
@@
 \end{tabular}
-	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
-	\label{Parameters Modified}
+
+	\caption{Kinetic parameters of model \eqref{system}. Case 1 is taken from Dumont \textit{et al} \cite{Dumont2016}. Case 2 is a modification of the original parameters for model exploration.}
+	\label{kinetic_parameters}
 \end{table}
-\begin{figure}[ht]
-	\centering	
+
+\begin{figure}[h]
+\begin{subfigure}[b]{0.45\textwidth}
+	\includegraphics[width=\textwidth]{Interactions_Parameters_Dumont}
+	\caption{Case 1 interaction matrix.}
+	\label{Interaction_1}
+\end{subfigure}
+~
 \begin{subfigure}[b]{0.45\textwidth}
 	\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
-	\end{subfigure}
+	\caption{Case 2 interaction matrix.}
+	\label{Interaction_2}
+\end{subfigure}
+	\caption{Interaction matrices for each case for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
+Note how OTU 1 affect very positively OTU 3 and 4 in figure \ref{Interaction_2} with respect to case \ref{Interaction_1}, this seems the key factor in the difference seen in the operating diagrams.}
+	\label{Interactions}
+\end{figure}
+
+The ecological diagrams for each case are presented in figure \ref{ecological_diagrams}.
+One can see that coexistence in the same functional group is never attained for case 1, whereas for case 2 a more complex situation takes places; even a zone where more than one stable equilibria is found, implying that the outcome in that zone depends on initial conditions of the system.
+Ecological diagrams show that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
+However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law (as shown in here) or model structure involving other biological processes is required to include microbial diversity.
+
+Operating diagrams can be seen in \ref{operating_diagrams} note CN can be achieved at a more elevated dilution rate in case 2 than in case 1, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are positive and stronger in case 2, thus helping them survive through bigger dilution rates.
+The appearance of a zone in case 2 where both CN and PN might take place (depending on the initial conditions of the system) is due to the presence of multiple stable equilibrium at that operating conditions.
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{ED_parameters_Dumont}
+		\caption{Case 1 ecological diagram.}
+	\end{subfigure}
+~
+	\begin{subfigure}[b]{0.45\textwidth}
+	\includegraphics[width=\textwidth]{ED_parameters_modified}
+	\caption{Case 2 ecological diagram.}
+	\end{subfigure}
+	\caption{Ecological diagrams for both cases.
+The different zones represent the combination of surviving species in the steady state.
+PN takes place when neither $x_3$ nor $x_4$ are present.
+MSE means multiple stable equilibria.
+CN takes place if $x_3$ or $x_4$ are present.
+A complex situation emerges in ecological terms for case 2, depending on the operating parameters the community can go from a single species surviving in the chemostat to full coexistence.
+}
+	\label{ecological_diagrams}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering	
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{OD_parameters_Dumont}
+		\caption{Case 1 operating diagram.}
+	\end{subfigure}
+~
 	\begin{subfigure}[b]{0.45\textwidth}
 		\includegraphics[width=\textwidth]{OD_parameters_modified}
-	\end{subfigure}
-	\caption{Left: random interaction matrix associated with model \eqref{system} for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
-Right: associated operating diagram with parameters in Table \ref{Parameters Modified}.
-The 8 different zones represent the surviving species in the steady state.
-PN takes place when neither $x_3$ nor $x_4$ are present.
-CN takes place if $x_3$ or $x_4$ are present.}
-	\label{OD modified}
-\end{figure}
-
-\begin{figure}
-		\includegraphics[width=\textwidth]{ED_parameters_modified}
-		\caption{Ecological Diagram for system.
-A complex situation emerges in ecological terms, depending on the operating parameters the community can go from a single species surviving in the chemostat to full coexistence.}
-		\label{ED_modified}
-\end{figure}
-\clearpage
+		\caption{Case 2 operating diagram.}
+	\end{subfigure}
+	\caption{Operating Diagrams for both cases.
+Case 1 Operating diagram coincides with the ecological diagram.
+Note how in case 2 CN might occur at bigger dilution rates than case 1.
+There is also a thin line where both CN and PN may arise depending on initial conditions.}
+	\label{operating_diagrams}
+\end{figure}
 
@@
 In the previous sections interactions were modelled as an affine function of the OTU concentration that multiplies a substrate dependent growth equation.
-
 More generally the interaction function represents how the growth rate of species $i$ is affected by the concentration of other species, $x$:

### 2020-03-17 Stability Analysis no interactions/dynamic_jacobian.m
bug fix parameter muB

@@ -2,7 +2,7 @@ function J = dynamic_jacobian(z,kA,kB,muA,muB,kSA,kSB,D)
 J = zeros(5,5);
 J(1,1) = muA*z(3)/(kSA+z(3))-D;
 J(1,3) = muA*kSA*z(1)/(kSA+z(3))^2;
-J(2,2) = muA*z(4)/(kSB+z(4))-D;
+J(2,2) = muB*z(4)/(kSB+z(4))-D;
 J(2,4) = muB*kSB*z(2)/(kSB+z(4))^2;
 J(3,1) = -kA*muA*z(3)/(kSA+z(3));
 J(3,3) = -D-kA*muA*kSA*z(1)/(kSA+z(3))^2;

### 2020-03-17 Tracking/regroup_functional_groups.m
add file for regrouping functional classification in AOB and NOB

@@ -1,0 +1,13 @@
+close all
+clear
+load('MAT_files\Classification_day_183_315_gurobi')
+index_AOB = find(class_AOB);
+index_NOB = find(class_NOB);
+total_AOB = sum(OTU_interp(:,index_AOB),2);
+total_NOB = sum(OTU_interp(:,index_NOB),2);
+OTU_interp = [total_AOB total_NOB];
+yields_AOB = [1/yA_ref ; 0];
+yields_NOB = [0 ; 1/yB_ref];
+class_AOB = [1; 0];
+class_NOB = [0; 1];
+save('MAT_files\Classification_day183_315_regroup_OTU')

### 2020-03-19 tex/Article_Interactions.tex
changes in stability analysis presentation

@@
 \begin{align}
-\label{Reaction1} \tag{R G1} 	s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_1 \quad \forall i \in G_1 \\
+\label{Reaction1} \tag{R G1} 	s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
 \label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
@@
 Operating and ecological diagrams are created from this stability analysis.
-Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$.
-
-For checking local asymptotic stability of the equilibria points, the Jacobian of the system is provided and evaluated at each of these points.
+Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$: In a $D-S_{in}$ plane different zones representing the stability properties of system \eqref{system} are identified.
+
+For checking local asymptotic stability of the equilibrium points, the Jacobian of the system is provided and evaluated at each of these points.
 The resulting matrix's eigenvalues must have negative real part.
@@
 
-Operating and ecological diagrams are created by running algorithm \ref{StabilityAnalysis} for different pairs $(s_{in},D)$ \cite{lobry2017chemostat}.
-In the case of operating diagrams all the pairs $(s_{in},D)$ are regrouped such that the points of the set $\mathcal{P}$ represent when partial nitrification (PN), complete nitrification (CN), washout (WO), or a combination of them may arise \cite{KHIN2004519}.
+Operating and ecological diagrams are created by running algorithm \ref{StabilityAnalysis} for different pairs $(s_{in},D)$.
+In the case of operating diagrams\cite{lobry2017chemostat} (OD) all the pairs $(s_{in},D)$ are regrouped such that the points of the set $\mathcal{P}$ represent when partial nitrification (PN), complete nitrification (CN), washout (WO), or a combination of them may arise \cite{KHIN2004519}.
 PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ are washed out and thus no conversion from $s_2$  to $s_3$ takes place.
@@
 
-In the case of ecological diagrams the pairs are regrouped such that the points in the set $\mathcal{P}$ have the same non-active coordinates.
+In the case of ecological diagrams (ED) the pairs are regrouped such that the points in the set $\mathcal{P}$ have the same non-active coordinates.
 Ecological diagrams provide more information than operating diagrams, in the sense that one can infer the operating diagram from an ecological diagram.
-However for exposure of the subject both of them are shown.
-
-Two examples are used for illustrating the diversity of situations that may arise from this type of system.
-Kinetic parameters of cases 1 and 2 can be seen in table \ref{kinetic_parameters}.
+However for exposure of the subject OD are used in the first case study, while ED are used in the second case study.
+
+A first example using operating diagrams is presented to illustrate how adding interactions in a model consisting of 1 OTU in $G_1$ and 1 OTU in $G_2$ may lead to very different outcomes.
+
+\textbf{Case study 1: 1 AOB and 1 NOB}
+
+Consider the case where $n_1 = 1$ and $n_2 = 1$.
+Two set of parameters for For gaining some insight the comparison of the operating diagrams where no interactions take place ($A = 0$) and with a non-zero, as shown in \ref{case1_no_interactions} and \ref{case1_interactions}.
+When $A=0$ the analysis above presented is no longer valid (A is not invertible), nevertheless the stability analysis is much simpler and is given in the supplementary material section.
+Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while the interaction matrices.
+
+The operating diagram can be seen in figure \ref{OD_no_interactions}, note how partial nitrification (washout of $G_2$).
+When compared to \ref{OD_no_interactions} one notes that at low $s_{in}$ the curve dividing the PN zone from the CN zone are alike.
+But since more $s_{in}$ means more $x_1$, at high $s_{in}$ the affine part $(1+ a_{21}x_1 +a_{22}x_2)$ of the growth function of $x_2$ plays a bigger role than substrate limitation ($\frac{s_2}{s_2+K_2}$).
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|l|l|l|l|}
+		\hline
+		Kinetic Parameters & $\mu_i\,[1/day]$ & $K_i\,[g/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+		$x_1 \in G_1$ & 0.77  & 0.7 & 3.98  \\ \hline
+		$x_2\in G_2$ & 1.07 & 0.3 &  16.12 \\ \hline
+	\end{tabular}	
+	\caption{A set of kinetic parameters of model \eqref{system}.}
+	\label{kinetic_parameters_case_study_1}
+\end{table}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width = \textwidth]{Stability/Interactions_case_study_1_no_interactions}
+		\caption{Interaction matrix of model \eqref{system} with no interactions.}
+		\label{case1_no_interactions}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width = \textwidth]{Stability/Interactions_case_study_1}
+		\caption{Interaction matrix of model \eqref{system}.}
+		\label{case1_interactions}
+	\end{subfigure}
+	\caption{Interaction matrices.
+Note how the presence of $x_1$ affects very negatively $x_2$ in \eqref{case1_interactions}.
+The sign of terms in the diagonal entries of the matrix represents interspecies interactions.}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width = \textwidth]{Stability/OD_case_study_1_no_interactions}
+		\caption{Operating diagram of model \eqref{system} with no interactions (interaction matrix represented by \eqref{case1_no_interactions}).}
+		\label{OD_no_interactions}
+	\end{subfigure}
+~
+	\begin{subfigure}[b]{0.45\textwidth}
+	\includegraphics[width = \textwidth]{Stability/OD_case_study_1}
+	\caption{Operating diagram of model \eqref{system} with interactions represented by \eqref{case1_interactions}.}
+	\label{OD_interactions}
+	\end{subfigure}
+	\caption{Note how \ref{OD_interactions} has a much larger zone where partial nitrification takes place. This is due to the negative interaction $x_1$ plays against $x_2$.}
+\end{figure} 
+\clearpage
+
+\textbf{Case study 2: 2 AOB and 2 NOB}
+
+Kinetic parameters of case study 2 can be seen in table \ref{kinetic_parameters}.
 Interaction matrices of each case are shown in figure \ref{Interactions}.
 Case 1 was taken from Dumont \textit{et al.}\cite{Dumont2016} where they proposed a distribution of parameters obtained with a Bayesian estimation method.
-Their fit describes well the dynamics of the OTU two most abundant OTU in each functional group, but is not the case for measured substrates.
+Their fit describes well the dynamics of the two most abundant OTU in each functional group, but it still fails to capture the measured substrates dynamics.
 
@@
 		\hline
-		Case 1 & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+		Case study 2 kinetic parameters & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
 		$x_1 \in G_1$ & 0.828  & 0.147 & 3.85  \\ \hline
@@
 	\end{tabular}
-~
-\begin{tabular}{|l|l|l|l|}
-	\hline
-	Case 2  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
-	$x_1 \in G_1$ &0.828  &0.147  & 5 \\ \hline
-	$x_2\in G_1$ & 0.621 & 0.0147 & 3 \\ \hline
-	$x_3\in G_2$ & 0.18 & 0.026 & 110 \\ \hline
-	$x_4\in G_2$ & 0.135& 0.0026& 90 \\ \hline
-\end{tabular}
-
-	\caption{Kinetic parameters of model \eqref{system}. Case 1 is taken from Dumont \textit{et al} \cite{Dumont2016}. Case 2 is a modification of the original parameters for model exploration.}
+	\caption{Kinetic parameters of model \eqref{system}.
+Case 1 is taken from Dumont \textit{et al} \cite{Dumont2016}.
+Case 2 is a modification of their original interaction matrix for model exploration.}
 	\label{kinetic_parameters}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-	\includegraphics[width=\textwidth]{Interactions_Parameters_Dumont}
-	\caption{Case 1 interaction matrix.}
+	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_Dumont}
+	\caption{Originally calibrated interaction matrix.}
 	\label{Interaction_1}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-	\includegraphics[width=\textwidth]{Interactions_Parameters_modifed}
-	\caption{Case 2 interaction matrix.}
+	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified}
+	\caption{Modified interaction matrix.}
 	\label{Interaction_2}
@@
 	\caption{Interaction matrices for each case for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
-Note how OTU 1 affect very positively OTU 3 and 4 in figure \ref{Interaction_2} with respect to case \ref{Interaction_1}, this seems the key factor in the difference seen in the operating diagrams.}
+Only the entries $a_{11}$, $a_{12}$, and $a_{21}$ were modified, accounting for reciprocal positive interactions between $x_1$ and $x_2$.}
 	\label{Interactions}
@@
 One can see that coexistence in the same functional group is never attained for case 1, whereas for case 2 a more complex situation takes places; even a zone where more than one stable equilibria is found, implying that the outcome in that zone depends on initial conditions of the system.
-Ecological diagrams show that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+Note that CN can be achieved at a more elevated dilution rate in case 2 than in case 1, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are positive and stronger in case 2, thus helping them survive through bigger dilution rates.
+
+ Ecological diagrams also show that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
 The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
@@
 
-Operating diagrams can be seen in \ref{operating_diagrams} note CN can be achieved at a more elevated dilution rate in case 2 than in case 1, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are positive and stronger in case 2, thus helping them survive through bigger dilution rates.
+%
+%Operating diagrams can be seen in \ref{operating_diagrams} note CN can be achieved at a more elevated dilution rate in case 2 than in case 1, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are positive and stronger in case 2, thus helping them survive through bigger dilution rates.
 The appearance of a zone in case 2 where both CN and PN might take place (depending on the initial conditions of the system) is due to the presence of multiple stable equilibrium at that operating conditions.
+%
 
@@
 	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=\textwidth]{ED_parameters_Dumont}
-		\caption{Case 1 ecological diagram.}
+		\includegraphics[width=\textwidth]{Stability/ED_parameters_Dumont}
+		\caption{Original parameters ecological diagram.}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{0.45\textwidth}
-	\includegraphics[width=\textwidth]{ED_parameters_modified}
-	\caption{Case 2 ecological diagram.}
+	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified}
+	\caption{Modified interaction matrix ecological diagram.}
 	\end{subfigure}
@@
 
-\begin{figure}[ht]
-	\centering	
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=\textwidth]{OD_parameters_Dumont}
-		\caption{Case 1 operating diagram.}
-	\end{subfigure}
-~
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=\textwidth]{OD_parameters_modified}
-		\caption{Case 2 operating diagram.}
-	\end{subfigure}
-	\caption{Operating Diagrams for both cases.
+%
+%\begin{figure}[ht]
+%	\centering	
+%	\begin{subfigure}[b]{0.45\textwidth}
+%		\includegraphics[width=\textwidth]{Stability/OD_parameters_Dumont}
+%		\caption{Case 1 operating diagram.}
+%	\end{subfigure}
+%~
+%	\begin{subfigure}[b]{0.45\textwidth}
+%		\includegraphics[width=\textwidth]{Stability/OD_parameters_modified}
+%		\caption{Case 2 operating diagram.}
+%	\end{subfigure}
+%	\caption{Operating Diagrams for both cases.
 Case 1 Operating diagram coincides with the ecological diagram.
@@
 There is also a thin line where both CN and PN may arise depending on initial conditions.}
-	\label{operating_diagrams}
-\end{figure}
+%	\label{operating_diagrams}
+%\end{figure}
+%
+%
 
@@
 The approach was tested against synthetic data.
-The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2}, therefore the interaction function $I(x) = 1 + Ax$), $f_i(s) = \dfrac{s_1}{K_i +s_1}$ for $i \in G_1$, and $f_i(s) = \dfrac{s_2}{K_i +s_2}$ for $i \in G_2$, for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}.
-Parameters of the simulation can be seen in table .
-A simulation of the synthetic data is presented in figure \ref{fig:nonoise200121aobplot} and figure \ref{fig:nonoise200121nobplot} depending on operating parameters $D$ and $s_{in}$.
+The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2}.
+Therefore in the former framework the interaction function is $I(x) = 1 + Ax$, $f_i(s) = \dfrac{s_1}{K_i +s_1}$ for $i \in G_1$, and $f_i(s) = \dfrac{s_2}{K_i +s_2}$ for $i \in G_2$, for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}.
+Parameters of the simulation can be seen in table.
+The simulated synthetic OTU trajectories can be seen in figures \ref{fig:nonoise200121aobplot} and \ref{fig:nonoise200121nobplot}, and the metabolites can be seen in figure \ref{fig:nonoise200121metabolites}.
+
+The operating and ecological diagrams are shown in figure.
 
@@
 		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $k_i =\frac{1}{y_i} \, [gr/gr]$ \\ \hline
-		$x_i \in G_1$ &0.77  &0.07  & 3.94 \\ \hline
-		$x_i\in G_2$ & 0.621 & 0.0147 & 16.12 \\ \hline
+		$x_i \in G_1$ &0.77  &0.7  & 3.94 \\ \hline
+		$x_i\in G_2$ & 0.621 & 1.3 & 16.12 \\ \hline
 	\end{tabular}
@@
 	\begin{subfigure}{0.45 \linewidth}
-	\includegraphics[width=\linewidth]{Images/proof_of_concept/no_noise_200121_AOB_plot}
+	\includegraphics[width=\linewidth]{proof_of_concept/no_noise_200121_AOB_plot}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Images/proof_of_concept/no_noise_200121_NOB_plot}
+	\includegraphics[width=\linewidth]{proof_of_concept/no_noise_200121_NOB_plot}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{Images/proof_of_concept/no_noise_200121_metabolites}
+	\includegraphics[width=0.5\linewidth]{proof_of_concept/no_noise_200121_metabolites}
 	\caption{}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
+		\includegraphics[width=\linewidth]{Synthetic_data_no_noise/Interactions_synthetic_data_no_noise}
 		\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
@@
 For applying the optimal tracking approach, the choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
-$Q$ represents the covariance matrix of measurements, while $R$ is subject to interpretations depending on the context: in the case here it does not have a definite meaning, however its behaviour is studied when $\rho(R) \rightarrow 0$, with $\rho(R)$ being the spectral radius of matrix $R$.
+$Q$ represents the covariance matrix of measurements, while $R$ is subject to interpretations depending on the context: in the case here presented it does not have \textit{a priori} definite meaning.
+For gaining some insight, its behaviour is studied when $\rho(R) \rightarrow 0$, with $\rho(R)$ being the spectral radius of matrix $R$.
 In the simulations here presented $Q = I_n$ and $R = \lambda I_n$.
-$\lambda$ is varied from $10^{-1}$ to $10^{-7}$ in the supplementary material section.
+In the supplementary material section.
+$\lambda$ is varied from $10^{-1}$ to $10^{-7}$.
 The case $\lambda = 10^{-4}$ is shown in here for discussion.

### 2020-03-23 Stability Analysis gLV/parametres_modified.m
modified entry of gLV model

@@ -2,16 +2,22 @@ clear
 nA = 2;
 nB = 2;
 n = nA + nB;
-A =[   -0.0664    0.6279   -1.8849   -0.3030;
-    1.3460   -1.5750   -1.1231   -0.1666;
-    3.5464    0.3289   -0.2537    0.0796;
-    2.8857   -0.1071    0.6042   -0.4122];
-muA= [0.828 0.75*0.828]';
-muB= [0.18 0.75*0.18]';
-kSA = 10^(-3)*[0.147 0.0147]';
-kSB = 10^(-3)*[0.026 0.0026]';
+% A =[   -0.0664    0.6279   -1.8849   -0.3030;
+%     1.3460   -1.5750   -1.1231   -0.1666;
+%     3.5464    0.3289   -0.2537    0.0796;
+%     2.8857   -0.1071    0.6042   -0.4122];
+A =[ 0.087    0   -0.697   4.815;
+    0   0.476  0.995   -6.362;
+    0.437    0.1   -0.14    -1.225;
+    -0.66   -0.35    -0.837   3.25];
+muA= [0.828 0.828]';
+muB= [0.18 0.18]';
+kSA = 10^(-3)*[0.147 0.147]';
+kSB = 10^(-3)*[0.026 0.026]';
+% kSA = [0.147 0.147]';
+% kSB = [0.026 0.026]';
  %D = 1.1875; %0.7/6.5- 
 %D = 2.2/6.5;
-kA = [5; 3];
-kB = [110; 90];
+kA = 1./[0.26 0.26]';
+kB = 1./[0.01 0.01]';
 save('MAT_files\parameters_modified');

### 2020-03-23 Stability Analysis gLV/test_equilibria.m
added dynamic evaluation tolerance for justifying equilibria

@@ -21,24 +21,23 @@ fprintf('Trajectory at T= %d \n Point =%s \n Evaluated in dynamic = %s\n',...
 J = dynamic_jacobian(Y(end,:)',A,nA,nB,kA,kB,muA,muB,kSA,kSB,dilution);
 eigenvalues = eig(J);
 if all(real(eigenvalues) <0)
-    fprintf('Stable Equilibrium: %1.4f', Y(end,:)');
+    fprintf('Stable Equilibrium: %s\n',sprintf( '%1.4f', Y(end,:)'));
     disp(eigenvalues)
 end
 [possible_x, possible_s1, possible_s2, possible_s3]  = equilibria(A,...
     nA,nB,kA,kB,muA,muB,kSA,kSB,dilution,s_in);
 possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
-num_equilibria = 0;
-
+tolerance = 1e-10;
 for i=1:length(possible_equilibria(1,:))
-    if all(possible_equilibria(:,i) >=0) && isreal(possible_equilibria(:,i))
-        num_equilibria = num_equilibria +1;
-%         fprintf('\n Positive Equilibrium %d =', num_equilibria);
-%         disp(possible_equilibria(:,i)')
+    c_positivity = all(possible_equilibria(:,i) >=0);
+    c_real_number = isreal(possible_equilibria(:,i));
+    c_evaluation_in_dynamic =all(fun(1,possible_equilibria(:,i))< tolerance);
+    if c_positivity && c_real_number && c_evaluation_in_dynamic
         J = dynamic_jacobian(possible_equilibria(:,i),A,nA,nB,kA,kB,muA,muB,kSA,kSB,dilution);
         eigenvalues = eig(J);
         if all(real(eigenvalues) <0)
             disp(possible_equilibria(:,i)')
-            fprintf('Equilibrium %d: Stable Equilibrium! \n Eigenvalues of the Jacobian in the Equilibrium : \n', num_equilibria);
+            fprintf('Equilibrium %d: Stable Equilibrium! \n Eigenvalues of the Jacobian in the Equilibrium : \n', i);
             disp(eigenvalues)
         end
     end

### 2020-03-24 tex/Article_Interactions.tex
Changes in .tex and associated graphics

@@
 Consider the case where $n_1 = 1$ and $n_2 = 1$.
-Two set of parameters for For gaining some insight the comparison of the operating diagrams where no interactions take place ($A = 0$) and with a non-zero, as shown in \ref{case1_no_interactions} and \ref{case1_interactions}.
+For gaining some insight the comparison of the operating diagrams where no interactions take place ($A = 0$) and with a non-zero, as shown in \ref{case1_no_interactions} and \ref{case1_interactions}.
 When $A=0$ the analysis above presented is no longer valid (A is not invertible), nevertheless the stability analysis is much simpler and is given in the supplementary material section.
-Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while the interaction matrices.
+Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while the interaction matrices can be seen .
 
@@
 
+ The case study 2 is based on Dumont \textit{et al.}\cite{Dumont2016} model parameters.
+Again for studying the model behaviour a modification of the original interaction matrix is performed.
+They proposed a distribution of parameters obtained from a Bayesian estimation method.
+Their fit describes well the dynamics of the two most abundant OTU in each functional group, but it still fails to capture the measured substrates dynamics.
 Kinetic parameters of case study 2 can be seen in table \ref{kinetic_parameters}.
-Interaction matrices of each case are shown in figure \ref{Interactions}.
-Case 1 was taken from Dumont \textit{et al.}\cite{Dumont2016} where they proposed a distribution of parameters obtained with a Bayesian estimation method.
-Their fit describes well the dynamics of the two most abundant OTU in each functional group, but it still fails to capture the measured substrates dynamics.
+The original interaction matrix estimated by them is seen in \ref{Interaction_1}.
+A second matrix is presented, which is obtained from modification on the sign of coefficient $a_{11}$ as seen in \ref{Interaction_2}, and finally a third one is obtained by changing the value of $a_{12}$ from the original matrix.
 
@@
 \begin{figure}[h]
-\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{0.3\textwidth}
 	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_Dumont}
@@
 ~
-\begin{subfigure}[b]{0.45\textwidth}
+\begin{subfigure}[b]{0.3\textwidth}
 	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified}
-	\caption{Modified interaction matrix.}
+	\caption{Modified interaction matrix with positive intra species interaction for $x_1$.}
 	\label{Interaction_2}
 \end{subfigure}
+~
+\begin{subfigure}[b]{0.3\textwidth}
+	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified_2}
+	\caption{Modified interaction matrix with positive intra species interaction for $x_1$.}
+	\label{Interaction_3}
+\end{subfigure}
 	\caption{Interaction matrices for each case for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
-Only the entries $a_{11}$, $a_{12}$, and $a_{21}$ were modified, accounting for reciprocal positive interactions between $x_1$ and $x_2$.}
+Only the sign of the entry $a_{12}$ was modified with respect to the original matrix.
+Representing the a positive interspecies interaction of $x_2$ on $x_1$.}
 	\label{Interactions}
 \end{figure}
-
-The ecological diagrams for each case are presented in figure \ref{ecological_diagrams}.
-One can see that coexistence in the same functional group is never attained for case 1, whereas for case 2 a more complex situation takes places; even a zone where more than one stable equilibria is found, implying that the outcome in that zone depends on initial conditions of the system.
-Note that CN can be achieved at a more elevated dilution rate in case 2 than in case 1, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are positive and stronger in case 2, thus helping them survive through bigger dilution rates.
-
- Ecological diagrams also show that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
-The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
-However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law (as shown in here) or model structure involving other biological processes is required to include microbial diversity.
 
@@
 	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{subfigure}[b]{0.3\textwidth}
 		\includegraphics[width=\textwidth]{Stability/ED_parameters_Dumont}
@@
 ~
-	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{subfigure}[b]{0.3\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified}
@@
 	\end{subfigure}
+~
+\begin{subfigure}[b]{0.3\textwidth}
+	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified_2}
+	\caption{Modified interaction matrix ecological diagram.}
+\end{subfigure}
+
 	\caption{Ecological diagrams for both cases.
@@
 
+The ecological diagrams for each case are presented in figure \ref{ecological_diagrams}.
+One can see that coexistence in the same functional group is never attained for case 1, whereas for case 2 $x_1$ and $x_2$, both AOB, coexist in either partial or complete nitrification.
+Ecological diagrams also show that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
+However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law (as shown in here) or model structure involving other biological processes is required to include microbial diversity.
+
+\clearpage
 %

### 2020-03-26 Stability Analysis gLV/equilibria.m
Stability analysis changes, added better plotting.

@@ -10,6 +10,7 @@ k = [kA;kB];
 vec_aux1 = (D-[muA; muB])./[muA; muB];
 vec_aux2 = D*[kSA ; kSB]./[muA; muB];
 for i = 1:2^nA-1
+    %CN
     for j = 1:2^nB-1
         considered_species = find([de2bi(i,nA) de2bi(j,nB)]);
         A_act = A(considered_species, considered_species);
@@ -42,6 +43,7 @@ for i = 1:2^nA-1
         end
         counter = counter +4;
     end
+    %PN
     considered_species = find([de2bi(i,nA) de2bi(0,nB)]);
     A_act = A(considered_species, considered_species);
     B = diag(k(considered_species))/A_act;

### 2020-03-26 Stability Analysis gLV/operating_diagram.m

@@ -1,9 +1,9 @@
 close all
 clear
-file_name_in = 'default_case';
+file_name_in = 'parameters_modified_2';
 load(sprintf('MAT_files\\%s',file_name_in));
-file_name_out = 'default_case';
-number_of_points = 100;
+file_name_out = 'parameters_modified_2';
+number_of_points = 400;
 d_initial = 0.7/6.5;
 d_final =  2.2/6.5;
 s_in_initial = 0.5;
@@ -17,20 +17,28 @@ map_zones_ED = containers.Map;
 zones_OD = ones(n1,n2);
 zones_ED = zeros(n1,n2);
 percentage = round(linspace(1,n1,11));
+tolerance = 1e-9;
 tic
 for i = 1:n1
     for j = 1:n2
+        s_in = s_in_vector(i);
+        D = D_vector(j);
+%         fun =  dynamic(A,nA,nB,kA,kB,muA,muB,kSA,kSB,@(t) D,@(t) s_in);
         [possible_x, possible_s1, possible_s2, possible_s3] = equilibria(A,...
-            nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j),s_in_vector(i));
+            nA,nB,kA,kB,muA,muB,kSA,kSB,D,s_in);
         possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
         flag_PN = 0;
         flag_CN = 0;
         flag_washout = 0;
         key_string = '';
         for k=1:length(possible_equilibria(1,:))
-            if all(possible_equilibria(:,k) >=0) && isreal(possible_equilibria(:,k))
-                J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D_vector(j));
-                if all(real(eig(J)) <0)
+            c_positivity = all(possible_equilibria(:,k) >=0);
+            c_real_number = isreal(possible_equilibria(:,k));
+%             c_evaluation_in_dynamic =all(fun(1,possible_equilibria(:,k))< tolerance);
+            if c_positivity && c_real_number % && c_evaluation_in_dynamic
+                J = dynamic_jacobian(possible_equilibria(:,k),A,nA,nB,kA,kB,muA,muB,kSA,kSB,D);
+                eigenvalues = eig(J);
+                if all(real(eigenvalues) <0)
                     positive_equilibria = (possible_x(:,k)>0)';
                     index_aux = find(positive_equilibria);
[…]

### 2020-03-26 Stability Analysis gLV/parametres_modified.m

@@ -2,11 +2,11 @@ clear
 nA = 2;
 nB = 2;
 n = nA + nB;
-% A =[   -0.0664    0.6279   -1.8849   -0.3030;
-%     1.3460   -1.5750   -1.1231   -0.1666;
-%     3.5464    0.3289   -0.2537    0.0796;
-%     2.8857   -0.1071    0.6042   -0.4122];
-A =[ 0.087    0   -0.697   4.815;
+% A =[ 0.087    0   -0.697   4.815;
+%     0   0.476  0.995   -6.362;
+%     0.437    0.1   -0.14    -1.225;
+%     -0.66   -0.35    -0.837   3.25];
+A =[ -0.087    0.6  -0.697   4.815;
     0   0.476  0.995   -6.362;
     0.437    0.1   -0.14    -1.225;
     -0.66   -0.35    -0.837   3.25];
@@ -20,4 +20,4 @@ kSB = 10^(-3)*[0.026 0.026]';
 %D = 2.2/6.5;
 kA = 1./[0.26 0.26]';
 kB = 1./[0.01 0.01]';
-save('MAT_files\parameters_modified');
+save('MAT_files\parameters_modified_2');

### 2020-03-26 Stability Analysis gLV/plot_ecological_diagram.m

@@ -1,10 +1,16 @@
 clear
 close all
-file_name_in = 'default_case';
+file_name_in = 'parameters_modified';
 load(sprintf('MAT_files\\Operating_Diagram_%s',file_name_in))
-figure;
-number_of_zones = length(map_zones_ED);
+%Only for parameters_modifed
+number_of_zones = length(map_zones_ED)-1;
+zones_ED(zones_ED == 4) = 2;
+%end fix ED
+%Normal Zone
+% number_of_zones = length(map_zones_ED);
 cmap1 = hsv(number_of_zones);
+% End_zone
+figure;
 [X,Y] = meshgrid(s_in_vector,D_vector);
 surfc(X,Y,zones_ED','EdgeColor','none','LineStyle','none','FaceLighting','phong');%view(2)
 colormap(cmap1)
@@ -18,29 +24,31 @@ for i = map_zones_ED.keys
         if max(index_aux) == 0;
             label = 'Washout';
         elseif max(index_aux) <= nA;
-            label = sprintf('PN: %s',str_aux);
+            label = sprintf('%s',str_aux);
         else
-            label = sprintf('CN: %s',str_aux);
+            label = sprintf('%s',str_aux);
         end
-    else 
-        mat_aux = reshape(vec_aux,n,length_vec/n);
-        flag_PN_and_CN = sum(any(mat_aux(nA+1:end,:)))<length_vec/n;
-        flag_CN = all(any(mat_aux(nA+1:end,:)));
-        flag_washout_PN = ~all(any(mat_aux));
-        if flag_CN
-            str_aux = 'CN';
-        elseif flag_PN_and_CN
-            str_aux = 'CN & PN';
-        elseif flag_washout_PN
-            str_aux = 'Washout & PN';
+    else
+        number_of_eq = length_vec/n;
+        mat_aux = reshape(vec_aux,n,number_of_eq);
+        str_aux = '';
+        for j = 1:number_of_eq
+            index_aux = find(mat_aux(:,j));
+            str_aux = sprintf('%s%0.f) %s\\newline',str_aux,j,sprintf('x_{%.0f}',index_aux));
         end
-        label = sprintf('%s: MSE',str_aux);
+        str_aux = str_aux(1:end);
+%         text(
+%         flag_PN = sum(any(mat_aux(nA+1:end,:))) == 0;
[…]

### 2020-03-26 Stability Analysis gLV/plot_interactions.m

@@ -1,6 +1,6 @@
 clear
 close all
-file_in = 'default_case';
+file_in = 'parameters_modified_2';
 load(sprintf('MAT_files/%s',file_in));
 labels = cell(n);
 for i=1:n
@@ -13,8 +13,9 @@ text_strings = strtrim(cellstr(text_strings));  % Remove any space padding
 [x, y] = meshgrid(1:n);  % Create x and y coordinates for the strings
 hStrings = text(x(:), y(:), text_strings(:), ...  % Plot the strings
                 'HorizontalAlignment', 'center','fontsize',12);
-mid_value = mean(get(gca, 'CLim'));  % Get the middle value of the color range
-text_colors = repmat(A(:) > mid_value, 1, 3);  % Choose white or black for the
+color_range = get(gca, 'CLim');
+mid_value = mean(color_range)-0.8;  % Get the middle value of the color range
+text_colors = repmat(A(:) <mid_value, 1, 3);  % Choose white or black for the
                                                %   text color of the strings so
                                                %   they can be easily seen over
                                                %   the background color

### 2020-03-26 Stability Analysis gLV/test_equilibria.m

@@ -1,15 +1,15 @@
 clear
 close all
 % generateParameters;
-file_name_in = 'default_case';
+file_name_in = 'parameters_modified_2';
 load(sprintf('MAT_files\\%s',file_name_in));
 z0 = random('Uniform',0,1,n+3,1);
 OTU = 1:n;
 options = odeset('NonNegative',1:(nA+nB+3));
-dilution = 0.2359 ;
-D = @(t) dilution;
-s_in = 1.833;
+s_in = 1.602;
 sIn = @(t) s_in;
+dilution = 0.1925 ;
+D = @(t) dilution;
 tF = 20000;
 fun =  dynamic(A,nA,nB,kA,kB,muA,muB,kSA,kSB,D,sIn);
 [T,Y] = ode15s(fun,[0 tF], z0,options);
@@ -27,7 +27,7 @@ end
 [possible_x, possible_s1, possible_s2, possible_s3]  = equilibria(A,...
     nA,nB,kA,kB,muA,muB,kSA,kSB,dilution,s_in);
 possible_equilibria = [possible_x; possible_s1; possible_s2; possible_s3];
-tolerance = 1e-10;
+tolerance = 1e-6;
 for i=1:length(possible_equilibria(1,:))
     c_positivity = all(possible_equilibria(:,i) >=0);
     c_real_number = isreal(possible_equilibria(:,i));

### 2020-03-26 Stability Analysis no interactions/operating_diagram.m

@@ -3,7 +3,7 @@ clear
 file_name_in = 'default_case';
 load(sprintf('MAT_files\\%s',file_name_in));
 file_name_out = 'default_case';
-number_of_points = 100;
+number_of_points = 300;
 d_initial = 0.7/6.5;
 d_final =  2.2/6.5;
 s_in_initial = 0.5;

### 2020-03-26 Stability Analysis no interactions/test_equilibria.m

@@ -1,15 +1,14 @@
 clear
 close all
-% generateParameters;
 file_name_in = 'default_case';
 load(sprintf('MAT_files\\%s',file_name_in));
 % z0 = random('Uniform',0,1,5,1);
-z0 = [0.1 0.000001 0 0 0];
+z0 = [0.1 0.1 0 0 0];
 OTU = 1:2;
 options = odeset('NonNegative',1:5);
-dilution = 0.26 ;
+dilution = 0.3;
 D = @(t) dilution;
-s_in = 0.89;
+s_in = 1.25;
 sIn = @(t) s_in;
 tF = 20000;
 fun =  dynamic(kA,kB,muA,muB,kSA,kSB,D,sIn);
@@ -28,7 +27,6 @@ end
 [possible_x1, possible_x2, possible_s1, possible_s2, possible_s3]  = equilibria(kA,kB,muA,muB,kSA,kSB,dilution,s_in);
 possible_equilibria = [possible_x1'; possible_x2'; possible_s1'; possible_s2'; possible_s3'];
 num_equilibria = 0;
-
 for i=1:length(possible_equilibria(1,:))
     if all(possible_equilibria(:,i) >=0) && isreal(possible_equilibria(:,i))
         num_equilibria = num_equilibria +1;

### 2020-03-26 Tracking/plot_data_fit.m
synthetic data with perturbation

@@ -1,7 +1,7 @@
 %plotting
 clear
 close all
-name_file_in = 'MAT_Files\\191218_Reactor_A_iter_45';
+name_file_in = 'MAT_Files\\250309_POC_try4_iter_3';
 load(name_file_in);
 legend_tags_biomass{1} = 'Data: Sum of species biomass';
 legend_tags_biomass{2} = 'Tracking: Sum of species biomass';
@@ -13,7 +13,7 @@ s_vec = x_new(:,(n+1):end);
 growth_AOB = @(s) growth_monod(s,muA,kSA)';
 growth_NOB = @(s) growth_monod(s,muB,kSB)';
 growth_cell_AOB = arrayfun(growth_AOB,s_vec(:,1),'UniformOutput',false);
-growth_cell_NOB = arrayfun(growth_NOB,s_vec(:,1),'UniformOutput',false);
+growth_cell_NOB = arrayfun(growth_NOB,s_vec(:,2),'UniformOutput',false);
 growth_mat_AOB = cell2mat(growth_cell_AOB);
 growth_mat_NOB = cell2mat(growth_cell_NOB);
 growth_mat = [growth_mat_AOB growth_mat_NOB];
@@ -22,7 +22,7 @@ tic
 control_eval = arrayfun(control,t_new,'UniformOutput',false);
 toc
 control_eval_reshape = reshape(cell2mat(control_eval),n,length(t_new));
-growth_times_control = growth_mat'.*(control_eval_reshape+1);
+growth_times_control = growth_mat'.*(control_eval_reshape+1).*x_new(:,1:n)';
 %%Total Biomass
 figure
 hold on
@@ -88,7 +88,7 @@ for k = 1:number_of_AOB_plots
     figure
     growth_plot_AOB = plot(t_new,growth_times_control(OTU_plot_index,:),'LineWidth',1.5);
     xlabel('\fontsize{12}Time [days]'),...
-        ylabel('\fontsize{12}  f_i(s_1(t))u(t) [day^{-1}]'),...
+        ylabel('\fontsize{12}  f_i(s_1(t))u(t)x_i(t) [day^{-1}]'),...
         title(sprintf('Growth for AOB iter: %.0f',iter))
     set(gca,'fontsize',15),
     set(control_plot_AOB,{'Color'}, colors_AOB),
@@ -149,7 +149,7 @@ for k = 1:number_of_NOB_plots
     figure
[…]

### 2020-03-26 Tracking/synthetic_data.m

@@ -1,8 +1,8 @@
 close all
 clear
-name_file = 'no_noise';
-nA = 10;
-nB = 5;
+name_file = '250309_POC';
+nA = 1;
+nB = 1;
 n = nA + nB;
 a = ones(nA,1);
 b = ones(nB,1);
@@ -11,15 +11,21 @@ class_NOB = [zeros(nA,1); ones(nB,1)];
 time_steps_index = 1;
 muARef = 0.77;
 muBRef = 1.07;
-kSARef = 0.7e-1;
-kSBRef = 1.4982e-1;
+kSARef = 0.7;
+kSBRef = 1.3;
 kIRef = 1.217;
-x0 = [0.01*random('Unif',0,1,nA,1);0.001*random('Unif',0,1,nB,1); 0.1; 0.1; 0.1];
-d_interp = @(t) 0.2;
-s_in_interp = @(t) 0.5;
+x0 = [0.01*random('Unif',0,1,nA,1);0.01*random('Unif',0,1,nB,1); 0.1; 0.1; 0.1];
+tF = 300;
+t_pert = 150;
+s_in_init = 1.25;
+s_in_pert = 1.95;
+d_interp = @(t) 0.22;
+s_in_interp = @(t) s_in_init*(t<t_pert) + s_in_pert*(t >= t_pert);
 kA = 1/0.251*ones(nA,1);
 kB = 1/0.062*ones(nB,1);
-A = random('Normal',0,1,n,n);
+% A = random('Normal',0,1,n,n);
+A =[     1    0.1
+    -1.5   1];
 % A = zeros(n,n);
 growth1 = @(X) (1+A(1:nA,:)*X(1:n))*growth_monod(X(n+1),muARef,kSARef);
 growth2 = @(X) (1+A(nA+1:n,:)*X(1:n))*growth_monod(X(n+2),muBRef,kSBRef);
@@ -28,7 +34,7 @@ dynamic = @(t,X) [diag(growth1(X) - d_interp(t))*X(1:nA);
    (s_in_interp(t) - X(n+1))*d_interp(t) - kA'*diag(growth1(X))*X(1:nA);
     -X(n+2)*d_interp(t) + kA'*diag(growth1(X))*X(1:nA)-kB'*diag(growth2(X))*X(nA+1:n);
     -X(n+3)*d_interp(t) + kB'*diag(growth2(X))*X(nA+1:n);];
[…]

### 2020-03-26 tex/Article_Interactions.tex
adding tex and pdf files

@@
  The case study 2 is based on Dumont \textit{et al.}\cite{Dumont2016} model parameters.
-Again for studying the model behaviour a modification of the original interaction matrix is performed.
 They proposed a distribution of parameters obtained from a Bayesian estimation method.
@@
 
-The approach was tested against synthetic data.
-The test consisted in simulating system \eqref{system} with growth functions \eqref{gLV growth1} and \eqref{gLV growth2}.
-Therefore in the former framework the interaction function is $I(x) = 1 + Ax$, $f_i(s) = \dfrac{s_1}{K_i +s_1}$ for $i \in G_1$, and $f_i(s) = \dfrac{s_2}{K_i +s_2}$ for $i \in G_2$, for $n_1 = 10$ and $n_2 = 5$, with a randomly generated matrix $A$ in figure \ref{Interaction Matrix Simulation}.
-Parameters of the simulation can be seen in table.
-The simulated synthetic OTU trajectories can be seen in figures \ref{fig:nonoise200121aobplot} and \ref{fig:nonoise200121nobplot}, and the metabolites can be seen in figure \ref{fig:nonoise200121metabolites}.
-
-The operating and ecological diagrams are shown in figure.
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{|l|l|l|l|}
-		\hline
-		Modified Parameters  & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $k_i =\frac{1}{y_i} \, [gr/gr]$ \\ \hline
-		$x_i \in G_1$ &0.77  &0.7  & 3.94 \\ \hline
-		$x_i\in G_2$ & 0.621 & 1.3 & 16.12 \\ \hline
-	\end{tabular}
-	\caption{Kinetic parameters of model \eqref{system} modified from \cite{Dumont2016}.}
-	\label{Parameters_synthetic_data}
-\end{table}
+The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the study case 1 with interaction matrix given by \eqref{case1_interactions}.
+In the operating diagram of the same case (figure \eqref{OD_interactions}) the red zone implies complete nitrification, while the green zone means partial nitrification.
+For integrating the former phenomena in the simulation, the system was simulated for 300 days, and perturbed at day 150 from the CN zone ($(s_{in},D) = (1.25,0.22)$) to a PN zone ($(s_{in},D) = (1.95,0.22)$) .
 
@@
 	\begin{subfigure}{0.45 \linewidth}
-	\includegraphics[width=\linewidth]{proof_of_concept/no_noise_200121_AOB_plot}
+	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_AOB_plot}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=\linewidth]{proof_of_concept/no_noise_200121_NOB_plot}
+	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_NOB_plot}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=0.5\linewidth]{proof_of_concept/no_noise_200121_metabolites}
+	\includegraphics[width=0.5\linewidth]{proof_of_concept/250309_POC_metabolites}
 	\caption{}
 	\label{fig:nonoise200121metabolites}
-\end{figure}
-
-\begin{figure}[h]
-	\centering	
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{Synthetic_data_no_noise/Interactions_synthetic_data_no_noise}
-		\caption{Interaction matrix associated with model \eqref{system} for a simulated consortia of 15 bacterial species where $x_1$-$x_{10}$ are AOB and $x_{11}$-$x_{15}$ are NOB.}
-		\label{Interaction Matrix Simulation}
-	\end{subfigure}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Biomass_Iter_10}
-	\caption{Dotted line: simulated total biomass for model \eqref{system} with interactions shown in Figure \ref{Interaction Matrix Simulation} and parameters\iffalse quels paramètres ?\fi.
-Continuous line: total biomass as predicted  by the tracking procedure.}
+	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_Biomass_iter_2}
+	\caption{Dotted line: simulated total biomass for model \eqref{system} \iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
 	\label{Total Biomass no noise}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_AOB_Iter_10}
+	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_AOB_iter_2_plot_1}
 	\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_NOB_Iter_10}
+	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_NOB_iter_2_plot_1}
 	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_metabolites_Iter_10}
+	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_metabolites_iter_2}
 	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Control_AOB_Iter_10}
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_Control_AOB_iter_2_plot_1}
 	\caption{Control for the AOB population.}
 	\label{Control AOB no noise}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-4//191209_no_noise_Control_NOB_Iter_10}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_Control_NOB_iter_2_plot_1}
 	\caption{Control for the NOB population.}
 	\label{Control NOB no noise}
+	\end{subfigure}
+	\caption{}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_growth_AOB_iter_2_plot_1}
+		\caption{Growth rate of the model for AOB community.}
+		\label{AOB_growth_POC}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_growth_NOB_iter_2_plot_1}
+	\caption{Growth rate of the model for the NOV community.}
+	\label{NOB_growth_POC}
+	\end{subfigure}
+	\caption{}
 \end{figure}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//Comparison_different_control}
-	\caption{Obtained controled for different $\lambda$ for two OTU and the interaction function used in the simulation of synthetic data.}
-	\label{Comparison_lambda}
-\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//Comparison_different_control}
+%	\caption{Obtained controled for different $\lambda$ for two OTU and the interaction function used in the simulation of synthetic data.}
+%	\label{Comparison_lambda}
+%\end{figure}
 

### 2020-04-06 tex/Article_Interactions.tex
update of POC section

@@
 
-\textbf{Case study 1: 1 AOB and 1 NOB}
+\subsubsection{Case study 1: 1 AOB and 1 NOB}
 
 Consider the case where $n_1 = 1$ and $n_2 = 1$.
-For gaining some insight the comparison of the operating diagrams where no interactions take place ($A = 0$) and with a non-zero, as shown in \ref{case1_no_interactions} and \ref{case1_interactions}.
-When $A=0$ the analysis above presented is no longer valid (A is not invertible), nevertheless the stability analysis is much simpler and is given in the supplementary material section.
-Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while the interaction matrices can be seen .
+The operating diagrams where no interactions take place ($A = 0$) and a non-zero interaction matrix is presented.
+When $A=0$ algorithm \ref{StabilityAnalysis} is no longer valid (A is not invertible), nevertheless the stability analysis is much simpler and is given in the supplementary material section.
+Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while the interaction matrices are shown in \ref{case1_no_interactions} and \ref{case1_interactions}.
 
@@
 Kinetic parameters of case study 2 can be seen in table \ref{kinetic_parameters}.
-The original interaction matrix estimated by them is seen in \ref{Interaction_1}.
-A second matrix is presented, which is obtained from modification on the sign of coefficient $a_{11}$ as seen in \ref{Interaction_2}, and finally a third one is obtained by changing the value of $a_{12}$ from the original matrix.
+The estimated interaction matrix is shown in figure \ref{Interaction_1}.
+A second matrix is presented, which is obtained by the sign change of coefficient $a_{11}$ (figure \ref{Interaction_2}), and finally a third one is obtained by using a positive value for $a_{12}$ (figure \ref{Interaction_3}).
 
@@
 	\end{tabular}
-	\caption{Kinetic parameters of model \eqref{system}.
-Case 1 is taken from Dumont \textit{et al} \cite{Dumont2016}.
-Case 2 is a modification of their original interaction matrix for model exploration.}
+	\caption{Kinetic parameters of model \eqref{system} from Dumont \textit{et al.} \cite{Dumont2016}}
 	\label{kinetic_parameters}
@@
 \begin{figure}[h]
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_Dumont}
@@
 ~
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified}
-	\caption{Modified interaction matrix with positive intra species interaction for $x_1$.}
+	\caption{Modified interaction matrix with positive intraspecies interaction $a_{11}>0$.}
 	\label{Interaction_2}
@@
 ~
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified_2}
-	\caption{Modified interaction matrix with positive intra species interaction for $x_1$.}
+	\caption{Modified interaction matrix with positive interspecies interaction  $a_{12}>0$.}
 	\label{Interaction_3}
@@
 	\caption{Interaction matrices for each case for a consortia of 4 bacterial species where $x_1$ and $x_2$ are AOB and $x_3$ and $x_4$ are NOB.
-Only the sign of the entry $a_{12}$ was modified with respect to the original matrix.
-Representing the a positive interspecies interaction of $x_2$ on $x_1$.}
+Parameters $a_{11}$ and $a_{12}$ were modified in figures \eqref{Interaction_2} and \eqref{Interaction_3}, respectively.}
 	\label{Interactions}
@@
 
-%
-%Operating diagrams can be seen in \ref{operating_diagrams} note CN can be achieved at a more elevated dilution rate in case 2 than in case 1, which can be explained by noting that the interactions of $x_1$ on $x_3$ and $x_4$ are positive and stronger in case 2, thus helping them survive through bigger dilution rates.
-The appearance of a zone in case 2 where both CN and PN might take place (depending on the initial conditions of the system) is due to the presence of multiple stable equilibrium at that operating conditions.
-%
-
 \begin{figure}[ht]
 	\centering
-	\begin{subfigure}[b]{0.3\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_Dumont}
 	\caption{Original parameters ecological diagram.}
+	\label{ED 1}
 	\end{subfigure}
 ~
-	\begin{subfigure}[b]{0.3\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified}
 	\caption{Modified interaction matrix ecological diagram.}
+	\label{ED 2}
 	\end{subfigure}
 ~
-\begin{subfigure}[b]{0.3\textwidth}
+\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified_2}
 	\caption{Modified interaction matrix ecological diagram.}
+	\label{ED 3}
 \end{subfigure}
@@
 PN takes place when neither $x_3$ nor $x_4$ are present.
-MSE means multiple stable equilibria.
+Note that in figure \ref{ED 2} two stable equilibria exist for each zone.
 CN takes place if $x_3$ or $x_4$ are present.
-A complex situation emerges in ecological terms for case 2, depending on the operating parameters the community can go from a single species surviving in the chemostat to full coexistence.
 }
@@
 
-The ecological diagrams for each case are presented in figure \ref{ecological_diagrams}.
-One can see that coexistence in the same functional group is never attained for case 1, whereas for case 2 $x_1$ and $x_2$, both AOB, coexist in either partial or complete nitrification.
-Ecological diagrams also show that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
-The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws are non-decreasing in the resource, then only one of them will survive in the long run.
-However reports on wastewater treatment plants have shown coexistence between species in nitrifying reactors \cite{Wagner2002}, thus implying that a more complex growth law (as shown in here) or model structure involving other biological processes is required to include microbial diversity.
-
-\clearpage
-%
-%\begin{figure}[ht]
-%	\centering	
-%	\begin{subfigure}[b]{0.45\textwidth}
-%		\includegraphics[width=\textwidth]{Stability/OD_parameters_Dumont}
-%		\caption{Case 1 operating diagram.}
-%	\end{subfigure}
-%~
-%	\begin{subfigure}[b]{0.45\textwidth}
-%		\includegraphics[width=\textwidth]{Stability/OD_parameters_modified}
-%		\caption{Case 2 operating diagram.}
-%	\end{subfigure}
-%	\caption{Operating Diagrams for both cases.
-Case 1 Operating diagram coincides with the ecological diagram.
-Note how in case 2 CN might occur at bigger dilution rates than case 1.
-There is also a thin line where both CN and PN may arise depending on initial conditions.}
-%	\label{operating_diagrams}
-%\end{figure}
-%
-%
+The ecological diagrams are presented in figure \ref{ecological_diagrams}.
+Comparing figure \ref{ED 1} with \ref{ED 2} one can see a very different situation.
+Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is strongly determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or $x_2$ alone remains, because in operational terms this means that either PN or CN may take place.
+
+One can see that coexistence in the same functional group is never attained in figure \ref{ED 1}, whereas in figure \ref{ED 2} $x_1$ and $x_2$, both AOB, coexist in either partial or complete nitrification.
+That means that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws only depend non decreasingly on the resource, then only one of them will survive in the long run.
+This is interesting in light of reports on wastewater treatment plants where coexistence between species in nitrifying reactors has been shown \cite{Wagner2002}, thus implying that a more complex growth law (as shown in here) or model structure involving other biological processes is required to include microbial diversity in mathematical models.
 
@@
 It also shows a new mechanism by which the CEP no longer holds and where multiple stable equilibria may appear.
-Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a new model to study.
+Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a new model to study interactions.
 
@@
 
-The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the study case 1 with interaction matrix given by \eqref{case1_interactions}.
+The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the case study 1 with interaction matrix given by \eqref{case1_interactions}.
 In the operating diagram of the same case (figure \eqref{OD_interactions}) the red zone implies complete nitrification, while the green zone means partial nitrification.
-For integrating the former phenomena in the simulation, the system was simulated for 300 days, and perturbed at day 150 from the CN zone ($(s_{in},D) = (1.25,0.22)$) to a PN zone ($(s_{in},D) = (1.95,0.22)$) .
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \linewidth}
+For integrating the former phenomena in the simulation, the system was simulated for 300 days, and perturbed at day 150 from the CN zone ($(s_{in},D) = (1.25,0.22)$) to a PN zone ($(s_{in},D) = (1.95,0.22)$).
+Simulations can be seen in figure \ref{synthetic_data}.
+Note how from day 150 the NOB population represented in figure \eqref{PC_synthetic_NOB} decreases, which in turn implies a decrease in $s_3$, as seen in figure \eqref{PC_synthetic_metabolites}.
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.32 \linewidth}
 	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_AOB_plot}
-	\caption{}
-	\label{fig:nonoise200121aobplot}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \linewidth}
+	\caption{AOB.}
+	\label{PC_synthetic_AOB}
+	\end{subfigure}
+	\begin{subfigure}{0.32 \linewidth}
 	\centering
 	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_NOB_plot}
-	\caption{}
-	\label{fig:nonoise200121nobplot}
-	\end{subfigure}
-\caption{}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\linewidth]{proof_of_concept/250309_POC_metabolites}
-	\caption{}
-	\label{fig:nonoise200121metabolites}
-\end{figure}
-
-In all figures, asterisks represent the synthetic data, while the continuous lines represent the method's output.
-
-For applying the optimal tracking approach, the choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
+	\caption{NOB.}
+	\label{PC_synthetic_NOB}
+	\end{subfigure}
+	\begin{subfigure}{0.32 \linewidth}
+	\centering
+	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_metabolites}
+	\caption{Metabolites.}
+	\label{PC_synthetic_metabolites}
+	\end{subfigure}
+	\caption{Synthetic data generated by model \eqref{system}, with parameters from case study 1. Note the effects of the increased input $s_{in}$ generated in day 150.}
+	\label{synthetic_data}
+\end{figure}
+
+%For applying the optimal tracking approach, the choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator.
 $Q$ represents the covariance matrix of measurements, while $R$ is subject to interpretations depending on the context: in the case here presented it does not have \textit{a priori} definite meaning.
@@
 
-Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively.
+ The results of the procedure to identify interactions can be seen in figure in figure \ref{POC_tracking}.
+Figures \ref{PC_total_biomass}, \ref{PC_AOB}, and \ref{PC_NOB} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively.
 It can be seen that the method approaches well the trajectories.
-The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_Biomass_iter_2}
-	\caption{Dotted line: simulated total biomass for model \eqref{system} \iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
-	\label{Total Biomass no noise}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_AOB_iter_2_plot_1}
-	\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
-	\label{AOB no noise}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_NOB_iter_2_plot_1}
-	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{NOB no noise}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{proof_of_concept/250309_POC_try3_metabolites_iter_2}
-	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{Metabolites no noise}
-\end{figure}
-\clearpage
-
-The resulting controls that correct the growth rate can be seen in figures \eqref{Control AOB no noise} and \eqref{Control NOB no noise}.
+The metabolites concentration represented in figure \ref{PC_metabolites} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements.
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+	\includegraphics[width= \textwidth]{proof_of_concept/250309_POC_try3_iter_2_Biomass}
+	\caption{Total biomass.}
+	\label{PC_total_biomass}
+	\end{subfigure}
+~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{proof_of_concept/250309_POC_try3_iter_2_metabolites}
+		\caption{Metabolites. }
+		\label{PC_metabolites}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{proof_of_concept/250309_POC_try3_iter_2_AOB_plot_1}
+		\caption{AOB biomass.}
+		\label{PC_AOB}
+	\end{subfigure}
+	~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{proof_of_concept/250309_POC_try3_iter_2_NOB_plot_1}
+		\caption{NOB biomass. }
+		\label{PC_NOB}
+	\end{subfigure}
+\caption{Asterisks represent the synthetic data, while the continuous lines represent the method's output.
+The method is able to reconstruct the metabolites pattern, from the biomasses concentrations.}
+\label{POC_tracking}
+\end{figure}
+
+Figure \ref{POC_control} shows the controls and the corrected growth rate for each functional group.
+The control for each funcional group can be seen in figures \ref{Control AOB no noise} and \eqref{Control NOB no noise}.
 Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.
-It should be noted as well that since the synthesized control is not saturated (i.e.
-it does not reach the imposed bounds) it is optimal.
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_Control_AOB_iter_2_plot_1}
+Figures \ref{AOB_growth_POC} and \ref{NOB_growth_POC} show the resulting growth rates for $AOB$ and $NOB$, respectively, without the control $u_i(t)$.
+Figures \ref{AOB_growth_control_POC} and \ref{NOB_growth_control_POC} are the complete expression that determines growth rate, that is  $f_i(s(t))u_i(t)x_i(t)$.
+Note how little the shape changes with respect to figures \ref{AOB_growth_POC} and \ref{NOB_growth_POC}, which might mislead the reader to conclude that the control had reduced effects in the dynamics.
+The way out of this conundrum is to note that the control's effects are already included in $x_i(t)$ and $s_i(t)$, and thus in expression $f_i(s(t))x_i(t)$.
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_Control_AOB_plot_1}
 	\caption{Control for the AOB population.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_Control_NOB_iter_2_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_Control_NOB_plot_1}
 	\caption{Control for the NOB population.}
@@
 	\end{subfigure}
-	\caption{}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_growth_AOB_iter_2_plot_1}
+
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_AOB_plot_1}
 		\caption{Growth rate of the model for AOB community.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_growth_NOB_iter_2_plot_1}
-	\caption{Growth rate of the model for the NOV community.}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_NOB_plot_1}
+	\caption{Growth rate of the model for the NOB community.}
 	\label{NOB_growth_POC}
 	\end{subfigure}
-	\caption{}
-\end{figure}
-
-In figure \ref{Comparison_lambda} the different controls obtained by varying $\lambda$ for two species are compared to the interaction function simulated that is $1+A(x(t))$, where $x(t)$ is the synthetic data.
+
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_control_AOB_plot_1}
+		\caption{Growth rate of the model for AOB community.}
+		\label{AOB_growth_control_POC}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_control_NOB_plot_1}
+		\caption{Growth rate of the model for the NOB community.}
+		\label{NOB_growth_control_POC}
+	\end{subfigure}
+	\caption{Control and growth rates resulting from the tracking approach.}
+	\label{POC_control}
+\end{figure}
+
+%In figure \ref{Comparison_lambda} the different controls obtained by varying $\lambda$ for two species are compared to the interaction function simulated that is $1+A(x(t))$, where $x(t)$ is the synthetic data.
 One can see that due to this property of the end value becoming 1, the two do not coincide, however, when $\lambda$ is decreased one can see that the control roughly approaches the respective interaction function at the cost of very sharp changes.
@@
 
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|l|l|l|l|}
+		\hline
+		Kinetic Parameters & $\mu_i\,[1/day]$ & $K_i\,[g/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+		$x_1 \in G_1$ & 0.77  & 0.7 & 3.98  \\ \hline
+		$x_2\in G_2$ & 1.07 & 0.3 &  16.12 \\ \hline
+	\end{tabular}	
+	\caption{A set of kinetic parameters of model \eqref{system}.}
+	\label{kinetic_parameters_application}
+\end{table}
+
 The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}.
@@
 For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
-The system state dimension becomes 38.
+
+A first example of the procedure is performed on the regrouping of the selected OTU in their functional groups, thus a 5 dimensional dynamical system arises.
+The same procedure is applied when no regrouping occurs and the system state dimension becomes 38.
 
@@
 	\label{NOB_control}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width= \textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_Biomass_iter_12}
+		\caption{Dotted line: total biomass for model \eqref{system} \iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
+		\label{Total Biomass application}
+	\end{subfigure}
+	~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_metabolites_iter_12}
+		\caption{Metabolites. Dotted line:  data. Continuous line: the tracking procedure results.}
+		\label{Metabolites application}
+	\end{subfigure}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_AOB_iter_12_plot_1}
+		\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
+		\label{AOB application}
+	\end{subfigure}
+	~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_NOB_iter_12_plot_1}
+		\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+		\label{NOB application}
+	\end{subfigure}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_Control_AOB_iter_12_plot_1}
+		\caption{Control for the AOB population.}
+		\label{Control application}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_Control_NOB_iter_12_plot_1}
+		\caption{Control for the NOB population.}
+		\label{Control application}
+	\end{subfigure}
+	\caption{}
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_AOB_iter_12_plot_1}
+		\caption{Growth rate of the model for AOB community.}
+		\label{AOB_growth_application}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_NOB_iter_12_plot_1}
+		\caption{Growth rate of the model for the NOV community.}
+		\label{NOB_growth_application}
+	\end{subfigure}
+	\caption{}
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_control_AOB_iter_12_plot_1}
+		\caption{Growth rate of the model for AOB community.}
+		\label{AOB_growth_control_application}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_control_NOB_iter_12_plot_1}
+		\caption{Growth rate of the model for the NOV community.}
+		\label{NOB_growth_control_application}
+	\end{subfigure}
+	\caption{}
 \end{figure}

### 2020-04-08 Tracking/identify_interactions.m
use control matrix

@@ -37,7 +37,7 @@ p1 = plot(t_used,A*x_trajectories);
 set(p1,{'Color'},colors)
 p2 = plot(t_used,new_A*x_trajectories,'--');
 set(p2,{'Color'},colors)
-p3 = plot(t_used,control_matrix_med_filter,'*');
+p3 = plot(t_used,control_matrix,'*');
 set(p3,{'Color'},colors)
 
 

### 2020-04-08 Tracking/simulate_interactions.m
update simulate interactions

@@ -1,6 +1,6 @@
 clear 
 close all
-file_in = '191211_no_noise_iter_10_interactions';
+file_in = '250309_POC_try3_iter_2_interactions';
 load(sprintf('MAT_files/%s',file_in));%Simulation and plotting
 numbering_AOB = strsplit(num2str(1:nA)) ;
 legend_tags_AOB = strsplit(strcat(sprintf('OTU %s (model),', numbering_AOB{:}),...
@@ -15,9 +15,9 @@ numbering_diff = strsplit(num2str(1:n));
 legend_tags_diff = strsplit(sprintf('Difference %s,', numbering_diff{:}),',');
 legend_tags_diff(end) = [];
 %Quality of the Fit
-fit = new_A*x_new(index_control,1:n)';
-% control_matrix = reshape(cell2mat(control_eval),n,length(index_control))+1;
-diff = abs(control_matrix_med_filter - fit);
+fit = new_A*x_new(index_used,1:n)';
+% control_matrix = reshape(cell2mat(control_eval),n,length(index_used))+1;
+diff = abs(control_eval_reshape - fit);
 figure
 diff_plot = plot(t_used,diff,'LineWidth',1.5);
 xlabel('\fontsize{12}Time [days]'),...
@@ -30,15 +30,13 @@ legend(legend_tags_diff,'fontsize',7,'Location','bestoutside');
 fig.PaperUnits = 'inches';
 fig.PaperPosition = [0 0 9 3];
 fig.PaperPositionMode = 'auto';
-print(sprintf('Images\\%s',sprintf('%s_difference_fit_%.0f_LV',...
-    file_in,iter)),'-dpng','-r0')
+print(sprintf('Images\\%s',sprintf('%s_difference_fit_LV',...
+    file_in)),'-dpng','-r0')
 %Simulation
-muARef = 0.77;
-muBRef = 1.07;
-kSARef = 0.7e-1;
-kSBRef = 1.4982e-1;
-growth1 = @(X) (1+new_A(1:nA,:)*X(1:n))*growth_monod(X(n+1),muARef,kSARef);
-growth2 = @(X) (1+new_A(nA+1:n,:)*X(1:n))*growth_monod(X(n+2),muBRef,kSBRef);
+muA = mu_fit(1:nA);
+muB = mu_fit(nA+1:n);
[…]

### 2020-04-08 tex/Article_Interactions.tex
changes of rereading

@@
 \begin{abstract}
-	This article deals with the inclusion of microbial ecology advances in bioprocess modelling.
+	This article deals with the inclusion of microbial ecology measurements in bioprocess modelling.
 The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting.
@@
 They model a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression.
-Section 3 deals with the mathematical analysis of their model.
-It is shown that the number of possible equilibrium points grows exponentially with the number of species.
-Finally after a numerical analysis it is conjectured that there always exists a single stable equilibrium point depending on the operational parameters.
-
-Section 4 is the article's core contribution.
-The concept of interaction function is developed such that it generalizes the gLV model.
+Section 3 inspects through a mathematical analysis their model.
+Some interesting outputs of this analysis are that the number of possible equilibrium points grows exponentially with the number of species,  coexistence can be achieved within the same functional group, and bi-stability may arise.
+
+In section 4 the concept of interaction function is developed such that it generalizes the gLV model.
 For the identification of the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data.
-The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species, it is solved via state-dependent Ricatti equations \cite{Cimen2008}.
-
-In section 5 the methodology from section 4 is applied to all of the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 2\cite{Dumont2016}.
-The method shows that by following the community dynamics one can reconstruct the dynamics of the chemical substrate.
+The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}.
+
+In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}.
+The method shows that by following the community dynamics one can propose a growth rate that reconstructs the substrates dynamics.
 The article ends with a discussion on the scope of applicability of the method and perspectives.
@@
 	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
-	\item Let $A$ be a finite set with $m \in \N$ elements. Then $\vert A \vert := m$. 
+	\item Let $S$ be a finite set with $m \in \N$ elements. Then $\vert S \vert := m$. 
 \end{enumerate}
@@
 Let $A$ denote the matrix
-with entries $a_{ij}$, which will be referred to as the interaction matrix.
+with entries $a_{ij}$ from now on referred as the interaction matrix.
 The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
@@
 
-The proof can be seen in the appendix. A bound on the norm of $A$ is found such that every matrix $A$, respecting the bound, guaranties that $\Omega$ is a positively invariant set.
+The proof can be seen in the supplementary material. A bound on the norm of $A$ is found such that every matrix $A$, respecting the bound, guaranties that $\Omega$ is a positively invariant set.
 
@@
 
-The proof can be seen in the appendix.
+The proof can be seen in the supplementary material.
 
@@
 
-Observe that equilibrium points are by definition non-negative so the state variables can have physical meaning. Details of the calculations are given in the appendix.
+Observe that equilibrium points are by definition non-negative so the state variables can have physical meaning.
+Details of the calculations are given in the appendix.
+An important assumption throughout the work is that matrix $A$ and some submatrices have an inverse, this is stated properly in hypothesis \ref{inverse hypothesis}.
+
+\begin{hypo}
+	Let $A$ be the interaction matrix of size $n \in \N$ and $S$ be a proper subset of $[n]$ with $|S| = m$.
+Then the matrix $B \in \R^{(n-m) \times (n-m)}$ defined by taking out the $S$ rows and columns of matrix $A$ is invertible.
+	\label{inverse hypothesis}
+\end{hypo}
 
@@
 
-\subsubsection{Complete Coexistence}
-
-This section derives the equations for an equilibrium point with every OTU being positive: $x^{eq}_i>0$.
-
-From equation \eqref{Eq1} one gets that an equilibrium point satisfies: \begin{align*}
-\diag(x)(\diag(f(s)(1_{n\times 1} + Ax) - D_{n\times 1}) & = 0 \\
-\Rightarrow x_i = 0 \vee (\diag (f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i & = 0 \quad \forall i\in (1,\dots,n)
-\end{align*}
-
-Since $x_i>0$ one has 
-\begin{align}
-\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}=0 \\
-\label{xEquilibria}\Leftrightarrow x = A^{-1}(\diag (f(s))^{-1}D_{n\times 1} - 1_{n\times 1})
-\end{align}
-
-By replacing \eqref{xEquilibria} in equation \eqref{Eq2}:
-
-\begin{align}
-\label{s1Equilibria} (s_{in}-s_1)-	\begin{bmatrix}
-1_{n_1\times 1} \\0_{n_2\times 1}
-\end{bmatrix}^\top \diag (k) A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0 
-\end{align}
-
-A similar expression is obtained when replacing \eqref{xEquilibria} in equation \eqref{Eq3}
-
-\begin{align}
-\label{s2Equilibria}-s_2+
-1_{n\times 1}^{\top}\diag (k)  A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0
-\end{align}
-
-From equation \eqref{s1Equilibria} $s_2$ can be written as a function of $s_1$:
-\begin{align}
-s_2 = \frac{s_1}{c_1s_1^2+c_2s_1+c_3} \label{S2(S1)}
-\end{align}
-
-Then by replacing  \eqref{S2(S1)} in equation \eqref{s2Equilibria}, one gets a fourth degree polynomial for $s_1$.
-
-\begin{align}
-\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
-\end{align}
-
-Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
-
-Finally, in equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
-
-\begin{align}
-s_{in} = s_1+s_2+s_3 \label{s1s2s3}
-\end{align}
-
-If the system of equations \eqref{xEquilibria}, \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} provides only solutions with some negative entries then complete coexistence is not possible.
-
-\subsubsection{Washout of some OTU}
+Finally the set of non-active coordinates is defined.
 
@@
 
+\subsubsection{Complete Coexistence}
+
+This section derives the equations for an equilibrium point with every OTU being positive: $x^{eq}_i>0$, which is stated in hypothesis \ref{hypothesis complete coexistence}.
+
+\begin{hypo}
+	$\mathcal{J} =  \emptyset$
+	\label{hypothesis complete coexistence}
+\end{hypo}
+
+From equation \eqref{Eq1} one gets that an equilibrium point satisfies: \begin{align*}
+\diag(x)(\diag(f(s)(1_{n\times 1} + Ax) - D_{n\times 1}) & = 0 \\
+\Rightarrow x_i = 0 \vee (\diag (f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i & = 0 \quad \forall i\in (1,\dots,n)
+\end{align*}
+
+Since $x_i>0$ one has 
+\begin{align}
+\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}=0 \\
+\label{xEquilibria}\Leftrightarrow x = A^{-1}(\diag (f(s))^{-1}D_{n\times 1} - 1_{n\times 1})
+\end{align}
+
+By replacing \eqref{xEquilibria} in equation \eqref{Eq2}:
+
+\begin{align}
+\label{s1Equilibria} (s_{in}-s_1)-	\begin{bmatrix}
+1_{n_1\times 1} \\0_{n_2\times 1}
+\end{bmatrix}^\top \diag (k) A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0 
+\end{align}
+
+A similar expression is obtained when replacing \eqref{xEquilibria} in equation \eqref{Eq3}
+
+\begin{align}
+\label{s2Equilibria}-s_2+
+1_{n\times 1}^{\top}\diag (k)  A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0
+\end{align}
+
+From equation \eqref{s1Equilibria} $s_2$ can be written as a function of $s_1$:
+\begin{align}
+s_2 = \frac{s_1}{c_1s_1^2+c_2s_1+c_3} \label{S2(S1)}
+\end{align}
+
+Then by replacing  \eqref{S2(S1)} in equation \eqref{s2Equilibria}, one gets a fourth degree polynomial for $s_1$.
+
+\begin{align}
+\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
+\end{align}
+
+Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
+
+Finally, in equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
+
+\begin{align}
+s_{in} = s_1+s_2+s_3 \label{s1s2s3}
+\end{align}
+
+If the system of equations \eqref{xEquilibria}, \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} provides only solutions with some negative entries then complete coexistence is not possible.
+
+\subsubsection{Washout of some OTU}
+
+Hypothesis \ref{hypothesis CN} represents the case where in each functional group remains at least one OTU.
+
+\begin{hypo}The set $\mathcal{J}$ satisfies $ G_1 \not \subset \mathcal{J} , \, G_2 \not \subset \mathcal{J} $.
+	\label{hypothesis CN}
+\end{hypo}
+
 From equation \eqref{Eq1} equilibrium points satisfy:
@@
 But since $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ then the coefficients $a_{ij}$ play no role in the equation \eqref{Extinction} one can rewrite equation \eqref{Extinction} as $\diag(f^{act}(s))(1_{(n-m)\times 1} + A^{act}x^{act}) - D_{(n-m) \times 1}=0 $.
+Clearly matrix $A^{act}$, satisfies hypothesis \ref{inverse hypothesis}.
+This gives the following lemma.
 
@@
 
-The following hypothesis represents the case where in each functional group remains at least one OTU :
-\begin{hypo}The set $\mathcal{J}$ satisfies $ G_1 \not \subset \mathcal{J} , \, G_2 \not \subset \mathcal{J} $.
-	\label{noWashoutHyp}
-\end{hypo}
-
-Under H \ref{noWashoutHyp}, the equilibrium of the system is solved as described by equations \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} as before, but coefficients are calculated differently (essentially the same, but only uses the coefficients corresponding to the active points).
+The equilibrium of the system is solved as described by equations \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} as before, but coefficients are calculated differently (essentially the same, but only uses the coefficients corresponding to the active points).
 
@@
 
-The washout of $G_2$ is equivalent to  hypothesis \ref{WashoutG2}.
+The washout of $G_2$ is equivalent to  hypothesis \ref{hypothesis washout G2}.
 
@@
 	$G_2 \subset \mathcal{J}$ and $G_1 \not \subset \mathcal{J}$
-	\label{WashoutG2}
+	\label{hypothesis washout G2}
 \end{hypo}
@@
 \subsubsection{Washout}
-Notice that $x_i = 0$ for every $i \in \{1,\dots, n_1\}$ implies the washout equilibria (no OTU surviving):
+
+The washout equilibria means $x_i = 0$ for every $i \in \{1,\dots, n_1\}$. This is equivalent to hypothesis \ref{hypothesis washout}.
+\begin{hypo}
+	$\mathcal{J} = G_1 \cup G_2$
+	\label{hypothesis washout}
+\end{hypo}
 
@@
 Algorithm \ref{StabilityAnalysis} summarizes such a procedure.
-Algorithm \ref{StabilityAnalysis} implicitly assumes that every submatrix $A'$ is invertible.
 
@@
 	$\mathcal{P} = \emptyset$ \\
-	eig = Eigenvalues of $J(0,s_{in},0,0)$. \\
-	\If{$Real(eig) < 0$}{$PSP = PSP \cup (0,s_{in},0,0)$} 
-	\For{$A'$ square submatrix of $A$}{	Calculate $(x,s_1,s_2,s_3)$ from equations \eqref{Poly4}, \eqref{S2(S1)}, \eqref{s1s2s3}, and \eqref{xEquilibria} \\
+	\For{$S \subset [n]$ }{	Calculate equilibrium $(x,s_1,s_2,s_3)$ when $\mathcal{J}:= S$ according to hypothesis \ref{hypothesis complete coexistence} \ref{hypothesis CN}, \ref{hypothesis washout G2}, or \ref{hypothesis washout}.
+\\
 		\If{$(x,s_1,s_2,s_3) \geq 0$}{eig = Eigenvalues of $J(x,s_1,s_2,s_3)$ \\
@@
 From this hypothesis, note that $ \lim \limits_{x \rightarrow 0} I_i(x) = 1$ since if there is minimal presence of OTU, interactions can not exist.
-Furthermore for this first study it is assumed that $I_i(\cdot)$ is a continuously differentiable function on $x$.
+Furthermore for this study it is assumed that $I_i(\cdot)$ is a continuously differentiable function on $x$.
 For making explicit all of the former:
@@
 By using experimental measurements of $x$, represented by $z(t)$, the objective is to reconstruct function $I(x)$.
-For doing so, the terms $I_i(x)$ are replaced by controls $u_i(t)$, thus $I_i(x(t)) = u_i(t)$,  and a state feedback is obtained by solving a nonlinear optimal tracking problem.
-
-Consider the observable system \eqref{Controlsystem} ($y(t)$ being the observer) where $g(\cdot)$ is a known function.
+For doing so, the terms $I_i(x)$ are replaced by controls $u_i(t)$, thus $I_i(x(t)) = u_i(t)$.
+A control law is obtained by solving a nonlinear optimal tracking problem.
+
+Consider the observable system \eqref{Controlsystem} ($y(t) = x(t)$ being the observer) where $g(\cdot)$ is a known function.
 
@@
 \dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)u_i(t) x_i \\
-y(t) & = g(x,s)
+y(t) & = x
 \end{array}
@@
 The control $u(t)$ is intended to drive the system to be near a desired output $z(t)$, which in this context are the measurements of the concentrations of OTU.
-The term $\lambda \Vert(u -\vec{1}) \Vert_R$, was added for two reasons:
+The term $\Vert(u -\vec{1}) \Vert_R$, was added for two reasons:
 \begin{itemize}
@@
 
-The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the case study 1 with interaction matrix given by \eqref{case1_interactions}.
+The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the case study 1 (table \ref{kinetic_parameters_case_study_1}) with interaction matrix given by \eqref{case1_interactions}.
 In the operating diagram of the same case (figure \eqref{OD_interactions}) the red zone implies complete nitrification, while the green zone means partial nitrification.
@@
 
+ For the tracking procedure the functions $f_i(s)$ and the yields $y_i$ were the same as those used for simulating the synthetic data (parameters in table \ref{kinetic_parameters_case_study_1}) and the control is meant to account for the interaction term.
+The $Q$ and $R$ matrices are $\lambda I_n$ and $I_n$, respectively, with $\lambda = 10^{-4}$.
 The results of the procedure to identify interactions can be seen in figure in figure \ref{POC_tracking}.
 Figures \ref{PC_total_biomass}, \ref{PC_AOB}, and \ref{PC_NOB} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively.
-It can be seen that the method approaches well the trajectories.
+It can be seen that the method approaches well the trajectories of the OTU, with a better result for the AOB community, which can be explained by the one order of magnitude difference in their concentrations (which in turn is a consequence of the one order of magnitude difference in their yields).
 The metabolites concentration represented in figure \ref{PC_metabolites} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements.
@@
 Note how little the shape changes with respect to figures \ref{AOB_growth_POC} and \ref{NOB_growth_POC}, which might mislead the reader to conclude that the control had reduced effects in the dynamics.
-The way out of this conundrum is to note that the control's effects are already included in $x_i(t)$ and $s_i(t)$, and thus in expression $f_i(s(t))x_i(t)$.
+The way out of this conundrum is to remember that the control's effects are already included in $x_i(t)$ and $s_i(t)$, and thus in expression $f_i(s(t))x_i(t)$.
 
@@
 
-The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.\iffalse Cette phrase devrait figurer dans la partie précédente ?\fi
+%The method was stopped after 10 iterations where each iteration took approximately 800 seconds of computing time in a computer equipped with 8gb of RAM memory and Intel core i3-7100U CPU 2,40 GHz.\iffalse Cette phrase devrait figurer dans la partie précédente ?\fi
+
+The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}.
+For exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept as constant as possible.
+Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on kinetics.
+For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 31 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
 
@@
 		Kinetic Parameters & $\mu_i\,[1/day]$ & $K_i\,[g/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
-		$x_1 \in G_1$ & 0.77  & 0.7 & 3.98  \\ \hline
-		$x_2\in G_2$ & 1.07 & 0.3 &  16.12 \\ \hline
+		$x_1 \in G_1$ & 1.97  & $7\cdot 10^{-1}$ & 4.49  \\ \hline
+		$x_2\in G_2$ & 1.87 & $5.4\cdot 10^{-1}$ &  45.51 \\ \hline
 	\end{tabular}	
@@
 
-The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}.
-For exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept as constant as possible.
-Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on the kinetics.
-For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 30 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
-
-A first example of the procedure is performed on the regrouping of the selected OTU in their functional groups, thus a 5 dimensional dynamical system arises.
-The same procedure is applied when no regrouping occurs and the system state dimension becomes 38.
-
-The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}\iffalse est-ce que tu donnes les paramètres quelquepart ?\fi.
-Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$.
+A first example of the procedure is performed when the classified OTU are regrouped in their assigned functional groups by adding their concentrations.
+A 5 dimensional dynamical system is obtained.
+The same procedure is applied where no regrouping occurs and the system state grows to 39.
+
+The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
+Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application}.
+The yields were fitted to match the nitrogen mass balances.
+In this case the $Q$ and $R$ matrices were $\begin{bmatrix}
+\lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
+\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$ in order to better track the NOB trajectories.
+
 \begin{align}
@@
 For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e.
-$u(t)= 1$) in  Figure \ref{u=1_metabolites}.
+$u(t)= 1$) in  figure \ref{u=1 simulation.}.
 $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
-The community dynamics is neither captured by this simulation as seen in figure \ref{u=1_NOB} where the NOB community is shown.
 
@@
 	\centering	
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width=\textwidth]{Application//191218_Reactor_A_Biomass_iter_0}
+		\caption{Total Biomass.}
+		\label{biomass_no_control}
+	\end{subfigure}
 	\begin{subfigure}{0.45 \textwidth}
 		\includegraphics[width= \textwidth]{Application//191218_Reactor_A_metabolites_Iter_0}
-	\caption{Simulation when $u=1$. }
+		\caption{Metabolites.}
 		\label{u=1_metabolites}
 	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-	\includegraphics[width=\textwidth]{Application//191218_Reactor_A_Biomass_iter_0}
-	\label{biomass_no_control}
-	\end{subfigure}
+		\caption{Simulation of system \eqref{Controlsystem} when $u=1$, with functions as in \eqref{monod}. Data points are represented by a star. The continuous line represents the simulation.}
+		\label{u=1 simulation.}
 \end{figure}
@@
 	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
-	\caption{Simulation when $u=1$. }
-	\label{u=1_NOB}
-\end{figure}
-\pagebreak
-When applying the presented method one obtains the simulation that can be seen in figure \ref{ControlSimulation}.
-The method captures the tendencies in the measured substrates and products.
-The simulation of each functional $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOBSimulation} and \ref{NOB Simulation}, respectively.
-Note that the fit of $G_1$ seems better than the fit of $G_2$, which can be explained by the 1 order of magnitude difference of abundance between the members of the group.
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width=\textwidth]{Application//191218_Reactor_A_metabolites_Iter_45}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width=\textwidth]{Application//191218_Reactor_A_Biomass_Iter_45}
-	\end{subfigure}
-	\caption{Simulation applying the control strategy.}
-	\label{ControlSimulation}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_1}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-	\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_2}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-	\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_3}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-	\includegraphics[width =\textwidth]{Application//191218_Reactor_A_AOB_iter_45_plot_4}
-	\end{subfigure}
-	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
-	\label{AOBSimulation}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_iter_45_plot_1}
-	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
-	\label{NOB Simulation}
-\end{figure}
-
-In figures \ref{AOB_control} and \ref{NOB_control} it can be seen the obtained controls for each functional group.
-Both controls saturate at certain points, but in general terms they vary throughout the dynamic.
-At this point one can not be sure that the control is indeed optimal.
-Also note that when compared to the shape of controls obtained in the proof of concept section one might hypothesize that a gLV model can not capture the dynamic of the system.
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_1}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_2}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_3}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \textwidth}
-		\includegraphics[width =\textwidth]{Application//191218_Reactor_A_Control_AOB_iter_45_plot_4}
-	\end{subfigure}
-	\caption{Control obtained of $G_1$ (AOB).}
-	\label{AOB_control}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_NOB_iter_45_plot_1}
-	\caption{Control obtained of $G_2$ (NOB).}
-	\label{NOB_control}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width= \textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_Biomass_iter_12}
-		\caption{Dotted line: total biomass for model \eqref{system} \iffalse quels paramètres ?\fi. Continuous line: total biomass as predicted  by the tracking procedure.}
+		\includegraphics[width= \textwidth]{Application/200407_regroup_OTU_try2_iter_20_Biomass}
+		\caption{Total Biomass.}
 		\label{Total Biomass application}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_metabolites_iter_12}
-		\caption{Metabolites. Dotted line:  data. Continuous line: the tracking procedure results.}
+		\includegraphics[width=\textwidth]{Application/200407_regroup_OTU_try2_iter_20_metabolites}
+		\caption{Metabolites.}
 		\label{Metabolites application}
 	\end{subfigure}
-\end{figure}
-\begin{figure}[h]
-	\centering
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_AOB_iter_12_plot_1}
-		\caption{Dotted line: simulated AOB biomass. Continuous line: the tracking procedure results.}
+		\includegraphics[width=\textwidth]{Application/200407_regroup_OTU_try2_iter_20_AOB_plot_1}
+		\caption{AOB biomass.}
 		\label{AOB application}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_NOB_iter_12_plot_1}
-		\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+		\includegraphics[width=\textwidth]{Application/200407_regroup_OTU_try2_iter_20_NOB_plot_1}
+		\caption{NOB biomass.}
 		\label{NOB application}
 	\end{subfigure}
+\caption{Results on applying the tracking method to a nitrification experiment when regrouping OTU in their functional groups.
+Data points are represented by a star.
+The continuous line represents the tracking procedure results.}
+\label{regroup_results}
 \end{figure}
 
+When applying the presented method one obtains the simulation that can be seen in figure \ref{regroup_results}.
+The method captures the tendencies of the measured substrates as seen in figure \ref{Metabolites application}.
+The tracking of each functional group $G_1$ (AOB), and $G_2$ (NOB) can be seen in figures \ref{AOB application} and \ref{NOB application}, respectively.
+
+The growth rates of each functional group are shown in figure \ref{growth_application}.
+Note in the case of AOB (figure \ref{AOB_growth_control_application}) the resulting growth rate shows a noisy curve formed by pulses.
+The behaviour of the NOB community (figure \ref{NOB_growth_control_application}) is qualitatively very similar with somewhat stronger pulses and less noise.
+The former is to be expected since more OTU were regrouped to compose the AOB biomass, therefore more noise sources were added.
+
+The same procedure is applied without regrouping.
+The results on total biomass and metabolites are shown in figures \ref{Total Biomass application all} and \ref{Metabolites application all}, respectively.
+Both patterns still fit the data, but to a lesser degree of precision when compared to figure \ref{regroup_results}.
+This can be explained by noting in figure \ref{OTU abudance all} that the most abundant OTU are better tracked, thus the information contained in the least abundant species is not integrated in the model.
+When looking at the growth rates (figure \ref{growth all}) one again observes pulses for each OTU, note also that most OTU were present only for a fraction of the experiment's duration.
+
+In both cases, the regrouped and individual tracking, the growth rate varies strongly, raising the question whether the observed pulses are emerging from interactions within the microbial community.
+When growth rates are compared to the proof of section it seems doubtful that a linear pairwise interaction model such as the gLV model could capture the complexity of the particular chemostat analysed.
+Perhaps these interactions are not constant through time (as in the gLV model) or a different interaction function should be thought of.
+However the former questions can not be fully clarified, because the quality of the genetic sequencing from molecular fingerprints might not be the best when compared to more recent techniques, thus it is unclear if the pulses are due to noise of the measurements.
+
+The interpretation of the correction term as interactions is not the only possible reading.
+In other contexts the correction term might also be interpreted as a non accounted phenomena ranging from environmental factors (e.g.
+temperature, pH) to other biological factors (viruses, flock formation, pathogens).
+Alternative hypothesis for explaining the observed patterns in the microbial community should be considered as well.
+
 \begin{figure}[h]
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_Control_AOB_iter_12_plot_1}
-		\caption{Control for the AOB population.}
-		\label{Control application}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_Control_NOB_iter_12_plot_1}
-		\caption{Control for the NOB population.}
-		\label{Control application}
-	\end{subfigure}
-	\caption{}
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_AOB_iter_12_plot_1}
-		\caption{Growth rate of the model for AOB community.}
-		\label{AOB_growth_application}
-	\end{subfigure}
-	\begin{subfigure}{0.45 \linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_NOB_iter_12_plot_1}
-		\caption{Growth rate of the model for the NOV community.}
-		\label{NOB_growth_application}
-	\end{subfigure}
-	\caption{}
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_control_AOB_iter_12_plot_1}
+		\includegraphics[width=\linewidth]{Application/200407_regroup_OTU_try2_iter_20_growth_control_AOB_plot_1}
 		\caption{Growth rate of the model for AOB community.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Application/201703_day_183_315_gurobi_A_regroup_OTU_growth_control_NOB_iter_12_plot_1}
-		\caption{Growth rate of the model for the NOV community.}
+		\includegraphics[width=\linewidth]{Application/200407_regroup_OTU_try2_iter_20_growth_control_NOB_plot_1}
+		\caption{Growth rate of the model for the NOB community.}
 		\label{NOB_growth_control_application}
 	\end{subfigure}
-	\caption{}
+	\caption{Obtained growth rates when regrouping OTU in their functional groups.}
+	\label{growth_application}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width= \textwidth]{Application/200407_iter_20_Biomass}
+		\caption{Total Biomass.}
+		\label{Total Biomass application all}
+	\end{subfigure}
+	~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{Application/200407_iter_20_metabolites}
+		\caption{Metabolites.}
+		\label{Metabolites application all}
+	\end{subfigure}
+	\caption{Results on applying the tracking method to a nitrification experiment when all OTU are tracked independently.
+Data points are represented by a star.
+The continuous line represents the tracking procedure results.}
+	\label{all_OTU_results}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_1}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_2}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_3}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_4}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//200407_iter_20_NOB_plot_1}
+	\end{subfigure}
+	\caption{Tracking results when all OTU are tracked independently.}
+	\label{OTU abudance all}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_1}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_2}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_3}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_4}
+	\end{subfigure}
+	\begin{subfigure}{0.45 \textwidth}
+	\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_NOB_plot_1}
+	\end{subfigure}
+	\caption{Growth rates obtained for each OTU when applying the tracking procedure without aggregation.}
+	\label{growth all}
 \end{figure}
@@
 The interaction function introduced tries to address the issue of prediction from genetic sequencing.
-The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows a new mechanism by which the CEP may not hold, however we conjecture that the system seems to have only one positive stable equilibrium.
-From the application section one can see that by correcting the growth rate one is able to recuperate the substrates dynamics, implying that interactions are driving the system.
-The former correction varies strongly and when compared to the proof of section one may hypothesise that linear pairwise interaction model such as the gLV model can not capture the complexity of the particular chemostat analysed.
-This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems.
-The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
-
-The interpretation of the correction term as interactions is not the only possible reading.
-In other contexts the correction term might also be interpreted as a non accounted phenomena ranging from environmental factors (e.g.
-temperature, pH) to other biological factors (viruses, flock formation, pathogens).
-Alternative hypothesis for explaining the observed patterns in the microbial community should be considered as well.
-
-One of the next steps in this line of research would be to synthesize a control that is able to reconstruct interactions functions, and not just the dynamics of the species as is the case presented.
-One might bypass the end point issue of the current control scheme, by, for example, taking the derivative of the control in the cost function, instead of the control itself, or alternatively by eliminating the control cost and making a very thorough use of the pontryagin maximum principle and the switch function for the synthesis of the controls.
+The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows that such a model structure can give way to bi-stability, coexistence within a functional group, and unintuitive operational insights such as raising the input ammonium $s_{in}$ to achieve partial nitrification.
+From the application section one can see that by correcting the growth rate one is able to recuperate the substrates dynamics, suggesting that interactions are driving the system.
+This opens the question for a broader class of interaction functions that could represent well complex microbial ecosystems, particularly biorreactors.
+
+One of the next steps in this line of research would be to synthesize a control that is able to reconstruct the interaction functions, and not just the dynamics of the species.
+One might bypass the end point issue of the current control scheme by, for example, by a very thorough use of the pontryagin maximum principle for the synthesis of the control.
+In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability: integrating genetic sequencing could provide a path for more certainty in model calibration.
 
@@
 
-The first $n$ equations of system \eqref{system} may be written then as$\dot{x} =  h(x) = h_1(\diag(x), h_2(x))$, by the chain rule: 
+The first $n$ equations of system \eqref{system} may be written then as $\dot{x} =  h(x) = h_1(\diag(x), h_2(x))$, by the chain rule: 
 \begin{align} J_h(x) &= D_M h_1(\diag(x),h_2(x))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x))\circ D_xh_2(x)  \\ &=
@@
 They were solved using standard backward numerical integration.
-\subsection{Simulations proof of concept}
-\textbf{$\lambda = 10^{-1}$}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Biomass_iter_10}
-	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{Total Biomass no noise e1}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_AOB_iter_10_plot_1}
-	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{AOB no noise e1}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_NOB_iter_10_plot_1}
-	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{NOB no noise e1}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_metabolites_iter_10}
-	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{Metabolites no noise e1}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_AOB_iter_10_plot_1}
-	\caption{Control for the AOB population.}
-	\label{Control AOB no noise e1}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_NOB_iter_10_plot_1}
-	\caption{Control for the NOB population.}
-	\label{Control NOB no noise e1}
-\end{figure}
-\clearpage
-\textbf{$\lambda = 10^{-2}$}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Biomass_iter_10}
-	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{Total Biomass no noise e2}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_AOB_iter_10_plot_1}
-	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{AOB no noise e2}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_NOB_iter_10_plot_1}
-	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{NOB no noise e2}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_metabolites_iter_10}
-	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-	\label{Metabolites no noise e2}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_AOB_iter_10_plot_1}
-	\caption{Control for the AOB population.}
-	\label{Control AOB no noise e2}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_NOB_iter_10_plot_1}
-	\caption{Control for the NOB population.}
-	\label{Control NOB no noise e2}
-\end{figure}
-
-\clearpage
+%\subsection{Simulations proof of concept}
+%\textbf{$\lambda = 10^{-1}$}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Biomass_iter_10}
+%	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{Total Biomass no noise e1}
+%\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_AOB_iter_10_plot_1}
+%	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{AOB no noise e1}
+%\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_NOB_iter_10_plot_1}
+%	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{NOB no noise e1}
+%\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_metabolites_iter_10}
+%	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{Metabolites no noise e1}
+%\end{figure}
+%
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_AOB_iter_10_plot_1}
+%	\caption{Control for the AOB population.}
+%	\label{Control AOB no noise e1}
+%\end{figure}
+%
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_NOB_iter_10_plot_1}
+%	\caption{Control for the NOB population.}
+%	\label{Control NOB no noise e1}
+%\end{figure}
+%\clearpage
+%\textbf{$\lambda = 10^{-2}$}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Biomass_iter_10}
+%	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{Total Biomass no noise e2}
+%\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_AOB_iter_10_plot_1}
+%	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{AOB no noise e2}
+%\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_NOB_iter_10_plot_1}
+%	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{NOB no noise e2}
+%\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_metabolites_iter_10}
+%	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
+%	\label{Metabolites no noise e2}
+%\end{figure}
+%
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_AOB_iter_10_plot_1}
+%	\caption{Control for the AOB population.}
+%	\label{Control AOB no noise e2}
+%\end{figure}
+%
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_NOB_iter_10_plot_1}
+%	\caption{Control for the NOB population.}
+%	\label{Control NOB no noise e2}
+%\end{figure}
+%
+%\clearpage
 

### 2020-04-09 tex/Article_Interactions.tex
changes in tex

@@
-\documentclass[3p,times]{elsarticle}
-
-%% The `ecrc' package must be called to make the CRC functionality available
-\usepackage{ecrc}
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-%% Give the name of the journal
-\journalname{}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{procs}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The amssymb package provides various useful mathematical symbols
+\documentclass[3p,times]{article}
+
+\usepackage[margin=0.7in]{geometry}
+
 \usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
 \usepackage{amsthm}
@@
 \usepackage{hyperref}
-
 \usepackage{xcolor}
@@
 \newtheorem{theo}{Theorem}
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-% \biboptions{}
-
-% if you have landscape tables
 \usepackage[figuresright]{rotating}
@@
 \graphicspath{{Images/}}
-% put your own definitions here:
-%   \newcommand{\cZ}{\cal{Z}}
-%   \newtheorem{def}{Definition}[section]
-%   ...
-
-% add words to TeX's hyphenation exception list
-%\hyphenation{author another created financial paper re-commend-ed Post-Script}
-
-% declarations for front matter
 
@@
 
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\dochead{}
-%% Use \dochead if there is an article header, e.g. \dochead{Short communication}
-
-\title{Microbial interactions as drivers of a nitrifying ecosystem in a chemostat}
-%% \title{Correcting/Improving chemostat models from microbial interactions}
-%% Including microbial ecology in a chemostat model: tracking microbial interactions
-%% 
-%% Extending a chemostat model 
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
+\title{Microbial interactions as drivers of a nitrification process in a chemostat}
 
 \author{Pablo Ugalde-Salas, Jérôme Harmand, Elie Desmond Le-Quéméner, Héctor Ramirez}
-
-\address{}
+\date{}
+\maketitle
 
@@
 The limitations and the insights of such an approach are discussed.
-The main novelty of this work lies in the second part, where the use of an optimal tracking technique (developed within the framework of control theory) for the integration of genetic sequencing in chemostat models is presented.
-The method revisits the data used in the aforementioned chemostat setting.
+In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of genetic sequencing in chemostat models is presented.
+The optimal tracking revisits the data used in the aforementioned chemostat setting.
 \end{abstract}
-
-\end{frontmatter}
 
@@
 As a departing point the work of Dumont et al.\cite{Dumont2016} is reinspected in section 2.
-They model a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression.
+They model a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression: They fitted their model to the molecular fingerprints of the most abundant OTU.
 Section 3 inspects through a mathematical analysis their model.
@@
 	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
-	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites, or chemical species.
+	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites.
 	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
@@
 Let $A$ denote the matrix
-with entries $a_{ij}$ from now on referred as the interaction matrix.
+with entries $a_{ij}$ hereafter referred to as the interaction matrix.
 The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
@@
 Details of the calculations are given in the appendix.
-An important assumption throughout the work is that matrix $A$ and some submatrices have an inverse, this is stated properly in hypothesis \ref{inverse hypothesis}.
+An important assumption throughout the work is that matrix $A$ and some of its submatrices have an inverse, this is stated properly in hypothesis \ref{inverse hypothesis}.
 
@@
 But since $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ then the coefficients $a_{ij}$ play no role in the equation \eqref{Extinction} one can rewrite equation \eqref{Extinction} as $\diag(f^{act}(s))(1_{(n-m)\times 1} + A^{act}x^{act}) - D_{(n-m) \times 1}=0 $.
-Clearly matrix $A^{act}$, satisfies hypothesis \ref{inverse hypothesis}.
+From hypothesis \ref{inverse hypothesis} matrix $A^{act}$ has an inverse.
 This gives the following lemma.
@@
 Comparing figure \ref{ED 1} with \ref{ED 2} one can see a very different situation.
-Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is strongly determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or $x_2$ alone remains, because in operational terms this means that either PN or CN may take place.
+Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or $x_2$ alone remains, because in operational terms this means that either PN or CN may take place.
 
@@
 
-Consider the observable system \eqref{Controlsystem} ($y(t) = x(t)$ being the observer) where $g(\cdot)$ is a known function.
+Consider the observable system \eqref{Controlsystem}, with $y(t) = x(t)$ being the output, because we are observing measurements coming from genetic sequencing.
 
@@
 \dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)u_i(t) x_i \\
-y(t) & = x
+y  =& x
 \end{array}
@@
 
-For this model $g(x,s) = x$, since we are observing measurements coming from genetic sequencing.
  Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively, and a positive real $\bar{u}$.
@@
 \begin{align}
-\label{Optimal Control} \begin{array}{cc} \min &  \int \limits_{0}^{T} \Vert g(x,s) - z \Vert_Q + \Vert(u -\vec{1}) \Vert_R dt\\
+\label{Optimal Control} \begin{array}{cc} \min &  \int \limits_{0}^{T} \Vert y - z \Vert_Q + \Vert(u -\vec{1}) \Vert_R dt\\
 s.t.& 
@@
 
-The tracking problem was applied to data coming from a nitrification process; the experimental conditions are described in \cite{dumont2008observers}.
+The tracking problem was applied to data coming from a nitrification process with experimental conditions described in \cite{dumont2008observers}.
 For exploring the hypothesis of interactions as drivers of bioreactors performance environmental conditions should be kept as constant as possible.
@@
 For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 31 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
+
+A first example of the procedure is performed when the classified OTU are regrouped in their assigned functional groups by adding their concentrations.
+A 5 dimensional dynamical system is obtained.
+The same procedure is applied where no regrouping occurs and the system state grows to 39.
+
+The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
+Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application}.
+The yields were fitted to match the nitrogen mass balances.
+In this case the $Q$ and $R$ matrices were $\begin{bmatrix}
+\lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
+\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$ in order to better track the NOB trajectories.
+
+\begin{align}
+\label{monod} f_i(s) &= \bar{\mu}_2 \dfrac{s_1}{K_1 +s_1} \, \forall i \in G_1 \\
+\notag  f_i(s) &= \bar{\mu}_2 \dfrac{s_2}{K_2 +s_2 } \, \forall i \in G_2
+\end{align}
 
@@
 \end{table}
-
-A first example of the procedure is performed when the classified OTU are regrouped in their assigned functional groups by adding their concentrations.
-A 5 dimensional dynamical system is obtained.
-The same procedure is applied where no regrouping occurs and the system state grows to 39.
-
-The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
-Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application}.
-The yields were fitted to match the nitrogen mass balances.
-In this case the $Q$ and $R$ matrices were $\begin{bmatrix}
-\lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
-\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$ in order to better track the NOB trajectories.
-
-\begin{align}
-\label{monod} f_i(s) &= \bar{\mu}_2 \dfrac{s_1}{K_1 +s_1} \, \forall i \in G_1 \\
-\notag  f_i(s) &= \bar{\mu}_2 \dfrac{s_2}{K_2 +s_2 } \, \forall i \in G_2
-\end{align}
-
 For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e.
@@
 
-When applying the presented method one obtains the simulation that can be seen in figure \ref{regroup_results}.
+When applying the tracking method one obtains the simulation that can be seen in figure \ref{regroup_results}.
 The method captures the tendencies of the measured substrates as seen in figure \ref{Metabolites application}.
@@
 
-Last decades advances in genetic sequencing and microbial ecology has opened a gap for modellers in biochemical reactors to integrate this valuable information.
+Last decades advances in genetic sequencing and microbial ecology have opened a gap for modellers in biochemical processes to integrate this valuable information.
 Considering the success of mass balance models to predict and pilot bioreactors, one should build upon these existing models.
@@
 One might bypass the end point issue of the current control scheme by, for example, by a very thorough use of the pontryagin maximum principle for the synthesis of the control.
-In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability: integrating genetic sequencing could provide a path for more certainty in model calibration.
+In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability \cite{Dochain2003}: integrating genetic sequencing could provide a path for more certainty in model calibration.
 
@@
 \section{Acknowledgements}
- The authors would like to thank Alain Rapaport for the fruitful exchanges. This work was financed by project Thermomic ANR-16-CE04-0003.
+ The authors would like to thank Alain Rapaport for the exchanges and comments. This work was financed by project Thermomic ANR-16-CE04-0003.
 
@@
 The entries corresponding to the derivative of the first $n$ functions in the first $n$ variables can be calculated by the use of the chain rule.
-Define (for a fixed $s$):
+Define:
 \begin{align*} 
@@
 &\begin{array}{rl}
-h_2: \R^n \rightarrow & \R^n \\
-x \rightarrow & \diag(f(s))\left(1_{n\times 1}+ Ax\right)-D_{n\times 1}
+h_2: \R^n \times \R^3  \rightarrow & \R^n \\
+(x,s) \rightarrow & \diag(f(s))\left(1_{n\times 1}+ Ax\right)-D_{n\times 1}
 \end{array} 	
@@
 
-The first $n$ equations of system \eqref{system} may be written then as $\dot{x} =  h(x) = h_1(\diag(x), h_2(x))$, by the chain rule: 
-\begin{align} J_h(x) &= D_M h_1(\diag(x),h_2(x))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x))\circ D_xh_2(x)  \\ &=
-\diag(h_2(x))+\diag(x)\diag(f(s))A  \label{n2_entries}
+The first $n$ equations of system \eqref{system} may be written then as $\dot{x} =  h(x,s) = h_1(\diag(x), h_2(s,x))$, by the chain rule: 
+\begin{align} D_xh(x,s) &= D_M h_1(\diag(x),h_2(x,s))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x,s))\circ D_xh_2(x,s)  \\ &=
+\diag(h_2(x,s))+\diag(x)\diag(f(s))A  \label{n2_entries}
 \end{align}
@@
 Expression \eqref{n2_entries} corresponds to the first $n\times n$ entries of the Jacobian of system \eqref{system}.
+
+Define:
 
@@
 
-\section{References}
 \bibliographystyle{elsarticle-num}

### 2020-04-09 tex/Article_Interactions.tex
modified tex
word change

@@
 
-\author{Pablo Ugalde-Salas, Jérôme Harmand, Elie Desmond Le-Quéméner, Héctor Ramirez}
+\author{Pablo Ugalde-Salas, Héctor Ramirez C., Jérôme Harmand, Elie Desmond-Le Quéméner}
 \date{}
@@
 In section 4 the concept of interaction function is developed such that it generalizes the gLV model.
-For the identification of the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data.
+For approximating the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data.
 The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}.

### 2020-04-21 Tracking/main.m
adding weissman parameters

@@ -2,8 +2,8 @@
 %main: process and filter data to model.
 close all
 clear
-load('MAT_files\Classification_day_183_315_gurobi')
-name_file = '200116_day_183_315_gurobi';
+load('MAT_files\\Classification_day_183_315_gurobi')
+name_file = '200407';
 nA = round(sum(class_AOB));
 nB = round(sum(class_NOB)); 
 n = nA+nB;
@@ -21,11 +21,11 @@ biomass_filtered(biomass_filtered == 0) = min_biomass;
 z = @(t) interp1(t_OTU,biomass_filtered,t)';
 kA = yields_AOB(index_AOB);
 kB = yields_NOB(index_NOB);
-muARef = 0.77;
-muBRef = 1.07;
-kSARef = 0.7e-1;
-kSBRef = 1.4982e-1;
-kIRef = 1.217;
+muARef = 1.97; %Weissmann et al. Table 4. T = 30C
+muBRef = 1.87;  %Weissmann et al. Table 4. T = 30C
+kSARef = 7e-1;
+kSBRef = 5.4e-1;
+kIRef = 1;
 muA = muARef*ones(nA,1);
 muB = muBRef*ones(nB,1);
 kSA = kSARef*ones(nA,1);
@@ -33,8 +33,8 @@ kSB = kSBRef*ones(nB,1);
 kI = kIRef*ones(nB,1);
 % %%Parameters
 % lambda = 0.001;
-% lambda = [0.001*ones(nA,1); 0.001*ones(nB,1)];
-lambda = ones(n,1)*10^-7;
+lambda = [ones(nA,1)*1e-4; ones(nB,1)*1e-5];
+% lambda = ones(n,1)*10^-4;
 Q2= [kA; kB];
 % Q = Q2/norm(Q2,'inf');
 Q = [ones(nA,1); ones(nB,1)];

### 2020-04-21 Tracking/plot_data_fit.m
modified growth plots

@@ -1,7 +1,7 @@
 %plotting
 clear
 close all
-name_file_in = 'MAT_Files\\250309_POC_try4_iter_3';
+name_file_in = 'MAT_Files\\200407_iter_20';
 load(name_file_in);
 legend_tags_biomass{1} = 'Data: Sum of species biomass';
 legend_tags_biomass{2} = 'Tracking: Sum of species biomass';
@@ -22,6 +22,7 @@ tic
 control_eval = arrayfun(control,t_new,'UniformOutput',false);
 toc
 control_eval_reshape = reshape(cell2mat(control_eval),n,length(t_new));
+growth_rate = growth_mat'.*x_new(:,1:n)';
 growth_times_control = growth_mat'.*(control_eval_reshape+1).*x_new(:,1:n)';
 %%Total Biomass
 figure
@@ -30,13 +31,13 @@ total_biomass_plot = plot(t_OTU(index_t_OTU),sum(OTU_interp(index_t_OTU,:),2),'k
 total_biomass_plot2 = plot(t_new,sum(x_new(:,1:n),2),'k.-','LineWidth',1.5);
 xlabel('\fontsize{15}Time [days]'),...
     ylabel('\fontsize{15}  Concentration [g/l]'),...
-    title(sprintf('Tracking results total biomass iteration:%.0f',iter));
+    title(sprintf('Tracking results total biomass iteration: %.0f',iter));
 set(gca,'fontsize',15),
 legend(legend_tags_biomass,'fontsize',12);
 fig.PaperUnits = 'inches';
 fig.PaperPosition = [0 0 9 3];
 fig.PaperPositionMode = 'auto';
-print(sprintf('Images\\%s',sprintf('%s_Biomass_iter_%.0f',...
+print(sprintf('Images\\%s',sprintf('%s_iter_%.0f_Biomass',...
     name_file,iter)),'-dpng','-r0')
 %%AOB 
 number_of_AOB_plots = floor(nA/10) + logical(rem(nA,10));
@@ -56,7 +57,7 @@ for k = 1:number_of_AOB_plots
     AOB_data_plot = plot(t_OTU(index_t_OTU),biomass_filtered(index_t_OTU,OTU_plot_index),'*','LineWidth',0.7);
     xlabel('\fontsize{15}Time [days]'),...
         ylabel('\fontsize{15}  Concentration [g/l]'),...
-        title(sprintf('Tracking results AOB iteration:%.0f',iter));
[…]

### 2020-04-21 Tracking/plot_synthetic_data.m
added growth rate plot.

@@ -1,8 +1,12 @@
 clear
 close all
-name_file_in = 'no_noise_200121';
+name_file_in = '250309_POC';
 load(sprintf('MAT_files\\synthetic_data_%s',name_file_in))
-name_file_out = 'no_noise_200121';
+name_file_out = '250309_POC';
+[num_row, num_col] = size(Y);
+Y_cell = mat2cell(Y',num_col,ones(num_row,1));
+growth_AOB =  cellfun(growth1,Y_cell)'.*Y(:,1:nA);
+growth_NOB =  cellfun(growth2,Y_cell)'.*Y(:,nA+1:n);
 %AOB
 numbering_AOB = strsplit(num2str(1:nA));
 legend_tags_AOB = strsplit(strcat(sprintf('OTU %s,', numbering_AOB{:})),',');
@@ -51,4 +55,33 @@ fig.PaperUnits = 'inches';
 fig.PaperPosition = [0 0 9 3];
 fig.PaperPositionMode = 'auto';
 print(sprintf('Images\\%s',sprintf('%s_metabolites',name_file_out)),'-dpng','-r0')
+%%Growth Rate AOB
+figure
+growth_rate_AOB_plot = plot(t_obs,growth_AOB,'*','LineWidth',0.7);
+xlabel('\fontsize{15}Time [days]'),...
+    ylabel('\fontsize{15}  Rate [gBiomass/day]'),...
+    title('Synthetic data growth rate AOB');
+set(gca,'fontsize',15),
+set(growth_rate_AOB_plot,{'Color'},colors_AOB);
+legend('s_1','s_2','s_3','Location','bestoutside')
+fig.PaperUnits = 'inches';
+fig.PaperPosition = [0 0 9 3];
+fig.PaperPositionMode = 'auto';
+print(sprintf('Images\\%s',sprintf('%s_growth_rate',name_file_out)),'-dpng','-r0')
+%%Growth Rate NOB
+figure
+growth_rate_NOB_plot = plot(t_obs,growth_NOB,'*','LineWidth',0.7);
+xlabel('\fontsize{15}Time [days]'),...
+    ylabel('\fontsize{15}  Rate [gBiomass/day]'),...
+    title('Synthetic data growth rate NOB');
+set(gca,'fontsize',15),
+set(growth_rate_NOB_plot,{'Color'},colors_NOB);
+legend('s_1','s_2','s_3','Location','bestoutside')
[…]

### 2020-05-21 tex/Article_Interactions.tex
change of align of interaction function
changes intro + abstract

@@
 \begin{abstract}
-	This article deals with the inclusion of microbial ecology measurements in bioprocess modelling.
-The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting.
+	This article deals with the inclusion of microbial ecology measurements such as abundances of operative taxonomic units in bioprocess modelling.
+The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting where a nitrification process was operated for over 500 days.
 The limitations and the insights of such an approach are discussed.
-In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of genetic sequencing in chemostat models is presented.
+In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of data from genetic sequencing in chemostat models is presented.
 The optimal tracking revisits the data used in the aforementioned chemostat setting.
+The method is able to reconstruct the different forms of nitrogen in the reactor by using the abundances of the operative taxonomic units, even though the synthesized control can not be guaranteed to be optimal.
 \end{abstract}
@@
 Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}.
-A thorough review in current methodologies in the deterministic modelling approaches of microbial community dynamics is presented by Song \textit{et al.} \cite{Song2014}.
-Using their terminology this articles deals with population-based approaches where species are taken as the interacting units.
-
-The classical ecological concept of species and niche in the microbial world is an elusive one: In the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring.
+Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics, this articles deals with population-based approaches where species are taken as the interacting units.
+
+The classical ecological concept of species and niche in the microbial world is an elusive one: in the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring.
 In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}.
-Therefore as an ecological problem is hard to precise the 'niche' of 'species'.
-
+Therefore as an ecological problem is hard to precise the 'niche' of 'microbial species'.
 These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of 16S rDNA marker gene.
-There is a core genome in Bacteria, which is in turn related to the main metabolism of Bacteria, and thus their 'function' within a given ecosystem.
-The function of an OTU, from an engineering perspective, is given by which substances are transformed and at which growth rates and substrate to biomass conversion yields \cite{Muyzer1993}.
-
 In the past years considerable efforts have been made to measure the bacterial community composition.
-Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA, RNA, proteins, and metabolites have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.
+Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.
 
 The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances over time.
-This is a first step towards developing predictive models of a reactor's outcome based on the microbial community structure.
-
-As a departing point the work of Dumont et al.\cite{Dumont2016} is reinspected in section 2.
-They model a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression: They fitted their model to the molecular fingerprints of the most abundant OTU.
-Section 3 inspects through a mathematical analysis their model.
+In other words, while most models used in bioengineering are functional- in the sense they consider only one species per biological reaction considered- this work is a first attempt to merge classical population-based models used in ecology and those used by engineers in biotechnology.
+
+As a departing point, the work of Dumont et al.\cite{Dumont2016} is presented in section 2.
+They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints.
+Section 3 inspects the model through a mathematical analysis.
 Some interesting outputs of this analysis are that the number of possible equilibrium points grows exponentially with the number of species, coexistence can be achieved within the same functional group, and bi-stability may arise.
@@
 In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}.
+This approach explicitly assumes that dynamics of complex ecosystems are driven by interactions, that are the results of feedback loops of each species on the growth rate of others that they modulate depending on their own abundances.
 The method shows that by following the community dynamics one can propose a growth rate that reconstructs the substrates dynamics.
@@
 	\begin{enumerate}
-		\item\begin{align}
-		\I \left( (0,\dots,0)^\top \right) = 
-		(1,\dots,1)^\top 
-		\end{align}
+		\item $	\I \left( (0,\dots,0)^\top \right) = (1,\dots,1)^\top $
 		\item Let $\Omega$ be an open subset of $ \R^n $ then $\I \in C^1(\Omega)$.

### 2020-05-21 tex/Article_Interactions.tex
various changes

@@
 \newcommand{\I}{\mathcal{I}}
-\newcommand{\diag}{\textbf{diag}}
+\DeclareMathOperator{\diag}{diag}
 \newtheorem{defn}{Definition}
@@
 
-\author{Pablo Ugalde-Salas, Héctor Ramirez C., Jérôme Harmand, Elie Desmond-Le Quéméner}
+\author{Pablo Ugalde-Salas, Héctor Ramírez C., Jérôme Harmand, Elie Desmond-Le Quéméner}
 \date{}
@@
 Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}.
-Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics, this articles deals with population-based approaches where species are taken as the interacting units.
+Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics presented by Song \textit{et al.}\cite{Song2014}, this articles deals with population-based approaches where species are taken as the interacting units.
 
@@
 Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.
-
 The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances over time.
@@
 As a departing point, the work of Dumont et al.\cite{Dumont2016} is presented in section 2.
-They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints.
+They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model\cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints.
 Section 3 inspects the model through a mathematical analysis.
 Some interesting outputs of this analysis are that the number of possible equilibrium points grows exponentially with the number of species, coexistence can be achieved within the same functional group, and bi-stability may arise.
-
 In section 4 the concept of interaction function is developed such that it generalizes the gLV model.
@@
 The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}.
-
 In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}.
-This approach explicitly assumes that dynamics of complex ecosystems are driven by interactions, that are the results of feedback loops of each species on the growth rate of others that they modulate depending on their own abundances.
+This approach explicitly assumes that dynamics of complex ecosystems are driven by interactions, that are the results of feedback loops of each species on the growth rate of others.
 The method shows that by following the community dynamics one can propose a growth rate that reconstructs the substrates dynamics.
-The article ends with a discussion on the scope of applicability of the method and perspectives.
+The article ends with a discussion on the scope of applicability and perspectives of the method .
 
@@
 	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
+In the example $G_1$ corresponds to Ammonium oxidizing bacteria (AOB) and $G_2$ corresponds to Ammonium oxidizing bacteria (NOB).
 	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
@@
 	\item $x$: vector $(x_1,\dots,x_n)^\top$.
-	\item $s_1$ : concentration of substrate 1 in $[g/l]$.
-	\item $s_2$ : concentration of substrate 2 in $[g/l]$. 
-	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
+	\item $s_1$ : concentration of substrate 1 in $[g/l]$. In the example $s_1$ represents ammonium.
+	\item $s_2$ : concentration of substrate 2 in $[g/l]$. In the example $s_2$ represents nitrite. 
+	\item $s_3$ : concentration of substrate 3 in $[g/l]$. In the example $s_3$ represents nitrate.
+	\item $s_{in}$: entry concentration of substrate $1$ in $[g/l]$. May depend on time $s_{in} = s_{in}(t)$.
 	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites.
@@
 	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
-	\item $D$: dilution rate of the continuous reactor in $[1/day]$. 
-	\item $y_i$: yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
+	\item $D$: dilution rate of the continuous reactor in $[1/day]$. May depend on time $D=D(t)$.
+	\item $y_i$: yield of grams of dry biomass formed per gram of substrate consumed of OTU $i$.
 	\item $y$: vector $y_1,\dots,y_n$.
-	\item $k_i$: yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
+	\item $k_i$: yield of grams of substrate consumed per gram of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
 	\item $k$: vector $k_1,\dots,k_n$.
@@
 	\item Let $S$ be a finite set with $m \in \N$ elements. Then $\vert S \vert := m$. 
-\end{enumerate}
-
-\subsection{Stoichiometric Equations}
-A cascade (bio)reaction process is considered.
-Suppose $n$ different OTU are present in the chemostat.
-The cascade reaction refers to the situation where a group of microorganisms ($G_1 \subset [n] $) consumes a substrate $s_1$ and produces $s_2$ and biomass, while another group of microorganisms ($G_2\subset [n]$) consumes $s_2$ and produces $s_3$ and biomass.
-$G_1$ and $G_2$ are called functional groups.
-The number of organisms in each functional will be denoted $n_1$ and $n_2$ respectively, that is $\vert G_1 \vert = n_1$ and $\vert G_2 \vert = n_2$ .
-This work treats the case when $G_1$ and $G_2$ are disjoint sets:
-
-\begin{hypo}  Sets $G_1$ and $G_2$ satisfy: $G_1 \cap G_2 = \emptyset$ and $G_1 \cup G_2 = [n]$. 
-\end{hypo}
-
-The situation is described as simplified reactions \eqref{Reaction1} and \eqref{Reaction2}.
-The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather it represents the direction of the bioprocess and the proportions of different consumed and formed compounds of interest.
-
-The terms $y_i$ are known as yields, they represent the number of grams of biomass produced per gram of substrate consumed for OTU $i$.
-In this work the unit grams of dry biomass per gram of substrate is used for yields.
-Furthermore, for each $ i \in [n]$, OTU $i$ is characterized by its process rate (also known as growth function) $\mu_i(s,x)$.
-Notice that for being as generic as possible, the growth rate may be a function of the whole state in order to model the influence of all OTU on the growth rates of others.
-\begin{align}
-\label{Reaction1} \tag{R G1} 	s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
-\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
-\end{align}
-
-An example of this process is the nitrification process where group $G_1$ is known as Ammonium oxidizing Bacteria (AOB), and group $G_2$ is known as Nitrite oxidizing Bacteria (NOB) \cite{SHARMA1977897}.
-\subsection{Mass Balance Equations}
-
-Consider the scenario of an continuous and homogeneous reactor: the input flow is the same as the output flow, with a dilution rate $D$.
-The input flow contains a concentration $s_{in}$ of substrate $s_1$.
-Note that $s_{in}$ and $D$ are time dependent.
-Each OTU grows at a rate $\mu_i(s,x)$.
-System \eqref{system} represents this situation.
-A specific case of $\mu_i(s,x)$ is given in the next subsection.
-
-\begin{align} 
-\label{system}
-\begin{array}{cl}
-\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_1\\
-\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_2 \\
-\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i\in G_1} \frac{1}{y_i}\mu_i(s,x) x_i  \\
-\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in G_1}\frac{1}{y_i}\mu_i(s,x)x_i 		-\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i  \\
-\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i 
-\end{array}
-\end{align}
-
-\subsection{Kinetic Equations}
-In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rate seen in equations \eqref{gLV growth1} and \eqref{gLV growth2} was calibrated against experimental data for the two most abundant OTU of each functional group.
-
-\begin{align}
-\label{gLV growth1}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
-\label{gLV growth2}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2 
-\end{align}
-
-The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU, while the term $\bar{\mu}_i\dfrac{s_j}{K_i + s_j}$ represents the substrate limitation \cite{monod1942recherches}.
-Let $A$ denote the matrix
-with entries $a_{ij}$ hereafter referred to as the interaction matrix.
-The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
-
-\section{Mathematical Analysis}
-
-The system of equations \eqref{system} is defined in the region
-
-\begin{align*}
-\Omega := \{ (x_1,\dots,x_n,s_1,s_2,s_3)\in  \R^{n+3} | x_1,\dots,x_n,s_1,s_2,s_3  \geq 0  \}
-\end{align*}
-
-First sufficient conditions for the system to be well posed are established: meaning that solutions remain bounded and non-negative in time, this ultimately implies that the solution exists for every $t \geq 0$ \cite{Khalil1996}.
-
-Second the equilibria of the system are derived.
-Possible equilibrium points for this system grow exponentially with the number of OTU considered ($n$).
-Stability is not analytically addressed, a numerical scheme calculating every equilibrium point and the system's Jacobian eigenvalues at the equilibrium point was implemented for studying the system.
-
-\subsection{Properties of the system}
-
-By bounding the norm of the interaction matrix on the initial conditions and parameters one establishes that solutions will remain positive and bounded.
-
-\begin{lemma}
-	\label{l1}
-	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists positive scalars $M_1$, $M_2$, and $M_3$ such that solutions to \eqref{system} satisfy the following inequalities:
-	\begin{align}
-	&\sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1 \leq M_1 \\
-	&\sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 +s_2 \leq M_2 \\
-	&s_1 + s_2 + s_2 \leq M_3
-	\end{align}
-\end{lemma}
-
-The proof can be seen in the supplementary material. A bound on the norm of $A$ is found such that every matrix $A$, respecting the bound, guaranties that $\Omega$ is a positively invariant set.
-
-\begin{theo}
-	\label{theoWellPosedness}
-	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}, remain in $\Omega$ and are bounded.
-\end{theo}
-
-The proof can be seen in the supplementary material.
-
-\subsection{Equilibrium Points}
-
-In this section analytical expressions for equilibrium points are derived.
-However no analytic expression concerning the stability of such points is presented.
-To answer the question of stability a numeric scheme is used by evaluating the Jacobian at the equilibrium point.
-At the end of the section an algorithm is provided for exploring all the possible equilibria.
-
-\begin{defn} 
-	An equilibrium point (or steady state) is a point $(x^{eq},s^{eq}) \in \R^{n+3}_+$ so that the right hand side of equations \eqref{Eq1},\eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4} equals zero. 
-\end{defn}
-
-Observe that equilibrium points are by definition non-negative so the state variables can have physical meaning.
-Details of the calculations are given in the appendix.
-An important assumption throughout the work is that matrix $A$ and some of its submatrices have an inverse, this is stated properly in hypothesis \ref{inverse hypothesis}.
-
-\begin{hypo}
-	Let $A$ be the interaction matrix of size $n \in \N$ and $S$ be a proper subset of $[n]$ with $|S| = m$.
-Then the matrix $B \in \R^{(n-m) \times (n-m)}$ defined by taking out the $S$ rows and columns of matrix $A$ is invertible.
-	\label{inverse hypothesis}
-\end{hypo}
-
-This model \eqref{system} is restated in a more compact form using matrix notation.
-
-\begin{defn} Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
+	\item Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
 	\begin{align}
@@
 	\end{align}
-\end{defn}
-
-Function \eqref{diag_operator} places a vector $v$ in the diagonal of a matrix. Recalling $A$ the matrix with coefficients $a_{ij}$. The following notation is introduced.
+\end{enumerate}
+
+\subsection{Stoichiometric Equations}
+A cascade (bio)reaction process is considered.
+Suppose $n$ different OTU are present in the chemostat.
+A two step cascade reaction refers to the situation where a group of microorganisms ($G_1 \subset [n] $) consumes a substrate $s_1$ and produces $s_2$ and biomass, while another group of microorganisms ($G_2\subset [n]$) consumes $s_2$ and produces $s_3$ and biomass.
+$G_1$ and $G_2$ are called functional groups.
+The number of organisms in each functional will be denoted $n_1$ and $n_2$ respectively, that is $\vert G_1 \vert = n_1$ and $\vert G_2 \vert = n_2$.
+This work treats the case when $G_1$ and $G_2$ are disjoint sets:
+
+\begin{hypo}  Sets $G_1$ and $G_2$ satisfy: $G_1 \cap G_2 = \emptyset$ and $G_1 \cup G_2 = [n]$. 
+\end{hypo}
+
+The situation is described as simplified reactions \eqref{Reaction1} and \eqref{Reaction2}.
+The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather it represents the direction of the bioprocess and the proportions of different consumed and formed compounds of interest.
+
+The terms $y_i$ are known as yields, they represent the quantity (in grams of dry biomass produced per gram of substrate) consumed for OTU $i$.
+In this work the unit grams of dry biomass per gram of substrate is used for yields.
+Furthermore, for each $ i \in [n]$, OTU $i$ is characterized by its process rate (also known as growth function) $\mu_i(s,x)$.
+Notice that for being as generic as possible, the growth rate may be a function of the whole state in order to model the influence of all OTU on the growth rates of others.
+\begin{align}
+\label{Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
+\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
+\end{align}
+
+An example of this process is the nitrification process where group $G_1$ is known as Ammonium oxidizing Bacteria (AOB), and group $G_2$ is known as Nitrite oxidizing Bacteria (NOB) \cite{SHARMA1977897}.
+\subsection{Mass Balance Equations}
+
+Consider the scenario of a continuous and homogeneous reactor: the input flow is the same as the output flow, with a dilution rate $D$.
+The input flow contains a concentration $s_{in}$ of substrate $s_1$.
+Note that $s_{in}$ and $D$ are time dependent.
+Each OTU grows at a rate $\mu_i(s,x)$.
+System \eqref{system} represents this situation.
+A specific case of $\mu_i(s,x)$ is given in the next subsection.
+
+\begin{align} 
+\label{system}
+\begin{array}{cl}
+\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_1\\
+\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_2 \\
+\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i\in G_1} \frac{1}{y_i}\mu_i(s,x) x_i  \\
+\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in G_1}\frac{1}{y_i}\mu_i(s,x)x_i 		-\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i  \\
+\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i 
+\end{array}
+\end{align}
+
+\subsection{Kinetic Equations}
+In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rates seen in equations \eqref{gLV growth1} and \eqref{gLV growth2} were calibrated against experimental data for the two most abundant OTU of each functional group.
+
+\begin{align}
+\label{gLV growth1}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
+\label{gLV growth2}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2 
+\end{align}
+
+The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU, while the term $\bar{\mu}_i\dfrac{s_j}{K_i + s_j}$ is a Monod growth expression, where $\bar{\mu}_i$ represents the maximum growth rate, and $K_i$ the half saturation constant \cite{monod1942recherches}.
+Let $A$ denote the matrix
+with entries $a_{ij}$ hereafter referred to as the interaction matrix.
+Dumont\textit{ et al.} did not analyse their model but simply provided a number of simulation results using parameter values identified from experimental data.
+The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
+
+\section{Mathematical Analysis}
+
+The system of equations \eqref{system} is defined in the region
+
+\begin{align*}
+\Omega := \{ (x_1,\dots,x_n,s_1,s_2,s_3)\in  \R^{n+3} | x_1,\dots,x_n,s_1,s_2,s_3  \geq 0  \}
+\end{align*}
+
+First, sufficient conditions on the interaction matrix for the system to be well posed are established: meaning that solutions remain bounded and non-negative in time, this ultimately implies that the solution exists for every $t \geq 0$ \cite{Khalil1996}.
+
+Second, the equilibria of the system are derived.
+Possible equilibrium points for this system grow exponentially with the number of OTU considered ($n$).
+Stability is not analytically addressed, a numerical scheme calculating every equilibrium point and the system's Jacobian eigenvalues at the equilibrium point was implemented for studying the system.
+
+\subsection{Properties of the system}
+
+A bound on the norm of the interaction matrix that depends on the initial conditions and parameters one establishes that solutions will remain positive and bounded.
+
+\begin{lemma}
+	\label{l1}
+	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists positive scalars $M_1$, $M_2$, and $M_3$ such that solutions to \eqref{system} satisfy the following inequalities:
+	\begin{align}
+	&\sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1 \leq M_1 \\
+	&\sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 +s_2 \leq M_2 \\
+	&s_1 + s_2 + s_2 \leq M_3
+	\end{align}
+\end{lemma}
+
+The proof can be seen in the supplementary material. A bound on the norm of $A$ is found such that every matrix $A$, respecting the bound, guaranties that $\Omega$ is a positively invariant set.
+
+\begin{theo}
+	\label{theoWellPosedness}
+	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}, remain in $\Omega$ and are bounded.
+\end{theo}
+
+The proof can be seen in the supplementary material.
+
+\subsection{Equilibrium Points}
+
+In this section analytical expressions for equilibrium points are derived.
+However, no analytic expression concerning the stability of such points is presented.
+To answer the question of stability a numeric scheme is used by evaluating the Jacobian at the equilibrium point.
+At the end of the section an algorithm is provided for exploring all the possible equilibria.
+
+Model \eqref{system} is restated in a more compact form using matrix notation.
 
@@
 \end{bmatrix}\end{align}
- Where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$.
-$A_2$ is a matrix of dimension $n_2 \times n$ rows corresponding to the interaction coefficients of OTU $i \in G_2$.
-And  $f(s) \in \R^n$, such that 
+where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$.
+$A_2$ is a matrix of dimension $n_2 \times n$ rows corresponding to the interaction coefficients of OTU $i \in G_2$, and  $f(s) \in \R^n$ is such that
 \begin{align}
@@
 
-with the above system \eqref{system}, is rewritten in equations \eqref{Eq1}, \eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4}.
+Thus, system \eqref{system} is rewritten as follows.
 
@@
 
-Finally the set of non-active coordinates is defined.
-
 \begin{defn} 
-	Given an equilibria point $(x^{eq},s^{eq})$ of system \eqref{system}, then the set of non-active coordinates $\mathcal{J}\subset \{1,\dots,n\}$ is defined as:
+	An equilibrium point (or steady state) is a point $(x^{eq},s^{eq}) \in \Omega$ so that the right hand side of equations \eqref{Eq1},\eqref{Eq2}, \eqref{Eq3}, and \eqref{Eq4} equals zero. 
+\end{defn}
+
+Observe that equilibrium points are by definition non-negative so the state variables can have physical meaning.
+For studying the cases where $x^{eq}$ contains zero valued entries, the set of non-active coordinates is defined as follows:
+
+\begin{defn}
+	Given an equilibrium point $(x^{eq},s^{eq})$ of system \eqref{system}, then the set of non-active coordinates $\mathcal{J}\subset \{1,\dots,n\}$ is defined as:
 	$\mathcal{J} = \{j_1, \dots, j_m\ : \, x^{eq}_{j_i} = 0 , \;i \in [m] \} $.
@@
 
+	$n_1^{act}$ and $n_2^{act}$ denote the number of positive entries of $x^{eq}$ of functional groups $G_1$ and $G_2$, respectively.
+$n^{act} = n-m$ denotes the total number of positive entries of $x^{eq}$.
 The active growths $f^{act}(s)$ and yields $k^{act}$ are defined analogously by the positive entries of $x^{eq}$.
-The active interactions $A^{act}$ is defined as matrix $A$ without the $\mathcal{J}$ rows and columns.
+The active interactions $A^{act}$ is defined as the matrix $A$ without the $\mathcal{J}$ rows and columns.
 \end{defn}
 
-\subsubsection{Complete Coexistence}
-
-This section derives the equations for an equilibrium point with every OTU being positive: $x^{eq}_i>0$, which is stated in hypothesis \ref{hypothesis complete coexistence}.
+ Finally, for deriving the equilibrium points, it is desirable an invertible $A^{act}$ matrix.
+Therefore in what follows of the work it is assumed that matrix $A$ and some of its sub matrices have an inverse, this is stated properly in Hypothesis \ref{inverse hypothesis}.
 
 \begin{hypo}
-	$\mathcal{J} =  \emptyset$
-	\label{hypothesis complete coexistence}
+	Let $A$ be the interaction matrix of size $n \in \N$ and $S$ be a proper subset of $[n]$ with $|S| = m$.
+Then the matrix $B \in \R^{(n-m) \times (n-m)}$ defined by taking out the $S$ rows and columns of matrix $A$ is invertible.
+	\label{inverse hypothesis}
 \end{hypo}
 
-From equation \eqref{Eq1} one gets that an equilibrium point satisfies: \begin{align*}
-\diag(x)(\diag(f(s)(1_{n\times 1} + Ax) - D_{n\times 1}) & = 0 \\
-\Rightarrow x_i = 0 \vee (\diag (f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i & = 0 \quad \forall i\in (1,\dots,n)
-\end{align*}
-
-Since $x_i>0$ one has 
-\begin{align}
-\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}=0 \\
-\label{xEquilibria}\Leftrightarrow x = A^{-1}(\diag (f(s))^{-1}D_{n\times 1} - 1_{n\times 1})
-\end{align}
-
-By replacing \eqref{xEquilibria} in equation \eqref{Eq2}:
-
-\begin{align}
-\label{s1Equilibria} (s_{in}-s_1)-	\begin{bmatrix}
-1_{n_1\times 1} \\0_{n_2\times 1}
-\end{bmatrix}^\top \diag (k) A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0 
-\end{align}
-
-A similar expression is obtained when replacing \eqref{xEquilibria} in equation \eqref{Eq3}
-
-\begin{align}
-\label{s2Equilibria}-s_2+
-1_{n\times 1}^{\top}\diag (k)  A^{-1}(\diag(f(s))^{-1}D_{n\times 1}-1_{n\times 1}) = 0
-\end{align}
-
-From equation \eqref{s1Equilibria} $s_2$ can be written as a function of $s_1$:
-\begin{align}
-s_2 = \frac{s_1}{c_1s_1^2+c_2s_1+c_3} \label{S2(S1)}
-\end{align}
-
-Then by replacing  \eqref{S2(S1)} in equation \eqref{s2Equilibria}, one gets a fourth degree polynomial for $s_1$.
-
-\begin{align}
-\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
-\end{align}
-
-Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
-
-Finally, in equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
-
-\begin{align}
-s_{in} = s_1+s_2+s_3 \label{s1s2s3}
-\end{align}
-
-If the system of equations \eqref{xEquilibria}, \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} provides only solutions with some negative entries then complete coexistence is not possible.
-
-\subsubsection{Washout of some OTU}
-
-Hypothesis \ref{hypothesis CN} represents the case where in each functional group remains at least one OTU.
-
+\subsubsection{Both functional groups are present}
+
+The case where in each functional group remains at least one OTU is represented by Hypothesis \ref{hypothesis CN}.
 \begin{hypo}The set $\mathcal{J}$ satisfies $ G_1 \not \subset \mathcal{J} , \, G_2 \not \subset \mathcal{J} $.
@@
 
-But since $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ then the coefficients $a_{ij}$ play no role in the equation \eqref{Extinction} one can rewrite equation \eqref{Extinction} as $\diag(f^{act}(s))(1_{(n-m)\times 1} + A^{act}x^{act}) - D_{(n-m) \times 1}=0 $.
+note that $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ therefore the coefficients $a_{ij}$ play no role in equation \eqref{Extinction} and one can rewrite equation \eqref{Extinction} as $\diag(f^{act}(s))(1_{n^{act}\times 1} + A^{act}x^{act}) - D_{n^{act} \times 1}=0 $.
 From hypothesis \ref{inverse hypothesis} matrix $A^{act}$ has an inverse.
@@
 	\begin{align}
-	\label{EqSome}x^{act} = (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})
+	\label{EqSome}x^{act} = (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1})
 	\end{align} 
@@
 
-The equilibrium of the system is solved as described by equations \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} as before, but coefficients are calculated differently (essentially the same, but only uses the coefficients corresponding to the active points).
+By replacing \eqref{EqSome} in equation \eqref{Eq2}:
+
+\begin{align}
+\label{s1Equilibria} (s_{in}-s_1)-	\begin{bmatrix}
+1_{n_1^{act}\times 1} \\0_{n_2^{act}\times 1}
+\end{bmatrix}^\top \diag (k^{act}) (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1}-1_{n^{act}\times 1}) = 0 
+\end{align}
+
+A similar expression is obtained when replacing \eqref{EqSome} in equation \eqref{Eq3}
+
+\begin{align}
+\label{s2Equilibria}-s_2+
+	\begin{bmatrix}
+1_{n_1^{act}\times 1} \\-1_{n_2^{act}\times 1}
+\end{bmatrix}^\top\diag (k^{act})(A^{act})(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1}-1_{n^{act}\times 1}) = 0
+\end{align}
+
+From equation \eqref{s1Equilibria} $s_2$ can be written as a function of $s_1$:
+\begin{align}
+s_2 = \frac{s_1}{c_1s_1^2+c_2s_1+c_3} \label{S2(S1)}
+\end{align}
+
+Then by replacing  \eqref{S2(S1)} in equation \eqref{s2Equilibria}, one gets a fourth degree polynomial for $s_1$.
+
+\begin{align}
+\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
+\end{align}
+
+Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
+
+Finally, in equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
+
+\begin{align}
+s_{in} = s_1+s_2+s_3 \label{s1s2s3}
+\end{align}
+
+If the system of equations \eqref{EqSome}, \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} provides only solutions with some negative entries then the set $\mathcal{J}$ can not define an equilibrium point.
 
@@
 
-In the case that $x_i = 0, \, \forall i \in G_2$ then from equation \eqref{Eq4}.
+Equations \eqref{EqSome} and \eqref{s1Equilibria} still hold, but in this case note that $f^{act}(s)$ does not contain any term involving $s_2$, and therefore one obtains a quadratic equation for $s_1$:
+
+\begin{align}
+\label{poly2_s1} a'_2 s_1^2 + a'_1s_1 + a'_0 = 0
+\end{align}
+
+Where $a'_i$ can be found in the appendix.
+
+Since $x_i = 0, \, \forall i \in G_2$ then from equation \eqref{Eq4}.
 \begin{align}
@@
 
-Then by replacing  \eqref{EqSome} and \eqref{EquilibriaFormula} in \eqref{Eq2}.
-\begin{align}
-\label{S1NOBWashout}  (s_{in}-s_1)-1_{(n-m)\times 1}^\top
-\diag(k)(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1}) = 0 
-\end{align}
-
-Notice \eqref{S1NOBWashout} does not contain terms with $s_2$. By reordering the terms \eqref{S1NOBWashout} one finds a two degree polynomial of $s_1$:
-
-\begin{align}
-a'_2 s_1^2 + a'_1s_1 + a'_0 = 0
-\end{align}
-
-Where $a'_i$ can be found in the appendix.
-
 \subsubsection{Washout}
 
-The washout equilibria means $x_i = 0$ for every $i \in \{1,\dots, n_1\}$. This is equivalent to hypothesis \ref{hypothesis washout}.
+The washout equilibria means $x_i = 0$ for every $i \in \{1,\dots, n_1\}$.
+This is equivalent to hypothesis \ref{hypothesis washout}.Note that the structure of a cascade reaction implies that if $G_1$ gets washed out, then so is $G_2$.
+
 \begin{hypo} 
@@
 
-All the former discussion leads to a potential number of   $ (2^{n_1}-1)\cdot (4\cdot(2^{n_2}-1)+2)+1 $  different equilibria. 
+All the former discussion leads to a potential number of   $ (2^{n_1}-1)\cdot (4\cdot(2^{n_2}-1)+2)+1 $  different equilibria. Indeed: 
 \begin{align} \overbrace{(2^{n_1}-1)}^{\substack{\text{nonempty subsets} \\ \text{of }G_1 }} (\underbrace{4}_{\substack{\text{possible} \\ \text{solutions of} \\ \text{equation \eqref{Poly4}}}} \cdot\overbrace{(2^{n_2}-1)}^{\substack{\text{nonempty subsets} \\ \text{of  }G_2}}+\underbrace{2}_{\substack{G_2 \\ \text{Washout}}})+\overbrace{1}^\text{Washout}
@@
 Operating and ecological diagrams are created from this stability analysis.
-Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$: In a $D-S_{in}$ plane different zones representing the stability properties of system \eqref{system} are identified.
+Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$: In a $D-s_{in}$ plane different zones representing the stability properties of system \eqref{system} are identified.
 
@@
 A general formula for this Jacobian is presented in the supplementary material \eqref{Jacobian_system}.
-Algorithm \ref{StabilityAnalysis} summarizes such a procedure.
+Algorithm \ref{StabilityAnalysis} summarizes this procedure.
 
@@
 	$\mathcal{P} = \emptyset$ \\
-	\For{$S \subset [n]$ }{	Calculate equilibrium $(x,s_1,s_2,s_3)$ when $\mathcal{J}:= S$ according to hypothesis \ref{hypothesis complete coexistence} \ref{hypothesis CN}, \ref{hypothesis washout G2}, or \ref{hypothesis washout}.
-\\
+	\For{$S \subset [n]$ }{	Calculate equilibrium $(x,s_1,s_2,s_3)$ when $\mathcal{J}:= S$ according to hypothesis \ref{hypothesis CN}, \ref{hypothesis washout G2}, or \ref{hypothesis washout}. \\
 		\If{$(x,s_1,s_2,s_3) \geq 0$}{eig = Eigenvalues of $J(x,s_1,s_2,s_3)$ \\
@@
 Ecological diagrams provide more information than operating diagrams, in the sense that one can infer the operating diagram from an ecological diagram.
-However for exposure of the subject OD are used in the first case study, while ED are used in the second case study.
+In other words, instead of representing areas where either CN, PN or WO take place, ranges of pairs $(s_{in},D)$ where species coexist are represented.
 
@@
 When $A=0$ algorithm \ref{StabilityAnalysis} is no longer valid (A is not invertible), nevertheless the stability analysis is much simpler and is given in the supplementary material section.
-Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while the interaction matrices are shown in \ref{case1_no_interactions} and \ref{case1_interactions}.
+The interaction matrices are shown in \ref{case1_no_interactions} and \ref{case1_interactions}, the rational behind the second choice was to force a .
+Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while
 
@@
 Note how the presence of $x_1$ affects very negatively $x_2$ in \eqref{case1_interactions}.
-The sign of terms in the diagonal entries of the matrix represents interspecies interactions.}
+The terms in the diagonal entries of the matrix represents intraspecies interactions, while the terms off thepo
+		 diagonal represent the interspecies interactions.}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{Note how \ref{OD_interactions} has a much larger zone where partial nitrification takes place. This is due to the negative interaction $x_1$ plays against $x_2$.}
+	\caption{Note how \ref{OD_interactions} has a much larger zone where partial nitrification takes place. This is due to the negative interaction of $x_1$ on $x_2$.}
 \end{figure} 

### 2020-05-22 tex/Article_Interactions.tex
begin change of notation

@@
 	$\mathcal{J} = \{j_1, \dots, j_m\ : \, x^{eq}_{j_i} = 0 , \;i \in [m] \} $.
-
-	The active point $x^{act}\in \R^{n-m}$ is defined by the positive entries of $x^{eq}$. The relationship between the two is given by:
-
-	\begin{align}\label{EquilibriaFormula} (x^{eq})_i = \begin{cases}
-	x^{act}_i & \text{for } i < j_1\\
-	x^{act}_{i-k} & \text{for } j_{k}< i <j_{k+1}  \text{ and } k \in \{1,\dots,m-1\}\\
-	x^{act}_{i-m} & \text{for } j_{m}< i \\
-	0 & \text{for } i \in \{j_1, \dots, j_m\}
-	\end{cases} \end{align}
-
 $n_1^{act}$ and $n_2^{act}$ denote the number of positive entries of $x^{eq}$ of functional groups $G_1$ and $G_2$, respectively.
 $n^{act} = n-m$ denotes the total number of positive entries of $x^{eq}$.
+The active point $x^{act}\in \R^{n^{act}}$ is defined by the positive entries of $x^{eq}$.
 The active growths $f^{act}(s)$ and yields $k^{act}$ are defined analogously by the positive entries of $x^{eq}$.
 The active interactions $A^{act}$ is defined as the matrix $A$ without the $\mathcal{J}$ rows and columns.
+Let $M$ be the matrix defined by taking out the $\mathcal{J}$ columns of the identity matrix, then
+	 \begin{align}
+	 x^{eq} = Mx^{act} \\	
+	 f^{act}(s) = M^{\top}f(s) \\
+	 k^{act} = M^{\top}k \\
+	 A^{act} = M^{\top}AM
+	 \end{align}.
+
+%	\begin{align}\label{EquilibriaFormula} (x^{eq})_i = \begin{cases}
+%	x^{act}_i & \text{for } i < j_1\\
+%	x^{act}_{i-k} & \text{for } j_{k}< i <j_{k+1}  \text{ and } k \in \{1,\dots,m-1\}\\
+%	x^{act}_{i-m} & \text{for } j_{m}< i \\
+%	0 & \text{for } i \in \{j_1, \dots, j_m\}
+%	\end{cases} \end{align}
+
 \end{defn}
@@
 \begin{align}
+x_i = 0 \vee (\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n] \\
 \Rightarrow  (\diag (f(s))(1_{n\times 1}+ Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n]\setminus \mathcal{J} \\

### 2020-05-25 tex/Article_Interactions.tex
finished POC and application.

@@
 	\item $D$: dilution rate of the continuous reactor in $[1/day]$. May depend on time $D=D(t)$.
-	\item $y_i$: yield of grams of dry biomass formed per gram of substrate consumed of OTU $i$.
-	\item $y$: vector $y_1,\dots,y_n$.
-	\item $k_i$: yield of grams of substrate consumed per gram of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
-	\item $k$: vector $k_1,\dots,k_n$.
+	\item $y_{i}$: yield of grams of OTU $i$ formed per gram of substrate consumed. 
+	\item $y_{s_i/x_j}$: yield of grams of substrate $s_i$ consumed/produced per gram of OTU $j$ formed. If negative it represents consumption, if positive it represents production.
+	\item $Y$: matrix containing all yields such that $Y_{ij} = y_{s_i/x_j}$.
 	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
 	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
+	\item Let $M$ be a matrix, then $M_{i\bullet}$ represents the $i$-th row of matrix $M$.
 	\item Let $S$ be a finite set with $m \in \N$ elements. Then $\vert S \vert := m$. 
@@
 The situation is described as simplified reactions \eqref{Reaction1} and \eqref{Reaction2}.
-The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather it represents the direction of the bioprocess and the proportions of different consumed and formed compounds of interest.
-
-The terms $y_i$ are known as yields, they represent the quantity (in grams of dry biomass produced per gram of substrate) consumed for OTU $i$.
-In this work the unit grams of dry biomass per gram of substrate is used for yields.
+The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather they represent the direction of the bioprocess and the proportions of different consumed and formed compounds of interest.
+The terms $y_i$ are known as yields, they represent the quantity of g of biomass produced per g of substrate consumed by  OTU $i$.
+For example in the case of reaction \eqref{Reaction1}, one gram of $s_1$ is consumed, one gram of $s_2$ and $y_{x_i/s_1}$ grams of dry biomass of OTU $i$ are produced.
+\begin{align}
+\label{Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
+\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
+\end{align}
+However for expressing the system of differential equations further below, the terms $y_{s_i/x_j}$ are used.
+They express the grams of substrate $s_i$ consumed (negative sign) or produced (positive sign) per gram of OTU $j$ formed.
+They are related to $y_i$ as seen in table \ref{yields table}.
+This defines the stoichiometry matrix $Y \in \R^{3 \times n}$, such that $Y_{ij} = y_{s_i/x_j}$.
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|l|l|l|}
+		\hline
+		\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Yields per \\ Biomass formed\end{tabular}} & \multicolumn{1}{c|}{$j \in G_1$} & \multicolumn{1}{c|}{$j \in G_2$} \\ \hline   \rule{0pt}{3.5ex}
+		$y_{s_1/x_j}$ & $-\dfrac{1}{y_j}$ & $0$ \\  \hline   \rule{0pt}{3.5ex}
+		$y_{s_2/x_j}$ & $\dfrac{1}{y_j}$  & $-\dfrac{1}{y_j}$ \\ \hline   \rule{0pt}{3.5ex}
+		$y_{s_3/x_j}$ & $0$  & $\dfrac{1}{y_j}$  \\ \hline
+	\end{tabular}
+	\caption{Relationship of $y_{s_i/x_j}$ with $y_j$.}
+		\label{yields table}
+\end{table}
+
 Furthermore, for each $ i \in [n]$, OTU $i$ is characterized by its process rate (also known as growth function) $\mu_i(s,x)$.
 Notice that for being as generic as possible, the growth rate may be a function of the whole state in order to model the influence of all OTU on the growth rates of others.
-\begin{align}
-\label{Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
-\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
-\end{align}
 
@@
 \begin{array}{cl}
-\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_1\\
-\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in G_2 \\
-\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i\in G_1} \frac{1}{y_i}\mu_i(s,x) x_i  \\
-\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in G_1}\frac{1}{y_i}\mu_i(s,x)x_i 		-\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i  \\
-\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2}\frac{1}{y_i}\mu_i(s,x) x_i 
+\dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in [n] \\
+\dot{s_1} =& \displaystyle (s_{in}-s_1)D+\sum\limits_{i\in G_1} y_{s_1/x_i}\mu_i(s,x) x_i  \\
+\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in [n]}y_{s_2/x_i}\mu_i(s,x)x_i  \\
+\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2}y_{s_3/x_i}\mu_i(s,x) x_i 
 \end{array}
@@
 
-The proof can be seen in the supplementary material. A bound on the norm of $A$ is found such that every matrix $A$, respecting the bound, guaranties that $\Omega$ is a positively invariant set.
+The proof can be seen in the supplementary material. A bound on the norm of $A$ is found such that every matrix $A$ respecting the bound, guaranties that $\Omega$ is a positively invariant set.
 
@@
 
-Model \eqref{system} is restated in a more compact form using matrix notation.
-
-\begin{align} A = \begin{bmatrix}
-A_1\\A_2
-\end{bmatrix}\end{align}
-where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$.
+Model \eqref{system} is restated in a more compact form using matrix notation. Let $f(s)$ be such that,
+%
+%\begin{align} A = \begin{bmatrix}
+%A_1\\A_2
+%\end{bmatrix}\end{align}
+%where $A_1$ is a matrix of dimension $n_1 \times n$ corresponding to the interaction coefficients of OTU $i \in G_1$.
 $A_2$ is a matrix of dimension $n_2 \times n$ rows corresponding to the interaction coefficients of OTU $i \in G_2$, and  $f(s) \in \R^n$ is such that
@@
 
+Then $\mu(x,s) = \diag(f(s))(1_{n\times 1} + Ax)$
+
 Thus, system \eqref{system} is rewritten as follows.
 
-\begin{align}
-\label{Eq1}	\dot{x} = & \diag(x)(\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}) \\
-\label{Eq2}	\dot{s_1} = & (s_{in}-s_1)D + \begin{bmatrix}
--(1_{n_1\times 1} +A_1x) \\0
-\end{bmatrix}^\top \diag(k) \diag(f(s))x \\
+%\begin{align}
+%\label{Eq1}	\dot{x} = & \diag(x)(\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}) \\
+%\label{Eq2}	\dot{s_1} = & (s_{in}-s_1)D + \begin{bmatrix}
+%-(1_{n_1\times 1} +A_1x) \\0
+%\end{bmatrix}^\top \diag(k) \diag(f(s))x \\
+%\label{Eq3}	\dot{s_2} = & -s_2D+
+%\begin{bmatrix}
+%1_{n_1\times 1} +A_1x \\ -(1_{n_2\times 1} +A_2x)
+%\end{bmatrix}^\top \diag(k) \diag(f(s))x \\	
+%\label{Eq4}	\dot{s_3} = & -s_3D+\begin{bmatrix}
+%0	\\(1_{n_2\times 1} +A_2x) 
+%\end{bmatrix}^\top \diag(k) \diag(f(s))x 
+%\end{align} 
+\begin{align}
+\label{Eq1}	\dot{x} = & \diag(\mu(x,s) - D_{n\times 1})x \\
+\label{Eq2}	\dot{s_1} = & (s_{in}-s_1)D + Y_{1\bullet} \diag(\mu(x,s))x \\
 \label{Eq3}	\dot{s_2} = & -s_2D+
-\begin{bmatrix}
-1_{n_1\times 1} +A_1x \\ -(1_{n_2\times 1} +A_2x)
-\end{bmatrix}^\top \diag(k) \diag(f(s))x \\	
-\label{Eq4}	\dot{s_3} = & -s_3D+\begin{bmatrix}
-0	\\(1_{n_2\times 1} +A_2x) 
-\end{bmatrix}^\top \diag(k) \diag(f(s))x 
+Y_{2\bullet} \diag(\mu(x,s))x\\	
+\label{Eq4}	\dot{s_3} = & -s_3D+Y_{3\bullet} \diag(\mu(x,s))x 
 \end{align}
@@
 The active point $x^{act}\in \R^{n^{act}}$ is defined by the positive entries of $x^{eq}$.
-The active growths $f^{act}(s)$ and yields $k^{act}$ are defined analogously by the positive entries of $x^{eq}$.
+Analogously, the functions $f^{act}(s)$ and $\mu^{act}(x,s)$ are defined by the positive entries of $x^{eq}$.
 The active interactions $A^{act}$ is defined as the matrix $A$ without the $\mathcal{J}$ rows and columns.
-Let $M$ be the matrix defined by taking out the $\mathcal{J}$ columns of the identity matrix, then
+The active stoichiometry matrix $Y^{act}$ is the matrix $Y$ without the $\mathcal{J}$ columns.
+In summary, let $M$ be the matrix defined by taking out the $\mathcal{J}$ columns of the identity matrix of size $n$, then
 	 \begin{align}
@@
 	 f^{act}(s) = M^{\top}f(s) \\
-	 k^{act} = M^{\top}k \\
+	 \mu^{act}(x,s) = M^{\top}\mu(x,s)\\
+	 Y^{act} = YM \\
 	 A^{act} = M^{\top}AM
 	 \end{align}.   
-
-%	\begin{align}\label{EquilibriaFormula} (x^{eq})_i = \begin{cases}
-%	x^{act}_i & \text{for } i < j_1\\
-%	x^{act}_{i-k} & \text{for } j_{k}< i <j_{k+1}  \text{ and } k \in \{1,\dots,m-1\}\\
-%	x^{act}_{i-m} & \text{for } j_{m}< i \\
-%	0 & \text{for } i \in \{j_1, \dots, j_m\}
-%	\end{cases} \end{align}
-
 \end{defn}
@@
 
-By replacing \eqref{EqSome} in equation \eqref{Eq2}:
-
-\begin{align}
-\label{s1Equilibria} (s_{in}-s_1)-	\begin{bmatrix}
-1_{n_1^{act}\times 1} \\0_{n_2^{act}\times 1}
-\end{bmatrix}^\top \diag (k^{act}) (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1}-1_{n^{act}\times 1}) = 0 
+By replacing $x^{eq} = Mx^{act}$ in equation \eqref{Eq2}:
+
+\begin{align}
+ (s_{in}-s_1)D + Y_{1\bullet} \diag(\mu(x,s))Mx^{act}  = 0 \\
+(s_{in}-s_1)D + Y^{act}_{1\bullet} \diag(\mu^{act}(x,s))x^{act}  = 0 \\ 
+(s_{in}-s_1)D + Y^{act}_{1\bullet} \diag(D_{n^{act}\times 1})x^{act}  = 0  \\
+(s_{in}-s_1) + Y^{act}_{1\bullet} x^{act}  = 0  \\
+\label{s1Equilibria} (s_{in}-s_1) + Y^{act}_{1\bullet}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0
 \end{align}
@@
 \begin{align}
-\label{s2Equilibria}-s_2+
-	\begin{bmatrix}
-1_{n_1^{act}\times 1} \\-1_{n_2^{act}\times 1}
-\end{bmatrix}^\top\diag (k^{act})(A^{act})(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1}-1_{n^{act}\times 1}) = 0
+\label{s2Equilibria}-s_2+ Y^{act}_{2\bullet}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0
 \end{align}
@@
 In the case of ecological diagrams (ED) the pairs are regrouped such that the points in the set $\mathcal{P}$ have the same non-active coordinates.
-Ecological diagrams provide more information than operating diagrams, in the sense that one can infer the operating diagram from an ecological diagram.
-In other words, instead of representing areas where either CN, PN or WO take place, ranges of pairs $(s_{in},D)$ where species coexist are represented.
+In other words, instead of representing areas where either CN, PN or WO take place, ranges of pairs $(s_{in},D)$ where species coexist are represented.	ED provide more information than OD, in the sense that one can deduce the latter from the former.
 
@@
 Consider the case where $n_1 = 1$ and $n_2 = 1$.
-The operating diagrams where no interactions take place ($A = 0$) and a non-zero interaction matrix is presented.
+The operating diagrams when no interactions take place ($A = 0$) and a non-zero interaction matrix are presented.
 When $A=0$ algorithm \ref{StabilityAnalysis} is no longer valid (A is not invertible), nevertheless the stability analysis is much simpler and is given in the supplementary material section.
-The interaction matrices are shown in \ref{case1_no_interactions} and \ref{case1_interactions}, the rational behind the second choice was to force a .
-Parameters can be seen in table \ref{kinetic_parameters_case_study_1}, while
-
-The operating diagram can be seen in figure \ref{OD_no_interactions}, note how partial nitrification (washout of $G_2$).
-When compared to \ref{OD_no_interactions} one notes that at low $s_{in}$ the curve dividing the PN zone from the CN zone are alike.
-But since more $s_{in}$ means more $x_1$, at high $s_{in}$ the affine part $(1+ a_{21}x_1 +a_{22}x_2)$ of the growth function of $x_2$ plays a bigger role than substrate limitation ($\frac{s_2}{s_2+K_2}$).
+The interaction matrices are shown in Figures \ref{case1_no_interactions} and \ref{case1_interactions}, the rational behind the second choice was to force a very strong interaction of $x_1$ on $x_2$ and observe its effects.
+The rest of parameters can be seen in Table \ref{kinetic_parameters_case_study_1}.
+
+The operating diagrams can be seen in Figure \ref{OD_case_1}, note how partial nitrification (washout of $G_2$) of Figure \ref{OD_interactions} is much bigger when compared to Figure \ref{OD_no_interactions}.
+The shape of the PN region in \ref{OD_interactions} is somewhat unintuitive, because at a constant dilution rate (0.24 $day^{-1}$ for example) and an increasing $s_{in}$, one passes from a PN zone, to a CN zone, and then back again to a PN zone.
+The explanation lies in the fact that $x_1$ also increases with $s_{in}$, and the affine part $(1+ a_{21}x_1 +a_{22}x_2)$ of the growth function of $x_2$ plays a bigger role than substrate limitation ($\frac{s_2}{s_2+K_2}$).
 
@@
 		\includegraphics[width = \textwidth]{Stability/Interactions_case_study_1}
-		\caption{Interaction matrix of model \eqref{system}.}
+		\caption{A non-zero interaction matrix of model \eqref{system}.}
 		\label{case1_interactions}
@@
 	\caption{Interaction matrices.
-Note how the presence of $x_1$ affects very negatively $x_2$ in \eqref{case1_interactions}.
-The terms in the diagonal entries of the matrix represents intraspecies interactions, while the terms off thepo
-		 diagonal represent the interspecies interactions.}
+Note how the presence of $x_1$ affects very negatively $x_2$ in Figure \ref{case1_interactions}, with respect to other interactions.
+The terms in the diagonal entries of the matrix represents intraspecies interactions, while the terms off the diagonal represent the interspecies interactions.}
 \end{figure}
@@
 		\includegraphics[width = \textwidth]{Stability/OD_case_study_1_no_interactions}
-		\caption{Operating diagram of model \eqref{system} with no interactions (interaction matrix represented by \eqref{case1_no_interactions}).}
+		\caption{Operating diagram of model \eqref{system} with no interactions (interaction matrix represented by figure \ref{case1_no_interactions}).}
 		\label{OD_no_interactions}
@@
 	\includegraphics[width = \textwidth]{Stability/OD_case_study_1}
-	\caption{Operating diagram of model \eqref{system} with interactions represented by \eqref{case1_interactions}.}
+	\caption{Operating diagram of model \eqref{system} with interactions represented by figure \ref{case1_interactions}.}
 	\label{OD_interactions}
@@
 	\caption{Note how \ref{OD_interactions} has a much larger zone where partial nitrification takes place. This is due to the negative interaction of $x_1$ on $x_2$.}
+	\label{OD_case_1}
 \end{figure} 
@@
 Their fit describes well the dynamics of the two most abundant OTU in each functional group, but it still fails to capture the measured substrates dynamics.
-Kinetic parameters of case study 2 can be seen in table \ref{kinetic_parameters}.
-The estimated interaction matrix is shown in figure \ref{Interaction_1}.
-A second matrix is presented, which is obtained by the sign change of coefficient $a_{11}$ (figure \ref{Interaction_2}), and finally a third one is obtained by using a positive value for $a_{12}$ (figure \ref{Interaction_3}).
+Kinetic parameters of case study 2 can be seen in Table \ref{kinetic_parameters}.
+The estimated interaction matrix is shown in Figure \ref{Interaction_1}.
+A second matrix is presented, which is obtained by the sign change of coefficient $a_{11}$ (Figure \ref{Interaction_2}), and finally a third one is obtained by using a positive value for $a_{12}$ (Figure \ref{Interaction_3}).
+The idea is to show that qualitatively different outcomes can be obtained by changing one interaction at a time.
 
@@
 
-\begin{figure}[ht]
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[t]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_Dumont}
@@
 ~
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[t]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified}
-	\caption{Modified interaction matrix ecological diagram.}
+	\caption{Modified interaction matrix ecological diagram. In the legend 1) and 2) represent the two different stable equilibria in each zone.}
 	\label{ED 2}
@@
 ~
-\begin{subfigure}[b]{0.32\textwidth}
+\begin{subfigure}[t]{0.32\textwidth}
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified_2}
@@
 
-The ecological diagrams are presented in figure \ref{ecological_diagrams}.
-Comparing figure \ref{ED 1} with \ref{ED 2} one can see a very different situation.
-Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or $x_2$ alone remains, because in operational terms this means that either PN or CN may take place.
-
-One can see that coexistence in the same functional group is never attained in figure \ref{ED 1}, whereas in figure \ref{ED 2} $x_1$ and $x_2$, both AOB, coexist in either partial or complete nitrification.
-That means that the model is able to overcome the competitive exclusion principle \cite{lobry2017chemostat} (CEP) paradigm.
+The ecological diagrams are presented in Figure \ref{ecological_diagrams}, where the legend indicates the species surviving in the zone of the respective colour.
+In Figure \ref{ED 2}, the system exhibits bi-stability (it is represented in numbering as 1) and 2) of the different possible equilibriums) .
+Comparing Figures \ref{ED 1} with \ref{ED 2} one can see a very different situation.
+Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or $x_2$ only remains, because in operational terms this means that either PN or CN may take place.
+
+One can see that coexistence in the same functional group is never attained in Figure \ref{ED 1} and \ref{ED 2}, whereas in figure \ref{ED 3} $x_1$ and $x_2$, both AOB, coexist in either partial or complete nitrification.
+That means that the competitive exclusion principle \cite{lobry2017chemostat} (CEP) does not hold.
 The CEP roughly states that if two species are growing on the same limiting resource, and their growth laws only depend non decreasingly on the resource, then only one of them will survive in the long run.
@@
 
-\subsection{Remarks}
-
-The model here presented serves to illustrate that by considering a more complex growth rate that tries to model ecological interactions one might explain differences in reactors operating under similar conditions.
-It also shows a new mechanism by which the CEP no longer holds and where multiple stable equilibria may appear.
-Since the gLV model discussed (and calibrated in \cite{Dumont2016}) fails to completely capture the dynamics observed in the chemostat experiments, the next section proposes a new model to study interactions.
+\section*{Remarks}
+
+Model \eqref{system} serves to illustrate that by considering a more complex growth rate that tries to model ecological interactions one might explain differences in reactors operating under similar conditions.
+It also shows a new mechanism by which the CEP no longer holds and which explains how multiple stable equilibria may appear.
+Since the gLV model discussed fails to completely capture the dynamics observed in the chemostat experiments \cite{Dumont2016}, the next section proposes a new approach to study interactions.
 
@@
 
-Given a vector $(v_1,\dots,v_n)^\top$ the interaction function $\I$ is noted as:
+Given a vector $(v_1,\dots,v_n)^\top$ the interaction function $\I$ is denoted as:
 \begin{align}
@@
 		\item $	\I \left( (0,\dots,0)^\top \right) = (1,\dots,1)^\top $
-		\item Let $\Omega$ be an open subset of $ \R^n $ then $\I \in C^1(\Omega)$.
+		\item There is an open set $\Omega \subset \R^n $ such that $\I \in C^1(\Omega)$.
 	\end{enumerate} 
@@
 Therefore adding a penalization in the objective function for each control to remain near $1$ can be seen as an attempt to explain data without any interaction.
+In other words, if the control terms are found to drift from 1, it means that interactions are necessary to explain the system dynamics.
+
 \item Second, to force a regularized control.
@@
 
-The method consists on iteratively calculating trajectories of system \eqref{Controlsystem} with a certain control and feeding a non-autonomous Ricatti differential equation with the resulting trajectory.
-Then a control law that uses the solution of the Ricatti equation is proposed and a new trajectory is calculated.
+The method consists on iteratively calculating trajectories of System \eqref{Controlsystem} with a certain control and feeding a non-autonomous Ricatti differential equation with the resulting trajectory.
+Then, a control law that uses the solution of the Ricatti equation is proposed and a new trajectory is calculated.
 The iteration is stopped when a convergence in the output or  the control is observed.
@@
 Nevertheless, the methods of Cimen \textit{et al.}\cite{Cimen2004} were directly used with an explicit constraint in the synthesis of the control.
-Even though this is probably suboptimal when the control reaches its bounds, one at least is certain of its optimality when the control never reaches its constraints.
+Even though this is probably suboptimal when the control reaches its bounds, one at least is certain about its optimality when the control never reaches its constraints.
 
 Another departure from their method is that in their formulation an approximation of the dynamics for calculating the trajectories is used.
-They proved that such a linearisation converged to the original dynamics.
+They proved that such a linearisation converges to the original dynamics.
 In the case here presented the linearisation of the dynamics was not necessary.
@@
 Where matrix $P(t)$ and vector $s_f(t)$ solve differential equations.
-In the appendix it is proved that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method.
-Which renders the method- at least theoretically- scalable for a growing number of OTU.
+In the appendix it is proved that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method, which renders the method- at least theoretically- scalable for a growing number of OTU.
 
@@
 
-The approach was tested against synthetic data generated by simulating model \eqref{system} using the parameters of the case study 1 (table \ref{kinetic_parameters_case_study_1}) with interaction matrix given by \eqref{case1_interactions}.
+The approach was tested with data generated by simulating model \eqref{system} using the parameters of the case study 1 (Table \ref{kinetic_parameters_case_study_1}) with interaction matrix given by \eqref{case1_interactions}.
 In the operating diagram of the same case (figure \eqref{OD_interactions}) the red zone implies complete nitrification, while the green zone means partial nitrification.
@@
 Simulations can be seen in figure \ref{synthetic_data}.
-Note how from day 150 the NOB population represented in figure \eqref{PC_synthetic_NOB} decreases, which in turn implies a decrease in $s_3$, as seen in figure \eqref{PC_synthetic_metabolites}.
+Note how from day 150 the NOB population (OTU 2) represented in figure \eqref{PC_synthetic_NOB} decreases, which in turn implies a decrease in $s_3$, as seen in figure \eqref{PC_synthetic_metabolites}.
+In the case where no interactions take place, the OD seen in Figure \ref{OD_no_interactions} implies that $s_3$ would have accumulated all along the trajectory, since the perturbation still remains in the CN zone.
 
@@
 	\begin{subfigure}{0.32 \linewidth}
-	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_AOB_plot}
+ 	\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_AOB_plot}
 	\caption{AOB.}
@@
 	\centering
-	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_NOB_plot}
+	\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_NOB_plot}
 	\caption{NOB.}
@@
 	\centering
-	\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_metabolites}
+	\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_metabolites}
 	\caption{Metabolites.}
@@
  For the tracking procedure the functions $f_i(s)$ and the yields $y_i$ were the same as those used for simulating the synthetic data (parameters in table \ref{kinetic_parameters_case_study_1}) and the control is meant to account for the interaction term.
-The $Q$ and $R$ matrices are $\lambda I_n$ and $I_n$, respectively, with $\lambda = 10^{-4}$.
+The $Q$ and $R$ matrices were $\begin{bmatrix}
+ \lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
+ \end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$ in order to better track the NOB trajectories, since they are less abundant.
 The results of the procedure to identify interactions can be seen in figure in figure \ref{POC_tracking}.
@@
 	\begin{subfigure}{0.45 \linewidth}
-	\includegraphics[width= \textwidth]{proof_of_concept/250309_POC_try3_iter_2_Biomass}
+	\includegraphics[width= \textwidth]{proof_of_concept/200525_POC_iter_5_Biomass}
 	\caption{Total biomass.}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{proof_of_concept/250309_POC_try3_iter_2_metabolites}
+		\includegraphics[width=\textwidth]{proof_of_concept/200525_POC_iter_5_metabolites}
 		\caption{Metabolites. }
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{proof_of_concept/250309_POC_try3_iter_2_AOB_plot_1}
+		\includegraphics[width=\textwidth]{proof_of_concept/200525_POC_iter_5_AOB_plot_1}
 		\caption{AOB biomass.}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{proof_of_concept/250309_POC_try3_iter_2_NOB_plot_1}
+		\includegraphics[width=\textwidth]{proof_of_concept/200525_POC_iter_5_NOB_plot_1}
 		\caption{NOB biomass. }
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_Control_AOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_Control_AOB_plot_1}
 	\caption{Control for the AOB population.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_Control_NOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_Control_NOB_plot_1}
 	\caption{Control for the NOB population.}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_AOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_AOB_plot_1}
 		\caption{Growth rate of the model for AOB community.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_NOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_NOB_plot_1}
 	\caption{Growth rate of the model for the NOB community.}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_control_AOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_control_AOB_plot_1}
 		\caption{Growth rate of the model for AOB community.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/250309_POC_try3_iter_2_growth_control_NOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_control_NOB_plot_1}
 		\caption{Growth rate of the model for the NOB community.}
@@
 A first example of the procedure is performed when the classified OTU are regrouped in their assigned functional groups by adding their concentrations.
-A 5 dimensional dynamical system is obtained.
+A 5 dimensional dynamical system is obtained, thus there are only two interacting functional biomasses: this case is structurally the same as in the proof of concept, but here a real dataset is used.
 The same procedure is applied where no regrouping occurs and the system state grows to 39.
@@
 The yields were fitted to match the nitrogen mass balances.
-In this case the $Q$ and $R$ matrices were $\begin{bmatrix}
+The $Q$ and $R$ matrices were the same as in the proof of concept section, that is $\begin{bmatrix}
 \lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
-\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$ in order to better track the NOB trajectories.
+\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$.
 
@@
 For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e.
-$u(t)= 1$) in  figure \ref{u=1 simulation.}.
-$s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
+$u(t)= 1$) in  figure \ref{u=1 simulation.} nitrite ($s_3$) accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
 
@@
 Perhaps these interactions are not constant through time (as in the gLV model) or a different interaction function should be thought of.
-However the former questions can not be fully clarified, because the quality of the genetic sequencing from molecular fingerprints might not be the best when compared to more recent techniques, thus it is unclear if the pulses are due to noise of the measurements.
+However the former questions can not be fully clarified here, because the quality of the genetic sequencing from molecular fingerprints might not be the best when compared to more recent techniques, thus it is unclear if the pulses are due to noise of the measurements.
 
@@
 		\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_1}
+		\caption{Biomass OTU 1-10 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 	\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_2}
+	\caption{Biomass OTU 11-20 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 	\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_3}
+	\caption{Biomass OTU 21-30 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 	\includegraphics[width =\textwidth]{Application//200407_iter_20_AOB_plot_4}
+	\caption{Biomass OTU 31 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 	\includegraphics[width =\textwidth]{Application//200407_iter_20_NOB_plot_1}
-	\end{subfigure}
-	\caption{Tracking results when all OTU are tracked independently.}
+	\caption{Biomass OTU 32-36 in $G_2$ (NOB) }
+	\end{subfigure}
+	\caption{Tracking results when all OTU are tracked independently. Note the different y-axis scales of each plot.}
 	\label{OTU abudance all}
@@
 		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_1}
+		\caption{Growth rate of OTU 1-10 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_2}
+		\caption{Growth rate of OTU 11-20 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_3}
+		\caption{Growth rate of OTU 21-30 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 		\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_AOB_plot_4}
+		\caption{Growth rate of OTU 31 in $G_1$ (AOB) }
 	\end{subfigure}
@@
 	\includegraphics[width =\textwidth]{Application//200407_iter_20_growth_control_NOB_plot_1}
+	\caption{Growth rate of OTU 32-36 in $G_2$ (NOB) }
 	\end{subfigure}

### 2020-05-26 tex/Article_Interactions.tex
modofications to sup mat

@@
 \usepackage{amsthm}
+\usepackage{thmtools}
+\usepackage{thm-restate}
+\usepackage{hyperref}
 \usepackage{amsmath}
+\usepackage{cleveref}
 \usepackage{algorithm2e}
@@
 \usepackage{subcaption}
-\usepackage{hyperref}
 \usepackage{xcolor}
@@
 \DeclareMathOperator{\diag}{diag}
+\declaretheorem[name=Theorem]{thm}
+\declaretheorem[name=Lemma]{lemma}
 \newtheorem{defn}{Definition}
 \newtheorem{hypo}{H}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theo}{Theorem}
 \usepackage[figuresright]{rotating}
@@
 \dot{x_i} =& \left(\mu_i(s,x) -D \right)x_i \quad \forall i \in [n] \\
-\dot{s_1} =& \displaystyle (s_{in}-s_1)D+\sum\limits_{i\in G_1} y_{s_1/x_i}\mu_i(s,x) x_i  \\
-\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in [n]}y_{s_2/x_i}\mu_i(s,x)x_i  \\
-\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2}y_{s_3/x_i}\mu_i(s,x) x_i 
+\dot{s_1} =& \displaystyle (s_{in}-s_1)D - \sum\limits_{i\in G_1} \frac{1}{y_i} \mu_i(s,x) x_i  \\
+\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i\in G_1} \frac{1}{y_i} \mu_i(s,x) x_i -\sum\limits_{i\in G_2} \frac{1}{y_i} \mu_i(s,x) x_i \\
+\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i\in G_2} \frac{1}{y_i} \mu_i(s,x) x_i  
 \end{array}
+\end{align}
+
+Which can be written in a more compact notation using the stoichiometric matrix $Y$ and the $\diag$ operator.
+\begin{align}
+\label{Eq1X}	\dot{x} = & \diag(\mu(x,s) - D_{n\times 1})x \\
+\label{EqS}	\dot{s} = & \left(\begin{bmatrix} s_{in}&0&0 \end{bmatrix}^\top-s\right)D + Y\diag(\mu(x,s))x
 \end{align}
@@
 
-\begin{lemma}
+\begin{restatable}{lemma}{systembounds}
 	\label{l1}
@@
 	\end{align}
-\end{lemma}
+\end{restatable}
 
@@
 
-\begin{theo}
+\begin{restatable}{thm}{wellposedness}
 	\label{theoWellPosedness}
 	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}, remain in $\Omega$ and are bounded.
-\end{theo}
+\end{restatable}
 
@@
 
-In this section analytical expressions for equilibrium points are derived.
+In this section analytical expressions for equilibrium points are shown.
 However, no analytic expression concerning the stability of such points is presented.
@@
 At the end of the section an algorithm is provided for exploring all the possible equilibria.
+All the computations for deriving the equations of this section can be found in the supplementary material.
 
@@
 The active stoichiometry matrix $Y^{act}$ is the matrix $Y$ without the $\mathcal{J}$ columns.
-In summary, let $M$ be the matrix defined by taking out the $\mathcal{J}$ columns of the identity matrix of size $n$, then
-	 \begin{align}
-	 x^{eq} = Mx^{act} \\	
-	 f^{act}(s) = M^{\top}f(s) \\
-	 \mu^{act}(x,s) = M^{\top}\mu(x,s)\\
-	 Y^{act} = YM \\
-	 A^{act} = M^{\top}AM
-	 \end{align}.   
 \end{defn}
 
- Finally, for deriving the equilibrium points, it is desirable an invertible $A^{act}$ matrix.
+ In order to derive the equilibrium points, it is desirable an invertible $A^{act}$ matrix.
 Therefore in what follows of the work it is assumed that matrix $A$ and some of its sub matrices have an inverse, this is stated properly in Hypothesis \ref{inverse hypothesis}.
@@
 
+Assuming Hypothesis \ref{inverse hypothesis} a formula for the active points is derived from equation \eqref{Eq1}:
+
+\begin{align}
+\label{EqSome}x^{act} = (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1})
+\end{align}
+
+Note as well that at the equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
+
+\begin{align}
+s_{in} = s_1+s_2+s_3 \label{s1s2s3}
+\end{align}
+
 \subsubsection{Both functional groups are present}
@@
 
-From equation \eqref{Eq1} equilibrium points satisfy:
-
-\begin{align}
-x_i = 0 \vee (\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n] \\
-\Rightarrow  (\diag (f(s))(1_{n\times 1}+ Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n]\setminus \mathcal{J} \\
-\Leftrightarrow f_i(s)(1 + A_{i\bullet}x) - D = 0 \quad \forall i \in [n]\setminus \mathcal{J} \label{Extinction}
-\end{align}
-
-note that $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ therefore the coefficients $a_{ij}$ play no role in equation \eqref{Extinction} and one can rewrite equation \eqref{Extinction} as $\diag(f^{act}(s))(1_{n^{act}\times 1} + A^{act}x^{act}) - D_{n^{act} \times 1}=0 $.
-From hypothesis \ref{inverse hypothesis} matrix $A^{act}$ has an inverse.
-This gives the following lemma.
-
-\begin{lemma} 
-	The active point of the solution of \eqref{Extinction} solves the system of equations \eqref{EqSome}. 
-	\begin{align}
-	\label{EqSome}x^{act} = (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1})
-	\end{align} 
-\end{lemma}
-
-By replacing $x^{eq} = Mx^{act}$ in equation \eqref{Eq2}:
-
-\begin{align}
- (s_{in}-s_1)D + Y_{1\bullet} \diag(\mu(x,s))Mx^{act}  = 0 \\
-(s_{in}-s_1)D + Y^{act}_{1\bullet} \diag(\mu^{act}(x,s))x^{act}  = 0 \\ 
-(s_{in}-s_1)D + Y^{act}_{1\bullet} \diag(D_{n^{act}\times 1})x^{act}  = 0  \\
-(s_{in}-s_1) + Y^{act}_{1\bullet} x^{act}  = 0  \\
-\label{s1Equilibria} (s_{in}-s_1) + Y^{act}_{1\bullet}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0
-\end{align}
-
-A similar expression is obtained when replacing \eqref{EqSome} in equation \eqref{Eq3}
-
-\begin{align}
-\label{s2Equilibria}-s_2+ Y^{act}_{2\bullet}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0
-\end{align}
-
-From equation \eqref{s1Equilibria} $s_2$ can be written as a function of $s_1$:
+By replacing equation \eqref{EqSome} in equation \eqref{Eq2} $s_2$ can be written as a function of $s_1$:
 \begin{align}
@@
 
-Then by replacing  \eqref{S2(S1)} in equation \eqref{s2Equilibria}, one gets a fourth degree polynomial for $s_1$.
+Then by replacing  \eqref{S2(S1)} in equation \eqref{Eq3}, one gets a fourth degree polynomial for $s_1$.
 
@@
 
-Finally, in equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
-
-\begin{align}
-s_{in} = s_1+s_2+s_3 \label{s1s2s3}
-\end{align}
-
-If the system of equations \eqref{EqSome}, \eqref{S2(S1)}, \eqref{Poly4}, and \eqref{s1s2s3} provides only solutions with some negative entries then the set $\mathcal{J}$ can not define an equilibrium point.
+The equilibrium point can be calculated from the solutions of the system of equations \eqref{EqSome}, \eqref{s1s2s3}, \eqref{S2(S1)}, and \eqref{Poly4} with non negative coordinates.
+If the system only provides solutions with at least one negative entry then the set $\mathcal{J}$ can not define an equilibrium point.
 
@@
 
-Equations \eqref{EqSome} and \eqref{s1Equilibria} still hold, but in this case note that $f^{act}(s)$ does not contain any term involving $s_2$, and therefore one obtains a quadratic equation for $s_1$:
+Under this case note that $f^{act}(s)$ depends only on $s_1$. Therefore when equation \eqref{EqSome} is replaced in \eqref{Eq2}, one obtains a quadratic equation for $s_1$:
 
@@
 
-Since $x_i = 0, \, \forall i \in G_2$ then from equation \eqref{Eq4}.
+Since $x_i = 0 \, \forall i \in G_2$ then from equation \eqref{Eq4}.
 \begin{align}
 \dot{s_3} = 0 = -s_3D \\
-\Rightarrow s_3 = 0
-\end{align}
-
-Then by \eqref{s1s2s3} one obtains:
-
-\begin{align}
-s_{in} = s_1 + s_2
-\end{align}
+\Rightarrow s_3 = 0 \label{no_s3}
+\end{align}
+
+In this case the equilibrium point can be calculated from the solutions of the system of equations \eqref{EqSome}, \eqref{s1s2s3}, \eqref{poly2_s1}, and \eqref{no_s3} with non-negative coordinates.
+If the system only provides solutions with at least one negative entry then the set $\mathcal{J}$ can not define an equilibrium point.
 
@@
 \begin{align*} s_{in} = s_1 \end{align*}
-then \eqref{s1s2s3} implies \begin{align*}s_2 &= s_3 = 0 \\ \Rightarrow \dot{x_i} &= -Dx_i \quad \forall i = n_1+1, \dots, n\end{align*}   
-which has an equilibria at $x_i = 0$.
+then \eqref{s1s2s3} implies 
+\begin{align*}s_2 &= s_3 = 0 \end{align*}
+
+The equilibrium is then given by $\begin{pmatrix} 0_{1\times n}& s_{in}&0 &0 \end{pmatrix}^\top$.
 
@@
 		\hline
-		Kinetic Parameters & $\mu_i\,[1/day]$ & $K_i\,[g/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
+		Kinetic Parameters & $\bar{\mu}_i\,[1/day]$ & $K_i\,[g/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline
 		$x_1 \in G_1$ & 0.77  & 0.7 & 3.98  \\ \hline
@@
  	\begin{tabular}{|l|l|l|l|}
- 		\hline
+ 		\hline \rule{0pt}{3.5ex}
  		Case study 2 kinetic parameters & $\mu_i\,[1/day]$ & $K_i\,[mg/L]$ & $\frac{1}{y_i} \, [gr/gr]$ \\ \hline 
@@
 \dot{x_i} =& \left(f_i(s)u_i(t) -D \right)x_i \quad \forall i \in G_2\\
-\dot{s_1} =& \displaystyle (s_{in}-s_1)D-\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)u_i(t) x_i  \\
-\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)u_i(t)	-\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)u_i(t) x_i  \\
-\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)u_i(t) x_i \\
+\dot{s_1} =& \displaystyle (s_{in}-s_1)D + \sum\limits_{i \in G_1}y_{s_1/x_i}f_i(s)u_i(t) x_i  \\
+\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i \in G_1 \cup G_2}y_{s_2/x_i}f_i(s)u_i(t)x_i  \\
+\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}y_{s_3/x_i}f_i(s)u_i(t) x_i \\
 y  =& x
@@
 
- Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively, and a positive real $\bar{u}$.
+ Consider the weighted norms defined by positive definite matrices $Q$ and $R$, represented by $\Vert \cdot \Vert_Q$ and $\Vert \cdot \Vert_R$, respectively, and $\bar{u}>0$.
 The optimal tracking problem is defined as:
@@
 The method proposed involves the resolution of Approximating Sequences of Ricatti Equations (ASRE).
-
-The method consists on iteratively calculating trajectories of System \eqref{Controlsystem} with a certain control and feeding a non-autonomous Ricatti differential equation with the resulting trajectory.
-Then, a control law that uses the solution of the Ricatti equation is proposed and a new trajectory is calculated.
+It consists on iteratively calculating trajectories of System \eqref{Controlsystem} with a certain control law and subsequently feed a non-autonomous Ricatti differential equation with the resulting trajectory.
+Then, a new control law that uses the solution of the Ricatti equation is proposed and a new trajectory is calculated.
 The iteration is stopped when a convergence in the output or  the control is observed.
 
+The control term should remain positive for the system to be well posed (no negative states), and an upper bound was added to represent the fact that life cannot grow infinitely fast.
 The tracking problem does not consider a constrained control.
@@
 
-The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the supplementary material section. This in turn implies $v_i(t) \in [-1,\bar{u}-1]$.
-
-The feedback control $v(t)$, will be of the form $v(t) = -R^{-1}\tilde{B}^\top(t)\left(\tilde{P}(t)x(t)-s_f(t)\right)$.
+The change of variable $u_i(t) = v_i(t) + 1$ is used for technical reasons explained in the supplementary material section.
+This in turn implies $v_i(t) \in [-1,\bar{u}-1]$.
+The feedback control $v(t)$, will be of the form $v(t) = -R^{-1}\tilde{B}^ \top(t)\left(\tilde{P}(t)x(t)-s_f(t)\right)$.
 Where matrix $P(t)$ and vector $s_f(t)$ solve differential equations.
@@
 Therefore only data from day $183$ onwards was used because a change in the operating temperature happened at that point, which is known to have an effect on kinetics.
-For choosing which species belong in which functional group, the procedure described in \cite{Ugalde-Salas2019} was used: from day $183$ to day $315$: 31 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
+For choosing which species belong in which functional group, the procedure described of Ugalde-Salas \textit{et al.} \cite{Ugalde-Salas2019} was used.
+From day $183$ to day $315$ 31 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
 
@@
 The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
-Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application}.
+Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application} calculated from the equation of Table 2 of the same article.
 The yields were fitted to match the nitrogen mass balances.
@@
 	\end{tabular}	
-	\caption{A set of kinetic parameters of model \eqref{system}.}
+	\caption{A set of kinetic parameters of model \eqref{Controlsystem}.}
 	\label{kinetic_parameters_application}
@@
 Considering the success of mass balance models to predict and pilot bioreactors, one should build upon these existing models.
-This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, and observing what would that imply according to the (pseudo)stoichiometric equations involved.
+This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, .
 If one already posses a model for describing a particular bioprocess the use of the techniques here presented can be applied in a straightforward manner if one has already identified the microbial species involved with a particular functionality of the system.
@@
 
-\textbf{Proof of lemma \ref{l1}}
+\subsection{Proofs of \cref{l1} and \cref{theoWellPosedness}}
+
+\systembounds*
+
 \begin{proof}
@@
 
-\textbf{Proof of theorem \ref{theoWellPosedness}}
+\wellposedness*
 
@@
 
-	If $s_2 = 0$ then note first that by adding both inequalities from Lemma \eqref{l1} and since, $s_1,x_i \geq 0$ one has:
+	If $s_2 = 0$ then note first that by adding both inequalities from Lemma \eqref{l1}:
 	\begin{align*}
-	\sum \limits_{i \in G_1 \cup G_2}  \frac{1}{y_i} x_i + 2s_1 + s_2 \leq M_1 + M_2 \\
-	\Rightarrow \sum \limits_{i = 1}^{n}  \frac{1}{y_i} x_i + 2s_1 \leq M_1 + M_2 \\
-	\Rightarrow \sum \limits_{i = 1}^{n}  \frac{1}{y_i} x_i \leq M_1 + M_2\\ 
+	\sum \limits_{i \in G_1 \cup G_2}  \frac{1}{y_i} x_i + 2s_1 + s_2 \leq M_1 + M_2 
+	\end{align*}
+	let $\bar{k} = \min \left\{ \frac{1}{y_i}  : \; i\in [n] \right \}$ and since $s_1,x_i \geq 0$ one has:
+	\begin{align*}
 	\Rightarrow \bar{k} \sum  \limits_{i = 1}^{n}   x_i  \leq M_1 + M_2  \\
@@
 
-	Where $\bar{k} = \min \left\{ \frac{1}{y_i}  : \; i\in [n] \right \}$.
-
-	Define $M := \dfrac{\bar{k}}{M_1 + M_2}$, and let $A$ be a matrix such that $\Vert A \Vert_{\infty} \leq M$.
-Then since $\Vert Ax \Vert_{\infty} \leq 1 \Rightarrow \forall i=1,\dots,n \; (1 + A_{i\bullet}x) \geq 0 $, and $\Vert Ax \Vert_{\infty} \leq \Vert A \Vert_{\infty} \Vert x\Vert_{\infty} \leq M \frac{1}{M}$.
-	One has proven that:
-	\begin{align}
-	\label{Bound1} \forall i=1,\dots,n \;  \;  (1 + A_{i\bullet}x) \geq 0 
+	Define $M := \dfrac{\bar{k}}{M_1 + M_2}$, and let $A$ be a matrix such that $\Vert A \Vert_{\infty} \leq M$. Since
+	\begin{align*} \Vert Ax \Vert_{\infty} \leq 1 \Rightarrow   (1 + A_{i\bullet}x) \geq 0 \quad \forall i \in [n]
+	\end{align*}
+
+	and $\Vert Ax \Vert_{\infty} \leq \Vert A \Vert_{\infty} \Vert x\Vert_{\infty} \leq M \frac{1}{M}$. One has proven that:
+	\begin{align}
+	\label{Bound1}  \;   (1 + A_{i\bullet}x) \geq 0  \quad \forall i \in [n]
 	\end{align}
@@
 
-	For the boundedness it suffices to notice from Lemma \ref{l1} that the sum of positive elements is bounded, therefore each element is bounded.
+	For the boundedness it suffices to notice from \cref{l1} that the sum of positive elements is bounded, therefore each element is bounded.
 \end{proof}
 
-\subsection{Properties of diag operator}
-
-Notice that for two vectors $v_1$ and $v_2$ the following holds:
-\begin{align}
-\diag(v_1)\diag(v_2) = \diag(v_2)\diag(v_1) 
-\end{align}
-
-Suppose $v \in \R^n$ such that $v_i \neq 0 \forall i \in [n]$. Define $v^{-1}:= \left( \dfrac{1}{v_1},\dots,\dfrac{1}{v_n} \right)$ then the inverse of $\diag(v)$ exists and is $\diag(v^{-1})$:
-
-\begin{align}
-\diag(v)^{-1} = \diag(v^{-1}) 
-\end{align}
-
-\subsection{Inverse of A and products}
-Notice that $\begin{bmatrix}
-A_1 \\ A_2
-\end{bmatrix} A^{-1} = \begin{bmatrix}
-A_1A^{-1} \\ A_2A^{-1}
-\end{bmatrix}=I $.
-
-Then $A_1A^{-1}= \begin{bmatrix}
-I_{n_1}& 0_{n_2 \times 1} 
-\end{bmatrix}$ and $A_2A^{-1}= \begin{bmatrix}
-0_{n_1 \times 1} & I_{n_2}
-\end{bmatrix}$.
-
-For notation purposes it is useful to define: \begin{align}
-B := \diag(k) A^{-1}.
-\end{align}
-
-\subsection{Deduction of  \eqref{s1Equilibria}}
-
-Replacing \eqref{xEquilibria} in \eqref{Eq2} yields :
-\begin{align}
-(s_{in}-s_1)D- \begin{bmatrix}
-1_{n_1 \times 1}+A_1A^{-1}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1}) \\0_{n_2 \times 1}
-\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1})=0 \\
-(s_{in}-s_1)D-	\begin{bmatrix}
-1_{n_1 \times 1}+\begin{bmatrix}
-I_{n_1} & 0_{n_2 \times 1} 
-\end{bmatrix}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) \\0_{n_2\times 1}
-\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0 \\
-(s_{in}-s_1)D-	\begin{bmatrix}
-D_{n_1 \times 1}\\0_{n_2 \times 1}
-\end{bmatrix}^T\diag(f(s))^{-1}\diag(f(s)) \diag(k) A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0  \\
-(s_{in}-s_1)D-\begin{bmatrix}
-D_{n_1 \times 1} \\0_{n_2\times 1}
-\end{bmatrix}^\top \diag(k)A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n_1 \times 1}) = 0 \\
-(s_{in}-s_1)- \begin{bmatrix}
-1_{n_1 \times 1}\\0_{n_2 \times 1}
-\end{bmatrix}^\top B (\diag(f(s))^{-1}D_{n \times 1} - 1_{n \times 1}) = 0 
-\end{align}
-
-\subsection{Deduction of \eqref{s2Equilibria}}
-Analogous as before, replacing \eqref{xEquilibria} in \eqref{Eq3} yields :
-\begin{align}
--s_2D+
-\begin{bmatrix}
-(\diag(\mu_A)^{-1} \vec{D}) \\ -(\diag(\mu_B)^{-1} \vec{D})
-\end{bmatrix}^\top \diag(\mu)\diag(y)^{-1} A^{-1}(\diag(\mu)^{-1}\vec{D}-\vec{1}) = 0 \\
--s_2D+
-\begin{bmatrix}
-\vec{D} \\ - \vec{D}
-\end{bmatrix}^\top \diag(y)^{-1} A^{-1}(\diag(\mu)^{-1}\vec{D}-\vec{1}) = 0\\
--s_2+
-\begin{bmatrix}
-\vec{1} \\ - \vec{1}
-\end{bmatrix}^\top B(\diag(\mu)^{-1}\vec{D}-\vec{1}) = 0
-\end{align}
-\begin{align} 
--s_2D+ \begin{bmatrix}
-1_{n_1 \times 1}+A_1A^{-1}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1}) \\-(1_{n_1 \times 1}+A_2A^{-1}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1})
-\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0 \\
--s_2D+	\begin{bmatrix}
-1_{n_1 \times 1}+\begin{bmatrix}
-I_{n_1} & 0_{n_2 \times 1} 
-\end{bmatrix}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) \\-(1_{n_1 \times 1}+\begin{bmatrix}
-0_{n_1 \times 1} & I_{n_2} 
-\end{bmatrix}(\diag(f(s))^{-1}D_{n_1 \times 1}-1_{n_1 \times 1})
-\end{bmatrix}^\top \diag(k)\diag(f(s))A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0 \\
--s_2D +	\begin{bmatrix}
-D_{n_1 \times 1}\\-D_{n_2 \times 1}
-\end{bmatrix}^T\diag(f(s))^{-1}\diag(f(s)) \diag(k) A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n \times 1}) = 0  \\
--s_2D+\begin{bmatrix}
-D_{n_1 \times 1} \\-D_{n_2\times 1}
-\end{bmatrix}^\top \diag(k)A^{-1}(\diag(f(s))^{-1}D_{n \times 1}-1_{n_1 \times 1}) = 0 \\
--s_2 + \begin{bmatrix}
-1_{n_1 \times 1}\\1_{n_2 \times 1}
-\end{bmatrix}^\top B (\diag(f(s))^{-1}D_{n \times 1} - 1_{n \times 1}) = 0 
-\end{align}
-\subsection{Deduction of \eqref{S2(S1)}}
-
-Note that 
-\begin{align}  (\diag(f(s))^{-1}D_{n\times 1}-1_{n\times1})  & = \begin{array}{cc} 
-\begin{bmatrix}
-\left(D\frac{K_1+s_1}{\bar{\mu}_{1}s_1}-1 \right) \\ \vdots \\ \left(D\frac{K_n+s_2}{\bar{\mu}_{n}s_2}-1\right) 
-\end{bmatrix} & \hspace{-0.5cm}\begin{array}{c} \left\} n_1\right. \\ \\ \left\} n_2\right.\end{array}
-\end{array} \\
-\label{invMu} 
-& = \begin{bmatrix}
-\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_n+(D-\bar{\mu}_n)s_2}{\bar{\mu}_{n}s_2} 
-\end{bmatrix}
-\end{align}
-
-Replacing \eqref{invMu} in \eqref{s1Equilibria}.
-
-\begin{align}
-(s_{in}-s_1)-	\begin{bmatrix}
-1_{n_1 \times 1} \\0_{n_2\times 1}
-\end{bmatrix}^\top  B\begin{bmatrix}
-\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_n+(D-\bar{\mu}_n)s_2}{\bar{\mu}_{n}s_2} 
-\end{bmatrix} = 0 \\
-(s_{in}-s_1) - \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1} +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}s_2} \right) = 0 \quad / \cdot s_1s_2 \\
-(s_{in}-s_1)s_1s_2 - \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}}s_1 \right) = 0 \\
-(s_{in}-s_1)s_1s_2 - \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_2s_1 + \sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1 \right) = 0  \\
-s_2\left((s_{in}-s_1)s_1 - \sum \limits_{i=1}^{n_1}  \left( \sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}} + \sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_1 \right)  \right) =  \sum \limits_{i=1}^{n_1}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1 \\
-s_2\left(-s_{1}^2  +  \left( s_{in}\underbrace{- \sum \limits_{i=1}^{n_1} \sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}}_{\beta_1}\right) s_1 \underbrace{ - \sum \limits_{i=1}^{n_1}  \sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_2}  \right) = \underbrace{\sum \limits_{i=1}^{n_1}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_3}s_1 \\
-s_2\left(-s_{1}^2  +  \left( s_{in}+\beta_1 \right) s_1 +\beta_2  \right) = \beta_3 s_1
-\end{align}
-
-From the last expression it should be clear that formula \eqref{S2(S1)} holds, it is just a matter of identifying the coefficients.
-\begin{itemize}
-	\item $\beta_1 =  - \sum \limits_{i=1}^{n_1} \sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}$
-	\item $\beta_2 =-\sum \limits_{i=1}^{n_1}  \sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$
-	\item $\beta_3 = \sum \limits_{i=1}^{n_1}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}} $
-	\item $c_1 = \dfrac{-1}{\beta_3}$
-	\item $c_2 =  \dfrac{s_{in} + \beta_1}{\beta_3}$
-	\item $c_3 = \dfrac{\beta_2}{\beta_3}$
-\end{itemize}
-
-\subsection{Deduction of \eqref{Poly4}}
-
-Again, replacing \eqref{invMu} in \eqref{s2Equilibria}.
-\begin{align}
--s_2+
-\begin{bmatrix}
-1_{n_1 \times 1}\\ - 1_{n_2 \times 1}
-\end{bmatrix}^\top B\begin{bmatrix}
-\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_n+(D-\bar{\mu}_n)s_2}{\bar{\mu}_{n}s_2} 
-\end{bmatrix} = 0 \\
-\begin{array}{c} \displaystyle  -s_2 + \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1} +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}s_2} \right) \\
-\displaystyle - \sum \limits_{i=n_1+1}^{n}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1} +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}s_2} \right)= 0
-\end{array} \quad / \cdot s_1s_2 \\
-\begin{array}{c} \displaystyle  -s_1s_2^2 +\sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}}s_1 \right) \\
-\displaystyle -  \sum \limits_{i=n_1+1}^{n}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_2}{\bar{\mu}_{j}}s_1 \right)= 0
-\end{array} \\
-\begin{array}{c} \displaystyle  -s_1s_2^2 + \sum \limits_{i=1}^{n_1}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_2s_1 + \sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1\right) \\
-\displaystyle -  \sum \limits_{i=n_1+1}^{n}\left(\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_2 +\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}s_2s_1 + \sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}s_1 \right)= 0
-\end{array}\\
-\begin{array}{c} \displaystyle  -s_1s_2^2  - \beta_2s_2 -\beta_1s_1s_2 + \beta_3s_1 
-\underbrace{- \sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_4}s_2 \underbrace{-\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}}_{\beta_5}s_2s_1\underbrace{ -\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}}_{\beta_6}s_1 = 0
-\end{array}\\
--s_1s_2^2  - \beta_2s_2 -\beta_1s_1s_2 + \beta_3s_1 + \beta_4s_2 +\beta_5s_1s_2 + \beta_6s_1  = 0 \\
-\label{Prepoly4} (\beta_4-\beta_2)s_2 + (\beta_3+\beta_6)s_1 + (\beta_5 - \beta_1)s_1s_2- s_1s_2^2 = 0 
-\end{align}
-\begin{itemize}
-	\item  $\displaystyle  \beta_4 = - \sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n_1} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$
-	\item $\displaystyle  \beta_5 = -\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = 1}^{n} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}$
-	\item $\displaystyle \beta_6 =  -\sum \limits_{i=n_1+1}^{n}\sum \limits_{j = n_1+1}^{n} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$
-\end{itemize}
-
-Then replace \eqref{S2(S1)} in \eqref{Prepoly4}: 
-\begin{align}
-(\beta_4-\beta_2)\dfrac{s_1}{c_1s_1^2+c_2s_1+c_3} + (\beta_3+\beta_6)s_1 + (\beta_5 - \beta_1)s_1\dfrac{s_1}{c_1s_1^2+c_2s_1+c_3}- s_1\left(\frac{s_1}{c_1s_1^2+c_2s_1+c_3}\right)^2 = 0 \quad / \cdot \frac{1}{s_1} \\
-(\beta_4-\beta_2)\dfrac{1}{c_1s_1^2+c_2s_1+c_3} + (\beta_3+\beta_6) + (\beta_5 - \beta_1)\dfrac{s_1}{c_1s_1^2+c_2s_1+c_3}- \left(\frac{s_1}{c_1s_1^2+c_2s_1+c_3}\right)^2 = 0  \quad / \cdot (c_1s_1^2+c_2s_1+c_3)^2 \\
-(\beta_4-\beta_2)(c_1s_1^2+c_2s_1+c_3)+ (\beta_3+\beta_6)(c_1s_1^2+c_2s_1+c_3)^2 + (\beta_5 - \beta_1)(c_1s_1^2+c_2s_1+c_3)s_1 - s_1^2 = 0   \\
-\begin{array}{c}(\beta_4-\beta_2)(c_1s_1^2+c_2s_1+c_3)+ (\beta_3+\beta_6)(c_1^2s_1^4+c_2^2s_1^2+c_3^2 + 2 c_1c_2s_1^3 + 2c_2c_3s_1 + 2 c_1c_3s_1^2)\\ \\  + (\beta_5 - \beta_1)(c_1s_1^2+c_2s_1+c_3)s_1 - s_1^2 = 0 \end{array} \\
-\begin{array}{c} \underbrace{(\beta_3+\beta_6)c_1^2}_{a_4} s_1^4 + (\underbrace{(\beta_3 + \beta_6)(2c_1c_2) +  (\beta_5 -\beta_1)c_1}_{a_3})s_1^3 + (\underbrace{(\beta_4 - \beta_2)c_1 +(\beta_3 + \beta_6)(c_2^2 + 2c_1c_3) + (\beta_5-\beta_1)c_2-1}_{a_2})s_1^2 \\
-+(\underbrace{(\beta_4 -\beta_2)c_2 + (\beta_3 + \beta_6)2c_2c_3+(\beta_5-\beta_1)c_3}_{a_1})s_1 + \underbrace{(\beta_4-\beta_2)c_3 + (\beta_3 + \beta_6)c_3^2}_{a_0} = 0
-\end{array}
-\end{align}
-
-Which yields \eqref{Poly4}.
-\begin{itemize}
-	\item $a_4 = (\beta_3+\beta_6)c_1^2$ 
-	\item $a_3 = (\beta_3 + \beta_6)(2c_1c_2) +  (\beta_5 -\beta_1)c_1$
-	\item $a_2 = (\beta_4 - \beta_2)c_1 +(\beta_3 + \beta_6)(c_2^2 + 2c_1c_3) + (\beta_5-\beta_1)c_2-1$
-	\item $a_1 = (\beta_4 -\beta_2)c_2 + (\beta_3 + \beta_6)2c_2c_3+(\beta_5-\beta_1)c_3$
-	\item $a_0 = (\beta_4-\beta_2)c_3 + (\beta_3 + \beta_6)c_3^2$
-\end{itemize}
-
-\textbf{Note:} When calculating the equilibria with the extinction of some OTU under H \ref{noWashoutHyp}, coefficients are calculated with $B = \diag(k^{act})(A^{act})^{-1}$.
-The indexes are redefined to be taken only in $i,j \in [n] \setminus \mathcal{J}$ by formula \eqref{EquilibriaFormula}.
-
-\subsection{Deduction of \eqref{S1NOBWashout}}
-For auxiliary purposes $B:= \diag(k^{act})(A^{act})^{-1}$.
-
-Under hypothesis \ref{WashoutG2}, the $j \in \mathcal{J}$ entries of vector $\diag(k) \diag(f(s))x^{eq} $ are zero. 
-Note also that $(A_1x^{eq})_i = (A^{act}x^{act})_i, \, \forall i \in [n] \setminus \mathcal{J}$.
-
-Then the cross product in equation \eqref{Eq2} can be reduced:
-\begin{align} 
-\begin{bmatrix}
-1_{n_1\times 1}+A_1x^{eq} \\0
-\end{bmatrix}^\top \diag(k) \diag(f(s))x^{eq} = [1_{(n-m)\times 1} - A^{act}x^{act}]^\top \diag(k^{act}) \diag(f^{act}(s))x^{act} 
-\end{align} 
-Therefore replacing \eqref{EquilibriaFormula} and \eqref{EqSome} in \eqref{Eq2}.
-
-\begin{align}
-0 &= (s_{in}-s_1)D- [1_{(n-m)\times 1} - A^{act}x^{act}]^\top \diag(k^{act}) \diag(f^{act}(s))x^{act}\\
-&= (s_{in}-s_1)D- [1_{(n-m)\times 1} - A^{act}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})]^\top \dots \\ & \diag(k^{act}) \diag(f^{act}(s))(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})\\
-&  =  (s_{in}-s_1)-1_{(n-m)\times 1}^\top
-B(\diag(f^{act}(s))^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1})
-\end{align}
-
-$s_2$ does not appear in the previous equation. Then as before (using the numeration of active indexes):
-\begin{align}
-\diag(\mu^{act})^{-1}D_{(n-m)\times 1} - 1_{(n-m)\times 1} = \begin{bmatrix}
-\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_{n-m}+(D-\bar{\mu}_{n-m})s_1}{\bar{\mu}_{n-m}s_1}
-\end{bmatrix}
-\end{align}
-
-Therefore:
-
-\begin{align}
-(s_{in}-s_1)- 1_{(n-m)\times 1}^\top 
-B\begin{bmatrix}
-\dfrac{DK_1+(D-\bar{\mu}_1)s_1}{\bar{\mu}_{1}s_1} \\ \vdots \\ \dfrac{DK_{n-m}+(D-\bar{\mu}_{n-m})s_1}{\bar{\mu}_{n-m}s_1}
-\end{bmatrix} = 0 \\
-(s_{in}-s_1) -\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}s_1}  = 0 \quad /\cdot s_1 \\
-(s_{in} - s_1)s_1   -\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{DK_j+(D-\bar{\mu}_j)s_1}{\bar{\mu}_{j}}  = 0 \\
--s_1^2 + \left( s_{in}-\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}} \right)s_1 - \frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j=1}^{n-m} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}} =0
-\end{align}
-
-Identifying coefficients
-\begin{itemize}
-	\item $a'_2 = -1$
-	\item $a'_1 = s_{in}-\frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j = 1}^{n-m} B_{ij}\dfrac{(D-\bar{\mu}_j)}{\bar{\mu}_{j}}$
-	\item $a'_0 =- \frac{1}{y_A} \sum \limits_{i=1}^{n-m}\sum \limits_{j = 1}^{n-m} B_{ij}\dfrac{DK_j}{\bar{\mu}_{j}}$ 
-\end{itemize}
+\subsection{Deduction of  Equilibrium points}
+
+Recall that
+
+\begin{align}
+f_i(s) = \begin{cases}
+\bar{\mu}_i \dfrac{s_1}{K_i + s_1} \quad \forall i \in G_1 \\
+\bar{\mu}_i \dfrac{s_2}{K_i + s_2} \quad \forall i \in G_2
+\end{cases}
+\end{align}
+
+then $\mu(x,s) = \diag(f(s))(1_{n\times 1} + Ax)$ thus, system \eqref{system} is rewritten as follows.
+
+%\begin{align}
+%\label{Eq1}	\dot{x} = & \diag(x)(\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1}) \\
+%\label{Eq2}	\dot{s_1} = & (s_{in}-s_1)D + \begin{bmatrix}
+%-(1_{n_1\times 1} +A_1x) \\0
+%\end{bmatrix}^\top \diag(k) \diag(f(s))x \\
+%\label{Eq3}	\dot{s_2} = & -s_2D+
+%\begin{bmatrix}
+%1_{n_1\times 1} +A_1x \\ -(1_{n_2\times 1} +A_2x)
+%\end{bmatrix}^\top \diag(k) \diag(f(s))x \\	
+%\label{Eq4}	\dot{s_3} = & -s_3D+\begin{bmatrix}
+%0	\\(1_{n_2\times 1} +A_2x) 
+%\end{bmatrix}^\top \diag(k) \diag(f(s))x 
+%\end{align} 
+\begin{align}
+\tag{\ref{Eq1}}	\dot{x} = & \diag(\mu(x,s) - D_{n\times 1})x \\
+\tag{\ref{Eq2}}	\dot{s_1} = & (s_{in}-s_1)D + Y_{1\bullet} \diag(\mu(x,s))x \\
+\tag{\ref{Eq3}}	\dot{s_2} = & -s_2D+
+Y_{2\bullet} \diag(\mu(x,s))x\\	
+\tag{\ref{Eq4}}	\dot{s_3} = & -s_3D+Y_{3\bullet} \diag(\mu(x,s))x 
+\end{align}
+
+Recall $\mathcal{J}$ the set of non-active coordinates.
+Let $M$ be the matrix defined by taking out the $\mathcal{J}$ columns of the identity matrix of size $n$.
+When $M$ multiplies from the left it adds rows of zeros to the multiplied matrix in the $\mathcal{J}$ coordinates.
+When matrix $M$ multiplies from the right it takes out the $\mathcal{J}$ columns of the multiplied matrix.
+When $M^\top$ multiplies from the left it takes out the $\mathcal{J}$ rows of the multiplied matrix.
+When $M^{\top}$ multiplies from the right it adds columns of zeros to the multipled matrix in the $\mathcal{J}$ coordinates.
+This gives the following relationships:
+	\begin{align}
+	x^{eq} = Mx^{act} \\	
+	f^{act}(s) = M^{\top}f(s) \\
+	\mu^{act}(x,s) = M^{\top}\mu(x,s)\\
+	Y^{act} = YM \\
+	M^\top M = I_{n^{act}}
+	\end{align}.
+
+From equation \eqref{Eq1} equilibrium points satisfy:
+
+\begin{align}
+x_i = 0 \vee (\diag(f(s))(1_{n\times 1} + Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n] \\
+\Rightarrow  (\diag (f(s))(1_{n\times 1}+ Ax) - D_{n\times 1})_i = 0 \quad \forall i \in [n]\setminus \mathcal{J} \\
+\Leftrightarrow f_i(s)(1 + A_{i\bullet}x) - D = 0 \quad \forall i \in [n]\setminus \mathcal{J} \label{Extinction}
+\end{align}
+
+note that $\forall j \in \mathcal{J}, \; x^{eq}_j = 0 $ therefore the coefficients $a_{ij}$ play no role in equation \eqref{Extinction} and one can rewrite equation \eqref{Extinction} as 
+\begin{align} 
+\label{mu=D}\mu^{act}(x,s) = \diag(f^{act}(s))(1_{n^{act}\times 1} + A^{act}x^{act}) = D_{n^{act} \times 1} 
+\end{align}
+
+From hypothesis \ref{inverse hypothesis} matrix $A^{act}$ has an inverse. This gives the following formula
+	\begin{align}
+	x^{act} = (A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) \tag{\ref{EqSome}}
+	\end{align}
+
+Note as well that at the equilibrium, $s_3$ can be defined in terms of $s_1$, $s_2$ and $s_{in}$. This is done by adding equations \eqref{Eq2}, \eqref{Eq3},  and \eqref{Eq4} which gives :
+
+\begin{align}
+s_{in} = s_1+s_2+s_3 \tag{\ref{s1s2s3}}
+\end{align}
+
+\subsubsection{Both functional groups are present}
+
+The case where in each functional group remains at least one OTU is represented by Hypothesis \ref{hypothesis CN}.
+
+By replacing $x^{eq} = Mx^{act}$ in equation \eqref{Eq2} yields
+
+\begin{align}
+(s_{in}-s_1)D + Y_{1\bullet} \diag(\mu(x,s))Mx^{act}  = 0 \\
+(s_{in}-s_1)D + Y^{act}_{1\bullet} \diag(\mu^{act}(x,s))x^{act}  = 0 
+\end{align}
+
+Replacing \eqref{mu=D} gives:
+
+\begin{align} 
+(s_{in}-s_1)D + Y^{act}_{1\bullet} \diag(D_{n^{act}\times 1})x^{act}  = 0  \\
+(s_{in}-s_1) + Y^{act}_{1\bullet} x^{act}  = 0  \\
+\label{s1Equilibria} (s_{in}-s_1) + Y^{act}_{1\bullet}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0
+\end{align}
+
+For notation and indexing purposes it is useful to define: 
+\begin{align}
+B := Y^{act}_{1\bullet} (A^{act})^{-1}M^\top.
+\end{align}
+(note $B_j = 0 \, \forall j \in \mathcal{J}$) and equation \eqref{s1Equilibria} reads as follows:
+
+\begin{align}
+(s_{in}-s_1) + Y^{act}_{1\bullet}(A^{act})^{-1}\underbrace{M^\top M}_{I_{n^{act}}}(\diag(f^{act}(s))^{-1} D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0\\
+\displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1} B_i \left(\dfrac{K_i+s_1}{\bar{\mu_i}s_1}D - 1 \right) + \sum \limits_{i \in G_2 } B_i \left(\dfrac{K_i+s_2}{\bar{\mu_i}s_2}D - 1 \right)= 0 \\
+\displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1 } DB_i \dfrac{K_i+s_1}{\bar{\mu_i}s_1}+ \sum \limits_{i \in G_2 } DB_i \dfrac{K_i+s_2}{\bar{\mu_i}s_2} - \sum \limits_{i \in G_1 \cup G_2}B_i= 0 \quad /\cdot s_1s_2
+\\
+\displaystyle s_1s_2 s_{in}- s^2_1s_2 + \sum \limits_{i \in G_1} s_2DB_i \dfrac{K_i+s_1}{\bar{\mu_i}}+ \sum \limits_{i \in G_2 } s_1DB_i \dfrac{K_i+s_2}{\bar{\mu_i}} - s_1s_2\sum \limits_{i \in G_1 \cup G_2}B_i= 0 \\
+\displaystyle s_1s_2 s_{in}- s^2_1s_2 + s_2\sum \limits_{i \in G_1 } \frac{DB_iK_i}{\bar{\mu_i}}+s_1s_2\sum \limits_{i \in G_1 } \frac{DB_i}{\bar{\mu_i}}+ s_1\sum \limits_{i \in G_2 } \frac{DB_iK_i}{\bar{\mu_i}} + s_1s_2\sum \limits_{i \in G_2 } \dfrac{DB_i}{\bar{\mu_i}} - s_1s_2\sum \limits_{i \in G_1 \cup G_2}B_i= 0 \\
+\displaystyle s_2\left(s_1s_{in} - s^2_1 + \sum \limits_{i \in G_1} \frac{DB_iK_i}{\bar{\mu_i}} +s_1\sum \limits_{i \in G_1 } \dfrac{DB_i}{\bar{\mu_i}}+s_1\sum \limits_{i \in G_2 } \dfrac{DB_i}{\bar{\mu_i}}  - s_1\sum \limits_{i \in G_1 \cup G_2}B_i  \right) = - s_1\sum \limits_{i \in G_2 } \frac{DB_iK_i}{\bar{\mu_i}} \\
+\displaystyle s_2\left( - s^2_1 +s_1\left(s_{in}+\sum \limits_{i \in G_1 \cup \in G_2 } B_i\left(\dfrac{D}{\bar{\mu_i}}-1\right) \right) + \sum \limits_{i \in G_1} \frac{DB_iK_i}{\bar{\mu_i}}\right) = - s_1\sum \limits_{i \in G_2 } \frac{DB_iK_i}{\bar{\mu_i}}
+\end{align}
+
+and so we arrive to formula
+\begin{align}
+s_2 = \frac{s_1}{b_1s_1^2+b_2s_1+b_3} \tag{\ref{S2(S1)}}
+\end{align}
+
+where
+\begin{align}
+\displaystyle b_1 & =  \left(\sum \limits_{i \in G_2 } \frac{DB_iK_i}{\bar{\mu_i}} \right)^{-1} \\
+\displaystyle b_2 & = -\left(s_{in}+\sum \limits_{i \in G_1 \cup \in G_2 } B_i\left(\dfrac{D}{\bar{\mu_i}}-1\right) \right) \left(\sum \limits_{i \in G_2 } \frac{DB_iK_i}{\bar{\mu_i}} \right)^{-1} \\
+\displaystyle b_3 & = -\sum \limits_{i \in G_1} \frac{DB_iK_i}{\bar{\mu_i}} \left(\sum \limits_{i \in G_2 } \frac{DB_iK_i}{\bar{\mu_i}} \right)^{-1} \\
+\end{align}
+
+The same computations must be done with equation \eqref{Eq3}, which is structurally very similar to \eqref{Eq2}.
+So some steps are skipped.
+By replacing $x^{eq} = Mx^{act}$ in equation \eqref{Eq2} yields
+
+\begin{align}
+\label{s2Equilibria} -s_2 + Y^{act}_{2\bullet}(A^{act})^{-1}(\diag(f^{act}(s))^{-1}D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0
+\end{align}
+
+It is again useful to define:
+
+\begin{align}
+C: = Y^{act}_{2\bullet} (A^{act})^{-1}M^\top.
+\end{align}
+
+\begin{align}
+-s_2 + Y^{act}_{2\bullet}(A^{act})^{-1}\underbrace{M^\top M}_{I_{n^{act}}}(\diag(f^{act}(s))^{-1} D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0\\
+- s_2 + \sum \limits_{i \in G_1 } DC_i \dfrac{K_i+s_1}{\bar{\mu_i}s_1}+ \sum \limits_{i \in G_2 } DC_i \dfrac{K_i+s_2}{\bar{\mu_i}s_2} - \sum \limits_{i \in G_1 \cup G_2}C_i= 0 \quad /\cdot s_1s_2
+\\
+\displaystyle- s_1s_2^2 + s_2\sum \limits_{i \in G_1 } \frac{DC_iK_i}{\bar{\mu_i}}+s_1s_2\sum \limits_{i \in G_1 } \frac{DC_i}{\bar{\mu_i}}+ s_1\sum \limits_{i \in G_2 } \frac{DC_iK_i}{\bar{\mu_i}} + s_1s_2\sum \limits_{i \in G_2 } \dfrac{DC_i}{\bar{\mu_i}} - s_1s_2\sum \limits_{i \in G_1 \cup G_2}C_i= 0 \\
+\displaystyle s_1\left( - s^2_2 +s_2\sum \limits_{i \in G_1 \cup \in G_2 } C_i\left(\dfrac{D}{\bar{\mu_i}}-1\right)  + \sum \limits_{i \in G_2} \frac{DC_iK_i}{\bar{\mu_i}}\right) = - s_2\sum \limits_{i \in G_1 } \frac{DC_iK_i}{\bar{\mu_i}}
+\end{align}
+
+and one arrives to expression:
+\begin{align}
+\label{s1(s2)} s_1 = \dfrac{s_2}{c_1s_2^2 + c_2s_2 + c_3}
+\end{align}
+where
+\begin{align}
+\displaystyle c_1 & =  \left(\sum \limits_{i \in G_1 } \frac{DC_iK_i}{\bar{\mu_i}} \right)^{-1} \\
+\displaystyle c_2 & = -\sum \limits_{i \in G_1 \cup \in G_2 } C_i\left(\dfrac{D}{\bar{\mu_i}}-1\right)  \left(\sum \limits_{i \in G_1 } \frac{DC_iK_i}{\bar{\mu_i}} \right)^{-1} \\
+\displaystyle c_3 & = -\sum \limits_{i \in G_2} \frac{DC_iK_i}{\bar{\mu_i}} \left(\sum \limits_{i \in G_1 } \frac{DC_iK_i}{\bar{\mu_i}} \right)^{-1} \\
+\end{align} 
+Then by replacing  \eqref{S2(S1)} in equation \eqref{s1(s2)}, one gets a fifth degree polynomial for $s_1$.
+
+\begin{align}
+s_1\left( c_1\left( \frac{s_1}{b_1s_1^2+b_2s_1+b_3} \right)^2 + c_2\left( \frac{s_1}{b_1s_1^2+b_2s_1+b_3} \right) + c_3 \right) =  \frac{s_1}{b_1s_1^2+b_2s_1+b_3}  \quad /\cdot  \left(b_1s_1^2+b_2s_1+b_3\right)^2\\
+s_1\left( c_1s_1 + c_2s_1\left(b_1s_1^2+b_2s_1+b_3\right)  + c_3\left(b_1s_1^2+b_2s_1+b_3\right)^2 \right) =  s_1\left(b_1s_1^2+b_2s_1+b_3\right) \\
+s_1\left( c_1s_1 + c_2s_1\left(b_1s_1^2+b_2s_1+b_3\right)  + c_3\left(b_1s_1^2+b_2s_1+b_3\right)^2 - \left(b_1s_1^2+b_2s_1+b_3\right) \right) = 0 
+\end{align}
+
+\begin{align}
+\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
+\end{align}
+
+Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
+
+The equilibrium point can be calculated from the solutions of the system of equations \eqref{EqSome}, \eqref{s1s2s3}, \eqref{S2(S1)}, and \eqref{Poly4} with non negative coordinates.
+If the system only provides solutions with at least one negative entry then the set $\mathcal{J}$ can not define an equilibrium point.
+
+\subsubsection{Washout of $G_2$}
+
+The washout of $G_2$ is represented in Hypothesis \ref{hypothesis washout G2}.
+
+Under this case note that $f^{act}(s)$ depends only on $s_1$. Therefore when equation \eqref{EqSome} is replaced in \eqref{Eq2}, one obtains a quadratic equation for $s_1$:
+
+\begin{align}
+\label{poly2_s1} a'_2 s_1^2 + a'_1s_1 + a'_0 = 0
+\end{align}
+
+Since $x_i = 0 \, \forall i \in G_2$ then from equation \eqref{Eq4}.
+\begin{align}
+\dot{s_3} = 0 = -s_3D \\
+\Rightarrow s_3 = 0 \tag{\ref{no_s3}}
+\end{align}
+
+In this case the equilibrium point can be calculated from the solutions of the system of equations \eqref{EqSome}, \eqref{s1s2s3}, \eqref{poly2_s1}, and \eqref{no_s3} with non-negative coordinates.
+If the system only provides solutions with at least one negative entry then the set $\mathcal{J}$ can not define an equilibrium point.
 
@@
 \begin{align} 
+\label{Controlsystem_CV}
 \begin{array}{cl}
@@
 \dot{x_i} =& \left(f_i(s)(1+v_i(t)) -D \right)x_i \quad \forall i \in G_2\\
-\dot{s_1} =& \displaystyle s_1\left(\frac{s_{in}}{s_1}-1\right)D-\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)(1+v_i(t)) x_i  \\
-\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i \in G_1}\frac{1}{y_i}f_i(s)(1+v_i(t))	-\sum\limits_{i \in G_2}\frac{1}{y_i}f_i(s)(1+v_i(t)) x_i  \\
-\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}^{n_1+n_2}\frac{1}{y_i}f_i(s)(1+v_i(t)) x_i \\
-y(t) & = g(x,s)
+\dot{s_1} =& \displaystyle s_1\left(\frac{s_{in}}{s_1}-1\right)D+\sum\limits_{i \in G_1}y_{s_1/x_i}f_i(s)(1+v_i(t)) x_i  \\
+\dot{s_2} = & \displaystyle -s_2D+\sum\limits_{i \in G_1 \cup G_2}y_{s_2/x_i}f_i(s)(1+v_i(t))x_i	  \\
+\dot{s_3} =&  \displaystyle -s_3D+\sum\limits_{i \in G_2}^{n_1+n_2}y_{s_3/x_i}f_i(s)(1+v_i(t)) x_i \\
+y(t) & =x(t)
 \end{array}
 \end{align}	
-
-Define $k_{G_1} = \left ( \frac{1}{y_1},\dots,\frac{1}{y_{nA}}\right )^\top \in \R^{n_1}$,  $k_{G_2} = \left(\frac{1}{y_{n_1+1}},\dots,\frac{1}{y_{n}}\right )^\top \in \R^{n_2}$, and
-
+Define: 
 \begin{align}
@@
 \end{align}
-
+with 
 \begin{align}
 A_{11}(X) &= \diag(f(s)- D_{n\times 1} ) \\
-A_{21}(X) &=  \begin{bmatrix} 
-f(s)^\top \begin{bmatrix} -\diag(k_{G_1}) & 0_{n_1 \times n_2} \end{bmatrix}^\top  \\
-f(s)^\top \begin{bmatrix} \diag(k_{G_1}) & -\diag(k_{G_2}) \end{bmatrix}^\top   \\
-f(s)^\top \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top 
-\end{bmatrix}  \\
+A_{21}(X) &=  Y\diag(f(s))\\
 A_{12}(X) &=  0_{n \times 3} \\
@@
 B_1(X) &= \diag(f(s))\diag(x)  \\
-B_2(X) &= \begin{bmatrix}
-f(s)^\top \diag(x) \begin{bmatrix} -\diag(k_{G_1}) & 0_{n_1 \times n_2} \end{bmatrix}^\top \\
-f(s)^\top \diag(x) \begin{bmatrix} \diag(k_{G_1}) & -\diag(k_{G_2}) \end{bmatrix}^\top  \\
-f(s)^\top \diag(x) \begin{bmatrix} 0_{n_2 \times n_1} & \diag(k_{G_2}) \end{bmatrix}^\top  
+B_2(X) &= Y\diag(f(s))\diag(x)
+\end{align}
+\begin{align}
+C(X) & = \begin{bmatrix}
+\diag(I_n) & 0_{n\times 3}
 \end{bmatrix}
 \end{align} 
-
-Then the system \eqref{Controlsystem} can be rewritten as:
+Then the system \eqref{Controlsystem_CV} can be rewritten as:
 
@@
 where $F,Q$ and $R$ are positive definite matrices.
-Particularly in all simulations $R = \lambda I_n$ for some $\lambda >0$, so all controls have the same weight.
-Since there is no interest in the final time, we define $F = 0$.
-$Q$ is a diagonal matrix.
-
-Define the dynamic sequences for $i \in \N \cup \{0\}$, $\dot{X}^{[i]}$ as :
+Since there is no interest in the final time $F = 0$.
+$Q$ and $R$ are taken as diagonal matrices, in that way the system can be reduced as shown below.
+Particularly after testing the model in the proof of concept and data, the $Q$ and $R$ matrices were $\begin{bmatrix}
+\lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
+\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$.
+
+Define the dynamic sequences for $i \in \N $, $\dot{X}^{[i]}$ as :
 
@@
 
-And for $i = -1$ define $X^{[-1]}(t) = X_0$.
+And for $i = 0$ define $X^{[0]}(t)$ as the solution of \eqref{Controlsystem_CV} with $v(t) \equiv 0 $.
 
@@
 Inspecting the former equation one notices that if $i\neq j$, $P_{ij}(t) = 0$ is a solution of all non diagonal entries when $R$ is diagonal.
-And therefore by existence and uniqueness they should be constantly zero.
+And therefore, once again, by existence and uniqueness they should be constantly zero.
 Hence only the diagonal entries should be calculated.

### 2020-05-30 tex/Article_Interactions.tex
final modifications

@@
 	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
-In the example $G_1$ corresponds to Ammonium oxidizing bacteria (AOB) and $G_2$ corresponds to Ammonium oxidizing bacteria (NOB).
+In the example $G_1$ corresponds to ammonium oxidizing bacteria (AOB) and $G_2$ corresponds to nitrite oxidizing bacteria (NOB).
 	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
@@
 	\item $s_{in}$: entry concentration of substrate $1$ in $[g/l]$. May depend on time $s_{in} = s_{in}(t)$.
-	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites.
+	\item $s$:  vector $(s_1,s_2,s_3)^\top$. Referred to as metabolites.
 	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
@@
 The input flow contains a concentration $s_{in}$ of substrate $s_1$.
-Note that $s_{in}$ and $D$ are time dependent.
 Each OTU grows at a rate $\mu_i(s,x)$.
@@
 
-Which can be written in a more compact notation using the stoichiometric matrix $Y$ and the $\diag$ operator.
+System \eqref{system} can also be written in a more compact form using the stoichiometric matrix $Y$ and the $\diag$ operator.
 \begin{align}
@@
 with entries $a_{ij}$ hereafter referred to as the interaction matrix.
-Dumont\textit{ et al.} did not analyse their model but simply provided a number of simulation results using parameter values identified from experimental data.
+Dumont\textit{ et al.} did not analyse their model but simply provided several simulations using parameter values identified from experimental data.
 The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
@@
 
-Model \eqref{system} is restated in a more compact form using matrix notation. Let $f(s)$ be such that,
+Let $f(s)$ be such that,
 %
@@
  In order to derive the equilibrium points, it is desirable an invertible $A^{act}$ matrix.
-Therefore in what follows of the work it is assumed that matrix $A$ and some of its sub matrices have an inverse, this is stated properly in Hypothesis \ref{inverse hypothesis}.
+Therefore in what follows of the work it is assumed that matrix $A$ and some of its submatrices have an inverse, this is stated properly in Hypothesis \ref{inverse hypothesis}.
 
@@
 \begin{align}
-s_2 = \frac{s_1}{c_1s_1^2+c_2s_1+c_3} \label{S2(S1)}
+s_2 = \frac{s_1}{b_1s_1^2+b_2s_1+b_3} \label{S2(S1)}
 \end{align}
@@
 
-Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
+Formulae for coefficients $b_1, b_2, b_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
 
@@
 In the case of operating diagrams\cite{lobry2017chemostat} (OD) all the pairs $(s_{in},D)$ are regrouped such that the points of the set $\mathcal{P}$ represent when partial nitrification (PN), complete nitrification (CN), washout (WO), or a combination of them may arise \cite{KHIN2004519}.
-PN refers to the state when nitrite $s_2$, accumulates because the OTU of $G_2$ are washed out and thus no conversion from $s_2$  to $s_3$ takes place.
+PN refers to the state when nitrite ($s_2$) accumulates because the OTU of $G_2$ are washed out and thus no conversion from $s_2$  to $s_3$ takes place.
 On the contrary CN is when nitrate ($s_3$) accumulates because of the presence of OTU of $G_2$.
@@
 A first example using operating diagrams is presented to illustrate how adding interactions in a model consisting of 1 OTU in $G_1$ and 1 OTU in $G_2$ may lead to very different outcomes.
+
+The important question of the existence of limit cycles was not resolved in this work.
+In the numerical analysis of this model at least one stable equilibrium was found for any choice of parameters.
+This obviously does not exclude the existence of limit cycles, but to what concerns the authors' intuitions there always seems to be at least one stable equilibrium point.
 
@@
 Note how the presence of $x_1$ affects very negatively $x_2$ in Figure \ref{case1_interactions}, with respect to other interactions.
-The terms in the diagonal entries of the matrix represents intraspecies interactions, while the terms off the diagonal represent the interspecies interactions.}
+The terms in the diagonal entries of the matrix represent intraspecies interactions, while the terms off the diagonal represent the interspecies interactions.}
 \end{figure}
@@
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified}
-	\caption{Modified interaction matrix ecological diagram. In the legend 1) and 2) represent the two different stable equilibria in each zone.}
+	\caption{ED from interaction matrix on Figure \ref{Interaction_2}. In the legend 1) and 2) represent the two different stable equilibria in each zone.}
 	\label{ED 2}
@@
 	\includegraphics[width=\textwidth]{Stability/ED_parameters_modified_2}
-	\caption{Modified interaction matrix ecological diagram.}
+	\caption{ED from interaction matrix on Figure \ref{Interaction_3}.}
 	\label{ED 3}
@@
 
-	\caption{Ecological diagrams for both cases.
+	\caption{Ecological diagrams.
 The different zones represent the combination of surviving species in the steady state.
 PN takes place when neither $x_3$ nor $x_4$ are present.
+CN takes place if $x_3$ or $x_4$ are present.
 Note that in figure \ref{ED 2} two stable equilibria exist for each zone.
-CN takes place if $x_3$ or $x_4$ are present.
 }
@@
 The ecological diagrams are presented in Figure \ref{ecological_diagrams}, where the legend indicates the species surviving in the zone of the respective colour.
-In Figure \ref{ED 2}, the system exhibits bi-stability (it is represented in numbering as 1) and 2) of the different possible equilibriums) .
-Comparing Figures \ref{ED 1} with \ref{ED 2} one can see a very different situation.
-Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or $x_2$ only remains, because in operational terms this means that either PN or CN may take place.
+In Figure \ref{ED 2}, the system exhibits bi-stability (it is represented in numbering as 1) and 2) of the different possible equilibriums).
+Note how every zone in figure \ref{ED 2} has two stable equilibria, meaning that the outcome of the system is determined by its initial conditions, particularly interesting is the green zone where either $x_1,x_3$ coexist or only $x_2$ remains, because in operational terms this means that either PN or CN may take place.
+When compared to Figure \ref{ED 1}, one can see that this change in the interactions of the microbial community can dramatically change the outcome of the reactor in a large operating zone.
 
@@
 The method proposed involves the resolution of Approximating Sequences of Ricatti Equations (ASRE).
-It consists on iteratively calculating trajectories of System \eqref{Controlsystem} with a certain control law and subsequently feed a non-autonomous Ricatti differential equation with the resulting trajectory.
+It consists of iteratively calculating trajectories of System \eqref{Controlsystem} with a certain control law to later feed a non-autonomous Ricatti differential equation with the resulting trajectory.
 Then, a new control law that uses the solution of the Ricatti equation is proposed and a new trajectory is calculated.
@@
 Where matrix $P(t)$ and vector $s_f(t)$ solve differential equations.
-In the appendix it is proved that because of the structure of the system one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method, which renders the method- at least theoretically- scalable for a growing number of OTU.
+In the supplementary material it is proved that, thanks to the structure of the system, one only needs to calculate $2n$ differential equations for the synthesis of the control, instead of $(n+3)^2 + (n+3)$ that would imply the direct application of the method, which renders the method- at least theoretically- scalable for a growing number of OTU.
 
@@
 The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
-Particularly given the system's ammonium and nitrate concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application} calculated from the equation of Table 2 of the same article.
+Particularly given the system's ammonium and nitrite concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application} calculated from the equation of Table 2 of the same article.
 The yields were fitted to match the nitrogen mass balances.
@@
 When growth rates are compared to the proof of section it seems doubtful that a linear pairwise interaction model such as the gLV model could capture the complexity of the particular chemostat analysed.
-Perhaps these interactions are not constant through time (as in the gLV model) or a different interaction function should be thought of.
+Perhaps these interactions are not constant through time (as opposed to the gLV model) or a different interaction function should be thought of.
 However the former questions can not be fully clarified here, because the quality of the genetic sequencing from molecular fingerprints might not be the best when compared to more recent techniques, thus it is unclear if the pulses are due to noise of the measurements.
@@
 Last decades advances in genetic sequencing and microbial ecology have opened a gap for modellers in biochemical processes to integrate this valuable information.
-Considering the success of mass balance models to predict and pilot bioreactors, one should build upon these existing models.
-This article proposed a naïve approach to start filling the gap of microbial ecology and biochemical process modelling: The approach can be simply described as correcting the growth rate of each individual species from genetic sequencing measurements, .
-If one already posses a model for describing a particular bioprocess the use of the techniques here presented can be applied in a straightforward manner if one has already identified the microbial species involved with a particular functionality of the system.
-
-The tracking model was proposed  in a chemostat setting as a way to correct a substrate limited expression.
-However the technique could be used in contexts where less information on the growth function of microbes is known.
+Considering the success of mass balance models to predict and pilot bioreactors, new models should be built upon them.
+This article exposed what can be gained from combining population-based models as used in ecology with functional group based approaches as used in bioengineering.
+The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} already shows that such a combination can give way to models that include bi-stability, coexistence within a functional group, and unintuitive operational insights such as raising the input ammonium $s_{in}$ to achieve partial nitrification.
+The increased number of parameters of this particular model obviously hinders its potential application, but it surely helps to illustrate what can be gained by joining both types of models.
+The mathematical analysis focused on the particular case of pairwise interactions, which can be seen as a first order approximation of the introduced concept of interaction function.
+This opens the question for a broader class of interaction functions that could represent well complex microbial ecosystems, particularly bioreactors.
+
+In that line of reasoning, in order to understand what this interaction function should look like, a data-driven approach was presented.
+It can be simply described as correcting the growth rate expression of each individual species in a mass balance model, by explicitly assuming a control loop on the growth rate depending on the species state variables and the measured abundances.
+The reconstructed growth rates seem to consist of pulses, suggesting that a form of a possible interaction function should reproduce this behaviour, however since the quality of molecular fingerprints is not the best, one can not discard the possibility that this is due to noise of the measurements.
+In spite of the former, one is able to recover the substrates dynamics, implying that the hypothesis of microbial interactions as drivers of a bioprocess, in the form of feedback loops affecting each others growth rates, is not far-fetched.
+
+The use of the tracking technique can be applied in a straightforward manner to already existing models in mixed homogeneous bioreactors, under the condition that the the microbial species have already been identified with a particular functionality of the system.
+Even though the tracking model was proposed for a chemostat setting as a way to correct a substrate limited expression, the method could be used in contexts where less information on the growth function of microbes is known.
 If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model becomes a linear model and one recovers a classic quadratic regulator for linear systems.
 Nevertheless, even in the former case, the synthesis of the optimal bounded control remains an open theoretical challenge.
-
-The interaction function introduced tries to address the issue of prediction from genetic sequencing.
-The analysis of the gLV model proposed by Dumont \textit{et al.} \cite{Dumont2016} shows that such a model structure can give way to bi-stability, coexistence within a functional group, and unintuitive operational insights such as raising the input ammonium $s_{in}$ to achieve partial nitrification.
-From the application section one can see that by correcting the growth rate one is able to recuperate the substrates dynamics, suggesting that interactions are driving the system.
-This opens the question for a broader class of interaction functions that could represent well complex microbial ecosystems, particularly biorreactors.
-
-One of the next steps in this line of research would be to synthesize a control that is able to reconstruct the interaction functions, and not just the dynamics of the species.
-One might bypass the end point issue of the current control scheme by, for example, by a very thorough use of the pontryagin maximum principle for the synthesis of the control.
-In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability \cite{Dochain2003}: integrating genetic sequencing could provide a path for more certainty in model calibration.
+One might bypass this issue of the current control scheme by, for example, a very thorough use of the Pontryagin maximum principle for the synthesis of the control.
+In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability\cite{Dochain2003}, integrating genetic sequencing could provide a path for more certainty in model calibration.
 
@@
 (s_{in}-s_1) + Y^{act}_{1\bullet}(A^{act})^{-1}\underbrace{M^\top M}_{I_{n^{act}}}(\diag(f^{act}(s))^{-1} D_{n^{act}\times 1} - 1_{n^{act}\times 1}) = 0\\
-\displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1} B_i \left(\dfrac{K_i+s_1}{\bar{\mu_i}s_1}D - 1 \right) + \sum \limits_{i \in G_2 } B_i \left(\dfrac{K_i+s_2}{\bar{\mu_i}s_2}D - 1 \right)= 0 \\
+\displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1} B_i \left(\dfrac{K_i+s_1}{\bar{\mu_i}s_1}D - 1 \right) + \sum \limits_{i \in G_2 } B_i \left(\dfrac{K_i+s_2}{\bar{\mu_i}s_2}D - 1 \right)= 0 \label{to_be_reused}\\
 \displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1 } DB_i \dfrac{K_i+s_1}{\bar{\mu_i}s_1}+ \sum \limits_{i \in G_2 } DB_i \dfrac{K_i+s_2}{\bar{\mu_i}s_2} - \sum \limits_{i \in G_1 \cup G_2}B_i= 0 \quad /\cdot s_1s_2
@@
 s_1\left( c_1\left( \frac{s_1}{b_1s_1^2+b_2s_1+b_3} \right)^2 + c_2\left( \frac{s_1}{b_1s_1^2+b_2s_1+b_3} \right) + c_3 \right) =  \frac{s_1}{b_1s_1^2+b_2s_1+b_3}  \quad /\cdot  \left(b_1s_1^2+b_2s_1+b_3\right)^2\\
-s_1\left( c_1s_1 + c_2s_1\left(b_1s_1^2+b_2s_1+b_3\right)  + c_3\left(b_1s_1^2+b_2s_1+b_3\right)^2 \right) =  s_1\left(b_1s_1^2+b_2s_1+b_3\right) \\
-s_1\left( c_1s_1 + c_2s_1\left(b_1s_1^2+b_2s_1+b_3\right)  + c_3\left(b_1s_1^2+b_2s_1+b_3\right)^2 - \left(b_1s_1^2+b_2s_1+b_3\right) \right) = 0 
-\end{align}
-
-\begin{align}
-\label{Poly4} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0
-\end{align}
-
-Formulae for coefficients $c_1, c_2, c_3, a_0, a_1, a_2, a_3, a_4$ can be found in supplementary material.
-
-The equilibrium point can be calculated from the solutions of the system of equations \eqref{EqSome}, \eqref{s1s2s3}, \eqref{S2(S1)}, and \eqref{Poly4} with non negative coordinates.
-If the system only provides solutions with at least one negative entry then the set $\mathcal{J}$ can not define an equilibrium point.
+s_1\left( c_1s_1^2 + c_2s_1\left(b_1s_1^2+b_2s_1+b_3\right)  + c_3\left(b_1s_1^2+b_2s_1+b_3\right)^2 \right) =  s_1\left(b_1s_1^2+b_2s_1+b_3\right) \\
+s_1\left( c_1s_1^2 + c_2s_1\left(b_1s_1^2+b_2s_1+b_3\right)  + c_3\left(b_1s_1^2+b_2s_1+b_3\right)^2 - \left(b_1s_1^2+b_2s_1+b_3\right) \right) = 0 \\
+s_1\left( c_3b_1^2s_1^4+(c_2b_1+2c_3b_1b_2)s_1^3+(c_1+c_2b_2 +c_3(b_2^2 + 2b_1b_3)-b_1)s_1^2+(c_2b_3+2c_3b_3b_2 -b_2)s_1+(b_3 + c_3b_3^2)\right) = 0 
+\end{align}
+
+thus 
+\begin{align}
+\tag{\ref{Poly4}} a_4s_1^4+a_3s_1^3+a_2s_1^2+a_1s_1+a_0 = 0 \quad  \vee \quad s_1 = 0
+\end{align}
+
+where 
+\begin{align}
+a_0 & = b_3 + c_3b_3^2\\
+a_1 & = c_2b_3+2c_3b_3b_2 -b_2\\
+a_2 & = c_1+c_2b_2 +c_3(b_2^2 + 2b_1b_3)-b_1 \\
+a_3 & = c_2b_1+2c_3b_1b_2\\
+a_4 & = c_3b_1^2
+\end{align}
 
@@
 
-Under this case note that $f^{act}(s)$ depends only on $s_1$. Therefore when equation \eqref{EqSome} is replaced in \eqref{Eq2}, one obtains a quadratic equation for $s_1$:
-
-\begin{align}
-\label{poly2_s1} a'_2 s_1^2 + a'_1s_1 + a'_0 = 0
-\end{align}
-
-Since $x_i = 0 \, \forall i \in G_2$ then from equation \eqref{Eq4}.
-\begin{align}
-\dot{s_3} = 0 = -s_3D \\
-\Rightarrow s_3 = 0 \tag{\ref{no_s3}}
-\end{align}
-
-In this case the equilibrium point can be calculated from the solutions of the system of equations \eqref{EqSome}, \eqref{s1s2s3}, \eqref{poly2_s1}, and \eqref{no_s3} with non-negative coordinates.
-If the system only provides solutions with at least one negative entry then the set $\mathcal{J}$ can not define an equilibrium point.
+Under this case note that $f^{act}(s)$ depends only on $s_1$.
+By replacing again $x^{eq} = Mx^{act}$ in equation \eqref{Eq1}, one obtains the same computations as in the previous section, so retake equation \eqref{to_be_reused}
+
+\begin{align}
+\displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1} B_i \left(\dfrac{K_i+s_1}{\bar{\mu_i}s_1}D - 1 \right) + \sum \limits_{i \in G_2 } B_i \left(\dfrac{K_i+s_2}{\bar{\mu_i}s_2}D - 1 \right)= 0  \tag{\ref{to_be_reused}}
+\end{align}
+
+Since $G_1 \subset \mathcal{J} $ then $B_i = 0 \forall i \in G_2$ thus \eqref{to_be_reused} becomes:
+
+\begin{align}
+\displaystyle s_{in} - s_1 + \sum \limits_{i \in G_1} B_i \left(\dfrac{K_i+s_1}{\bar{\mu_i}s_1}D - 1 \right) = 0 \quad /\cdot s_1 \\
+\displaystyle s_1s_{in} - s_1^2 + \sum \limits_{i \in G_1} B_i \left(\dfrac{K_i+s_1}{\bar{\mu_i}}D - s_1 \right)= 0 \\
+\displaystyle s_1s_{in} - s_1^2 + \sum \limits_{i \in G_1} B_i \dfrac{DB_iK_i}{\bar{\mu_i}} + s_1\sum \limits_{i \in G_1}B_i\left(\dfrac{D}{\bar{\mu_i}}-1\right) = 0
+\end{align}
+
+And so a quadratic equation for $s_1$ is obtained.
+\begin{align}
+\tag{\ref{poly2_s1}} a'_2 s_1^2 + a'_1s_1 + a'_0 = 0
+\end{align}
+where
+\begin{align}
+a'_2 &= -1 \\
+a'_1 &= s_{in} + \sum \limits_{i \in G_1}B_i\left(\dfrac{D}{\bar{\mu_i}}-1\right) \\
+a'_0 &=\sum \limits_{i \in G_1} B_i \dfrac{DB_iK_i}{\bar{\mu_i}} 
+\end{align}
 
 \subsection{Jacobian of the system}
-The jacobian is a square matrix of dimension $n\times 3$.
-The entries corresponding to the derivative of the first $n$ functions in the first $n$ variables can be calculated by the use of the chain rule.
-Define:
+
+ Recall that $f:X\rightarrow Y$ is a function, then its derivative is $f':X \rightarrow L(X,Y)$ where $L(X,Y)$ denotes the set of continuous linear mappings from $X$ to $Y$, such that $\Vert f(x)-f(a) -f'(a)[x-a] \Vert = o(\Vert x-a \Vert) $, where the linear mapping $f'(a)$ is evaluated at $[x-a]$ \cite{cartan1971differential}.
+In the case where $X=\R^n$ and $Y = \R^m$, $f'(x)$ is the Jacobian matrix evaluated at point x, furthermore $f'(x)[e_j]$ (where $e_j$ is the canonical $j$-th vector) is the $j$-th column of the Jacobian matrix evaluated at point $x$.
+
+If $f$ is linear then $f'(a)= f$ for any $a \in X$. In the case of the $\diag$ operator, we observe it is linear, therefore $\diag'(a)[x]= \diag(x) $
+
+In the case of bilinear mappings another formula holds, let $h: X_1 \times X_2 \rightarrow Y$ be bilinear. Then $h'(a_1,a_2)[x_1,x_2] = h(x_1,a_2) + h(a_1,x_2)$.
+In the case of the function $h_1: \mathcal{M}_{n\times n}(\R) \times \R^n \mapsto \R^n$ such that $h_1(M,x) = Mx$, one can see that $h_1'(A,x)[B,y] = Bx + Ay$.
+
+The chain rule states that $f:X \rightarrow Y$ and $g: Y\rightarrow Z$, if $h:= g \circ f$ then $h'(a) = g'(f(a))\circ f'(a)$. 
+Take the expression $h: (x,y)\in \R^n\times \R^n \mapsto \diag(x)y$. It is clear that $h = h_1(\diag(x), y) $. By the chain rule:
+
+\begin{align}
+h'(x,y)[a,b] &= h_1'(\diag(x),y)\circ( \diag'(x), \, I_n)[a,b] \\
+& = h_1'(\diag(x),y)[ \diag(a), b] \\
+ &= \diag(a)y + \diag(x)b
+\end{align}
+Note finally that function $h$ is symmetric, i.e. $h(x,y) = h(y,x)$.
+Then going back to our system.
+\begin{align}
+	\dot{x} = & g_1(x,s)= \diag(\mu(x,s) - D_{n\times 1})x \\
+	\dot{s} = & g_2(x,s)= \left(\begin{bmatrix} s_{in}&0&0 \end{bmatrix}^\top-s\right)D + Y\diag(\mu(x,s))x
+\end{align} 
+where $\mu(x,s) = \diag(f(s))(1_{n\times 1}+Ax)$
+For a fixed $s$, let $\mu_s(x): x \mapsto  \diag(f(s))(1+Ax)$ then, $\mu_s'(x) = \diag(f(s))A$ . Let $g_{1s}(x):= h(\mu_s(x) - D_{n\times 1},x)=g_1(x,s)$, then compute $g_{1s}'$:
+\begin{align} 
+g_{1s}'(x)[e_j]&=h'(\mu_s(x) - D_{n\times 1},x) \circ (\mu_s'(x),I_n)[e_j, e_j]\\
+&=h'(\mu_s(x)- D_{n\times 1},x) [\diag(f(s))Ae_j , e_j]  \\
+&=\diag(\diag(f(s))Ae_j)x +  \diag(\mu_s(x)- D_{n\times 1})e_j \\
+&=\diag(f(s))\diag(A_{\bullet j})x +  \diag(\mu_s(x)- D_{n\times 1})e_j \\
+&=\diag(f(s))\diag(x)A_{\bullet j} +  \diag(\mu_s(x)- D_{n\times 1})e_j \\
+\Rightarrow  g_{1s}'(x) &= \diag(f(s))\diag(x)A +  \diag(\mu_s(x)- D_{n\times 1})
+\end{align}
+
+Again, for a fixed $s$, let $g_{2s}(x):= \left(\begin{bmatrix} s_{in}&0&0 \end{bmatrix}^\top-s\right)D + Yh(\mu_s(x),x)=g_2(x,s)$, then compute $g_{2s}'$:
+
+\begin{align} 
+g_{2s}'(x)[e_j]&=Yh'(\mu_s(x),x) \circ (\mu_s'(x),I_n)[e_j, e_j]\\
+&=Y\left(\diag(f(s))\diag(x)A_{\bullet j} +  \diag(\mu_s(x))e_j \right) \\
+\Rightarrow g_{2s}'(x) &= Y(\diag(f(s))\diag(x)A +  \diag(\mu_s(x)))
+\end{align}
+
+Let $f_{G_1}(s_1)$ the function containing the first $n_1$ components of function $f(s)$ and $f_{G_2}(s_2)$ the function containing the last $n_2$ components of function $f(s)$ so one can write
+
+\begin{align}
+f(s) = \begin{pmatrix}
+f_{G_1}(s_1) \\
+f_{G_2}(s_2)
+\end{pmatrix}
+\end{align}
+
+One can see then that:
+
+\begin{align}
+f'(s)= \begin{bmatrix}
+f_{G_1}'(s_1) & 0_{n_1\times 2} \\
+0_{n_2\times 1} & \begin{matrix} f_{G_2}'(s_2) & 0_{n_2\times 1} \end{matrix}  \\ 
+\end{bmatrix}
+\end{align}
+
+Now for a fixed $x$ let $\mu_x(s): s \mapsto   \diag(f(s))(1_{n\times 1}+Ax)$, therefore $\mu_x'(s) =\diag(1+Ax)f'(s)$.
+Let $g_{1x}(s):= h(\mu_x(s) - D_{n\times 1},x)=g_1(x,s)$, then compute $g_{1x}'$:
+
+\begin{align} 
+g_{1x}'(s)[e_j]&=h'(\mu_x(s) - D_{n\times 1},x) \circ (\mu_x'(s),0)[e_j, e_j]\\
+g_{1x}'(s)[e_j]&=h'(\mu_x(s) - D_{n\times 1},x) [\mu_x'(s)e_j, 0]\\
+g_{1x}'(s)[e_j]&=\diag(\mu_x'(s)e_j)x \\
+g_{1x}'(s)[e_j]&=\diag(x)\mu_x'(s)e_j \\
+g_{1x}' &= \diag(x)\diag(1+Ax)f'(s)
+\end{align}
+
+Again, for a fixed $x$ let $g_{2x}(s):= \left(\begin{bmatrix} s_{in}&0&0 \end{bmatrix}^\top-s\right)D + Yh(\mu_s(x),x)=g_2(x,s)$, then compute $g_{1x}'$:
+
+\begin{align}
+g_{2x}'(s)[e_j] = -DI_ne_j + Y h'(\mu_x(s),x)\circ (\mu_x'(s),0)[e_j,e_j] \\
+g_{2x}'(s)[e_j] &= -DI_ne_j + Y h'(\mu_x(s),x)[\mu_x'(s)e_j, 0] \\
+g_{2x}'(s)[e_j] &= -DI_ne_j + Y \diag(x)\mu_x'(s)e_j \\
+g_{2x}'(s) &= -DI_n+ Y \diag(x)\diag(1+Ax)f'(s)
+\end{align}
+
+Finally note that:
 \begin{align*}
-& \begin{array}{rc}
-h_1:\mathcal{M}_{n \times n}(\R) \times \R^n \rightarrow & \R^n \\
-(M,y) \rightarrow & My
-\end{array}  \\
-&\begin{array}{rl}
-h_2: \R^n \times \R^3  \rightarrow & \R^n \\
-(x,s) \rightarrow & \diag(f(s))\left(1_{n\times 1}+ Ax\right)-D_{n\times 1}
-\end{array} 	
+f_{G_1}' := \left( \dfrac{\partial f_1}{\partial s_1}, \dots, \dfrac{\partial f_{n_1}}{\partial s_1} \right)^\top = \left(\dfrac{\bar{\mu}_1K_1}{(K_1 + s_1)^2},\dots, \dfrac{\bar{\mu}_{n_1}K_{n_1}}{(K_{n_1} + s_1)^2} \right)^\top \in \R^{n_1} \\
+f_{G_2}' := \left( \dfrac{\partial f_{n_1+1}}{\partial s_2}, \dots, \dfrac{\partial f_{n}}{\partial s_2} \right)^\top = \left( \dfrac{\bar{\mu}_{n_1+1}K_{n_1+1}}{(K_{n_1+1} + s_2)^2},\dots, \dfrac{\bar{\mu}_{n}K_{n}}{(K_{n} + s_2)^2} \right)^\top \in \R^{n_2}
 \end{align*}
 
-The first $n$ equations of system \eqref{system} may be written then as $\dot{x} =  h(x,s) = h_1(\diag(x), h_2(s,x))$, by the chain rule: 
-\begin{align} D_xh(x,s) &= D_M h_1(\diag(x),h_2(x,s))\circ D_x \diag (x) + D_yh_1(\diag(x),h_2(x,s))\circ D_xh_2(x,s)  \\ &=
-\diag(h_2(x,s))+\diag(x)\diag(f(s))A  \label{n2_entries}
-\end{align}
-
-Expression \eqref{n2_entries} corresponds to the first $n\times n$ entries of the Jacobian of system \eqref{system}.
-
-Define:
-
-\begin{align*}
-f_A' := \left( \dfrac{\partial f_1}{\partial s_1}, \dots, \dfrac{\partial f_{n_1}}{\partial s_1} \right)^\top = \left(\dfrac{\bar{\mu}_1K_1}{(K_1 + s_1)^2},\dots, \dfrac{\bar{\mu}_{n_1}K_{n_1}}{(K_{n_1} + s_1)^2} \right)^\top \in \R^{n_1} \\
-f_B' := \left( \dfrac{\partial f_{n_1+1}}{\partial s_2}, \dots, \dfrac{\partial f_{n}}{\partial s_2} \right)^\top = \left( \dfrac{\bar{\mu}_{n_1+1}K_{n_1+1}}{(K_{n_1+1} + s_2)^2},\dots, \dfrac{\bar{\mu}_{n}K_{n}}{(K_{n} + s_2)^2} \right)^\top \in \R^{n_2}
-\end{align*}
-
 Then the Jacobian of the system may be expressed as:
@@
 \label{Jacobian_system}
- J(x,s_1,s_2,s_3) = \begin{bmatrix}
-J_{11} & J_{12} & J_{13} & J_{14} \\
-J_{21} & J_{22} & J_{23} & J_{24} \\
-J_{31} & J_{32} & J_{33} & J_{34} \\
-J_{41} & J_{42} & J_{43} & J_{44} 
+ J(x,s) = \begin{bmatrix}
+g_{1s}'(x) & g_{1x}'(s) \\
+g_{2s}'(x) & g_{2x}'(s) \\
 \end{bmatrix} 
-\end{align} 
-with 
-\begin{align}
-J_{11} &=  \diag(\diag(f(s))(1_{n\times 1} +Ax)-D_{n\times 1})
-+\diag(f(s))\diag(x)A \\
-J_{12} &= \diag(x)\diag(1_{n \times 1}+Ax)\begin{bmatrix} f_A' \\ 0_{n_2 \times 1} \end{bmatrix}  \\
-J_{13} &=\diag(x)\diag(1_{n\times 1}+Ax)\begin{bmatrix} 0_{n_1 \times 1} \\ f_B' \end{bmatrix} \\
-J_{14} &= 0_{n\times 3}\\
-J_{21} &= -\begin{bmatrix}
-1_{n_1 \times 1} + A_1 x \\ 0_{n_2 \times 1} \end{bmatrix}^\top \diag(y)^{-1} \diag (f(s))  + (\diag(k)\diag(f(s))x)^\top\begin{bmatrix} A_1 \\ 0 \end{bmatrix}  \\
-J_{22} &= -D  - \begin{bmatrix} 1_{n_1 \times 1} + A_1x \\ 0 \end{bmatrix}^\top \diag(k) \diag\left( \begin{bmatrix}\mu_A' \\ 0 \end{bmatrix}\right)x \\
-J_{23} & = 0 \\
-J_{24} &= 0 \\
-J_{31} &= \begin{bmatrix} \left(1_{n_1 \times 1}+A_1x \right)\\ - \left(1_{n_2 \times 1} + A_2x \right)  \end{bmatrix}^\top \diag(k) \diag(f(s)) 
-+  (\diag(k)\diag(f(s))x)^\top \begin{bmatrix}A_1 \\ -A_2\end{bmatrix} \\
-J_{32} &= \begin{bmatrix}\left(1_{n_1 \times 1} + A_1x\right)\\ -\left(1_{n_2 \times 1} + A_2x\right)\end{bmatrix}^\top \diag(k) \diag\left( \begin{bmatrix}
-f_A' \\ 0\end{bmatrix}\right)x \\
-J_{33} &= -D + \begin{bmatrix} \left(1_{n_1 \times 1} + A_1x\right) \\ -\left(1_{n_2\times 1}+ A_2x\right) \end{bmatrix}^\top \diag(k)\diag\left(
-\begin{bmatrix}
-0 \\ f_B'
-\end{bmatrix}\right)x  \\
-J_{34} &= 0 \\
-J_{41} &= \begin{bmatrix}0 \\ 1_{n_2 \times 1} + A_2x \end{bmatrix}^\top\diag(k) \diag(f(s)) 
-+ (\diag(k)\diag(f(s))x)^\top\begin{bmatrix} 
-0 \\ A_2
-\end{bmatrix} \\
-J_{42} &= 0 \\
-J_{43} &= \begin{bmatrix} 0 \\(1_{n_2\times 1} + A_2x) \end{bmatrix}^\top \diag(k) \diag\left(\begin{bmatrix}
-0 \\ f_B'
-\end{bmatrix}\right) x \\
-J_{44} &= -D
 \end{align}

### 2020-05-30 Classification/observer_study.m
implemented observer

@@ -1,58 +1,69 @@
 clear
 close all
 addpath('..\\General Functions')
-reactor = 'A';
+reactor = 'B';
 [t_obs,biomass,s_in,S1,S2,S3,dilution_rate] = load_biomass(reactor);
 [t_OTU_rel,OTU_rel] = load_relative_abundance(reactor);
 d_inter = @(t) interp1(t_obs,dilution_rate,t,'previous');
 s_in_inter = @(t) interp1(t_obs,s_in,t,'previous');
 s1_inter = @(t) interp1(t_obs,S1,t);
 s2_inter = @(t) interp1(t_obs,S2,t);
+s3_inter = @(t) interp1(t_obs,S3,t);
+biomas_inter = @(t) interp1(t_obs,biomass,t);
 t_initial = 183; %incrase of temperature day = 183
 delta_t = 132;
 time_steps_index = find(t_obs > t_initial & t_obs < t_initial + delta_t);
+yA_ref = 0.147;
+yB_ref = 0.042;
+Y = [-yA_ref 0; yA_ref -yB_ref;0 yB_ref];
 t_used = t_obs(time_steps_index);
-dynamic = @(t,z) -1*d_inter(t)*(z - s_in_inter(t));
+z0 = [s1_inter(t_used(1)) s2_inter(t_used(1)) s3_inter(t_used(1))]' ;
+dynamic = @(t,z) -1*d_inter(t)*(z - [s_in_inter(t) 0 0]');
 % z0 = random('Uniform',0,4,3,1);
 t0 = t_obs(time_steps_index(1));
-z0 = [0.3 s_in_inter(t_initial) 3]';
-[T, Z] = ode15s(dynamic,[t_used(1) t_used(end)],z0(1));
-[T2, Z2] = ode15s(dynamic,[t_used(1) t_used(end)],z0(2));
-[T3, Z3] = ode15s(dynamic,[t_used(1) t_used(end)],z0(3));
+[T, Z] = ode15s(dynamic,[t_used(1) t_used(end)],z0);
 figure
 hold on
 plot(T,Z,'--','LineWidth',2.5);
-plot(T2,Z2,'--','LineWidth',2.5);
-plot(T3,Z3,'--','LineWidth',2.5);
-[ax,p1,p2] = plotyy(T2,arrayfun(s_in_inter,T2),T2,arrayfun(d_inter,T2));
+% [ax,p1,p2] = plotyy(T,arrayfun(s_in_inter,T),T,arrayfun(d_inter,T));
+hold on
[…]

### 2020-08-04 tex/Article_Processes.tex
adding article processes format

--- 2020-05-30 tex/Article_Interactions.tex
@@
-\documentclass[3p,times]{article}
-
-\usepackage[margin=0.7in]{geometry}
-
+%  LaTeX support: latex@mdpi.com 
+%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+
+%=================================================================
+\documentclass[processes,article,submit,moreauthors,pdftex]{Definitions/mdpi}
+
+% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'.
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, applmech, applnano, applsci, arts, asc, asi, atmosphere, atoms, automation, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomedinformatics, biomimetics, biomolecules, biosensors, bloods, brainsci, breath, buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cyber, dairy, data, dentistry, dermatopathology, designs, diabetology, diagnostics, digital, diseases, diversity, drones, earth, econometrics, ecologies, economies, education, ejbc, ejihpe, electricity, electrochem, electronicmat, electronics, endocrines, energies, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, fuels, futureinternet, futurephys, galaxies, games, gardens, gases, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, hearts, heritage, highthroughput, horticulturae, humanities, hydrogen, hydrology, ijerph, ijfs, ijgi, ijms, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jce, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jne, jnt, jof, joitmc, journalmedia, jpm, jrfm, jsan, land, languages, laws, life, literature, livers, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, ijns, neurosci, neuroglia, nitrogen, notspecified, nutrients, obesities, oceans, ohbm, osteology, optics, organics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, pollutants, polymers, polysaccharides, preprints , proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, religions, remotesensing, reprodmed, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, surfaces, surgeries, suschem, sustainability, world, symmetry, systems, technologies, telecom, test, tourismhosp, toxics, toxins, transplantology, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj, women
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+%=================================================================
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{xx}
+\issuenum{1}
+\articlenumber{5}
+\pubyear{2020}
+\copyrightyear{2020}
+%\externaleditor{Academic Editor: name}
+\history{Received: date; Accepted: date; Published: date}
+%\updates{yes} % If there is an update available, un-comment this line
+
+%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
+%\continuouspages{yes}
+
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
+
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx,epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Microbial Interactions as Drivers of a Nitrification Process in a Chemostat}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0001-9224-291X} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{Pablo Ugalde-Salas $^{1,\dagger,\ddagger}$\orcidA{\orcidauthorA}, Héctor Ramírez C. $^{1,\ddagger}$, Jérôme Harmand, and Elie Desmond-Le Quéméner $^{2,}$*}
+
+% Authors, for metadata in PDF
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
+$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+
+% Contact information of the corresponding author
+\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+
+% Current address and/or shared authorship
+\firstnote{Current address: Affiliation 3} 
+\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
+
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{ 	This article deals with the inclusion of microbial ecology measurements such as abundances of operative taxonomic units in bioprocess modelling.
+The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting where a nitrification process was operated for over 500 days.
+The limitations and the insights of such an approach are discussed.
+In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of data from genetic sequencing in chemostat models is presented.
+The optimal tracking revisits the data used in the aforementioned chemostat setting.
+The method is able to reconstruct the different forms of nitrogen in the reactor by using the abundances of the operative taxonomic units, even though the synthesized control can not be guaranteed to be optimal.
+}
+
+% Keywords
+\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Diversity
+%\LSID{\url{http://}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences:
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data:
+%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
+If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
+In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
+
+%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Toxins
+%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
+
+%\setcounter{secnumdepth}{4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{amssymb}
@@
 \DeclareMathOperator{\diag}{diag}
-\declaretheorem[name=Theorem]{thm}
-\declaretheorem[name=Lemma]{lemma}
+%\declaretheorem[name=Theorem]{thm}
+%\declaretheorem[name=Lemma]{lemma}
 \newtheorem{defn}{Definition}
@@
 \graphicspath{{Images/}}
-
 \begin{document}
-
-\title{Microbial interactions as drivers of a nitrification process in a chemostat}
-
-\author{Pablo Ugalde-Salas, Héctor Ramírez C., Jérôme Harmand, Elie Desmond-Le Quéméner}
-\date{}
-\maketitle
-
-\begin{abstract}
-	This article deals with the inclusion of microbial ecology measurements such as abundances of operative taxonomic units in bioprocess modelling.
-The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting where a nitrification process was operated for over 500 days.
-The limitations and the insights of such an approach are discussed.
-In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of data from genetic sequencing in chemostat models is presented.
-The optimal tracking revisits the data used in the aforementioned chemostat setting.
-The method is able to reconstruct the different forms of nitrogen in the reactor by using the abundances of the operative taxonomic units, even though the synthesized control can not be guaranteed to be optimal.
-\end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
 
@@
 Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}.
-Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics presented by Song \textit{et al.}\cite{Song2014}, this articles deals with population-based approaches where species are taken as the interacting units.
-
-The classical ecological concept of species and niche in the microbial world is an elusive one: in the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring.
-In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}.
+Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics presented by Song \textit{et al.} \cite{Song2014}, this articles deals with population-based approaches where species are taken as the interacting units.
+
+The classical ecological concept of species and niche in the microbial world is an elusive one: in the macro world one can clearly differentiate one species from another for reproductive reasons and their ability to give birth to offspring.
+In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (e.g.
+the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}.
 Therefore as an ecological problem is hard to precise the 'niche' of 'microbial species'.
-These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of 16S rDNA marker gene.
+These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of the 16S rDNA marker gene.
 In the past years considerable efforts have been made to measure the bacterial community composition.
-Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.
+Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA have become a standard tool for studying  microbial diversity \cite{FERRERA2016790}.
 The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances over time.
@@
 
-As a departing point, the work of Dumont et al.\cite{Dumont2016} is presented in section 2.
-They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model\cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints.
+As a departing point, the work of Dumont\textit{ et al.} \cite{Dumont2016} is presented in section 2.
+They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints.
 Section 3 inspects the model through a mathematical analysis.
@@
 For approximating the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data.
-The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}.
-In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}.
+The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations \cite{Cimen2008}.
+In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al.} \cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}.
 This approach explicitly assumes that dynamics of complex ecosystems are driven by interactions, that are the results of feedback loops of each species on the growth rate of others.
@@
 	\end{pmatrix}
-	\end{array} \label{diag_operator}
+	\end{array} \label{inter:diag_operator}
 	\end{align}
@@
 
-The situation is described as simplified reactions \eqref{Reaction1} and \eqref{Reaction2}.
+The situation is described as simplified reactions \eqref{inter:Reaction1} and \eqref{inter:Reaction2}.
 The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather they represent the direction of the bioprocess and the proportions of different consumed and formed compounds of interest.
 The terms $y_i$ are known as yields, they represent the quantity of g of biomass produced per g of substrate consumed by  OTU $i$.
-For example in the case of reaction \eqref{Reaction1}, one gram of $s_1$ is consumed, one gram of $s_2$ and $y_{x_i/s_1}$ grams of dry biomass of OTU $i$ are produced.
-\begin{align}
-\label{Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
-\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
+For example in the case of reaction \eqref{inter:Reaction1}, one gram of $s_1$ is consumed, one gram of $s_2$ and $y_{x_i/s_1}$ grams of dry biomass of OTU $i$ are produced.
+\begin{align}
+\label{inter:Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
+\label{inter:Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
 \end{align}
@@
 \subsection{Kinetic Equations}
-In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rates seen in equations \eqref{gLV growth1} and \eqref{gLV growth2} were calibrated against experimental data for the two most abundant OTU of each functional group.
-
-\begin{align}
-\label{gLV growth1}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
-\label{gLV growth2}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2 
+In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rates seen in equations \eqref{gLV growth} were calibrated against experimental data for the two most abundant OTU of each functional group.
+
+\begin{align}
+\label{gLV growth} \begin{array}{lc}
+\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
+\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2
+\end{array}  
 \end{align}
@@
 Dumont\textit{ et al.} did not analyse their model but simply provided several simulations using parameter values identified from experimental data.
-The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.
+The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth}.
 
@@
 \subsection{Properties of the system}
+\label{Properties_of_the_system}
 
@@
 
-\begin{restatable}{lemma}{systembounds}
+\begin{Lemma}
 	\label{l1}
@@
 	\end{align}
-\end{restatable}
+\end{Lemma}
 
@@
 
-\begin{restatable}{thm}{wellposedness}
+\begin{Lemma}
 	\label{theoWellPosedness}
-	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}, remain in $\Omega$ and are bounded.
-\end{restatable}
+	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth}, remain in $\Omega$ and are bounded.
+\end{Lemma}
 
@@
 Operating and ecological diagrams are created from this stability analysis.
-Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$: In a $D-s_{in}$ plane different zones representing the stability properties of system \eqref{system} are identified.
+Both are an illustrative way of representing the long term behaviour of a reactor depending on operating parameters, namely $D$ and $s_{in}$: In a $D-s_{in}$ plane different zones representing the stability properties of system \eqref{system} are identified \cite{Pavlou1999}.
 
@@
 Operating and ecological diagrams are created by running algorithm \ref{StabilityAnalysis} for different pairs $(s_{in},D)$.
-In the case of operating diagrams\cite{lobry2017chemostat} (OD) all the pairs $(s_{in},D)$ are regrouped such that the points of the set $\mathcal{P}$ represent when partial nitrification (PN), complete nitrification (CN), washout (WO), or a combination of them may arise \cite{KHIN2004519}.
+In the case of operating diagrams \cite{lobry2017chemostat} (OD) all the pairs $(s_{in},D)$ are regrouped such that the points of the set $\mathcal{P}$ represent when partial nitrification (PN), complete nitrification (CN), washout (WO), or a combination of them may arise \cite{KHIN2004519}.
 PN refers to the state when nitrite ($s_2$) accumulates because the OTU of $G_2$ are washed out and thus no conversion from $s_2$  to $s_3$ takes place.
@@
 	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{subfigure}[t]{0.45\textwidth}
 		\includegraphics[width = \textwidth]{Stability/OD_case_study_1_no_interactions}
@@
 	~
-	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{subfigure}[t]{0.45\textwidth}
 		\includegraphics[width = \textwidth]{Stability/OD_case_study_1}
@@
 
- The case study 2 is based on Dumont \textit{et al.}\cite{Dumont2016} model parameters.
+The case study 2 is based on Dumont \textit{et al.} \cite{Dumont2016} model parameters.
 They proposed a distribution of parameters obtained from a Bayesian estimation method.
@@
 \begin{figure}[h]
-\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[t]{0.32\textwidth}
 		\includegraphics[width=\textwidth]{Stability/Interactions_parameters_Dumont}
@@
 	~
-\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[t]{0.32\textwidth}
 		\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified}
@@
 	~
-\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[t]{0.32\textwidth}
 		\includegraphics[width=\textwidth]{Stability/Interactions_parameters_modified_2}
@@
 	\centering
-	\begin{subfigure}[t]{0.32\textwidth}
+	\begin{subfigure}[t]{0.31\textwidth}
 		\includegraphics[width=\textwidth]{Stability/ED_parameters_Dumont}
@@
 	~
-	\begin{subfigure}[t]{0.32\textwidth}
+	\begin{subfigure}[t]{0.31\textwidth}
 		\includegraphics[width=\textwidth]{Stability/ED_parameters_modified}
@@
 	~
-\begin{subfigure}[t]{0.32\textwidth}
+	\begin{subfigure}[t]{0.31\textwidth}
 		\includegraphics[width=\textwidth]{Stability/ED_parameters_modified_2}
@@
 	\end{subfigure}
-
 	\caption{Ecological diagrams.
@@
 Note $J_I(x)$ the Jacobian matrix of function $\mathcal{I}$, then a first order approximation of $\I(\cdot)$ centred at $\bar{x}$ gives: $\I(x) = \I(\bar{x}) + J_I(\bar{x})(x-\bar{x}) + o(\Vert x- \bar{x} \Vert)$.
-When $\bar{x}= 0$ one recovers the growth expression from the previous section (equations \eqref{gLV growth1} and \eqref{gLV growth2}) implying that $J_I(\bar{0})$ can be seen as the interaction matrix from model \eqref{system}.
+When $\bar{x}= 0$ one recovers the growth expression from the previous section (equations \eqref{gLV growth}) implying that $J_I(\bar{0})$ can be seen as the interaction matrix from model \eqref{system}.
 
@@
 The tracking problem does not consider a constrained control.
-Nevertheless, the methods of Cimen \textit{et al.}\cite{Cimen2004} were directly used with an explicit constraint in the synthesis of the control.
+Nevertheless, the methods of Cimen \textit{et al.} \cite{Cimen2004} were directly used with an explicit constraint in the synthesis of the control.
 Even though this is probably suboptimal when the control reaches its bounds, one at least is certain about its optimality when the control never reaches its constraints.
@@
 In the operating diagram of the same case (figure \eqref{OD_interactions}) the red zone implies complete nitrification, while the green zone means partial nitrification.
-For integrating the former phenomena in the simulation, the system was simulated for 300 days, and perturbed at day 150 from the CN zone ($(s_{in},D) = (1.25,0.22)$) to a PN zone ($(s_{in},D) = (1.95,0.22)$).
+For integrating the former phenomena in the simulation, the system was simulated for 300 days, and perturbed at day 150 from the CN zone ($(s_{in},D) = (1.25,0.24)$) to a PN zone ($(s_{in},D) = (1.95,0.24)$).
 Simulations can be seen in figure \ref{synthetic_data}.
@@
 	\begin{subfigure}{0.32 \linewidth}
- 	\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_AOB_plot}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_AOB_plot}
 		\caption{AOB.}
@@
 		\centering
-	\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_NOB_plot}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_NOB_plot}
 		\caption{NOB.}
@@
 		\centering
-	\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_metabolites}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_metabolites}
 		\caption{Metabolites.}
@@
 \end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$ in order to better track the NOB trajectories, since they are less abundant.
+The values were obtained by trial and error, by using a single $\lambda$ for both functional groups, beginning with $\lambda = 1$, in which case one can see how the optimal control becomes $u = 1$, thus no tracking is performed.
+Further diminishing the value from $10^{-5}$ adds too much noise to the control, without significant gains on the quality of the tracking.
+
 The results of the procedure to identify interactions can be seen in figure in figure \ref{POC_tracking}.
@@
 The metabolites concentration represented in figure \ref{PC_metabolites} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements.
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45 \linewidth}
-	\includegraphics[width= \textwidth]{proof_of_concept/200525_POC_iter_5_Biomass}
-	\caption{Total biomass.}
-	\label{PC_total_biomass}
-	\end{subfigure}
-~
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{proof_of_concept/200525_POC_iter_5_metabolites}
-		\caption{Metabolites. }
-		\label{PC_metabolites}
-	\end{subfigure}
-
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{proof_of_concept/200525_POC_iter_5_AOB_plot_1}
-		\caption{AOB biomass.}
-		\label{PC_AOB}
-	\end{subfigure}
-	~
-	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\textwidth]{proof_of_concept/200525_POC_iter_5_NOB_plot_1}
-		\caption{NOB biomass. }
-		\label{PC_NOB}
-	\end{subfigure}
-\caption{Asterisks represent the synthetic data, while the continuous lines represent the method's output.
-The method is able to reconstruct the metabolites pattern, from the biomasses concentrations.}
-\label{POC_tracking}
-\end{figure}
 
@@
 
+A final comment on the identifiability of the interaction terms.
+Even though one might propose a growth rate with the tracking control $u(t)$ that accurately replicates the OTU trajectory $x(t)$, retrieving the original interaction coefficients from the obtained control for this example was not possible.
+The former was tried by minimizing function $\displaystyle f(A) = \left \Vert \int \limits_{0}^Tu(t)-(1+Ax(t)) dt \right\Vert $ with a non linear optimization solver for a 1000 initial random guesses for matrix $A$.
+If one also takes into account $\bar{\mu}_i$ and $K_i$ as parameters to fit this adds even more degrees of freedom, thus suggesting that the identifiability of growth functions \eqref{gLV growth} in model \eqref{system} might be very low.
+
 \begin{figure}[h]
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_Control_AOB_plot_1}
-	\caption{Control for the AOB population.}
+		\includegraphics[width= \textwidth]{proof_of_concept/200701_POC_iter_5_Biomass}
+		\caption{Total biomass.}
+		\label{PC_total_biomass}
+	\end{subfigure}
+	~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{proof_of_concept/200701_POC_iter_5_metabolites}
+		\caption{Metabolites. }
+		\label{PC_metabolites}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{proof_of_concept/200701_POC_iter_5_AOB_plot_1}
+		\caption{AOB biomass.}
+		\label{PC_AOB}
+	\end{subfigure}
+	~
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\textwidth]{proof_of_concept/200701_POC_iter_5_NOB_plot_1}
+		\caption{NOB biomass. }
+		\label{PC_NOB}
+	\end{subfigure}
+	\caption{Asterisks represent the synthetic data, while the continuous lines represent the method's output.
+The method is able to reconstruct the metabolites pattern, from the biomasses concentrations.}
+	\label{POC_tracking}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45 \linewidth}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_iter_5_Control_AOB_plot_1}
+		\caption{Control for the AOB community.}
 		\label{Control AOB no noise}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_Control_NOB_plot_1}
-	\caption{Control for the NOB population.}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_iter_5_Control_NOB_plot_1}
+		\caption{Control for the NOB community.}
 		\label{Control NOB no noise}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_AOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_iter_5_growth_AOB_plot_1}
 		\caption{Growth rate of the model for AOB community.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_NOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_iter_5_growth_NOB_plot_1}
 		\caption{Growth rate of the model for the NOB community.}
@@
 	\begin{subfigure}{0.45 \linewidth}
-		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_control_AOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_iter_5_growth_control_AOB_plot_1}
 		\caption{Growth rate of the model for AOB community.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{proof_of_concept/200525_POC_iter_5_growth_control_NOB_plot_1}
+		\includegraphics[width=\linewidth]{proof_of_concept/200701_POC_iter_5_growth_control_NOB_plot_1}
 		\caption{Growth rate of the model for the NOB community.}
@@
 For choosing which species belong in which functional group, the procedure described of Ugalde-Salas \textit{et al.} \cite{Ugalde-Salas2019} was used.
-From day $183$ to day $315$ 31 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
+From day $183$ to day $315$, 31 OTU were identified in the $G_1$ group (AOB) and 5 in the $G_2$ functional group (NOB).
 
@@
 
-The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters\cite{Wiesmann1994}.
+The knowledge of functions $f_i(s)$ was based on a study of nitrification's kinetic parameters \cite{Wiesmann1994}.
 Particularly given the system's ammonium and nitrite concentration a Monod function (eq \eqref{monod}) was used for $G_1$ and $G_2$ with parameters given in table \ref{kinetic_parameters_application} calculated from the equation of Table 2 of the same article.
@@
 \lambda_1 I_{n_1} &0  \\ 0& \lambda_2 I_{n_2}
-\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$.
+\end{bmatrix}$ and $I_n$, respectively, with $\lambda_1 = 10^{-4}$ and $\lambda_2 = 10^{-5}$, because data lies in the same order of magnitude than synthetic data.
 
@@
 For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e.
-$u(t)= 1$) in  figure \ref{u=1 simulation.} nitrite ($s_3$) accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
+$u(t)= 1$) in  figure \ref{u=1 simulation.} nitrate ($s_3$) accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.
 
@@
 This can be explained by noting in figure \ref{OTU abudance all} that the most abundant OTU are better tracked, thus the information contained in the least abundant species is not integrated in the model.
+It may be the case that using appropriate weight matrices that account for the difference between OTU abundances could help in this aspect; in that sense only one rational was tested (inverse of the mean abundance of each OTU in the diagonal entries of matrix $Q$) and did not improve the results.
 When looking at the growth rates (figure \ref{growth all}) one again observes pulses for each OTU, note also that most OTU were present only for a fraction of the experiment's duration.
@@
 In both cases, the regrouped and individual tracking, the growth rate varies strongly, raising the question whether the observed pulses are emerging from interactions within the microbial community.
-When growth rates are compared to the proof of section it seems doubtful that a linear pairwise interaction model such as the gLV model could capture the complexity of the particular chemostat analysed.
+When growth rates are compared to the proof of concept section it seems doubtful that a linear pairwise interaction model such as the gLV model could capture the complexity of the particular chemostat analysed.
 Perhaps these interactions are not constant through time (as opposed to the gLV model) or a different interaction function should be thought of.
@@
 
-The use of the tracking technique can be applied in a straightforward manner to already existing models in mixed homogeneous bioreactors, under the condition that the the microbial species have already been identified with a particular functionality of the system.
+The use of the tracking technique can be applied in a straightforward manner to already existing models in mixed homogeneous bioreactors, under the condition that the microbial species have already been identified with a particular functionality of the system.
 Even though the tracking model was proposed for a chemostat setting as a way to correct a substrate limited expression, the method could be used in contexts where less information on the growth function of microbes is known.
 If one supposes nothing on the growth expression but the fact that is bounded (life cannot grow infinitely fast) the model becomes a linear model and one recovers a classic quadratic regulator for linear systems.
+This was tested for the data presented in this article and, unfortunately, negative substrate appeared as an output, suggesting that the substrate limitation term is crucial for the model to be well-posed.
 Nevertheless, even in the former case, the synthesis of the optimal bounded control remains an open theoretical challenge.
 One might bypass this issue of the current control scheme by, for example, a very thorough use of the Pontryagin maximum principle for the synthesis of the control.
-In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability\cite{Dochain2003}, integrating genetic sequencing could provide a path for more certainty in model calibration.
-
-\section{Codes}
-
-All the codes can be recovered from the following repository \url{https://github.com/paus-5/Class-and-Track}.
-\section{Acknowledgements}
- The authors would like to thank Alain Rapaport for the exchanges and comments. This work was financed by project Thermomic ANR-16-CE04-0003.
-
-\section{Supplementary Material}
-
-\subsection{Proofs of \cref{l1} and \cref{theoWellPosedness}}
-
-\systembounds*
+In a more general view the reconstruction of the growth function in chemostat systems is already subject to problems of identifiability \cite{Dochain2003}, integrating genetic sequencing could provide a path for more certainty in model calibration.
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{Conceptualization J.H., P.U., and E.D, Formal analysis P.U. and H.R., Supervision J.H., E.D. Writing - review \& editing J.H. P.U. E.D. Software P.U.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\funding{This work was financed by project Thermomic ANR-16-CE04-0003. }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\acknowledgments{The authors would like to thank Alain Rapaport for the enriching exchanges and comments.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\conflictsofinterest{The authors declare no conflict of interest.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\abbreviations{The following abbreviations are used in this manuscript:\\
+
+\noindent 
+\begin{tabular}{@{}ll}
+AOB & Ammonium oxidizing bacteria\\
+NOB & Nitrite oxidizing bacteria\\
+OTU & Operative Taxonomic Unit
+\end{tabular}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendix
+
+\section{Proofs of section \ref{Properties_of_the_system}}
+
+\begin{Lemma}
+	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists positive scalars $M_1$, $M_2$, and $M_3$ such that solutions to \eqref{system} satisfy the following inequalities:
+	\begin{align}
+	&\sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1 \leq M_1 \\
+	&\sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 +s_2 \leq M_2 \\
+	&s_1 + s_2 + s_2 \leq M_3
+	\end{align}
+\end{Lemma}
 
 \begin{proof}
-	Define 
-	\begin{align}
-	z_1 &: = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1  \\
-	z_2 &: = \sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 + s_2 \\
-	z_3 &: = s_1 + s_2 + s_3
-	\end{align}
-
-	Computing $\dot{z_{1}}$ one gets:
+	Define $ \displaystyle z_1 : = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1  ;\quad 
+	z_2 : = \sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 + s_2 ;\quad 
+	z_3 : = s_1 + s_2 + s_3$. Computing $\dot{z_{1}}$ one gets:
 	\begin{align*}
-	\dot{z_{1}} &=\sum \limits_{i \in G_1} \frac{1}{y_i}\dot{x_i} + \dot{s_1} \\
-	& = \sum \limits_{i \in G_1} \frac{1}{y_i}\left(\mu_i(s_1,x) -D \right)x_i + (s_{in}-s_1)D-\sum\limits_{i \in G_1}\frac{1}{y_i}\mu_i(s_1,x) x_i   \\
-	&= 	D\left(-\sum \limits_{i \in G_1} \frac{1}{y_i}x_i - s_1 + s_{in}\right)  \\
-	& = D(s_{in} - z_1)
+	\dot{z_{1}} =\sum \limits_{i \in G_1} \frac{1}{y_i}\dot{x_i} + \dot{s_1} = D\left(-\sum \limits_{i \in G_1} \frac{1}{y_i}x_i - s_1 + s_{in}\right)  = D(s_{in} - z_1)
 	\end{align*}
-
 	Define $\bar{s} =\max\{s_{in}(t) | t\geq 0\}$ and consider the differential equation:
-
 	\begin{align}
@@
 	\begin{array}{l}
-	\dot{w} = D(\bar{s} - w) \\
+	\dot{w} = D(\bar{s} - w) ; \quad 
 	w(0) = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i(0) + s_1(0)
@@
 
-	Consider  
+	Now consider  
 	\begin{align}
 	\label{z1} \begin{array}{l}
-	\dot{z_1} =  D(s_{in} - z_1)\\
+	\dot{z_1} =  D(s_{in} - z_1) ;\quad 
 	z_1(0) = \sum \limits_{i \in G_1} \frac{1}{y_i}x_i(0) + s_1(0)
@@
 
-	By defining $M_2 = \max\left \{ \displaystyle \sum \limits_{i=n_1 +1 }^{n} \frac{1}{y_i}x_i(0) + s_1(0) +s_2(0), \bar{s} \right\}$, and $M_3 =\max\left \{ s_1(0) +s_2(0) + s_3(0), \bar{s} \right\} $ and noting that $z_2(t)$ and $z_3(t)$ satisfies the same differential equations as $z_1$ the above reasoning may be applied and one has the desired bounds.
+	Define $M_2 = \max\left \{ \displaystyle \sum \limits_{i=n_1 +1 }^{n} \frac{1}{y_i}x_i(0) + s_1(0) +s_2(0), \bar{s} \right\}$, and $M_3 =\max\left \{ s_1(0) +s_2(0) + s_3(0), \bar{s} \right\} $ and noting that $z_2(t)$ and $z_3(t)$ satisfies the same differential equations as $z_1$ the above reasoning may be applied and one has the desired bounds.
 \end{proof}
 
-\wellposedness*
+\begin{Lemma}
+	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth}, remain in $\Omega$ and are bounded.
+\end{Lemma}
 
@@
 
-	Note that for any $i \in \{1,\dots, n\} $ if $x_i = 0$ then $\dot{x_{i}} = 0$, therefore all solutions of system \eqref{system} with initial condition $x_i(t_0) = 0$ remain in these planes.
+	Note that for any $i \in [n] $, if $x_i = 0$ then $\dot{x_{i}} = 0$, therefore all solutions of system \eqref{system} with initial condition $x_i(t_0) = 0$ remain in these planes.
 By the Picard Lindeloff theorem a solution starting in $int(\Omega)$ cannot cross these planes, therefore $x_i(t)\geq 0$ for $t \geq 0$.
-
-	If $s_1 = 0$, then $\dot{s_1} = Ds_{in} > 0$. Therefore $s_1(t) \geq 0$.
-
-	If $s_2 = 0$ then note first that by adding both inequalities from Lemma \eqref{l1}:
-	\begin{align*}
-	\sum \limits_{i \in G_1 \cup G_2}  \frac{1}{y_i} x_i + 2s_1 + s_2 \leq M_1 + M_2 
-	\end{align*}
-	let $\bar{k} = \min \left\{ \frac{1}{y_i}  : \; i\in [n] \right \}$ and since $s_1,x_i \geq 0$ one has:
-	\begin{align*}
-	\Rightarrow \bar{k} \sum  \limits_{i = 1}^{n}   x_i  \leq M_1 + M_2  \\
-	\Leftrightarrow \bar{k} \sum  \limits_{i = 1}^{n}   \vert x_i \vert  \leq M_1 + M_2  \\
-	\Leftrightarrow \bar{k} \Vert x \Vert_1  \leq M_1 + M_2  \\
-	\Rightarrow   \bar{k} \Vert x \Vert_{\infty} \leq M_1 + M_2
-	\end{align*}
-
-	Define $M := \dfrac{\bar{k}}{M_1 + M_2}$, and let $A$ be a matrix such that $\Vert A \Vert_{\infty} \leq M$. Since
-	\begin{align*} \Vert Ax \Vert_{\infty} \leq 1 \Rightarrow   (1 + A_{i\bullet}x) \geq 0 \quad \forall i \in [n]
-	\end{align*}
-
-	and $\Vert Ax \Vert_{\infty} \leq \Vert A \Vert_{\infty} \Vert x\Vert_{\infty} \leq M \frac{1}{M}$. One has proven that:
+If $s_1 = 0$, then $\dot{s_1} = Ds_{in} > 0$.
+Therefore $s_1(t) \geq 0$.
+	If $s_2 = 0$, let $\bar{k} = \min \left\{ \frac{1}{y_i}  : \; i\in [n] \right \}$, by adding both inequalities from Lemma \eqref{l1} and since $s_1\geq 0$ one has $\bar{k} \sum  \limits_{i = 1}^{n}   x_i  \leq M_1 + M_2  $, which in turn implies: $ \bar{k} \Vert x \Vert_{\infty} \leq M_1 + M_2$.
+Define $M := \dfrac{\bar{k}}{M_1 + M_2}$, and let $A$ be a matrix such that $\Vert A \Vert_{\infty} \leq M$.
+It follows that $\Vert Ax \Vert_{\infty} \leq \Vert A \Vert_{\infty} \Vert x\Vert_{\infty} \leq M \frac{1}{M} = 1$, and therefore:
 	\begin{align}
@@
 	\end{align} 
-
-	Therefore $\dot{s_2} = \displaystyle \sum \limits_{i \in G_1 } \frac{1}{y_i}\mu_i(s_1,x)x_i =  \sum \limits_{i \in G_1 } \frac{1}{y_i}\bar{\mu_i}f_i(s)(1+A_{i \bullet }x)x_i \geq 0$.
-Therefore $s_2(t) \geq 0$.
-
-	Note that since one has proven that $s_2 \geq 0$, bound \eqref{Bound1} is valid for any time, and not only when $s_2 = 0$. 
-	If $s_3 = 0$ then $\dot{s_3} = \sum \limits_{i \in G_2 }^{n}\frac{1}{y_i}\mu_i(s_2,x)\geq 0$. Therefore $s_3 \geq 0$.
-
-	For the boundedness it suffices to notice from \cref{l1} that the sum of positive elements is bounded, therefore each element is bounded.
+	Computing $\dot{s_2} = \sum \limits_{i \in G_1 } \frac{1}{y_i}\bar{\mu_i}f_i(s)(1+A_{i \bullet }x)x_i \geq 0$, and thus $s_2(t) \geq 0$.
+	Note that since $s_2 \geq 0$, bound \eqref{Bound1} is valid for any time, and not only when $s_2 = 0$.
+If $s_3 = 0$ then $\dot{s_3} = \sum \limits_{i \in G_2 }^{n}\frac{1}{y_i}\mu_i(s_2,x)\geq 0$.
+Therefore $s_3 \geq 0$.	For the boundedness it suffices to notice from \cref{l1} that the sum of positive elements is bounded, therefore each element is bounded.
 \end{proof}
 
-\subsection{Deduction of  Equilibrium points}
-
-Recall that
-
-\begin{align}
-f_i(s) = \begin{cases}
+\section{Deduction of  Equilibrium points}
+
+Recall that $ f_i(s) = \begin{cases}
 \bar{\mu}_i \dfrac{s_1}{K_i + s_1} \quad \forall i \in G_1 \\
 \bar{\mu}_i \dfrac{s_2}{K_i + s_2} \quad \forall i \in G_2
-\end{cases}
-\end{align}
-
-then $\mu(x,s) = \diag(f(s))(1_{n\times 1} + Ax)$ thus, system \eqref{system} is rewritten as follows.
-
+\end{cases}$ then $\mu(x,s) = \diag(f(s))(1_{n\times 1} + Ax)$ thus, system \eqref{system} is rewritten as follows. 
 %\begin{align}
@@
 
-\subsubsection{Both functional groups are present}
+\subsection{Both functional groups are present}
 
@@
 
-and so we arrive to formula
+and so we get to formula
 \begin{align}
@@
 
-and one arrives to expression:
+and one gets to expression:
 \begin{align}
@@
 
-\subsubsection{Washout of $G_2$}
+\subsection{Washout of $G_2$}
 
@@
 
-\subsection{Tracking Problem reformulation and details}
+\section{Tracking Problem reformulation and details}
 
@@
 They were solved using standard backward numerical integration.
-%\subsection{Simulations proof of concept}
-%\textbf{$\lambda = 10^{-1}$}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Biomass_iter_10}
-%	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{Total Biomass no noise e1}
-%\end{figure}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_AOB_iter_10_plot_1}
-%	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{AOB no noise e1}
-%\end{figure}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_NOB_iter_10_plot_1}
-%	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{NOB no noise e1}
-%\end{figure}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_metabolites_iter_10}
-%	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{Metabolites no noise e1}
-%\end{figure}
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_AOB_iter_10_plot_1}
-%	\caption{Control for the AOB population.}
-%	\label{Control AOB no noise e1}
-%\end{figure}
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-1//191210_no_noise_Control_NOB_iter_10_plot_1}
-%	\caption{Control for the NOB population.}
-%	\label{Control NOB no noise e1}
-%\end{figure}
-%\clearpage
-%\textbf{$\lambda = 10^{-2}$}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Biomass_iter_10}
-%	\caption{Total biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{Total Biomass no noise e2}
-%\end{figure}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_AOB_iter_10_plot_1}
-%	\caption{AOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{AOB no noise e2}
-%\end{figure}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_Control_NOB_iter_10_plot_1}
-%	\caption{NOB biomass. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{NOB no noise e2}
-%\end{figure}
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_metabolites_iter_10}
-%	\caption{Metabolites. Dotted line: simulated data. Continuous line: the tracking procedure results.}
-%	\label{Metabolites no noise e2}
-%\end{figure}
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_AOB_iter_10_plot_1}
-%	\caption{Control for the AOB population.}
-%	\label{Control AOB no noise e2}
-%\end{figure}
-%
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{Synthetic_data//lambda_=_e-2//191210_no_noise_2_NOB_iter_10_plot_1}
-%	\caption{Control for the NOB population.}
-%	\label{Control NOB no noise e2}
-%\end{figure}
-%
-%\clearpage
-
-\bibliographystyle{elsarticle-num}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%=====================================
+% References, variant A: external bibliography
+%=====================================
+\externalbibliography{yes}
 \bibliography{mybibfile}
+
+%=====================================
+% References, variant B: internal bibliography
+%=====================================
+%\begin{thebibliography}{999}
+%% Reference 1
+%\bibitem[Author1(year)]{ref-journal}
+%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
+%% Reference 2
+%\bibitem[Author2(year)]{ref-book}
+%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
+%\end{thebibliography}
+
+% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
+For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
+% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
+% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
+328; \citeyear{ref-journal-3b}, p.475).
+This produces: Wong (1999, p.
+328; 2000, p.
+475)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\sampleavailability{All the codes can be recovered from the following repository \url{https://github.com/paus-5/Class-and-Track}.}
+
+%% for journal Sci
+%\reviewreports{\\
+%Reviewer 1 comments and authors’ response\\
+%Reviewer 2 comments and authors’ response\\
+%Reviewer 3 comments and authors’ response
+%}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}
